### 2021-04-26 R/DraftFunctions.Rmd
'datacheckformat' function & its test

---
title: "DraftFunctions"
author: "Vincyane Badouard"
date: "26/04/2021"
output: html_document
---

# Fonction de contrôle & formatage de l’INPUT “data” de la fonction pilot (“datacheckformat”):
INPUT: data = Inventaires botaniques Guyafor/ONF (data frame)
OUTPUT: data = Inventaires botaniques type “Guyafor”(data frame)

vérification du type d’inventaire : 
* Test présence des variables.
* Test class des variables.
Si les tests précédents ont tous reçu =TRUE, STOP de la fonction dataformat. 
Sinon mettre en forme “inventaire Guyafor” (nom des var, leurs classes, unités (mettre des limites avec range),...)
re-vérification du type d’inventaire : 
* Test présence des variables
* Test class des variables
Si les tests précédent ont tous reçu =TRUE, STOP de la fonction dataformat.
Sinon Message : “Votre format de données renseignés à l’argument “data”, n’est pas compatible. Voir la vignette du package pour y trouver le format requis.”

```{r}
data("Paracou6_2016") #data in the environment
lapply(Paracou6_2016, class) #give the class of alla the data variables
```

```{r Create a broken dataset}
#in inst/extdata
BrokenParacou6_2016 <- Paracou6_2016 %>% 
  select(-Species) %>% # missing column
  rename(DBH = CircCorr) %>% # other column name
  rename(PLOT = Plot) %>% # variable name in upper case
  mutate(idTree = as.character(as.numeric(idTree))) %>% #an other variable class
  mutate(Lon = round(Lon, digits =0)) %>% # no digits
  mutate(Genus = toupper(Genus)) # values in upper case
```

```{r My tests}

'pouet' %in% names(Paracou6_2016)
if (!is.null(Paracou6_2016$pouet)) 
    stop("pouet parameter should be an integer (column name), or NULL if no presence column.")

```

```{r}
# Variables presence check
"Plot" %in% names(Paracou6_2016)
"CensusYear" %in% names(Paracou6_2016)
"idTree" %in% names(Paracou6_2016)
"Family" %in% names(Paracou6_2016)
"Genus" %in% names(Paracou6_2016)
"Species" %in% names(Paracou6_2016)
"CircCorr" %in% names(Paracou6_2016)
"CodeAlive" %in% names(Paracou6_2016)
"CommercialSp" %in% names(Paracou6_2016)
"UTMZone" %in% names(Paracou6_2016)
'Lat' %in% names(Paracou6_2016)
'Lon' %in% names(Paracou6_2016)
'VernName' %in% names(Paracou6_2016)
'Xfield' %in% names(Paracou6_2016)
'Yfield' %in% names(Paracou6_2016)
'Xutm' %in% names(Paracou6_2016)
'Yutm' %in% names(Paracou6_2016)

```

```{r}
# Variables class check
 if (!inherits(Paracou6_2016$idTree, "integer") && !is.null(idTree)) #majuscule ?
    stop("idTree parameter should be an integer (column name), or NULL if no presence column.")

if (!inherits(Paracou6_2016$Plot, "character") && !is.null(Plot))
    stop("Plot parameter should be a character (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$Xfield, "numeric") && !is.null(Xfield))
    stop("Xfield parameter should be numeric (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$Yfield, "numeric") && !is.null(Yfield))
    stop("Yfield parameter should be numeric (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$Xutm, "numeric") && !is.null(Xutm))
    stop("Xutm parameter should be numeric (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$Yutm, "numeric") && !is.null(Yutm))
    stop("Yutm parameter should be numeric (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$UTMZone, "integer") && !is.null(UTMZone))
    stop("UTMZone parameter should be an integer (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$Lat, "numeric") && !is.null(Lat))
    stop("Lat parameter should be numeric (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$Lon, "numeric") && !is.null(Lon))
    stop("Lon parameter should be numeric (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$Family, "character") && !is.null(Family))
    stop("Family parameter should be a character (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$Genus, "character") && !is.null(Genus))
    stop("Genus parameter should be a character (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$Species, "character") && !is.null(Species))
    stop("Species parameter should be a character (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$VernName, "character") && !is.null(VernName))
    stop("VernName parameter should be a character (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$CommercialSp, "logical") && !is.null(CommercialSp))
    stop("CommercialSp parameter should be logical (column name), or NULL if no presence column.")

   if (!inherits(Paracou6_2016$CensusYear, "integer") && !is.null(CensusYear))
    stop("CensusYear parameter should be an integer (column name), or NULL if no presence column.")

  if (!inherits(Paracou6_2016$CodeAlive, "logical") && !is.null(CodeAlive))
    stop("CodeAlive parameter should be logical (column name), or NULL if no presence column.")

  if (!inherits(Paracou6_2016$CircCorr, "numeric") && !is.null(CircCorr)) #DBH
    stop("CircCorr parameter should be numeric (column name), or NULL if no presence column.")

# 
# if (!inherits(Paracou6_2016$Forest, "character"))
#     stop("Forest parameter should be a character (column name), or NULL if no presence column.") #pas besoin
#    if (!inherits(Paracou6_2016$idVern, "integer") && !is.null(idVern))
#     stop("idVern parameter should be an integer (column name), or NULL if no presence column.") #pas besoin
# 
#   
#    
#    if (!inherits(Paracou6_2016$PlotArea, "numeric") && !is.null(PlotArea))
#     stop("PlotArea parameter should be numeric (column name), or NULL if no presence column.") #pas besoin
#   
#    if (!inherits(Paracou6_2016$SubPlot, "integer") && !is.null(SubPlot))
#     stop("SubPlot parameter should be an integer (column name), or NULL if no presence column.") #pas besoin
#   
#    if (!inherits(Paracou6_2016$TreeFieldNum, "numeric") && !is.null(TreeFieldNum))
#     stop("TreeFieldNum parameter should be numeric (column name), or NULL if no presence column.") #pas besoin
#   
#    if (!inherits(Paracou6_2016$Project, "character") && !is.null(Project))
#     stop("Project parameter should be a character (column name), or NULL if no presence column.") #pas besoin
#   
#    if (!inherits(Paracou6_2016$Protocole, "character") && !is.null(Protocole))
#     stop("Protocole parameter should be a character (column name), or NULL if no presence column.") #pas besoin
```

```{r all with error message}
if(!all("Plot" %in% names(Paracou6_2016),
"CensusYear" %in% names(Paracou6_2016),
"idTree" %in% names(Paracou6_2016),
"Family" %in% names(Paracou6_2016),
"Genus" %in% names(Paracou6_2016),
"Species" %in% names(Paracou6_2016),
"CircCorr" %in% names(Paracou6_2016),
"CodeAlive" %in% names(Paracou6_2016),
"CommercialSp" %in% names(Paracou6_2016),
"UTMZone" %in% names(Paracou6_2016),
'Lat' %in% names(Paracou6_2016),
'Lon' %in% names(Paracou6_2016),
'VernName' %in% names(Paracou6_2016),
'Xfield' %in% names(Paracou6_2016),
'Yfield' %in% names(Paracou6_2016),
'Xutm' %in% names(Paracou6_2016),
'Yutm' %in% names(Paracou6_2016),
if (!inherits(Paracou6_2016$idTree, "integer") && !is.null(idTree)) #majuscule ?
    stop("idTree parameter should be an integer (column name), or NULL if no presence column."),

if (!inherits(Paracou6_2016$Plot, "character") && !is.null(Plot))
    stop("Plot parameter should be a character (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$Xfield, "numeric") && !is.null(Xfield))
    stop("Xfield parameter should be numeric (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$Yfield, "numeric") && !is.null(Yfield))
    stop("Yfield parameter should be numeric (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$Xutm, "numeric") && !is.null(Xutm))
    stop("Xutm parameter should be numeric (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$Yutm, "numeric") && !is.null(Yutm))
    stop("Yutm parameter should be numeric (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$UTMZone, "integer") && !is.null(UTMZone))
    stop("UTMZone parameter should be an integer (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$Lat, "numeric") && !is.null(Lat))
    stop("Lat parameter should be numeric (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$Lon, "numeric") && !is.null(Lon))
    stop("Lon parameter should be numeric (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$Family, "character") && !is.null(Family))
    stop("Family parameter should be a character (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$Genus, "character") && !is.null(Genus))
    stop("Genus parameter should be a character (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$Species, "character") && !is.null(Species))
    stop("Species parameter should be a character (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$VernName, "character") && !is.null(VernName))
    stop("VernName parameter should be a character (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$CommercialSp, "logical") && !is.null(CommercialSp))
    stop("CommercialSp parameter should be logical (column name), or NULL if no presence column."),

   if (!inherits(Paracou6_2016$CensusYear, "integer") && !is.null(CensusYear))
    stop("CensusYear parameter should be an integer (column name), or NULL if no presence column."),

  if (!inherits(Paracou6_2016$CodeAlive, "logical") && !is.null(CodeAlive))
    stop("CodeAlive parameter should be logical (column name), or NULL if no presence column."),

  if (!inherits(Paracou6_2016$CircCorr, "numeric") && !is.null(CircCorr)) #DBH
    stop("CircCorr parameter should be numeric (column name), or NULL if no presence column.")))
    stop("Your data format, as specified in the 'data' argument, is not compatible. See the package vignette for the required format.") 
```

### 2021-05-07 R/DraftFunctions.Rmd
"addtreedim" function

@@
 
-# Fonction de contrôle & formatage de l’INPUT “data” de la fonction pilot (“datacheckformat”):
-INPUT: data = Inventaires botaniques Guyafor/ONF (data frame)
-OUTPUT: data = Inventaires botaniques type “Guyafor”(data frame)
+```{r}
+library(dplyr)
+library(tibble)
+library(tidyr)
+```
+
+```{r}
+ParamCrownDiameterAllometry <- read_delim("D:/VSC Kourou/DATA/ParamCrownDiameterAllometry.csv", 
+    ";", escape_double = FALSE, col_types = cols(alpha = col_number(), 
+        beta = col_number()), locale = locale(decimal_mark = ","), 
+    trim_ws = TRUE) %>%
+  separate(ScientificName, sep = "_", into = c("Genus", "Species"), remove = F) %>% 
+  mutate(Family = ifelse(Taxo == "fam", Genus, NA)) %>% 
+  mutate(Genus = ifelse(is.na(Family), Genus, NA))
+
+usethis::use_data(ParamCrownDiameterAllometry)
+```
+
+# Data loading
+```{r}
+data(Paracou6_2016) #data inventory in the global environment
+data("ForestZoneVolumeParametersTable") # The volume parameters data in the global environment
+load(system.file("extdata", "BrokenParacou6_2016.rda", package = "Maria")) # the test inventory in the global environment
+load(system.file("extdata", "ParamCrownDiameterAllometry.rda", package = "Maria"))
+```
+```{r}
+lapply(Paracou6_2016, class) #give the class of all the data variables
+```
+
+# Create a broken dataset
+```{r Create a broken dataset}
+#in inst/extdata
+library(schoolmath)
+library(dplyr)
+
+BrokenParacou6_2016 <- Paracou6_2016 %>% 
+  select(-Species) %>% # missing column
+  rename(Vernacular = VernName) %>% # other column name
+  rename(PLOT = Plot) %>% # variable name in upper case
+  mutate(idTree = as.character(as.numeric(idTree))) %>% #an other variable class
+  mutate(Lon = round(Lon, digits =0)) %>% # no digits
+  mutate(Genus = toupper(Genus)) %>%  # values in upper case
+  mutate(CodeAlive = ifelse(is.even(Paracou6_2016$idTree), "FALSE", CodeAlive)) %>% # Some FALSE in CodeAlive
+  mutate(CensusYear = ifelse(is.even(Paracou6_2016$idTree), CensusYear, CensusYear+1)) # different years inventory
+BrokenParacou6_2016[1:3, "idTree"] <- "200" # create a 2 time present tree
+BrokenParacou6_2016[4, "CircCorr"] <- "6" # DBH < 10
+BrokenParacou6_2016[5, "Plot"] <- "100" # a tree in another plot
+
+# pour l'enregistrer : usethis::use_data(BrokenParacou6_2016) puis le move dans ins/exdata
+```
+
+# inventorycheckformat
+INPUT: inventory = Inventaires botaniques Guyafor/ONF (data frame)
+OUTPUT: inventory = Inventaires botaniques type “Guyafor”(data frame)
 
@@
 * Test class des variables.
-Si les tests précédents ont tous reçu =TRUE, STOP de la fonction dataformat. 
+Si les tests précédents ont tous reçu =TRUE, STOP de la fonction inventorycheckformat 
 Sinon mettre en forme “inventaire Guyafor” (nom des var, leurs classes, unités (mettre des limites avec range),...)
@@
 * Test class des variables
-Si les tests précédent ont tous reçu =TRUE, STOP de la fonction dataformat.
-Sinon Message : “Votre format de données renseignés à l’argument “data”, n’est pas compatible. Voir la vignette du package pour y trouver le format requis.”
-
-```{r}
-data("Paracou6_2016") #data in the environment
-lapply(Paracou6_2016, class) #give the class of alla the data variables
-```
-
-```{r Create a broken dataset}
-#in inst/extdata
-BrokenParacou6_2016 <- Paracou6_2016 %>% 
-  select(-Species) %>% # missing column
-  rename(DBH = CircCorr) %>% # other column name
-  rename(PLOT = Plot) %>% # variable name in upper case
-  mutate(idTree = as.character(as.numeric(idTree))) %>% #an other variable class
-  mutate(Lon = round(Lon, digits =0)) %>% # no digits
-  mutate(Genus = toupper(Genus)) # values in upper case
-```
+Si les tests précédent ont tous reçu =TRUE, STOP de la fonction inventorycheckformat
+Sinon Message : “Votre format de données renseignés à l’argument “inventory”, n’est pas compatible. Voir la vignette du package pour y trouver le format requis.”
 
@@
 if (!is.null(Paracou6_2016$pouet)) 
-    stop("pouet parameter should be an integer (column name), or NULL if no presence column.")
+    stop("pouet variable should be an integer.")
 
@@
 # Variables presence check
-"Plot" %in% names(Paracou6_2016)
-"CensusYear" %in% names(Paracou6_2016)
-"idTree" %in% names(Paracou6_2016)
-"Family" %in% names(Paracou6_2016)
-"Genus" %in% names(Paracou6_2016)
-"Species" %in% names(Paracou6_2016)
-"CircCorr" %in% names(Paracou6_2016)
-"CodeAlive" %in% names(Paracou6_2016)
-"CommercialSp" %in% names(Paracou6_2016)
-"UTMZone" %in% names(Paracou6_2016)
-'Lat' %in% names(Paracou6_2016)
-'Lon' %in% names(Paracou6_2016)
-'VernName' %in% names(Paracou6_2016)
-'Xfield' %in% names(Paracou6_2016)
-'Yfield' %in% names(Paracou6_2016)
-'Xutm' %in% names(Paracou6_2016)
-'Yutm' %in% names(Paracou6_2016)
+if(!("Plot" %in% names(Paracou6_2016)))
+  stop("Plot variable is not found")
+if(!("CensusYear" %in% names(Paracou6_2016)))
+    stop("CensusYear variable is not found")
+if(!("idTree" %in% names(Paracou6_2016)))
+    stop("idTree variable is not found")
+if(!("Family" %in% names(Paracou6_2016)))
+    stop("Family variable is not found")
+if(!("Genus" %in% names(Paracou6_2016)))
+    stop("Genus variable is not found")
+if(!("Species" %in% names(Paracou6_2016)))
+    stop("Species variable is not found")
+if(!("CircCorr" %in% names(Paracou6_2016)))
+  stop("CircCorr variable is not found")
+if(!("CodeAlive" %in% names(Paracou6_2016)))
+    stop("CodeAlive variable is not found")
+if(!("CommercialSp" %in% names(Paracou6_2016)))
+    stop("CommercialSp variable is not found")
+if(!("UTMZone" %in% names(Paracou6_2016)))
+    stop("UTMZone variable is not found")
+if(!('Lat' %in% names(Paracou6_2016)))
+    stop("Lat variable is not found")
+if(!('Lon' %in% names(Paracou6_2016)))
+    stop("Lon variable is not found")
+if(!('VernName' %in% names(Paracou6_2016)))
+    stop("VernName variable is not found")
+if(!('Xfield' %in% names(Paracou6_2016)))
+    stop("Xfield variable is not found")
+if(!('Yfield' %in% names(Paracou6_2016)))
+    stop("Yfield variable is not found")
+if(!('Xutm' %in% names(Paracou6_2016)))
+    stop("Xutm variable is not found")
+if(!('Yutm' %in% names(Paracou6_2016)))
+    stop("Yutm variable is not found")
 
@@
  if (!inherits(Paracou6_2016$idTree, "integer") && !is.null(idTree)) #majuscule ?
-    stop("idTree parameter should be an integer (column name), or NULL if no presence column.")
+    stop("idTree variable should be an integer.")
 
 if (!inherits(Paracou6_2016$Plot, "character") && !is.null(Plot))
-    stop("Plot parameter should be a character (column name), or NULL if no presence column.")
+    stop("Plot variable should be a character.")
 
    if (!inherits(Paracou6_2016$Xfield, "numeric") && !is.null(Xfield))
-    stop("Xfield parameter should be numeric (column name), or NULL if no presence column.")
+    stop("Xfield variable should be numeric.")
 
    if (!inherits(Paracou6_2016$Yfield, "numeric") && !is.null(Yfield))
-    stop("Yfield parameter should be numeric (column name), or NULL if no presence column.")
+    stop("Yfield variable should be numeric.")
 
    if (!inherits(Paracou6_2016$Xutm, "numeric") && !is.null(Xutm))
-    stop("Xutm parameter should be numeric (column name), or NULL if no presence column.")
+    stop("Xutm variable should be numeric.")
 
    if (!inherits(Paracou6_2016$Yutm, "numeric") && !is.null(Yutm))
-    stop("Yutm parameter should be numeric (column name), or NULL if no presence column.")
+    stop("Yutm variable should be numeric.")
 
    if (!inherits(Paracou6_2016$UTMZone, "integer") && !is.null(UTMZone))
-    stop("UTMZone parameter should be an integer (column name), or NULL if no presence column.")
+    stop("UTMZone variable should be an integer.")
 
    if (!inherits(Paracou6_2016$Lat, "numeric") && !is.null(Lat))
-    stop("Lat parameter should be numeric (column name), or NULL if no presence column.")
+    stop("Lat variable should be numeric.")
 
    if (!inherits(Paracou6_2016$Lon, "numeric") && !is.null(Lon))
-    stop("Lon parameter should be numeric (column name), or NULL if no presence column.")
+    stop("Lon variable should be numeric.")
 
    if (!inherits(Paracou6_2016$Family, "character") && !is.null(Family))
-    stop("Family parameter should be a character (column name), or NULL if no presence column.")
+    stop("Family variable should be a character.")
 
    if (!inherits(Paracou6_2016$Genus, "character") && !is.null(Genus))
-    stop("Genus parameter should be a character (column name), or NULL if no presence column.")
+    stop("Genus variable should be a character.")
 
    if (!inherits(Paracou6_2016$Species, "character") && !is.null(Species))
-    stop("Species parameter should be a character (column name), or NULL if no presence column.")
+    stop("Species variable should be a character.")
 
    if (!inherits(Paracou6_2016$VernName, "character") && !is.null(VernName))
-    stop("VernName parameter should be a character (column name), or NULL if no presence column.")
+    stop("VernName variable should be a character.")
 
    if (!inherits(Paracou6_2016$CommercialSp, "logical") && !is.null(CommercialSp))
-    stop("CommercialSp parameter should be logical (column name), or NULL if no presence column.")
+    stop("CommercialSp variable should be logical.")
 
    if (!inherits(Paracou6_2016$CensusYear, "integer") && !is.null(CensusYear))
-    stop("CensusYear parameter should be an integer (column name), or NULL if no presence column.")
+    stop("CensusYear variable should be an integer.")
 
   if (!inherits(Paracou6_2016$CodeAlive, "logical") && !is.null(CodeAlive))
-    stop("CodeAlive parameter should be logical (column name), or NULL if no presence column.")
+    stop("CodeAlive variable should be logical.")
 
   if (!inherits(Paracou6_2016$CircCorr, "numeric") && !is.null(CircCorr)) #DBH
-    stop("CircCorr parameter should be numeric (column name), or NULL if no presence column.")
+    stop("CircCorr variable should be numeric.")
 
@@
 # if (!inherits(Paracou6_2016$Forest, "character"))
-#     stop("Forest parameter should be a character (column name), or NULL if no presence column.") #pas besoin
+#     stop("Forest variable should be a character.") #pas besoin
 #    if (!inherits(Paracou6_2016$idVern, "integer") && !is.null(idVern))
-#     stop("idVern parameter should be an integer (column name), or NULL if no presence column.") #pas besoin
+#     stop("idVern variable should be an integer.") #pas besoin
 # 
@@
 #    if (!inherits(Paracou6_2016$PlotArea, "numeric") && !is.null(PlotArea))
-#     stop("PlotArea parameter should be numeric (column name), or NULL if no presence column.") #pas besoin
+#     stop("PlotArea variable should be numeric.") #pas besoin
 #   
 #    if (!inherits(Paracou6_2016$SubPlot, "integer") && !is.null(SubPlot))
-#     stop("SubPlot parameter should be an integer (column name), or NULL if no presence column.") #pas besoin
+#     stop("SubPlot variable should be an integer.") #pas besoin
 #   
 #    if (!inherits(Paracou6_2016$TreeFieldNum, "numeric") && !is.null(TreeFieldNum))
-#     stop("TreeFieldNum parameter should be numeric (column name), or NULL if no presence column.") #pas besoin
+#     stop("TreeFieldNum variable should be numeric.") #pas besoin
 #   
 #    if (!inherits(Paracou6_2016$Project, "character") && !is.null(Project))
-#     stop("Project parameter should be a character (column name), or NULL if no presence column.") #pas besoin
+#     stop("Project variable should be a character.") #pas besoin
 #   
 #    if (!inherits(Paracou6_2016$Protocole, "character") && !is.null(Protocole))
-#     stop("Protocole parameter should be a character (column name), or NULL if no presence column.") #pas besoin
+#     stop("Protocole variable should be a character.") #pas besoin
 ```
@@
 ```{r all with error message}
-if(!all("Plot" %in% names(Paracou6_2016),
-"CensusYear" %in% names(Paracou6_2016),
-"idTree" %in% names(Paracou6_2016),
-"Family" %in% names(Paracou6_2016),
-"Genus" %in% names(Paracou6_2016),
-"Species" %in% names(Paracou6_2016),
-"CircCorr" %in% names(Paracou6_2016),
-"CodeAlive" %in% names(Paracou6_2016),
-"CommercialSp" %in% names(Paracou6_2016),
-"UTMZone" %in% names(Paracou6_2016),
-'Lat' %in% names(Paracou6_2016),
-'Lon' %in% names(Paracou6_2016),
-'VernName' %in% names(Paracou6_2016),
-'Xfield' %in% names(Paracou6_2016),
-'Yfield' %in% names(Paracou6_2016),
-'Xutm' %in% names(Paracou6_2016),
-'Yutm' %in% names(Paracou6_2016),
-if (!inherits(Paracou6_2016$idTree, "integer") && !is.null(idTree)) #majuscule ?
-    stop("idTree parameter should be an integer (column name), or NULL if no presence column."),
+if(!("Plot" %in% names(Paracou6_2016)))
+  stop("Plot variable is not found")
+if(!("CensusYear" %in% names(Paracou6_2016)))
+    stop("CensusYear variable is not found")
+if(!("idTree" %in% names(Paracou6_2016)))
+    stop("idTree variable is not found")
+if(!("Family" %in% names(Paracou6_2016)))
+    stop("Family variable is not found")
+if(!("Genus" %in% names(Paracou6_2016)))
+    stop("Genus variable is not found")
+if(!("Species" %in% names(Paracou6_2016)))
+    stop("Species variable is not found")
+if(!("CircCorr" %in% names(Paracou6_2016)))
+  stop("CircCorr variable is not found")
+if(!("CodeAlive" %in% names(Paracou6_2016)))
+    stop("CodeAlive variable is not found")
+if(!("CommercialSp" %in% names(Paracou6_2016)))
+    stop("CommercialSp variable is not found")
+if(!("UTMZone" %in% names(Paracou6_2016)))
+    stop("UTMZone variable is not found")
+if(!('Lat' %in% names(Paracou6_2016)))
+    stop("Lat variable is not found")
+if(!('Lon' %in% names(Paracou6_2016)))
+    stop("Lon variable is not found")
+if(!('VernName' %in% names(Paracou6_2016)))
+    stop("VernName variable is not found")
+if(!('Xfield' %in% names(Paracou6_2016)))
+    stop("Xfield variable is not found")
+if(!('Yfield' %in% names(Paracou6_2016)))
+    stop("Yfield variable is not found")
+if(!('Xutm' %in% names(Paracou6_2016)))
+    stop("Xutm variable is not found")
+if(!('Yutm' %in% names(Paracou6_2016)))
+    stop("Yutm variable is not found")
+if (!inherits(Paracou6_2016$idTree, "integer.")) #majuscule ?
+    stop("idTree variable should be an integer.")
 
-if (!inherits(Paracou6_2016$Plot, "character") && !is.null(Plot))
-    stop("Plot parameter should be a character (column name), or NULL if no presence column."),
+if (!inherits(Paracou6_2016$Plot, "character"))
+    stop("Plot variable should be a character.")
 
-   if (!inherits(Paracou6_2016$Xfield, "numeric") && !is.null(Xfield))
-    stop("Xfield parameter should be numeric (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$Xfield, "numeric"))
+    stop("Xfield variable should be numeric.")
 
-   if (!inherits(Paracou6_2016$Yfield, "numeric") && !is.null(Yfield))
-    stop("Yfield parameter should be numeric (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$Yfield, "numeric"))
+    stop("Yfield variable should be numeric.")
 
-   if (!inherits(Paracou6_2016$Xutm, "numeric") && !is.null(Xutm))
-    stop("Xutm parameter should be numeric (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$Xutm, "numeric"))
+    stop("Xutm variable should be numeric.")
 
-   if (!inherits(Paracou6_2016$Yutm, "numeric") && !is.null(Yutm))
-    stop("Yutm parameter should be numeric (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$Yutm, "numeric"))
+    stop("Yutm variable should be numeric.")
 
-   if (!inherits(Paracou6_2016$UTMZone, "integer") && !is.null(UTMZone))
-    stop("UTMZone parameter should be an integer (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$UTMZone, "integer"))
+    stop("UTMZone variable should be an integer.")
 
-   if (!inherits(Paracou6_2016$Lat, "numeric") && !is.null(Lat))
-    stop("Lat parameter should be numeric (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$Lat, "numeric"))
+    stop("Lat variable should be numeric.")
 
-   if (!inherits(Paracou6_2016$Lon, "numeric") && !is.null(Lon))
-    stop("Lon parameter should be numeric (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$Lon, "numeric"))
+    stop("Lon variable should be numeric.")
 
-   if (!inherits(Paracou6_2016$Family, "character") && !is.null(Family))
-    stop("Family parameter should be a character (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$Family, "character"))
+    stop("Family variable should be a character.")
 
-   if (!inherits(Paracou6_2016$Genus, "character") && !is.null(Genus))
-    stop("Genus parameter should be a character (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$Genus, "character"))
+    stop("Genus variable should be a character.")
 
-   if (!inherits(Paracou6_2016$Species, "character") && !is.null(Species))
-    stop("Species parameter should be a character (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$Species, "character"))
+    stop("Species variable should be a character.")
 
-   if (!inherits(Paracou6_2016$VernName, "character") && !is.null(VernName))
-    stop("VernName parameter should be a character (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$VernName, "character"))
+    stop("VernName variable should be a character.")
 
-   if (!inherits(Paracou6_2016$CommercialSp, "logical") && !is.null(CommercialSp))
-    stop("CommercialSp parameter should be logical (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$CommercialSp, "logical"))
+    stop("CommercialSp variable should be logical.")
 
-   if (!inherits(Paracou6_2016$CensusYear, "integer") && !is.null(CensusYear))
-    stop("CensusYear parameter should be an integer (column name), or NULL if no presence column."),
+   if (!inherits(Paracou6_2016$CensusYear, "integer"))
+    stop("CensusYear variable should be an integer.")
 
-  if (!inherits(Paracou6_2016$CodeAlive, "logical") && !is.null(CodeAlive))
-    stop("CodeAlive parameter should be logical (column name), or NULL if no presence column."),
+  if (!inherits(Paracou6_2016$CodeAlive, "logical"))
+    stop("CodeAlive variable should be logical.")
 
-  if (!inherits(Paracou6_2016$CircCorr, "numeric") && !is.null(CircCorr)) #DBH
-    stop("CircCorr parameter should be numeric (column name), or NULL if no presence column.")))
-    stop("Your data format, as specified in the 'data' argument, is not compatible. See the package vignette for the required format.") 
+  if (!inherits(Paracou6_2016$CircCorr, "numeric")) #DBH
+    stop("CircCorr variable should be numeric.")
 ```
+
+# cleaninventory
+INPUT: inventory = Inventaires botaniques type “Guyafor” (Paracou6_2016)(data frame)
+OUTPUT: inventory = Inventaires botaniques exploitable (Paracou6_2016Clean) (data frame)
+
+Ne prendre que les arbres vivants : lignes ayant la valeur “TRUE” à la colonne “CodeAlive” de inventory. 
+Check si les valeurs de ID sont uniques. Si FALSE message d’erreur “Les identifiants des arbres ne sont pas uniques”
+Enlever les arbres hors de la parcelle s’il y en a : coordonnées de l’arbre non comprises dans les coordonnées de la parcelle.
+Ne prendre que les lignes pour lesquelles “DBH”> 10.
+```{r}
+duplicated(Paracou6_2016)
+unique(Paracou6_2016) #same rows number
+
+#duplicated() gives "FALSE" when the row is unique
+# any() : at least one of the values true?
+any(duplicated(Paracou6_2016)) # at least one row is duplicated?
+all(Paracou6_2016$Plot==Paracou6_2016$Plot[1]) #all the Plot values are equal?
+```
+
+```{r}
+
+if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA) #if DBH doesn't exist create it
+   Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi} # and compute it
+
+InventoryClean <- Paracou6_2016 %>% 
+  filter(CodeAlive == "TRUE") %>% #only alive trees
+  filter(DBH >= 10) # DBH >= 10
+
+  if (any(duplicated(Paracou6_2016)==TRUE))
+    stop ("Tree identifiers (idTree) are not unique.") # stop function if the tree identifiers (idTree) are not unique
+  if (all(Paracou6_2016$Plot==Paracou6_2016$Plot[1])==FALSE) #all the Plot values are equal?
+    stop ("Your inventory concerns different plots (Plot). Our function simulates logging at the plot level.") 
+  # Remove out-plot trees (A faire)
+
+```
+
+# addtreedim
+Fonction d’ajout de variables pour l’INPUT “inventory” :
+INPUT: inventory = InventoryClean (data frame)
+OUTPUT: inventory = Inventory_addtreedim (data frame)
+
+calculer pour tous les arbres : 
+  + TreeBiomass : biomasse de tous les arbres (BIOMASS package)
+  + TreeHeight : hauteur de l’arbre (H) (BIOMASS package)
+  + TreeHarvestableVolume : volume exploitable à partir du tarif de cubage (= a + b*DBH2) que représente chaque arbre (a et b dépendent de la localisation)
+  + TrunkHeight : hauteur de fût (TreeHarvestableVolume  = π(DBH/2)² x TrunkHeight)
+  + CrownDiameter : diamètre de couronne (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺 (allométries de Mélaine)
+  + CrownHeight : TreeHeight - TrunkHeight
+
+```{r TreeHeight}
+library(BIOMASS)
+library(knitr)
+# TreeHeight = hauteur de l’arbre (H) (en mètre) (BIOMASS package)
+# 3 options :
+# - get my tree heights from the location (from continent or region specific model, or from coordinates)
+# - from other Guyanese trees heights data, fit different H-D models, select the best and apply on my data.
+
+RegionTreeHeight <- retrieveH(D = Paracou6_2016$CircCor, region = "GuianaShield") #continent or region specific model (Feldpaush et al. (2012))
+# GuianaShield = Guyana, French Guiana (piste St Elie (Chave 2005)), Venezuela
+
+n <- length(Paracou6_2016$CircCor)
+coord <- cbind(long = rep(-52.92, n), lat = rep(5.27, n)) # Paracou P6 coordinates
+CoordTreeHeight <- retrieveH(D = Paracou6_2016$CircCor, coord = coord) #by coordinates (Chave et al. (2012))
+
+result <- modelHD(D = , H = , useWeight = TRUE) #from Guyanese trees heights data
+kable(result)
+# Compute the local H-D model with the lowest RSE (Root Squared Error)
+selectedHDmodel <- modelHD(D = , H = , method = "log2", useWeight = TRUE)
+
+predictHeight(CircCor, model)
+
+```
+
+```{r TreeHarvestableVolume}
+# TreeHarvestableVolume = volume exploitable à partir du tarif de cubage (= a + b*DBH2) que représente chaque arbre (a et b dépendent de la localisation)
+
+ForestZoneVolumeParametersTable <- data.frame (Forest = c("Acarouany","BAFOG","Kaw","Laussat","Montagne Plomb","Montagne Tortue","Nouragues","Organabo","Paracou","Régina St Georges","Risquetout","Tibourou"), # Guyafor forests
+                  Zone = c("East", "West", "Central", "FrenchGuiana")) %>% # Volume formules zones
+  mutate(Zone = ifelse(Forest == "Acarouany"| Forest =="BAFOG" |Forest =="Laussat", "West", NA)) %>% # West zone
+  mutate(Zone = ifelse(Forest == "Montagne Plomb"| Forest =="Organabo"|Forest =="Paracou"|Forest =="Risquetout", "Central", Zone)) %>% # Central zone
+  mutate(Zone = ifelse(Forest == "Kaw"| Forest =="Montagne Tortue"|Forest =="Nouragues"|Forest =="Régina St Georges"|Forest =="Tibourou", "East", Zone)) %>% # East zone
+  left_join(VolumeParametersTable)
+
+Paracou6_2016_volume <- Paracou6_2016 %>% 
+  left_join(ForestZoneVolumeParametersTable) %>% 
+mutate(TreeHarvestableVolume = aCoef + bCoef * CircCorr^2) # compute the tree harvestable volume
+
+# West  = c("Acarouany", "BAFOG", "Laussat")
+# Central  = c("Montagne Plomb", "Organabo","Paracou", "Risquetout")
+# East = c("Kaw", "Montagne Tortue","Nouragues", "Régina St Georges", "Tibourou")
+# Guyane = le reste par défaut
+# et possibilité à l'utilisateur de mettre ses propres tarifs
+
+```
+
+```{r TrunkHeight & CrownHeight}
+mutate(TrunkHeight = TreeHarvestableVolume/(π(DBH/2)^2)) # compute the trunk height (cylinderVolume= π(DBH/2)² x H)
+mutate(CrownHeight = TreeHeight - TrunkHeight) # compute the crown height
+
+```
+
+```{r}
+spParamCrownDiameter <- ParamCrownDiameterAllometry %>% #parameters at species scale
+  filter(Taxo == "sp") %>% 
+  select(-Family)
+genParamCrownDiameter <- ParamCrownDiameterAllometry %>% #parameters at genus scale
+  filter(Taxo == "gen") %>% 
+  select(-Family, -ScientificName, -Species)
+famParamCrownDiameter <- ParamCrownDiameterAllometry %>% #parameters at family scale
+  filter(Taxo == "fam") %>% 
+  select(-Genus, -ScientificName, -Species)
+
+Paracou6_2016 %>% 
+  sample_n(100) %>% # short data
+  select(idTree, Family, Genus, Species) %>% #only useful columns 
+  left_join(select(spParamCrownDiameter, -Taxo, -ScientificName, -beta), by = c("Genus","Species")) %>% 
+  left_join(select(genParamCrownDiameter, -Taxo, -beta), by = c("Genus"), suffix = c(".species", ".genus")) %>% 
+  left_join(select(famParamCrownDiameter, -Taxo, -beta) %>% 
+              rename(alpha.family = alpha), by = c("Family")) %>% 
+  mutate(alpha = alpha.species) %>% #mutate(alpha = alpha.species,beta = beta.species)
+  mutate(alpha = ifelse(is.na(alpha), alpha.genus, alpha)) %>% 
+  mutate(alpha = ifelse(is.na(alpha), alpha.family, alpha)) %>% 
+  mutate(alpha = ifelse(is.na(alpha), mean(alpha, na.rm =T), alpha)) %>% 
+  select(-alpha.species, -alpha.genus, -alpha.family)
+```
+
+```{r CrownDiameter}
+
+spParamCrownDiameter <- ParamCrownDiameterAllometry %>% #parameters at species scale
+  filter(Taxo == "sp") %>% 
+  select(-Family)
+genParamCrownDiameter <- ParamCrownDiameterAllometry %>% #parameters at genus scale
+  filter(Taxo == "gen") %>% 
+  select(-Family, -ScientificName, -Species)
+famParamCrownDiameter <- ParamCrownDiameterAllometry %>% #parameters at family scale
+  filter(Taxo == "fam") %>% 
+  select(-Genus, -ScientificName, -Species)
+
+error <- rnorm(2000, mean = 0, sd = 0.0295966977) #Mélaine's model error distribution (hist(error))
+
+Paracou6_2016_crown <- Paracou6_2016 %>% 
+  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 
+  left_join(spParamCrownDiameter, by = c("ScientificName","Genus","Species")) %>% #Add parameters at species scale
+  left_join(genParamCrownDiameter, by = "Genus", suffix = c(".species", ".genus")) %>% #Add parameters at genus scale
+  left_join(famParamCrownDiameter, by = "Family") %>% #Add parameters at family scale
+
+  rename(Taxo.family = Taxo, alpha.family = alpha, beta.family = beta) %>% 
+  mutate(alpha = alpha.species, beta = beta.species, Taxo = Taxo.species) %>% # create the future & unique alpha,beta,taxo columns 
+  mutate(alpha = ifelse(is.na(alpha), alpha.genus, alpha)) %>% #if species parameters are absent, take genus parameters
+  mutate(alpha = ifelse(is.na(alpha), alpha.family, alpha)) %>% #if species&genus parameters are absent, take family parameters
+  mutate(alpha = ifelse(is.na(alpha), mean(alpha, na.rm =T), alpha)) %>% #if species,genus&family parameters are absent, take parameters mean
+  select(-alpha.species, -alpha.genus, -alpha.family) %>% #remove obsolete columns
+
+  mutate(beta = ifelse(is.na(beta), beta.genus, beta)) %>% #if species parameters are absent, take genus parameters
+  mutate(beta = ifelse(is.na(beta), beta.family, beta)) %>% #if species&genus parameters are absent, take family parameters
+  mutate(beta = ifelse(is.na(beta), mean(beta, na.rm =T), beta)) %>% #if species,genus&family parameters are absent, take parameters mean
+  select(-beta.species, -beta.genus, -beta.family) %>% #remove obsolete columns
+
+  mutate(Taxo = ifelse(is.na(Taxo), Taxo.genus, Taxo)) %>% #if species parameters are absent, take genus parameters
+  mutate(Taxo = ifelse(is.na(Taxo), Taxo.family, Taxo)) %>% #if species&genus parameters are absent, take family parameters
+  mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
+  select(-Taxo.species, -Taxo.genus, -Taxo.family) %>%  #remove obsolete columns
+  mutate(CrownDiameter = exp((
+  (ln(DBH)-alpha-error)/beta)
+  )/TreeHeight) # compute the crown diameter (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺, with 𝜺~N(0,σ^2) and meanσ^2 = 0.0295966977. (Mélaine's allometries))
+
+# Informations:
+# How many individuals have find their Crown diameter parameters at species, genus, family or no scale:
+sum(Paracou6_2016_crown$Taxo == "fam") #442 individuals with family scale parameters
+sum(Paracou6_2016_crown$Taxo == "gen") #742 individuals with genus scale parameters
+sum(Paracou6_2016_crown$Taxo == "sp") #2364 individuals with family scale parameters
+sum(Paracou6_2016_crown$Taxo == "mean") #72 individuals no recognize at any scale, so with plot mean parameters
+
+unique(Paracou6_2016_crown[(Paracou6_2016_crown$Taxo == "mean"),]$ScientificName) #which species are no recognized
+length(unique(Paracou6_2016_crown$ScientificName)) #How many species are in the plot
+```
+
+```{r All addtreedim}
+# allometry parameters data preparation:
+spParamCrownDiameter <- ParamCrownDiameterAllometry %>% #parameters at species scale
+  filter(Taxo == "sp") %>% 
+  select(-Family)
+genParamCrownDiameter <- ParamCrownDiameterAllometry %>% #parameters at genus scale
+  filter(Taxo == "gen") %>% 
+  select(-Family, -ScientificName, -Species)
+famParamCrownDiameter <- ParamCrownDiameterAllometry %>% #parameters at family scale
+  filter(Taxo == "fam") %>% 
+  select(-Genus, -ScientificName, -Species)
+
+error <- rnorm(2000, mean = 0, sd = 0.0295966977) #Mélaine's model error distribution (hist(error))
+
+# Variables computation:
+InventoryAddtreedim <- InventoryClean %>%
+
+# TreeHarvestableVolume
+  left_join(ForestZoneVolumeParametersTable) %>% 
+  mutate(TreeHarvestableVolume = aCoef + bCoef * CircCorr^2) %>%  # compute the tree harvestable volume
+
+# TrunkHeight & CrownHeight  
+  mutate(TrunkHeight = TreeHarvestableVolume/(pi*(DBH/2)^2)) %>%  # compute the trunk height (cylinderVolume= π(DBH/2)² x H)
+  # mutate(CrownHeight = TreeHeight - TrunkHeight) %>%  # compute the crown height TREEHEIGHT EN ATTENTE
+
+# CrownDiameter
+  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 
+  left_join(spParamCrownDiameter, by = c("ScientificName","Genus","Species")) %>% #Add parameters at species scale
+  left_join(genParamCrownDiameter, by = "Genus", suffix = c(".species", ".genus")) %>% #Add parameters at genus scale
+  left_join(famParamCrownDiameter, by = "Family") %>% #Add parameters at family scale
+
+  rename(Taxo.family = Taxo, alpha.family = alpha, beta.family = beta) %>% 
+  mutate(alpha = alpha.species, beta = beta.species, Taxo = Taxo.species) %>% # create the future & unique alpha,beta,taxo columns 
+  mutate(alpha = ifelse(is.na(alpha), alpha.genus, alpha)) %>% #if species parameters are absent, take genus parameters
+  mutate(alpha = ifelse(is.na(alpha), alpha.family, alpha)) %>% #if species&genus parameters are absent, take family parameters
+  mutate(alpha = ifelse(is.na(alpha), mean(alpha, na.rm =T), alpha)) %>% #if species,genus&family parameters are absent, take parameters mean
+  select(-alpha.species, -alpha.genus, -alpha.family) %>% #remove obsolete columns
+
+  mutate(beta = ifelse(is.na(beta), beta.genus, beta)) %>% #if species parameters are absent, take genus parameters
+  mutate(beta = ifelse(is.na(beta), beta.family, beta)) %>% #if species&genus parameters are absent, take family parameters
+  mutate(beta = ifelse(is.na(beta), mean(beta, na.rm =T), beta)) %>% #if species,genus&family parameters are absent, take parameters mean
+  select(-beta.species, -beta.genus, -beta.family) %>% #remove obsolete columns
+
+  mutate(Taxo = ifelse(is.na(Taxo), Taxo.genus, Taxo)) %>% #if species parameters are absent, take genus parameters
+  mutate(Taxo = ifelse(is.na(Taxo), Taxo.family, Taxo)) %>% #if species&genus parameters are absent, take family parameters
+  mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
+  select(-Taxo.species, -Taxo.genus, -Taxo.family) %>%  #remove obsolete columns
+  # mutate(CrownDiameter = exp((
+  # (ln(DBH)-alpha-error)/beta)
+  # )/TreeHeight) # compute the crown diameter (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺, with 𝜺~N(0,σ^2) and meanσ^2 = 0.0295966977. (Mélaine's allometries))
+
+#                                                !!!!!!!TREEHEIGHT EN ATTENTE!!!!!!
+
+```

### 2021-05-07 R/datacheckformat.R

@@ -1,84 +1,0 @@
-#' Check & format your inventory data for the package "Maria"
-#'
-#' @param data (dataframe) Your inventory data or the "Paracou6_2016" test data
-#' @param verbose (boolean) Print in console
-#'
-#' @return
-#' @export
-#'
-#' @examples
-#' datacheckformat(data=Paracou6_2016)
-datacheckformat <- function(
-  data = "Paracou6_2016",
-  verbose = TRUE # never use T or F
-){
-  if(!all("Plot" %in% names(data),
-          "CensusYear" %in% names(data),
-          "idTree" %in% names(data),
-          "Family" %in% names(data),
-          "Genus" %in% names(data),
-          "Species" %in% names(data),
-          "CircCorr" %in% names(data),
-          "CodeAlive" %in% names(data),
-          "CommercialSp" %in% names(data),
-          "UTMZone" %in% names(data),
-          'Lat' %in% names(data),
-          'Lon' %in% names(data),
-          'VernName' %in% names(data),
-          'Xfield' %in% names(data),
-          'Yfield' %in% names(data),
-          'Xutm' %in% names(data),
-          'Yutm' %in% names(data),
-          if (!inherits(data$idTree, "integer") && !is.null(idTree)) #majuscule ?
-            stop("idTree parameter should be an integer (column name), or NULL if no presence column."),
-
-          if (!inherits(data$Plot, "character") && !is.null(Plot))
-            stop("Plot parameter should be a character (column name), or NULL if no presence column."),
-
-          if (!inherits(data$Xfield, "numeric") && !is.null(Xfield))
-            stop("Xfield parameter should be numeric (column name), or NULL if no presence column."),
-
-          if (!inherits(data$Yfield, "numeric") && !is.null(Yfield))
-            stop("Yfield parameter should be numeric (column name), or NULL if no presence column."),
-
-          if (!inherits(data$Xutm, "numeric") && !is.null(Xutm))
-            stop("Xutm parameter should be numeric (column name), or NULL if no presence column."),
-
-          if (!inherits(data$Yutm, "numeric") && !is.null(Yutm))
-            stop("Yutm parameter should be numeric (column name), or NULL if no presence column."),
-
-          if (!inherits(data$UTMZone, "integer") && !is.null(UTMZone))
-            stop("UTMZone parameter should be an integer (column name), or NULL if no presence column."),
-
-          if (!inherits(data$Lat, "numeric") && !is.null(Lat))
[…]

### 2021-05-07 data-raw/BrokenParacou6_2016.R

@@ -1,10 +1,18 @@
 ## code to prepare `BrokenParacou6_2016` dataset goes here
 
 # Create a broken dataset (in inst/extdata)
+library(schoolmath)
+library(dplyr)
+
 BrokenParacou6_2016 <- Paracou6_2016 %>%
   select(-Species) %>% # missing column
-  rename(DBH = CircCorr) %>% # other column name
+  rename(Vernacular = VernName) %>% # other column name
   rename(PLOT = Plot) %>% # variable name in upper case
   mutate(idTree = as.character(as.numeric(idTree))) %>% #an other variable class
   mutate(Lon = round(Lon, digits =0)) %>% # no digits
-  mutate(Genus = toupper(Genus)) # values in upper case
+  mutate(Genus = toupper(Genus)) %>%  # values in upper case
+  mutate(CodeAlive = ifelse(is.even(Paracou6_2016$idTree), "FALSE", CodeAlive)) %>% # Some FALSE in CodeAlive
+  mutate(CensusYear = ifelse(is.even(Paracou6_2016$idTree), CensusYear, CensusYear+1)) # different years inventory
+BrokenParacou6_2016[1:3, "idTree"] <- "200" # create a 2 time present tree
+BrokenParacou6_2016[4, "CircCorr"] <- "6" # DBH < 10
+BrokenParacou6_2016[5, "Plot"] <- "100" # a tree in another plot

### 2021-05-10 R/DraftFunctions.Rmd
Global options (zzz file)

@@
 ```{r}
+library(readr)
 library(dplyr)
@@
 
-```{r}
+```{r ParamCrownDiameterAllometry table code}
 ParamCrownDiameterAllometry <- read_delim("D:/VSC Kourou/DATA/ParamCrownDiameterAllometry.csv", 
@@
 usethis::use_data(ParamCrownDiameterAllometry)
+```
+
+```{r SpeciesCriteria table code}
+SpeciesCriteria <- read_delim("D:/VSC Kourou/DATA/SpeciesCriteria.csv", 
+    ";", escape_double = FALSE, col_types = cols(Commercial = col_factor(levels = c("1", 
+        "2")), MinFD = col_number(), UpMinFD = col_number(), 
+        MaxFD = col_number()), locale = locale(encoding = "Latin1"), 
+    trim_ws = TRUE) %>% 
+  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T) %>% 
+  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F)
+
+usethis::use_data(SpeciesCriteria)
 ```
@@
 # pour l'enregistrer : usethis::use_data(BrokenParacou6_2016) puis le move dans ins/exdata
+```
+
+# My custom options
+faut ptetre mettre Maria. devant  chaque objet!
+```{r}
+# Mimimum DBH value = 10 cm
+# Maximum area slope = 27%
+# Maximum main&2nd trail centerline slope = 22%
+# Maximum main&2nd trail cross slope = 4%
+# Grapple maximum slope = 20%
+# Trees slope = 22%
+# Plateau maximum slope = 5%
+# Distance to compute slope = 6 m (3m for each side)
+# water sources buffer zone = 30 m
+# Main trail width = 5-6 m
+# 2nd trail width = 4 m
+# Big trees = 50 cm
+# Objective bonus = 20-30%
+# Cable = 40 m
+# Grapple = 6 m
+# Isolate tree minimum distance = 100 m
+# Future trees minimum diameter = 35 cm
+# TreefallSuccess proportion = 0.6
+# Treefall orientation = 30-45◦
+# (Hollow) Part taken from hollow trees for fuel exploitation = 1/3
+# Purge = 0.14
+# Maximum TrailDensity = 200 m/ha
+# Maximum landing area = 1 500 m^2
+
+# TrunkHeight formule : TrunkHeight = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2))
+# CrownDiameter formule : CrownDiameter = exp(((ln(DBH)-alpha-error)/beta))/TreeHeight
+# RottenModel
+
+pars <- list(MinDBHValue = 10, #in cm
+  MaxAreaSlope = 27, #in %
+  MaxTrailCenterlineSlope = 22, #in %
+  MaxTrailCrossSlope = 4, #in %
+  GrappleMaxslope = 20, #in %
+  TreeMaxSlope = 22, #in %
+  PlateauMaxSlope = 5, #in %
+  SlopeDistance = 6, #in m (3m for each side)
+  WaterSourcesBufferZone = 30, #in m
+  MainTrailWidth = 5-6, #in m
+  "2ndTrailWidth" = 4, #in m
+  BigTrees = 50, #in cm
+  ObjectiveBonus = 20-30, #in % (ObjectiveBonus >= 20 && ObjectiveBonus =< 30 ou c(20:30))
+  CableLength = 40, #in m
+  GrappleLength = 6, #in m
+  IsolateTreeMinDistance = 100, #in m
+  FutureTreesMinDiameter = 35, #in cm
+  TreefallSuccessProportion = 0.6,
+  TreefallOrientation = 30-45, #in degree (◦)
+  TreeHollowPartForFuel = 1/3, #(Hollow) Part taken from hollow trees for fuel exploitation
+  Purge = 0.14, # in m^3 of fuelwood/m^3 of logged trees  
+  MaxTrailDensity = 200, #in m/ha
+  MaxLandingArea = 1500, #in square meters
+  TrunkHeightAllometry = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2)),
+CrownDiameterAllometry = exp(((ln(DBH)-alpha-error)/beta))/TreeHeight,
+RottenModel = ) 
 ```
@@
 
-if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA) #if DBH doesn't exist create it
+if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA) #if DBH (cm) doesn't exist create it
    Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi} # and compute it
@@
 
-# TreeHarvestableVolume
+# TreeHarvestableVolume (m^3)
   left_join(ForestZoneVolumeParametersTable) %>% 
-  mutate(TreeHarvestableVolume = aCoef + bCoef * CircCorr^2) %>%  # compute the tree harvestable volume
+  mutate(TreeHarvestableVolume = aCoef + bCoef * (DBH/100)^2) %>%  # compute the tree harvestable volume
 
-# TrunkHeight & CrownHeight  
-  mutate(TrunkHeight = TreeHarvestableVolume/(pi*(DBH/2)^2)) %>%  # compute the trunk height (cylinderVolume= π(DBH/2)² x H)
+# TrunkHeight & CrownHeight (m)
+  mutate(TrunkHeight = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2))) %>%  # compute the trunk height (cylinderVolume= π(DBH/2)² x H) DBH in cm, in m in the formule.
   # mutate(CrownHeight = TreeHeight - TrunkHeight) %>%  # compute the crown height TREEHEIGHT EN ATTENTE
 
-# CrownDiameter
+# CrownDiameter (m)
   unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 
@@
   mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
-  select(-Taxo.species, -Taxo.genus, -Taxo.family) %>%  #remove obsolete columns
+  select(-Taxo.species, -Taxo.genus, -Taxo.family) #remove obsolete columns
   # mutate(CrownDiameter = exp((

### 2021-05-11 R/DraftFunctions.Rmd
Tree heights fitting models

@@
 ```{r}
+library(Maria)
 library(readr)
@@
 library(knitr)
+if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA) #if DBH (cm) doesn't exist create it
+   Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi} # and compute it
 # TreeHeight = hauteur de l’arbre (H) (en mètre) (BIOMASS package)
@@
 
-RegionTreeHeight <- retrieveH(D = Paracou6_2016$CircCor, region = "GuianaShield") #continent or region specific model (Feldpaush et al. (2012))
+RegionTreeHeight <- retrieveH(D = Paracou6_2016$DBH, region = "GuianaShield") #continent or region specific model (Feldpaush et al. (2012))
 # GuianaShield = Guyana, French Guiana (piste St Elie (Chave 2005)), Venezuela
@@
 coord <- cbind(long = rep(-52.92, n), lat = rep(5.27, n)) # Paracou P6 coordinates
-CoordTreeHeight <- retrieveH(D = Paracou6_2016$CircCor, coord = coord) #by coordinates (Chave et al. (2012))
+CoordTreeHeight <- retrieveH(D = Paracou6_2016$DBH, coord = coord) #by coordinates (Chave et al. (2012))
 
-result <- modelHD(D = , H = , useWeight = TRUE) #from Guyanese trees heights data
-kable(result)
-# Compute the local H-D model with the lowest RSE (Root Squared Error)
-selectedHDmodel <- modelHD(D = , H = , method = "log2", useWeight = TRUE)
+# Just with Nouragues data (measurement: laser rangefinder):
+ModelsresultNouraguesdata <- modelHD(
+  D = NouraguesHD$D,
+  H = NouraguesHD$H,
+  useWeight = TRUE
+)
+kable(ModelsresultNouraguesdata) #log2 has the lowest RSE (4.222718) (Root Squared Error)
+HDmodelNouraguesdata <- modelHD(
+  D = NouraguesHD$D,
+  H = NouraguesHD$H,
+  method = "log2", # Compute the local H-D model with the lowest RSE.
+  useWeight = TRUE
+)
+TreeHeightEstimation <- retrieveH(
+  D = Paracou6_2016$DBH,
+  model = HDmodelNouraguesdata
+)
+## Put these tree heights estimations in the inventory
+Paracou6_2016TreeHeight <- Paracou6_2016 %>% 
+mutate(TreeHeight = TreeHeightEstimation$H)
+plot(Paracou6_2016TreeHeight$DBH, Paracou6_2016TreeHeight$TreeHeight)#amazing !! It's a log2 form
 
-predictHeight(CircCor, model)
+# Different guyanese data:
+TreeheightGuyafordata <- read_delim("D:/VSC Kourou/DATA/TreeheightGuyafordata.csv", 
+    ";", escape_double = FALSE, col_types = cols(Circ = col_number(), 
+        CircCorr = col_number(), Hauteur = col_number()), 
+    locale = locale(encoding = "Latin1"), 
+    trim_ws = TRUE) %>% 
+  # filter(!(HeightHow == "Visual Estimate" | HeightHow == "Visual estimate"))
+    filter(HeightHow == "Sine Method (Larjavaara & Muller-Landau 2013) with Trimble LaserAce 1000 Rangefinder")
+if (!("DBH" %in% names(TreeheightGuyafordata))) {add_column(TreeheightGuyafordata, DBH = NA) #if DBH (cm) doesn't exist create it
+   TreeheightGuyafordata$DBH = TreeheightGuyafordata$CircCorr/pi} # and compute it
+
+unique(TreeheightGuyafordata$HeightHow)
+
+ModelsresultGuiana <- modelHD(
+  D = TreeheightGuyafordata$DBH,
+  H = TreeheightGuyafordata$Hauteur,
+  useWeight = TRUE
+)
+kable(ModelsresultGuiana) #log2 has the lowest RSE (4.749107 with all data, 4.316927 without "Visual E/estimate", 3.059860 with just "Sine Method")
+#Don't forget, you have the model form, and its parameters, and there are different according to the data.
+
+HDmodelGuiana <- modelHD(
+  D = TreeheightGuyafordata$DBH,
+  H = TreeheightGuyafordata$Hauteur,
+  method = "log2", # Compute the local H-D model with the lowest RSE.
+  useWeight = TRUE
+)
+TreeHeightGuianaEstimation <- retrieveH(
+  D = Paracou6_2016$DBH,
+  model = HDmodelGuiana
+)
+## Put these tree heights estimations in the inventory
+Paracou6_2016TreeHeight <- Paracou6_2016 %>% 
+mutate(TreeHeight = TreeHeightGuianaEstimation$H)
+plot(Paracou6_2016TreeHeight$DBH, Paracou6_2016TreeHeight$TreeHeight)#amazing !! It's a log2 form
 

### 2021-05-11 R/DraftFunctions.Rmd
Debugging zzz, other package import

@@
 # TrunkHeight formule : TrunkHeight = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2))
-# CrownDiameter formule : CrownDiameter = exp(((ln(DBH)-alpha-error)/beta))/TreeHeight
+# CrownDiameter formule : CrownDiameter = exp(((log(DBH)-alpha-error)/beta))/TreeHeight
 # RottenModel
@@
   TrunkHeightAllometry = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2)),
-CrownDiameterAllometry = exp(((ln(DBH)-alpha-error)/beta))/TreeHeight,
+CrownDiameterAllometry = exp(((log(DBH)-alpha-error)/beta))/TreeHeight,
 RottenModel = ) 
@@
   mutate(CrownDiameter = exp((
-  (ln(DBH)-alpha-error)/beta)
+  (log(DBH)-alpha-error)/beta)
   )/TreeHeight) # compute the crown diameter (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺, with 𝜺~N(0,σ^2) and meanσ^2 = 0.0295966977. (Mélaine's allometries))
@@
 ```
+#' @examples
+#' data(Paracou6_2016)
+#' if (!("DBH" %in% names(inventory))) {add_column(inventory, DBH = NA) #if DBH doesn't exist create it
+#' inventory$DBH = inventory$CircCorr/pi} # and compute it
+#' cleaninventory(inventory = Paracou6_2016)
 
@@
   # mutate(CrownDiameter = exp((
-  # (ln(DBH)-alpha-error)/beta)
-  # )/TreeHeight) # compute the crown diameter (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺, with 𝜺~N(0,σ^2) and meanσ^2 = 0.0295966977. (Mélaine's allometries))
+  # (log(DBH)-alpha-error)/beta)
+  # )/TreeHeight) # compute the crown diameter (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺, with 𝜺~N(0,σ^2) and meanσ^2 = 0.0295966977. (Mélaine's allometries)) # Mettre finalement l'objet créé dans le zzz.R
 

### 2021-05-11 R/zzz.R

@@ -1,4 +1,4 @@
-#' Maria package global options
+# Maria package global options
 NULL
 
 .PkgEnv <- new.env()
@@ -6,9 +6,11 @@ NULL
   packageStartupMessage('Welcome to the ForestLogging package.')
 }
 
+
 .onLoad <- function(libname, pkgname) {
-  op <- options()
-  op.Maria <- list(
+  op <- options() #Get the current options from the envmt and store them in op
+  op.Maria <- list( # creation of objects (future options)
+    # Package options
     Maria.path = "~/R-dev",
     Maria.install.args = "",
     Maria.name = "Vincyane Badouard, Guillaume Salzet, Thomas Gaquiere, Géraldine Derroire and Sylvain Schmitt",
@@ -26,7 +28,62 @@ NULL
           "geraldine.derroire@cirad.fr"),
   person("Sylvain","Schmitt",
          role = "ctb",
-          "sylvain.m.schmitt@gmail.com "'))
-    Maria.desc.license = "GPL-3"
+          "sylvain.m.schmitt@gmail.com "'),
+    Maria.desc.license = "GPL-3",
+
+    # Simulator options
+    MinDBHValue = 10, #in cm
+    MaxAreaSlope = 27, #in %
+    MaxTrailCenterlineSlope = 22, #in %
+    MaxTrailCrossSlope = 4, #in %
+    GrappleMaxslope = 20, #in %
+    TreeMaxSlope = 22, #in %
+    PlateauMaxSlope = 5, #in %
+    SlopeDistance = 6, #in m (3m for each side)
+    WaterSourcesBufferZone = 30, #in m
+    MinMainTrailWidth = 5, #in m
+    MaxMainTrailWidth = 6, #in m
+    "2ndTrailWidth" = 4, #in m
+    BigTrees = 50, #in cm
+    ObjectiveBonus = 30, #in % [20;30%]
+    CableLength = 40, #in m
+    GrappleLength = 6, #in m
+    IsolateTreeMinDistance = 100, #in m
+    FutureTreesMinDiameter = 35, #in cm
+    TreefallSuccessProportion = 0.6,
+    MinTreefallOrientation = 30, #in degree (◦)
+    MaxTreefallOrientation = 45, #in degree (◦)
+    TreeHollowPartForFuel = 1/3, #(Hollow) Part taken from hollow trees for fuel exploitation
[…]

### 2021-05-20 R/DraftFunctions.Rmd
Better functions and tests

@@
 BrokenParacou6_2016[1:3, "idTree"] <- "200" # create a 2 time present tree
-BrokenParacou6_2016[4, "CircCorr"] <- "6" # DBH < 10
-BrokenParacou6_2016[5, "Plot"] <- "100" # a tree in another plot
+BrokenParacou6_2016[4, "CircCorr"] <- 6 # DBH < 10
+BrokenParacou6_2016[5, "PLOT"] <- "100" # a tree in another plot
 

### 2021-05-20 R/DraftFunctions.Rmd
Better functions and tests

@@
 library(tidyr)
+library(schoolmath)
 ```
@@
 #in inst/extdata
-library(schoolmath)
-library(dplyr)
 

### 2021-05-21 R/DraftFunctions.Rmd
addtreedim function writing

@@
 data("ForestZoneVolumeParametersTable") # The volume parameters data in the global environment
-load(system.file("extdata", "BrokenParacou6_2016.rda", package = "Maria")) # the test inventory in the global environment
+# load(system.file("extdata", "BrokenParacou6_2016.rda", package = "Maria")) # the test inventory in the global environment
 load(system.file("extdata", "ParamCrownDiameterAllometry.rda", package = "Maria"))
@@
 library(knitr)
-if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA) #if DBH (cm) doesn't exist create it
+
+#if DBH (cm) doesn't exist create it
+if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA)
   Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi} # and compute it
+
 # TreeHeight = hauteur de l’arbre (H) (en mètre) (BIOMASS package)
@@
 
-RegionTreeHeight <- retrieveH(D = Paracou6_2016$DBH, region = "GuianaShield") #continent or region specific model (Feldpaush et al. (2012))
-# GuianaShield = Guyana, French Guiana (piste St Elie (Chave 2005)), Venezuela
+#continent or region specific model (Feldpaush et al. (2012))
+RegionTreeHeight <- retrieveH(D = Paracou6_2016$DBH, region = "GuianaShield") # GuianaShield = Guyana, French Guiana (piste St Elie (Chave 2005)), Venezuela
 
+#by coordinates (Chave et al. (2012))
 n <- length(Paracou6_2016$CircCor)
 coord <- cbind(long = rep(-52.92, n), lat = rep(5.27, n)) # Paracou P6 coordinates
-CoordTreeHeight <- retrieveH(D = Paracou6_2016$DBH, coord = coord) #by coordinates (Chave et al. (2012))
+CoordTreeHeight <- retrieveH(D = Paracou6_2016$DBH, coord = coord)
 
 # Just with Nouragues data (measurement: laser rangefinder):
-ModelsresultNouraguesdata <- modelHD(
+# Fit first different height-diameter models
+ModelsresultNouraguesdata <- modelHD( # modelHD = .
   D = NouraguesHD$D,
   H = NouraguesHD$H,
-  useWeight = TRUE
+  useWeight = TRUE # model weights will be (D^2)*H (weights are proportional to tree volume, so that larger trees have a stronger influence during the construction of the model)
 )
+# choose the best model
 kable(ModelsresultNouraguesdata) #log2 has the lowest RSE (4.222718) (Root Squared Error)
@@
 )
+# Applicate the model to retrieve tree heights ---- HERE
 TreeHeightEstimation <- retrieveH(
@@
 ```
-#' @examples
-#' data(Paracou6_2016)
-#' if (!("DBH" %in% names(inventory))) {add_column(inventory, DBH = NA) #if DBH doesn't exist create it
-#' inventory$DBH = inventory$CircCorr/pi} # and compute it
-#' cleaninventory(inventory = Paracou6_2016)
 
@@
   # CrownDiameter (m)
+  # Add crown diameter parameters at the inventory:
   unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 

### 2021-05-31 R/DraftFunctions.Rmd
TreeHeights and Codecov scripts

@@
 library(schoolmath)
+library(ggplot2)
+library(reshape)
 ```
@@
 
+```{r}
+
+TreeheightGuyafordata <- read_delim("D:/VSC Kourou/DATA/TreeheightGuyafordata.csv", 
+                                    ";", escape_double = FALSE, col_types = cols(Circ = col_number(), 
+                                                                                 CircCorr = col_number(), Hauteur = col_number()), 
+                                    locale = locale(encoding = "Latin1"), 
+                                    trim_ws = TRUE) %>% 
+  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 
+  mutate(DBH = ifelse(is.na(CircCorr), Circ/pi, CircCorr/pi)) %>% 
+  mutate(HeightHow = recode(HeightHow, 'Visual estimate' = 'Visual Estimate'))
+
+any(is.na(TreeheightGuyafordata$DBH)) # all the DBH have been computed?
+
+# esquisse::esquisser()
+
+#Methods facet
+TreeheightGuyafordata %>%
+ ggplot() +
+  aes(x = DBH, y = Hauteur) +
+  geom_point(shape = "circle", size = 0.5, colour = "#440154") +
+  geom_smooth(span = 0.75) + # using method = 'gam' and formula 'y ~ s(x, bs = "cs")'
+  theme_minimal() +
+  facet_wrap(vars(HeightHow))
+
+# Colored multilignes
+TreeheightGuyafordata %>%
+ ggplot() +
+  aes(x = DBH, y = Hauteur, colour = HeightHow) +
+  geom_line(size = 0.2) +
+  scale_color_hue(direction = 1) +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+
+# Methods Box-Plot
+TreeheightGuyafordata %>%
+ggplot(aes(x=DBH, y=Hauteur, fill=HeightHow)) +
+  theme(legend.position = "bottom") +
+  geom_boxplot()
+
+# DBH distribution per method
+TreeheightGuyafordata %>%
+ ggplot() +
+  aes(x = DBH) +
+  geom_histogram(bins = 30L, fill = "#440154") +
+  theme_minimal() +
+  facet_wrap(vars(HeightHow), scales = "free_y") #or "fixed"
+
+# Ind/sp distribution per method
+ggplot(TreeheightGuyafordata) +
+  aes(x = ScientificName) +
+  geom_bar(fill = "#440154") +
+  theme_minimal() +
+  facet_wrap(vars(HeightHow), scales = "free") #or "fixed"
+
+```
+```{r}
+library(BIOMASS)
+library(knitr)
+
+ModelsresultGuiana <-modelHD(
+  D = TreeheightGuyafordata$DBH,
+  H = TreeheightGuyafordata$Hauteur,
+  useWeight = TRUE
+)
+kable(ModelsresultGuiana) #log2 has the lowest RSE (4.699261 with all data, 4.316927 without "Visual E/estimate", 3.059860 with just "Sine Method")
+#Don't forget, you have the model form, and its parameters, and there are different according to the data.
+
+HDmodelGuiana <- modelHD(
+  D = TreeheightGuyafordata$DBH,
+  H = TreeheightGuyafordata$Hauteur,
+  method = "log2", # Compute the H-D model with the lowest RSE.
+  useWeight = TRUE
+)
+TreeHeightGuianaEstimation <- retrieveH(
+  D = TreeheightGuyafordata$DBH,
+  model = HDmodelGuiana
+)
+#Put these tree heights estimations in the inventory
+TreeheightGuyafordataEstim <- TreeheightGuyafordata %>% 
+  mutate(HauteurEstimee = TreeHeightGuianaEstimation$H)
+plot(TreeheightGuyafordataEstim$DBH, TreeheightGuyafordataEstim$HauteurEstimee)#amazing !! It's a log2 form
+
+#facet obs/estim :
+TreeheightGuyafordataEstim %>%
+ # filter(!is.na(CircCorr)) %>%
+ ggplot() +
+  aes(x = Hauteur, y = HauteurEstimee) +
+  geom_point(shape = "circle", size = 0.5, colour = "#440154") +
+  geom_smooth(span = 0.75) + # try with method = lm
+  theme_minimal() +
+  facet_wrap(vars(HeightHow))
+```
+
 ```{r TreeHeight}
@@
 # Fit first different height-diameter models
-ModelsresultNouraguesdata <- modelHD( # modelHD = .
+ModelsresultNouraguesdata <- modelHD(
   D = NouraguesHD$D,
@@
 
+```
+
+```{r}
+# Question : ya t'il des arbres mesurés par plsrs méthodes la même année ?
+
+TreeheightMethods <- TreeheightGuyafordata %>% 
+  select(Forest, Plot, SubPlot, TreeFieldNum, Genus, Species, CensusYear) %>% 
+  unique()
 ```

### 2021-05-31 R/Tree height exploration.Rmd
TreeHeights and Codecov scripts

---
title: "Tree height exploration"
author: "Vincyane Badouard"
date: "28/05/2021"
output: html_document
---
```{r}
TreeheightGuyafordata <- read_delim("D:/VSC Kourou/DATA/TreeheightGuyafordata.csv", 
                                    ";", escape_double = FALSE, col_types = cols(Circ = col_number(), 
                                                                                 CircCorr = col_number(), Hauteur = col_number()), 
                                    locale = locale(encoding = "Latin1"), 
                                    trim_ws = TRUE) %>% 
  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 
  mutate(DBH = ifelse(is.na(CircCorr), Circ/pi, CircCorr/pi)) %>% 
  mutate(HeightHow = recode(HeightHow, 'Visual estimate' = 'Visual Estimate'))

any(is.na(TreeheightGuyafordata$DBH)) # all the DBH have been computed?
```

```{r}
#Methods facet

# png(file = "D:/VSC Kourou/TreeHeights/MethodsFacet.png", width=1500, height=612)
TreeheightGuyafordata %>%
 ggplot() +
  aes(x = DBH, y = Hauteur) +
  geom_point(shape = "circle", size = 0.5, colour = "#440154") +
  geom_smooth(span = 0.75) + # using method = 'gam' and formula 'y ~ s(x, bs = "cs")'
  theme_minimal() +
  facet_wrap(vars(HeightHow))

# dev.off()

```

```{r}
# Colored multilignes
# png(file = "D:/VSC Kourou/TreeHeights/Colored multilignes.png", width=1500, height=612)

TreeheightGuyafordata %>%
  filter(HeightHow != "Visual Estimate") %>% #je l'enlève pcq ça cache tout
 ggplot() +
  aes(x = DBH, y = Hauteur, colour = HeightHow) +
  geom_line(size = 0.2) +
  scale_color_hue(direction = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")

# dev.off()

```

```{r}
# Methods Box-Plot
# png(file = "D:/VSC Kourou/TreeHeights/Methods Box-Plot.png", width=1500, height=612)

TreeheightGuyafordata %>%
ggplot(aes(x=DBH, y=Hauteur, fill=HeightHow)) +
  theme(legend.position = "bottom") +
  geom_boxplot()

# dev.off()

```

```{r}
# DBH distribution per method
# png(file = "D:/VSC Kourou/TreeHeights/DBH distribution per method.png", width=1500, height=612)

TreeheightGuyafordata %>%
 ggplot() +
  aes(x = DBH) +
  geom_histogram(bins = 30L, fill = "#440154") +
  theme_minimal() +
  facet_wrap(vars(HeightHow), scales = "free") #or free_y, "fixed", or "free"

# dev.off()

```

```{r}
# Ind/sp distribution per method
# png(file = "D:/VSC Kourou/TreeHeights/Ind-sp distribution per method.png", width=1500, height=612)

ggplot(TreeheightGuyafordata) +
  aes(x = ScientificName) +
  geom_bar(fill = "#440154") +
  theme_minimal() +
  facet_wrap(vars(HeightHow), scales = "free") #or "fixed"

# dev.off()
```

```{r}
library(BIOMASS)
library(knitr)

ModelsresultGuiana <-modelHD(
  D = TreeheightGuyafordata$DBH,
  H = TreeheightGuyafordata$Hauteur,
  useWeight = TRUE
)
kable(ModelsresultGuiana) #log2 has the lowest RSE (4.699261 with all data, 4.316927 without "Visual E/estimate", 3.059860 with just "Sine Method")
#Don't forget, you have the model form, and its parameters, and there are different according to the data.

HDmodelGuiana <- modelHD(
  D = TreeheightGuyafordata$DBH,
  H = TreeheightGuyafordata$Hauteur,
  method = "log2", # Compute the H-D model with the lowest RSE.
  useWeight = TRUE
)
TreeHeightGuianaEstimation <- retrieveH(
  D = TreeheightGuyafordata$DBH,
  model = HDmodelGuiana
)
#Put these tree heights estimations in the inventory
TreeheightGuyafordataEstim <- TreeheightGuyafordata %>% 
  mutate(HauteurEstimee = TreeHeightGuianaEstimation$H)
plot(TreeheightGuyafordataEstim$DBH, TreeheightGuyafordataEstim$HauteurEstimee)#amazing !! It's a log2 form

```

```{r}
#facet obs/estim :
# png(file = "D:/VSC Kourou/TreeHeights/facet obs-estim.png", width=1500, height=612)

TreeheightGuyafordataEstim %>%
 ggplot() +
  aes(x = Hauteur, y = HauteurEstimee) +
  geom_point(shape = "circle", size = 0.5, colour = "#440154") +
  geom_smooth(span = 0.75) + # try with method = lm
  theme_minimal() +
  facet_wrap(vars(HeightHow))

# dev.off()

```

### 2021-05-31 R/bonjour.R

@@ -1,9 +1,9 @@
 #' Say "Bonjour !" with a name
 #'
-#' @param nom (character) Name of the person to say bonjour.
-#' @param verbose (boolean) Print in console
+#' @param nom Name of the person to say "Bonjour !" (character).
+#' @param verbose Print in console (boolean).
 #'
-#' @return a character string ""Bonjour! name"
+#' @return A character string "Bonjour! Name"
 #' @export
 #'
 #' @examples

### 2021-05-31 tests/testthat/test-addtreedim.R

@@ -1,9 +1,21 @@
-test_that("addtreedim", {
-
-
-
-
-})
+# test_that("addtreedim", {
+#
+#   # Test data preparation
+#   if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA) #if DBH (cm) doesn't exist create it
+#     Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi}
+#
+#   # check their class (integer)
+#   lapply(c("TreeHeight", "TreeHarvestableVolume", "TrunkHeight", "CrownHeight", "CrownDiameter"),
+#          function(element) expect_type(addtreedim(Paracou6_2016)$element, integer))
+#
+#   # check that variables are not empty, or contains NA's
+#   lapply(c("TreeHeight", "TreeHarvestableVolume", "TrunkHeight", "CrownHeight", "CrownDiameter"),
+#          function(element) expect_vector(addtreedim(Paracou6_2016)$element, ptype = integer(), size = length(idTree)))
+#
+#   # check if formulas are respected
+#
+#   # check coherence
+# })
 
 
 # compute for all trees:
@@ -20,4 +32,4 @@ test_that("addtreedim", {
 # -> is not empty, or contains NA's
 # -> check coherence
 
-# -> check if formules are respected
+# -> check if formulas are respected

### 2021-06-02 R/DraftFunctions.Rmd
loggingparameters and addtreedim functions

--- 2021-05-21 R/DraftFunctions.Rmd
@@
 # pour l'enregistrer : usethis::use_data(BrokenParacou6_2016) puis le move dans ins/exdata
-```
-
-# My custom options
-faut ptetre mettre Maria. devant  chaque objet!
-```{r}
-# Mimimum DBH value = 10 cm
-# Maximum area slope = 27%
-# Maximum main&2nd trail centerline slope = 22%
-# Maximum main&2nd trail cross slope = 4%
-# Grapple maximum slope = 20%
-# Trees slope = 22%
-# Plateau maximum slope = 5%
-# Distance to compute slope = 6 m (3m for each side)
-# water sources buffer zone = 30 m
-# Main trail width = 5-6 m
-# 2nd trail width = 4 m
-# Big trees = 50 cm
-# Objective bonus = 20-30%
-# Cable = 40 m
-# Grapple = 6 m
-# Isolate tree minimum distance = 100 m
-# Future trees minimum diameter = 35 cm
-# TreefallSuccess proportion = 0.6
-# Treefall orientation = 30-45◦
-# (Hollow) Part taken from hollow trees for fuel exploitation = 1/3
-# Purge = 0.14
-# Maximum TrailDensity = 200 m/ha
-# Maximum landing area = 1 500 m^2
-
-# TrunkHeight formule : TrunkHeight = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2))
-# CrownDiameter formule : CrownDiameter = exp(((log(DBH)-alpha-error)/beta))/TreeHeight
-# RottenModel
-
-pars <- list(MinDBHValue = 10, #in cm
-             MaxAreaSlope = 27, #in %
-             MaxTrailCenterlineSlope = 22, #in %
-             MaxTrailCrossSlope = 4, #in %
-             GrappleMaxslope = 20, #in %
-             TreeMaxSlope = 22, #in %
-             PlateauMaxSlope = 5, #in %
-             SlopeDistance = 6, #in m (3m for each side)
-             WaterSourcesBufferZone = 30, #in m
-             MainTrailWidth = 5-6, #in m
-             "2ndTrailWidth" = 4, #in m
-             BigTrees = 50, #in cm
-             ObjectiveBonus = 20-30, #in % (ObjectiveBonus >= 20 && ObjectiveBonus =< 30 ou c(20:30))
-             CableLength = 40, #in m
-             GrappleLength = 6, #in m
-             IsolateTreeMinDistance = 100, #in m
-             FutureTreesMinDiameter = 35, #in cm
-             TreefallSuccessProportion = 0.6,
-             TreefallOrientation = 30-45, #in degree (◦)
-             TreeHollowPartForFuel = 1/3, #(Hollow) Part taken from hollow trees for fuel exploitation
-             Purge = 0.14, # in m^3 of fuelwood/m^3 of logged trees  
-             MaxTrailDensity = 200, #in m/ha
-             MaxLandingArea = 1500, #in square meters
-             TrunkHeightAllometry = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2)),
-             CrownDiameterAllometry = exp(((log(DBH)-alpha-error)/beta))/TreeHeight,
-             RottenModel = ) 
 ```
@@
 
+```{r}
+library(BIOMASS)
+library(knitr)
+
+TreeheightGuyafordata <- read_delim("D:/VSC Kourou/DATA/TreeheightGuyafordata.csv", 
+                                    ";", escape_double = FALSE, col_types = cols(Circ = col_number(), 
+                                                                                 CircCorr = col_number(), Hauteur = col_number()), 
+                                    locale = locale(encoding = "Latin1"), 
+                                    trim_ws = TRUE) %>% 
+  mutate(HeightHow = recode(HeightHow, 'Visual estimate' = 'Visual Estimate')) %>% 
+  # filter(!(HeightHow == "Visual Estimate" | HeightHow == "Visual estimate")) %>% 
+  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 
+  mutate(DBH = ifelse(is.na(CircCorr), Circ/pi, CircCorr/pi)) # add DBH column
+
+any(is.na(TreeheightGuyafordata$DBH)) # all the DBH have been computed?
+
+SineTelemeter <- TreeheightGuyafordata %>% #data to fit model
+  filter(HeightHow == "Sine Method (Larjavaara & Muller-Landau 2013) with Trimble LaserAce 1000 Rangefinder"| HeightHow == "Telemeter")
+
+ModelsresultGuiana <-modelHD(
+  D = SineTelemeter$DBH,
+  H = SineTelemeter$Hauteur,
+  useWeight = TRUE
+)
+kable(ModelsresultGuiana) #log2 has the lowest RSE (4.699261 with all data, 4.316927 without "Visual E/estimate", 3.059860 with just "Sine Method", 3.809011 with sine and telemeter)
+
+HDmodelGuiana <- modelHD(
+  D = SineTelemeter$DBH,
+  H = SineTelemeter$Hauteur,
+  method = "log2", # Compute the H-D model with the lowest RSE.
+  useWeight = TRUE
+)
+TreeHeightGuianaEstimation <- retrieveH(
+  D = TreeheightGuyafordata$DBH,
+  model = HDmodelGuiana
+)
+#Put these tree heights estimations in the inventory
+TreeheightGuyafordataEstim <- TreeheightGuyafordata %>% 
+  mutate(HauteurEstimee = TreeHeightGuianaEstimation$H)
+plot(TreeheightGuyafordataEstim$DBH, TreeheightGuyafordataEstim$HauteurEstimee)
+
+# obs/estim regression:
+TreeheightGuyafordataEstim %>%
+  ggplot() +
+  aes(x = Hauteur, y = HauteurEstimee) +
+  geom_point(shape = "circle", size = 0.5, colour = "#440154") +
+  geom_smooth(span = 0.75) + 
+  theme_minimal()
+# We are well between 10 and 35m height
+```
+
 ```{r TreeHeight}
@@
 
-#if DBH (cm) doesn't exist create it
-if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA)
-  Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi} # and compute it
-
-# TreeHeight = hauteur de l’arbre (H) (en mètre) (BIOMASS package)
-# 3 options :
-# - get my tree heights from the location (from continent or region specific model, or from coordinates)
-# - from other Guyanese trees heights data, fit different H-D models, select the best and apply on my data.
-
-#continent or region specific model (Feldpaush et al. (2012))
-RegionTreeHeight <- retrieveH(D = Paracou6_2016$DBH, region = "GuianaShield") # GuianaShield = Guyana, French Guiana (piste St Elie (Chave 2005)), Venezuela
-
-#by coordinates (Chave et al. (2012))
-n <- length(Paracou6_2016$CircCor)
-coord <- cbind(long = rep(-52.92, n), lat = rep(5.27, n)) # Paracou P6 coordinates
-CoordTreeHeight <- retrieveH(D = Paracou6_2016$DBH, coord = coord)
-
 # Just with Nouragues data (measurement: laser rangefinder):
 # Fit first different height-diameter models
-ModelsresultNouraguesdata <- modelHD( # modelHD = .
+ModelsresultNouraguesdata <- modelHD(
   D = NouraguesHD$D,
@@
 
-  rename(Taxo.family = Taxo, alpha.family = alpha, beta.family = beta) %>% 
+  dplyr::rename(Taxo.family = Taxo, alpha.family = alpha, beta.family = beta) %>%
   mutate(alpha = alpha.species, beta = beta.species, Taxo = Taxo.species) %>% # create the future & unique alpha,beta,taxo columns 

### 2021-06-02 R/Tree height exploration.Rmd
loggingparameters and addtreedim functions

@@
 any(is.na(TreeheightGuyafordata$DBH)) # all the DBH have been computed?
+
+# DBH range per method
+TreeheightGuyafordata %>% 
+  group_by(HeightHow) %>% #pour réaliser les opérations suivantes par groupes de modalités
+  summarise(MinDBH = min(DBH)) %>% 
+  arrange(MinDBH)
+
+TreeheightGuyafordata %>% 
+  group_by(HeightHow) %>% #pour réaliser les opérations suivantes par groupes de modalités
+  summarise(MaxDBH = max(DBH)) %>% 
+  arrange(desc(MaxDBH))
+# Visual Estimate: 0.416986 - 256.23946
+# Telemeter: 9.867606 - 159.15494
+# Optical Telemeter Birnbaum: 7.591691 -131.46198
+# Vertex Laser: 10.185916 - 95.73170
+# Sine Method: 6.073353 - 88.80846
+
+# measurements number per method
+TreeheightGuyafordata %>% 
+  count(HeightHow) %>% 
+  arrange(desc(n))
+# Visual Estimate	: 27986			
+# Optical Telemeter Birnbaum: 4902	
+# Telemeter: 1454			
+# Sine Method:  998	
+# Vertex Laser: 441
+
+TreeheightGuyafordata %>% 
+  group_by(HeightHow) %>% 
+  n_distinct(ScientificName) %>% 
+  count(ScientificName) %>% 
+  arrange(desc(n))
+
+TreeheightGuyafordata %>% 
+  group_by(HeightHow) %>%
+  n_distinct(TreeheightGuyafordata$ScientificName) %>% 
+  count(ScientificName)
 ```
@@
 ```
+
+```{r}
+# Fit Height-Diameter model
+library(BIOMASS)
+
+SineTelemeter <- read_delim("D:/VSC Kourou/DATA/TreeheightGuyafordata.csv",
+                                    ";", escape_double = FALSE, col_types = cols(Circ = col_number(),
+                                                                                 CircCorr = col_number(), Hauteur = col_number()),
+                                    locale = locale(encoding = "Latin1"),
+                                    trim_ws = TRUE) %>%
+  filter(HeightHow == "Sine Method (Larjavaara & Muller-Landau 2013) with Trimble LaserAce 1000 Rangefinder"| HeightHow == "Telemeter") %>%
+  mutate(DBH = ifelse(is.na(CircCorr), Circ/pi, CircCorr/pi)) # add DBH column
+
+HDmodel <- modelHD(
+  D = SineTelemeter$DBH,
+  H = SineTelemeter$Hauteur,
+  method = "log2", # Compute the H-D model with the lowest RSE.
+  useWeight = TRUE
+)
+
+Dmodel[["coefficients"]]
+
+# log 2: log(H) = a + b*log(D) + c*log(D)^2
+
+# log(H) = 0.07359191 + 1.34241216*log(D) + -0.12282344*log(D)^2
+# H = exp(0.07359191 + 1.34241216*log(D) + -0.12282344*log(D)^2)
+
+# (Intercept)  0.07359191
+# I(log(D)^1)  1.34241216
+# I(log(D)^2) -0.12282344
+```

### 2021-06-02 tests/testthat/test-cleaninventory.R

@@ -1,5 +1,9 @@
 test_that("cleaninventory", {
 
+  #Check the function argument
+  MatrixInventory <- as.matrix(Paracou6_2016)
+  expect_error(cleaninventory(MatrixInventory), regexp = "inventory must be a data.frame")
+
   #Create the test inventory
   TestInventory <- Paracou6_2016
   TestInventory[10, "CodeAlive"] <- "FALSE" # Some FALSE in CodeAlive
@@ -10,6 +14,8 @@ test_that("cleaninventory", {
 
   #check if DBH >= 10 (check if DBH exists in the same way)
   expect_true(all(cleaninventory(TestInventory)$DBH >= 10))
+
+  expect_false(any(is.na(cleaninventory(TestInventory)$DBH))) #check that all the DBH are computed
 
 
   #check if the stops work

### 2021-06-04 R/DESIGNATION_DRAFT.Rmd
Start Designation

---
title: "DESIGNATION_DRAFT"
author: "Vincyane Badouard"
date: "04/06/2021"
output: html_document
---

# Les arguments
inventory
speciescriteria
type
objective
diversification
specieslax
objectivelax
otherloggingparameters = loggingparameters()
multilignes "MainTrail"

# Fonctions internes à exporter
harvestable, selected, futurereserve

# Etapes préliminaires
+ Ne sélectionner que des arbres encore vivants (DeathCause = NULL) durant toute la fonction.
+ Identification à vue d'œil des arbres à défaut (proportion : valeur fixe ou modèle ?) : coder "1" dans une colonne "Defect" de la table, coder "0" les autres.
+ Ne considérer dans la désignation que les arbres "0" dans "Defect".
+ Désignation : fonction "TreeSelection"
+ Si type = "RILdamagerotten", "VO" = "objective"
+ Sinon "VO" = "objective" + 20-30% pour compenser le bois creux désigné.
```{r}
# filter(DeathCause = NULL) %>%  # select only still alived trees (after MainTrails) NULL ou NA
# mutate(Defect= ifelse(condition, "1", "0")) %>%  # 1 = default tree, 0 = no visible default
# filter(Defect = "0") %>%

# Désignation : fonction "TreeSelection"
if (type = "RILdamagerotten"){VO = objective
}else{
  VO = objective + otherloggingparameters$ObjectiveBonus # to compensate for the designated hollow wood.
} 
```

# harvestable
+ Étiqueter "harvestable", dans une colonne "LoggingStatus", sélection des individus :
Essences :
- Si diversification=T ou si diversification=F & specieslax=T : = "1" & "2" dans colonne "Commercial"
- Sinon (diversification=F & specieslax=F): = "1" dans colonne "Commercial"
Diamètre exploitable (speciescriteria data): individus dont le DBH est compris entre la valeur dans colonne "MinFD" pour leur sp, de la table speciescriteria , et le MaxFD.
Distribution spatiale:
- Arbres sur <22% de pente et arbres sur pente >22% si à 40 m maximum d’une zone <22%.
- arbre non isolé : élimination des arbres à >100m des autres individus de la même espèce.
- hors des pistes principales : dont les coordonnées n'appartiennent pas aux multilignes "MainTrail".
+ Si diversification=F & specieslax=T, étiqueter "harvestable2nd" à la place d’"harvestable", les "Commercial"= "2" dans la colonne "LoggingStatus".
+ Étiqueter "UPeco2" à la place d’"harvestable" dans colonne "LoggingStatus", les individus "Commercial"= "2" de "DBH" > à leur "UpMinFD".
+ HVinit= somme des valeurs de "TreeHarvestableVolume " des arbres dont "LoggingStatus" = "harvestable".
```{r}
HarverstableConditions  
#select essences
if (diversification || (!diversification && specieslax)) {
  filter(Commercial %in% c("1", "2"))
} else if (!diversification && !specieslax) {
  filter(Commercial == "1")
}
#select diameters
left_join(speciescriteria, by = "ScientificName") #or by VernName
filter(DBH >= MinFD & DBH <= MaxFD)

#select spatially
#slope
#isolement
#MainTrails out

mutate(LoggingStatus = ifelse(HarverstableConditions,
                              "harvestable", "non-harvestable")) %>% 
  mutate(LoggingStatus = ifelse(
    !diversification & 
      specieslax & 
      LoggingStatus == "harvestable" & 
      Commercial == "2",
    "harvestable2nd", LoggingStatus)) %>% 
  mutate(LoggingStatus = ifelse(
    LoggingStatus == "harvestable" &
      Commercial == "2" & 
      DBH >= UpMinFD, 
    "UPeco2", LoggingStatus))

HVinit <- data %>%
  filter(LoggingStatus == "harvestable") %>% 
  sum(TreeHarvestableVolume)

```

# selected
```{r}
add_column(data, Up = NA) # Create a column to indicate Which sp is FD uped. Or create this column d'office in speciescriteria.

# if objective achieved at the first attempt
mutate(Selected = ifelse(HVinit == VO & LoggingStatus == "harvestable",
                         "1", LoggingStatus))

if (HVinit < VO){ 
  if (!diversification && specieslax){
    # LoggingStatus = "harvestable2nd" | LoggingStatus = "harvestable"
    # Selected = "1"
    # prendre parmi les arbres étiquetés "harvestable2nd" ou "harvestable" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVlax = VO.
    # étiqueter ces arbres "1", dans une colonne "Selected".

    if (HVlax < VO && objectivelax) message("Le volume exploitable (= HVlax ) est encore inférieur (de VO- HVlax) à votre volume objectif malgré la diversification que vous avez permise (sans la diversification HVinit= HVinit). Vous avez choisi dans ce cas de poursuivre l’exploitation avec un volume inférieur à votre objectif.")

    if (HVlax < VO && !objectivelax) stop("Le volume exploitable (=HVlax ) est encore inférieur (de VO- HVlax) à votre volume objectif malgré la diversification que vous avez permise (sans la diversification HVinit= HVinit). Par défaut ou par votre choix, la simulation s’arrête. Si vous souhaitez poursuivre l’exploitation malgré un volume exploitable inférieur à votre volume objectif vous disposez de l‘argument "objectivelax".")

    if (!HVlax < VO) message("Le volume exploitable (=HVinit) est inférieur (de VO- HVinit) à votre volume objectif. Vous avez choisi de diversifier votre sélection d’espèces dans ce cas. L’exploitation s’est donc réalisée sur cette sélection diversifiée d’espèces.")
  }

  if ((!diversification && !specieslax && objectivelax) | (diversification && objectivelax))
    message("Le volume exploitable (=HVinit) est inférieur (de VO- HVinit) à votre volume objectif. Vous avez choisi dans ce cas de poursuivre l’exploitation sans diversifier vos essences.")

  if ((!specieslax & !objectivelax) | (diversification && !objectivelax)) 
    stop("Le volume exploitable (=HVinit) est inférieur (de VO- HVinit) à votre volume objectif. Par défaut ou par votre choix, la simulation s’arrête. Si vous souhaitez poursuivre l’exploitation malgré un volume exploitable inférieur à votre volume objectif vous disposez de l‘argument "objectivelax" ou de la diversification d’essences.")
}

if (HVinit > VO) {
  # rehaussement des DME des sp ECMP : étiqueter "harvestableUp" à la place d’"harvestable", dans la colonne "LoggingStatus", les individus "Commercial"= "1" dont le "DBH" est compris entre la valeur dans colonne "UpMinFD" pour leur sp, de la table speciescriteria , et le MaxFD.
  mutate(Up = ifelse(Commercial == "1", "1", Up))# Dans la table species renseigner "1" dans la colonne "Up" les "Commercial"= "1" (pour signifier que leur DME a été réhaussé)
  # test "Commercial"= "1" pour les "harvestableUp"

  if (!diversification) {
    # HVupCommercial1 = sum(TreeHarvestableVolume) des LoggingStatus == harvestableUp.
    if (HVupCommercial1 == VO){
      # Selected = "1" # étiqueter ces arbres "1", dans une colonne "Selected".
      message("Le volume exploitable (=HVinit) étant supérieur (de VO- HVinit) au volume objectif, les DME des ECMP ont été rehaussés. Le volume objectif est maintenant atteint.")
    }

    if (HVupCommercial1 > VO){ 
      # prendre parmi les arbres étiquetés "harvestableUp" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVupCommercial1adjust= VO.
      # Selected = "1" # étiqueter ces arbres "1", dans une colonne "Selected".
      message("Le volume exploitable (=HVupCommercial1) est toujours supérieur (de VO- HVupCommercial1) à votre volume objectif malgré le rehaussement des DME (Volume exploitable initial = HVinit). Afin d’atteindre votre volume objectif, les arbres ont été choisis par ordre décroissant de volume jusqu'à l’atteinte du volume objectif.")
    }
    if (HVupCommercial1 < VO){
      # prendre parmi les arbres étiquetés "harvestableUp" & "harvestable" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVupCommercial1adjust = VO.
      # Selected = "1" étiqueter ces arbres "1", dans une colonne "Selected".
      message("Le volume exploitable (=HVinit) étant supérieur (de VO- HVinit) au volume objectif, les DME des ECMP ont été rehaussés avec une conservation de certaines tiges dont le DBH est inférieur au UpMinFD afin d’assurer l’atteinte du volume objectif.")
    }
  }

  if (diversification) {
    # "HVupCommercial1" = sum(TreeHarvestableVolume) des LoggingStatus == "harvestableUp" | LoggingStatus == "harvestable."

    if (HVupCommercial1 == VO){
      # étiqueter ces arbres "1", dans une colonne "Selected".
      message("Le volume exploitable (=HVinit) étant supérieur (de VO- HVinit) au volume objectif, les DME des ECMP ont été rehaussés. Le volume objectif est maintenant atteint. Il n’a pas été nécessaire de rehausser les DME des autres espèces économiques")
    }

    if (HVupCommercial1 < VO){ 
      # prendre parmi les arbres "Commercial"= "1" étiquetés "harvestableUp" et "harvestable" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVupCommercial1adjust = VO.
      # Selected = "1" étiqueter ces arbres "1", dans une colonne "Selected".
      message("Le volume exploitable (=HVinit) étant supérieur (de VO - HVinit) au volume objectif, les DME des ECMP ont été rehaussés avec une conservation de certaines tiges dont le DBH est inférieur au UpMinFD afin d’assurer l’atteinte du volume objectif. Il n’a pas été nécessaire de rehausser les DME des autres espèces économiques.")
    }

    if (HVupCommercial1 > VO){ 
      # rehaussement des DME des autres sp eco: étiqueter "harvestableUp" à la place d’"UPeco2", dans la colonne "LoggingStatus"
      # Dans la table speciescriteria  renseigner "1" dans la colonne "Up" les "Commercial"= "2" (pour signifier que leur DME a été rehaussé)
      # "HVupCommercial12" = somme des valeurs de "TreeHarvestableVolume " des "harvestableUp".
      if (HVupCommercial12 == VO){
        # Selected = "1" étiqueter ces arbres "1", dans la colonne "Selected".
      }
      if (HVupCommercial12 < VO){
        # prendre parmi les arbres étiquetés "harvestableUp" et "harvestable" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVupCommercial12adjust = VO.
        # Selected = "1" étiqueter ces arbres "1", dans une colonne "Selected".
      }

      if (HVupCommercial12 > VO){
        # prendre parmi les arbres étiquetés "harvestableUp" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVupCommercial12adjust = VO.
        # Selected = "1" étiqueter ces arbres "1", dans une colonne "Selected".
        message("Le volume exploitable (=HVinit) étant supérieur (de VO- HVinit) au volume objectif, il a été nécessaire de rehausser les DME de toutes les essences. Le volume objectif est maintenant atteint.")
      }
    }
  }
}

# Lancer le modèle prédictif "Rotten" de S.Schmitt pour identifier les arbres désignés ("Selected"= "1") "véritablement"creux.

# Étiqueter ces arbres "1" dans une colonne "RottenModel" et dans la colonne "Defect". Passer ces "Selected"= "1" à "Selected"= "0".

# if type != "RILdamagerotten" : LoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
# if type = "RILdamagerotten" :
# pour les arbres RottenModel = "1", coder "hollowfuel" dans colonne "DeathCause"
# Ajout des coordonnées de ces arbres au vecteur "RottenTreesPoints" et si type = "RIL3fuelrotten", au vecteur "EnergywoodTreesPoints".
# NoRottenLoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
# LoggedVolume = ∑NoRottenLoggedVolume  et ⅔ du volume de ceux codés RottenModel = "1".
# if "Up" = NA remplacer NA par "0"

```

# futurereserve

```{r}
# Étiqueter "future", dans une colonne "LoggingStatus", sélection de tous les individus :
# Essence : "Commercial"= "1" uniquement (qqsoit la diversification)
# DBH : 
# si dans la table speciescriteria  la colonne "Up" = "1" pour son sp : le DBH des individus de cette sp doit être compris entre 35 et le "UpMinFD" de son sp.
# sinon entre 35 et le "MinFD" de son sp.
# 
# Sélectionner les arbres réservés (parmis les Avenirs, autant que d’arbres exploités) :
# "stem" = nombre de "1" dans colonne "Selected" (& Rottenmodel = 0 ?)
# Dans colonne "LoggingStatus", remplacer 1 "future"par "reserve" au hasard stem fois.

# Créer un vecteur ("HarvestableTreesPoints") de points de coordonnées des arbres LoggingStatus = "harvestable" ou "harvestableUp" ou "harvestable2nd".
# Créer un vecteur ("SelectedTreesPoints") de points de coordonnées des arbres Selected = 1.
# Créer un vecteur ("FutureTreesPoints") de points de coordonnées des arbres LoggingStatus = "future"
# Créer un vecteur ("ReserveTreesPoints") de points de coordonnées des arbres LoggingStatus = "reserve".
# Si diversification = F & specieslax = T & HVinit< VO LoggingStatus = "harvestable2nd"inchangé
# sinon LoggingStatus = "harvestable2nd" devient LoggingStatus = "NA".
# Si pour Commercial = "2" Up = "0" remplacer "UPeco2" par "NA" dans LoggingStatus.

```

### 2021-06-04 R/DraftFunctions.Rmd
Start Designation

@@
 ---
+```{r}
+# si on avait une ancienne version de withr pour rstan
+remove.packages("withr")
+install.packages("withr")
+```
 
@@
 lapply(Paracou6_2016, class) #give the class of all the data variables
-```
-
-# Create a broken dataset
-```{r Create a broken dataset}
-#in inst/extdata
-
-BrokenParacou6_2016 <- Paracou6_2016 %>% 
-  select(-Species) %>% # missing column
-  rename(Vernacular = VernName) %>% # other column name
-  rename(PLOT = Plot) %>% # variable name in upper case
-  mutate(idTree = as.character(as.numeric(idTree))) %>% #an other variable class
-  mutate(Lon = round(Lon, digits =0)) %>% # no digits
-  mutate(Genus = toupper(Genus)) %>%  # values in upper case
-  mutate(CodeAlive = ifelse(is.even(Paracou6_2016$idTree), "FALSE", CodeAlive)) %>% # Some FALSE in CodeAlive
-  mutate(CensusYear = ifelse(is.even(Paracou6_2016$idTree), CensusYear, CensusYear+1)) # different years inventory
-BrokenParacou6_2016[1:3, "idTree"] <- "200" # create a 2 time present tree
-BrokenParacou6_2016[4, "CircCorr"] <- 6 # DBH < 10
-BrokenParacou6_2016[5, "PLOT"] <- "100" # a tree in another plot
-
-# pour l'enregistrer : usethis::use_data(BrokenParacou6_2016) puis le move dans ins/exdata
 ```

### 2021-06-04 R/testaddtreedim_DRAFT.Rmd
Start Designation

---
title: "testaddtreedim_DRAFT"
author: "Vincyane Badouard"
date: "04/06/2021"
output: html_document
---

```{r}
if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA) #if DBH doesn't exist create it
Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi} # and compute it

inventory = Paracou6_2016
crowndiameterparameters = ParamCrownDiameterAllometry
volumeparameters = ForestZoneVolumeParametersTable
otherloggingparameters = loggingparameters()

spParamCrownDiameter <- crowndiameterparameters %>% #parameters at species scale
  filter(Taxo == "sp") %>%
  select(-Family)
genParamCrownDiameter <- crowndiameterparameters %>% #parameters at genus scale
  filter(Taxo == "gen") %>%
  select(-Family, -ScientificName, -Species)
famParamCrownDiameter <- crowndiameterparameters %>% #parameters at family scale
  filter(Taxo == "fam") %>%
  select(-Genus, -ScientificName, -Species)

# Variables computation:

prout <- inventory %>%

  # TreeHarvestableVolume (m3)
  left_join(volumeparameters) %>%
  mutate(TreeHarvestableVolume = otherloggingparameters$TreeHarvestableVolumeAllometry(aCoef, bCoef, DBH)) %>%

  # TrunkHeight (m)
  mutate(TrunkHeight = otherloggingparameters$TrunkHeightAllometry(DBH, TreeHarvestableVolume)) %>%

  # TreeHeight (m)
  mutate(TreeHeight = otherloggingparameters$TreeHeightAllometry(DBH)) %>%

  # CrownHeight (m)
  mutate(CrownHeight = TreeHeight - TrunkHeight) %>%

# CrownDiameter (m)
# Add crown diameter allometry parameters at the inventory:
unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% # create ScientificName column in the inventory
  left_join(spParamCrownDiameter, by = c("ScientificName","Genus","Species")) %>% # at species scale
  left_join(genParamCrownDiameter, by = "Genus", suffix = c(".species", ".genus")) %>% # at genus scale
  left_join(famParamCrownDiameter, by = "Family") %>% # at family scale
  dplyr::rename(Taxo.family = Taxo, alpha.family = alpha, beta.family = beta) %>%
  # manage the different scales parameters Species > Genus > Family:
  # alpha:
  mutate(alpha = alpha.species, beta = beta.species, Taxo = Taxo.species) %>% # create the future & unique alpha,beta,taxo columns
  mutate(alpha = ifelse(is.na(alpha), alpha.genus, alpha)) %>% #if species parameters are absent, take genus parameters
  mutate(alpha = ifelse(is.na(alpha), alpha.family, alpha)) %>% #if species&genus parameters are absent, take family parameters
  mutate(alpha = ifelse(is.na(alpha), mean(alpha, na.rm =T), alpha)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-alpha.species, -alpha.genus, -alpha.family) %>% #remove obsolete columns
  # beta:
  mutate(beta = ifelse(is.na(beta), beta.genus, beta)) %>% #if species parameters are absent, take genus parameters
  mutate(beta = ifelse(is.na(beta), beta.family, beta)) %>% #if species&genus parameters are absent, take family parameters
  mutate(beta = ifelse(is.na(beta), mean(beta, na.rm =T), beta)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-beta.species, -beta.genus, -beta.family) %>% #remove obsolete columns
  # scale:
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.genus, Taxo)) %>% #if species parameters are absent, take genus parameters
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.family, Taxo)) %>% #if species&genus parameters are absent, take family parameters
  mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-Taxo.species, -Taxo.genus, -Taxo.family) %>% #remove obsolete columns
  # compute the crown diameter
  mutate(CrownDiameter = otherloggingparameters$CrownDiameterAllometry(DBH, TreeHeight, alpha, beta))

return(inventory)

```

### 2021-06-15 R/DESIGNATION_DRAFT.Rmd
.ONFGuyafortaxojoin & .harvestable

@@
 type
+fuel
 objective
@@
 + Désignation : fonction "TreeSelection"
-+ Si type = "RILdamagerotten", "VO" = "objective"
++ Si type = "RIL3fuelhollow", "VO" = "objective"
 + Sinon "VO" = "objective" + 20-30% pour compenser le bois creux désigné.
+
+```{r Give values to the arguments to work}
+
+inventory = addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))) #3539 rows (Paracou: 3620 rows)
+speciescriteria = SpeciesCriteria
+type = "manual"
+fuel = "0"
+objective = 20
+diversification = TRUE
+specieslax = FALSE
+objectivelax = FALSE
+otherloggingparameters = loggingparameters()
+# MainTrail
+
+```
+
 ```{r}
+
+# inventory <- inventory %>% 
 # filter(DeathCause = NULL) %>%  # select only still alived trees (after MainTrails) NULL ou NA
-# mutate(Defect= ifelse(condition, "1", "0")) %>%  # 1 = default tree, 0 = no visible default
-# filter(Defect = "0") %>%
 
-# Désignation : fonction "TreeSelection"
-if (type = "RILdamagerotten"){VO = objective
+# mutate(VisibleDefectProba = otherloggingparameters$VisiblyRottenModel(DBH)) %>%
+# mutate(VisibleDefect = sample(c(0,1), size = 1, replace = F, prob = VisibleDefectProba)) # 1 = default tree, 0 = no visible default (là ma fct ne sait pas qd elle doit mettre 0 ou 1)
+
+# filter(VisibleDefect = "0") %>%
+
+if (type == "RIL3fuelhollow"| (type == "manual"& fuel =="2")){VO = objective #3604 rows
 }else{
@@
 }
+
+```
+
+# Joindre les taxonomies ONF/Guyafor (.ONFGuyafortaxojoin)
+```{r}
+# speciescriteriaVern <- speciescriteria %>% 
+#   select(-ScientificName)
+# 
+# speciescriteriaScientfc <- speciescriteria %>% 
+#   select(-VernName)
+
+speciescriteria = SpeciesCriteria
+
+genuscriteria <- speciescriteria %>% # for economic names that relate to entire genus
+  filter(Species == "spp")
+
+speciescriteria <- speciescriteria %>%
+  filter(Species != "spp")
+
+inventoryA <- inventory %>% 
+  left_join(genuscriteria, by = "Genus", suffix = c("", ".genus")) %>%
+  select(-Species.genus) %>% 
+  left_join(speciescriteria, by = c("Genus","Species"), suffix = c(".genus", ".species")) %>% 
+  dplyr::rename(VernName = VernName.genus) %>% 
+  mutate(ONFName = ifelse(is.na(VernName.species), VernName.genus.genus, VernName.species)) %>% 
+  select(-VernName.species, -VernName.genus.genus) %>% 
+  mutate(Commercial = ifelse(is.na(Commercial.species), Commercial.genus, Commercial.species)) %>%
+  mutate(MinFD = ifelse(is.na(MinFD.species), MinFD.genus, MinFD.species)) %>%
+  mutate(UpMinFD = ifelse(is.na(UpMinFD.species), UpMinFD.genus, UpMinFD.species)) %>%
+  mutate(MaxFD = ifelse(is.na(MaxFD.species), MaxFD.genus, MaxFD.species)) %>% 
+  select(-Commercial.species, -Commercial.genus, -MinFD.species, -MinFD.genus, -UpMinFD.species, -UpMinFD.genus, -MaxFD.species, -MaxFD.genus)
+
+ConcernedRows <- which(inventoryA$ONFName == "maho rouge" & (inventoryA$ScientificName == "Lecythis_poiteaui"| inventoryA$ScientificName == "Lecythis_praeclara" | inventoryA$ScientificName == "Lecythis_holcogyne" | inventoryA$ScientificName == "Lecythis_pneumatophora"| inventoryA$ScientificName == "Lecythis chartacea"| inventoryA$ScientificName == "Lecythis zabucajo"))
+if(length(ConcernedRows) > 0){
+  inventoryA$ONFName[ConcernedRows] <- NA
+  inventoryA$Commercial[ConcernedRows] <- NA
+  inventoryA$MinFD[ConcernedRows] <- NA
+  inventoryA$UpMinFD[ConcernedRows] <- NA
+  inventoryA$MaxFD[ConcernedRows] <- NA
+}
+
+ConcernedRows <- which(inventoryA$ONFName == "balata blanc" & (inventoryA$ScientificName == "Micropholis_melinoniana"| inventoryA$ScientificName == "Micropholis_egensis" | inventoryA$ScientificName == "Micropholis_cayennensis" | inventoryA$ScientificName == "Micropholis_obscura"))
+if(length(ConcernedRows) > 0){
+  inventoryA$ONFName[ConcernedRows] <- NA
+  inventoryA$Commercial[ConcernedRows] <- NA
+  inventoryA$MinFD[ConcernedRows] <- NA
+  inventoryA$UpMinFD[ConcernedRows] <- NA
+  inventoryA$MaxFD[ConcernedRows] <- NA
+}
+
+filter(inventoryA, ScientificName == "Micropholis_obscura")
+
+# Maho rouge = sauf "Lecythis_poiteaui", "Lecythis_praeclara" et "Lecythis_holcogyne" , "Lecythis_pneumatophora" et "Lecythis chartacea", "Lecythis zabucajo") 
+# Bakuman ou Balata blanc = sauf "Micropholis_melinoniana", "Micropholis_egensis",  "Micropholis_cayennensis" et "Micropholis_obscura")
+
+```
+
+```{r}
+# To control
+dupli <- inventoryA[duplicated(inventoryA$idTree), ] # les lignes dupliquées sont dues aux genres qui concernent plsrs essences
+
+NAtable <- inventoryA[is.na(inventoryA$Commercial),] #2101 ind not linked
+NAtablescfc <- as.data.frame(unique(inventoryA[is.na(inventoryA$Commercial),]$ScientificName)) #264 sp not linked
+NAtablevern <- as.data.frame(unique(inventoryA[is.na(inventoryA$Commercial),]$VernName)) #122 sp not linked
+
+NAtablevern <- unique(NAtable$VernName) #264 
+NAtablescfc <- unique(NAtable$ScientificName) #122
+
+filter(inventoryA, Commercial =="1") #177 ind
+filter(inventoryA, Commercial =="2") #1267 ind
+comerc <- filter(inventoryA, Commercial =="1"| Commercial =="2")
+all(comerc$CommercialSp == TRUE)
 ```
@@
 + HVinit= somme des valeurs de "TreeHarvestableVolume " des arbres dont "LoggingStatus" = "harvestable".
+
 ```{r}
-HarverstableConditions  
+# Il manque les scénarios dans les conditions -_-
+
 #select essences
+HarverstableConditions <- # = 1 boolean vector
   if (diversification || (!diversification && specieslax)) {
-  filter(Commercial %in% c("1", "2"))
+    inventoryA$Commercial =="1"| inventoryA$Commercial == "2" # now or maybe after we will diversify
   } else if (!diversification && !specieslax) {
-  filter(Commercial == "1")
+    Commercial == "1" # We will never diversify
   }
+
 #select diameters
-left_join(speciescriteria, by = "ScientificName") #or by VernName
-filter(DBH >= MinFD & DBH <= MaxFD)
+HarverstableConditions <- HarverstableConditions & (inventoryA$DBH >= inventoryA$MinFD & inventoryA$DBH <= inventoryA$MaxFD) # harvestable species, accord by their DBH
 
 #select spatially
-#slope
-#isolement
-#MainTrails out
+# HarverstableConditions <- HarverstableConditions & ()
+##slope
+##isolement
+##MainTrails out
+filter(inventoryB, LoggingStatus == "harvestable")#96 ind for the moment
 
-mutate(LoggingStatus = ifelse(HarverstableConditions,
+inventoryB <- inventoryA %>% 
+  mutate(LoggingStatus = ifelse(HarverstableConditions, #Under the above criteria, designate the harvestable species
                                 "harvestable", "non-harvestable")) %>% 
+  mutate(LoggingStatus = ifelse(is.na(Commercial), #The non-commercial species are non-harvestable.
+                                "non-harvestable", LoggingStatus)) %>%
+
   mutate(LoggingStatus = ifelse( 
     !diversification & 
-      specieslax & 
+      specieslax & #designate the secondarily harvestable species, because diversification only if necessary
       LoggingStatus == "harvestable" & 
@@
     "harvestable2nd", LoggingStatus)) %>%
+
   mutate(LoggingStatus = ifelse(
@@
       Commercial == "2" & 
-      DBH >= UpMinFD, 
+      DBH >= UpMinFD, #designate preferred species if the plot is species-rich.  
     "UPeco2", LoggingStatus))
 
-HVinit <- data %>%
-  filter(LoggingStatus == "harvestable") %>% 
-  sum(TreeHarvestableVolume)
+HarvestableTable <- inventoryB %>%
+  filter(LoggingStatus == "harvestable"| LoggingStatus == "UPeco2") #96 ind
+HVinit <- sum(HarvestableTable$TreeHarvestableVolume) #compute the harvestable volume in the plot for these criteria
+#all the inventory: HVinit = 2088.052 m3
+#just harvestable: HVinit = 365.3774 m3
 
@@
 ```{r}
-add_column(data, Up = NA) # Create a column to indicate Which sp is FD uped. Or create this column d'office in speciescriteria.
+add_column(data, Up = 0) # Create a column to indicate Which sp is FD uped. Or create this column d'office in speciescriteria. "0" = no uped, "1"= uped
 
@@
 mutate(Selected = ifelse(HVinit == VO & LoggingStatus == "harvestable",
-                         "1", LoggingStatus))
+                         "1", LoggingStatus))# if we have our volume, harvestable sp = selected sp
 
@@
 
-# Lancer le modèle prédictif "Rotten" de S.Schmitt pour identifier les arbres désignés ("Selected"= "1") "véritablement"creux.
+#Lancer le modèle prédictif "Rotten" de S.Schmitt pour identifier les arbres désignés ("Selected"= "1") "véritablement"creux.
+# mutate(ProbedHollowProba = ifelse(Selected == "1",otherloggingparameters$RottenModel(DBH), NULL) %>%
+# mutate(ProbedHollow = sample(c(0,1), size = 1, replace = F, prob = ProbedHollowProba)) # 1 = default tree, 0 = no visible default
 
-# Étiqueter ces arbres "1" dans une colonne "RottenModel" et dans la colonne "Defect". Passer ces "Selected"= "1" à "Selected"= "0".
+# Étiqueter ces arbres "1" dans une colonne "RottenModel". Passer ces "Selected"= "1" à "Selected"= "0".
 
-# if type != "RILdamagerotten" : LoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
-# if type = "RILdamagerotten" :
+# if (type != "RIL3fuelhollow"| (type == "manual"& fuel !="2")) : LoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
+# if (type = "RIL3fuelhollow"| (type == "manual"& fuel =="2")) :
 # pour les arbres RottenModel = "1", coder "hollowfuel" dans colonne "DeathCause"
-# Ajout des coordonnées de ces arbres au vecteur "RottenTreesPoints" et si type = "RIL3fuelrotten", au vecteur "EnergywoodTreesPoints".
+# Ajout des coordonnées de ces arbres au vecteur "RottenTreesPoints" et au vecteur "EnergywoodTreesPoints".
 # NoRottenLoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"

### 2021-06-15 R/DraftFunctions.Rmd
.ONFGuyafortaxojoin & .harvestable

@@
                               trim_ws = TRUE) %>% 
-  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T) %>% 
-  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F)
+  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T) 
+# unite(Genus, Species, col = "ScientificName", sep = "_", remove = F)
+
+SpeciesCriteria$VernName <- tolower(SpeciesCriteria$VernName)
 
@@
 data(Paracou6_2016) #data inventory in the global environment
-data("ForestZoneVolumeParametersTable") # The volume parameters data in the global environment
+data(ForestZoneVolumeParametersTable) # The volume parameters data in the global environment
 # load(system.file("extdata", "BrokenParacou6_2016.rda", package = "Maria")) # the test inventory in the global environment
-load(system.file("extdata", "ParamCrownDiameterAllometry.rda", package = "Maria"))
+data(ParamCrownDiameterAllometry)
+data(SpeciesCriteria)
 ```

### 2021-06-16 R/DESIGNATION_DRAFT.Rmd
.futurereserve

@@
 + Si type = "RIL3fuelhollow", "VO" = "objective"
-+ Sinon "VO" = "objective" + 20-30% pour compenser le bois creux désigné.
++ Sinon "VO" = "objective" * PlotArea + 20-30% pour compenser le bois creux désigné.
 
@@
 }else{
-  VO = objective + otherloggingparameters$ObjectiveBonus # to compensate for the designated hollow wood.
+  VO = (objective + (objective*((otherloggingparameters$ObjectiveBonus)/100))) * unique(inventory$PlotArea) # to compensate for the designated hollow wood.
 }
+
+(20 + (20*0.3))*6.25
+(20*6.25) + ((20*6.25)*0.3) #same
 
@@
 ```{r}
-# speciescriteriaVern <- speciescriteria %>% 
-#   select(-ScientificName)
-# 
-# speciescriteriaScientfc <- speciescriteria %>% 
-#   select(-VernName)
 
@@
 
+ConcernedRows <- which(inventoryA$ONFName == "kimboto" & (inventoryA$ScientificName == "Pradosia_cochlearia"| inventoryA$ScientificName == "Pradosia_huberi"))
+if(length(ConcernedRows) > 0){
+  inventoryA$ONFName[ConcernedRows] <- NA
+  inventoryA$Commercial[ConcernedRows] <- NA
+  inventoryA$MinFD[ConcernedRows] <- NA
+  inventoryA$UpMinFD[ConcernedRows] <- NA
+  inventoryA$MaxFD[ConcernedRows] <- NA
+}
+
 filter(inventoryA, ScientificName == "Micropholis_obscura")
 
-# Maho rouge = sauf "Lecythis_poiteaui", "Lecythis_praeclara" et "Lecythis_holcogyne" , "Lecythis_pneumatophora" et "Lecythis chartacea", "Lecythis zabucajo") 
-# Bakuman ou Balata blanc = sauf "Micropholis_melinoniana", "Micropholis_egensis",  "Micropholis_cayennensis" et "Micropholis_obscura")
+# Special cases:
+# Maho rouge = tous les Lecythis (sauf Lecythis poiteaui, Lecythis praeclara et Lecythis holcogyne , Lecythis pneumatophora et Lecythis chartacea, Lecythis zabucajo) 
+# Balata blanc = Tous les Micropholis (sauf Micropholis melinoniana, Micropholis egensis,  Micropholis cayennensis et M. obscura)
+# Kimboto = tous les Pradosia sauf Pradosia cochlearia et P. huberi
 
+# cèdre blanc = Ocotea guianensis, O. canaliculata, O. oblonga et O. argyrophylla.
+# cèdre noir = Ocotea tomentella, Ocotea schomburgkiana, O. glomerata et O. ceanothifolia.
+# Dodomissinga = Parkia decussata, P. gigantocarpa, P. nitida, P. reticulata, P. ulei et P. velutina.
+# Cèdre gris = les Lauraceae qui ne sont pas d'autres cèdres ...
 ```
@@
 + Si diversification=F & specieslax=T, étiqueter "harvestable2nd" à la place d’"harvestable", les "Commercial"= "2" dans la colonne "LoggingStatus".
-+ Étiqueter "UPeco2" à la place d’"harvestable" dans colonne "LoggingStatus", les individus "Commercial"= "2" de "DBH" > à leur "UpMinFD".
 + HVinit= somme des valeurs de "TreeHarvestableVolume " des arbres dont "LoggingStatus" = "harvestable".
@@
 ##MainTrails out
-filter(inventoryB, LoggingStatus == "harvestable")#96 ind for the moment
 
 inventoryB <- inventoryA %>% 
+  mutate(Commercial = ifelse(is.na(Commercial), "0", Commercial)) %>% #To avoid NA problems
   mutate(LoggingStatus = ifelse(HarverstableConditions, #Under the above criteria, designate the harvestable species
                                 "harvestable", "non-harvestable")) %>% 
-  mutate(LoggingStatus = ifelse(is.na(Commercial), #The non-commercial species are non-harvestable.
+  mutate(LoggingStatus = ifelse(Commercial == "0", #The non-commercial species are non-harvestable.
                                 "non-harvestable", LoggingStatus)) %>%
@@
       Commercial == "2",
-    "harvestable2nd", LoggingStatus)) %>%
-
-  mutate(LoggingStatus = ifelse(
-    LoggingStatus == "harvestable" &
-      Commercial == "2" & 
-      DBH >= UpMinFD, #designate preferred species if the plot is species-rich.  
-    "UPeco2", LoggingStatus))
+    "harvestable2nd", LoggingStatus))
 
 HarvestableTable <- inventoryB %>%
-  filter(LoggingStatus == "harvestable"| LoggingStatus == "UPeco2") #96 ind
+  filter(LoggingStatus == "harvestable") #96 ind
 HVinit <- sum(HarvestableTable$TreeHarvestableVolume) #compute the harvestable volume in the plot for these criteria
@@
 ```{r}
-add_column(data, Up = 0) # Create a column to indicate Which sp is FD uped. Or create this column d'office in speciescriteria. "0" = no uped, "1"= uped
+# if objective achieved at the first attempt
+inventoryC <- inventoryB %>% 
+  mutate(Selected = ifelse(HVinit == VO & LoggingStatus == "harvestable",
+                           "1", NA))# if we have our volume, harvestable sp = selected sp
 
-# if objective achieved at the first attempt
-mutate(Selected = ifelse(HVinit == VO & LoggingStatus == "harvestable",
-                         "1", LoggingStatus))# if we have our volume, harvestable sp = selected sp
+inventoryC <- add_column(inventoryC, Up = 0) # Create a column to indicate Which sp is FD uped.
+Or create this column d'office in speciescriteria.
+"0" = no uped, "1"= uped.
+dans speciescriteria ou inventory ?
 
-if (HVinit < VO){ 
+if (HVinit < VO){ #diversification is necessary, designate the secondary-economic-rank species too
   if (!diversification && specieslax){  
-    # LoggingStatus = "harvestable2nd" | LoggingStatus = "harvestable"
-    # Selected = "1"
-    # prendre parmi les arbres étiquetés "harvestable2nd" ou "harvestable" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVlax = VO.
-    # étiqueter ces arbres "1", dans une colonne "Selected".
+    inventoryD <- inventoryC %>%
+      mutate(Condition = ifelse(LoggingStatus == "harvestable2nd" | LoggingStatus == "harvestable", TRUE, FALSE)) %>% 
+      group_by(Condition) %>% 
+      arrange(desc(TreeHarvestableVolume)) %>% 
+      mutate(VolumeCumSum = cumsum(TreeHarvestableVolume)) %>% 
+      ungroup() %>% 
+      mutate(Selected = ifelse(Condition & VolumeCumSum <= VO, "1", NA)) %>%
+      select(-Condition)
 
-    if (HVlax < VO && objectivelax) message("Le volume exploitable (= HVlax ) est encore inférieur (de VO- HVlax) à votre volume objectif malgré la diversification que vous avez permise (sans la diversification HVinit= HVinit).
-Vous avez choisi dans ce cas de poursuivre l’exploitation avec un volume inférieur à votre objectif.")
+    HarvestableTable <- inventoryD %>% 
+      filter(Selected == "1")
+    HVlax <- sum(HarvestableTable$TreeHarvestableVolume) #49.69643 Harvestable volume, with specieslax permission
 
-    if (HVlax < VO && !objectivelax) stop("Le volume exploitable (=HVlax ) est encore inférieur (de VO- HVlax) à votre volume objectif malgré la diversification que vous avez permise (sans la diversification HVinit= HVinit).
-Par défaut ou par votre choix, la simulation s’arrête.
-Si vous souhaitez poursuivre l’exploitation malgré un volume exploitable inférieur à votre volume objectif vous disposez de l‘argument "objectivelax".")
+    if (HVlax < VO && objectivelax) message("The exploitable volume (= ",paste(HVlax),") is still lower (by ",paste(VO- HVlax),") than your objective volume despite the diversification you have allowed (without the diversification HVinit= ",paste(HVinit),").
+In this case, you have chosen to continue harvesting with a volume lower than your objective.")
 
-    if (!HVlax < VO) message("Le volume exploitable (=HVinit) est inférieur (de VO- HVinit) à votre volume objectif.
-Vous avez choisi de diversifier votre sélection d’espèces dans ce cas.
-L’exploitation s’est donc réalisée sur cette sélection diversifiée d’espèces.")
+    if (HVlax < VO && !objectivelax) stop("The harvestable volume = ",paste(HVlax),") is still lower (by ",paste(VO- HVlax),") than your objective volume despite the diversification you have allowed (without the diversification HVinit= ",paste(HVinit),").
+By default or by your choice, the simulation stops.
+If you wish to continue the exploitation in spite of an exploitable volume lower than your objective volume, you have the argument 'objectivelax'.")
+
+    if (!HVlax == VO) message("The harvestable volume (=",paste(HVinit),") was lower (by ",paste(VO- HVinit),") than your objective volume.
+You have chosen to diversify your species selection in this case.
+The exploitation was therefore carried out on this diversified selection of species.")
   }
 
-  if ((!diversification && !specieslax && objectivelax) | (diversification && objectivelax))
-    message("Le volume exploitable (=HVinit) est inférieur (de VO- HVinit) à votre volume objectif. Vous avez choisi dans ce cas de poursuivre l’exploitation sans diversifier vos essences.")
+  if (!diversification && !specieslax && objectivelax)
+    message("The harvestable volume (=",paste(HVinit),") is less (by ",paste(VO- HVinit),") than your objective volume.
+In this case you have chosen to continue logging without diversifying your species.")
+
+  if (diversification && objectivelax)
+    message("The harvestable volume (=",paste(HVinit),") is less (by ",paste(VO- HVinit),") than your objective volume. In this case you have chosen to continue logging.")
 
   if ((!specieslax & !objectivelax) | (diversification && !objectivelax)) 
-    stop("Le volume exploitable (=HVinit) est inférieur (de VO- HVinit) à votre volume objectif.
-Par défaut ou par votre choix, la simulation s’arrête.
-Si vous souhaitez poursuivre l’exploitation malgré un volume exploitable inférieur à votre volume objectif vous disposez de l‘argument "objectivelax" ou de la diversification d’essences.")
+    stop("The harvestable volume (=",paste(HVinit),") is lower (by ",paste(VO- HVinit),") than your objective volume.
+By default or by your choice, the simulation stops.
+If you wish to continue the exploitation in spite of a harvestable volume lower than your objective volume, you can use the argument 'objectivelax' or the diversification of species (if it is not already the case).")
 }
@@
 if (HVinit > VO) {
-  # rehaussement des DME des sp ECMP : étiqueter "harvestableUp" à la place d’"harvestable", dans la colonne "LoggingStatus", les individus "Commercial"= "1" dont le "DBH" est compris entre la valeur dans colonne "UpMinFD" pour leur sp, de la table speciescriteria , et le MaxFD.
-  mutate(Up = ifelse(Commercial == "1", "1", Up))# Dans la table species renseigner "1" dans la colonne "Up" les "Commercial"= "1" (pour signifier que leur DME a été réhaussé)
+
+  inventoryD <- inventoryC %>%
+    mutate(LoggingStatus = ifelse(
+      Commercial == "1" & (DBH >= UpMinFD & DBH <= MaxFD), #designate preferred individuals of first economic rank species, when the plot is species-rich.
+      "harvestableUp", LoggingStatus)) %>%
+
+    mutate(Up = ifelse(Commercial == "1", "1", Up))# to inform that the "1" ranks have been FD upgraded. Pas mieux de le faire à l'sp?
   # test "Commercial"= "1" pour les "harvestableUp"
@@
   if (!diversification) {
-    # HVupCommercial1 = sum(TreeHarvestableVolume) des LoggingStatus == harvestableUp.
+    HarvestableTable <- inventoryD %>%
+      filter(LoggingStatus == "harvestableUp")
+
+    HVupCommercial1 <- sum(HarvestableTable$TreeHarvestableVolume) #82.42823. compute the harvestable volume with upgraded FD individuals
+
     if (HVupCommercial1 == VO){
-      # Selected = "1" # étiqueter ces arbres "1", dans une colonne "Selected".
-      message("Le volume exploitable (=HVinit) étant supérieur (de VO- HVinit) au volume objectif, les DME des ECMP ont été rehaussés. Le volume objectif est maintenant atteint.")
+
+      inventoryE <- inventoryD %>%
+        mutate(Selected = ifelse(HVupCommercial1 == VO & LoggingStatus == "harvestableUp", "1", NA))# if harvestableUp individuals are sufficient to have our volume, harvestableUp ind = selected ind
+
+      message("As the harvestable volume (=",paste(HVinit),") was higher (by ",paste(VO- HVinit),") than the objective volume, the Minimum Falling Diameter (MinFD) of 1st economic rank species were increased.
+The objective volume has now been reached.")
     }
@@
     if (HVupCommercial1 > VO){
-      # prendre parmi les arbres étiquetés "harvestableUp" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVupCommercial1adjust= VO.
-      # Selected = "1" # étiqueter ces arbres "1", dans une colonne "Selected".
-      message("Le volume exploitable (=HVupCommercial1) est toujours supérieur (de VO- HVupCommercial1) à votre volume objectif malgré le rehaussement des DME (Volume exploitable initial = HVinit).
-Afin d’atteindre votre volume objectif, les arbres ont été choisis par ordre décroissant de volume jusqu'à l’atteinte du volume objectif.")
+      # only individuals with DBH > FD are taken, but not all because their volumes > VO
+      inventoryE<- inventoryD %>%
+        mutate(Condition = ifelse(LoggingStatus == "harvestableUp", TRUE, FALSE)) %>%
+        group_by(Condition) %>%
+        arrange(desc(TreeHarvestableVolume)) %>% 
+        mutate(VolumeCumSum = cumsum(TreeHarvestableVolume)) %>%
+        ungroup() %>%
+        mutate(Selected = ifelse(Condition & VolumeCumSum <= VO, "1", NA)) %>% 
+        select(-Condition)
+
+      HarvestableTable <- inventoryE %>%
+        filter(Selected == "1")
+      HVupCommercial1adjust <- sum(HarvestableTable$TreeHarvestableVolume) #49.69643 Harvestable volume, with "1" rank species and upgraded FD individuals only
+
+      message("The harvestable volume (=",paste(HVupCommercial1),") is always higher (by ",paste(VO- HVupCommercial1),") than your objective volume despite the increase in Minimum Falling Diameter (MinFD) (Initial harvestable volume = HVinit).
+In order to reach your objective volume, the trees were selected in decreasing order of volume until the objective volume was reached.")
     }
     if (HVupCommercial1 < VO){
-      # prendre parmi les arbres étiquetés "harvestableUp" & "harvestable" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVupCommercial1adjust = VO.
-      # Selected = "1" étiqueter ces arbres "1", dans une colonne "Selected".
-      message("Le volume exploitable (=HVinit) étant supérieur (de VO- HVinit) au volume objectif, les DME des ECMP ont été rehaussés avec une conservation de certaines tiges dont le DBH est inférieur au UpMinFD afin d’assurer l’atteinte du volume objectif.")
+
+      inventoryE<- inventoryD %>%
+        mutate(Condition = ifelse(LoggingStatus == "harvestableUp" | LoggingStatus == "harvestable", TRUE, FALSE)) %>%
+        group_by(Condition) %>%
+        arrange(desc(TreeHarvestableVolume)) %>% 
+        mutate(VolumeCumSum = cumsum(TreeHarvestableVolume)) %>%
+        ungroup() %>%
+        mutate(Selected = ifelse(Condition & VolumeCumSum <= VO, "1", NA)) %>% 
+        select(-Condition)
+
+      HarvestableTable <- inventoryE %>%
+        filter(Selected == "1")
+      HVupCommercial1adjust <- sum(HarvestableTable$TreeHarvestableVolume) #49.69643 Harvestable volume, with "1" rank species and upgraded FD individuals
+
+      message("As the harvestable volume (=",paste(HVinit),") was higher (by ",paste(VO- HVinit),") than the objective volume, the Minimum Falling Diameter (MinFD) of the 1st economic rank species were increased with retention of some stems with DBH lower than the UpMinFD to ensure that the objective volume was attained.")
     }
@@
   if (diversification) {
-    # "HVupCommercial1" = sum(TreeHarvestableVolume) des LoggingStatus == "harvestableUp" | LoggingStatus == "harvestable."
+
+    HarvestableTable <- inventoryD %>%
+      filter(LoggingStatus == "harvestableUp" | LoggingStatus == "harvestable") #the upgraded 1st rank and normal 2nd rank.
+
+    HVupCommercial1 <- sum(HarvestableTable$TreeHarvestableVolume) #173.334 m3
 
     if (HVupCommercial1 == VO){
-      # étiqueter ces arbres "1", dans une colonne "Selected".
-      message("Le volume exploitable (=HVinit) étant supérieur (de VO- HVinit) au volume objectif, les DME des ECMP ont été rehaussés.
-Le volume objectif est maintenant atteint.
-Il n’a pas été nécessaire de rehausser les DME des autres espèces économiques")
+      inventoryE <- inventoryD %>%
+        mutate(Selected = ifelse(LoggingStatus == "harvestableUp" | LoggingStatus == "harvestable",
+                                 "1", NA))# if we have our volume, harvestable ind = selected ind
+      message("As the harvestable volume (=",paste(HVinit),") was higher (by ",paste(VO- HVinit),") than the objective volume, the Minimum Falling Diameter (MinFD) of the 1st economic rank species were increased.
+The objective volume has now been reached.
+It was not necessary to increase the MinFD of the other economic species")
     }
@@
     if (HVupCommercial1 < VO){
-      # prendre parmi les arbres "Commercial"= "1" étiquetés "harvestableUp" et "harvestable" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVupCommercial1adjust = VO.
-      # Selected = "1" étiqueter ces arbres "1", dans une colonne "Selected".
-      message("Le volume exploitable (=HVinit) étant supérieur (de VO - HVinit) au volume objectif, les DME des ECMP ont été rehaussés avec une conservation de certaines tiges dont le DBH est inférieur au UpMinFD afin d’assurer l’atteinte du volume objectif.
-Il n’a pas été nécessaire de rehausser les DME des autres espèces économiques.")
+
+      inventoryE<- inventoryD %>%
+        mutate(Condition = ifelse(LoggingStatus == "harvestableUp" | LoggingStatus == "harvestable", TRUE, FALSE)) %>%
+        group_by(Condition) %>%
+        arrange(desc(TreeHarvestableVolume)) %>% 
+        mutate(VolumeCumSum = cumsum(TreeHarvestableVolume)) %>%
+        ungroup() %>%
+        mutate(Selected = ifelse(Condition & VolumeCumSum <= VO, "1", NA)) %>% 
+        select(-Condition)
+
+      HarvestableTable <- inventoryE %>%
+        filter(Selected == "1")
+      HVupCommercial1adjust <- sum(HarvestableTable$TreeHarvestableVolume) #49.69643 Harvestable volume, with "1" rank species and upgraded FD individuals, and 2nd rank no upgraded FD individuals
+
+      message("As the harvestable volume (=",paste(HVinit),") was higher (by ",paste(VO- HVinit),") than the objective volume, the Minimum Falling Diameter (MinFD) of the 1st economic rank species were increased with retention of some stems with DBH lower than the UpMinFD to ensure that the objective volume was attained.
+It was not necessary to raise the MinFDs of other economic species.")
     }
@@
     if (HVupCommercial1 > VO){
-      # rehaussement des DME des autres sp eco: étiqueter "harvestableUp" à la place d’"UPeco2", dans la colonne "LoggingStatus"
-      # Dans la table speciescriteria  renseigner "1" dans la colonne "Up" les "Commercial"= "2" (pour signifier que leur DME a été rehaussé)
-      # "HVupCommercial12" = somme des valeurs de "TreeHarvestableVolume " des "harvestableUp".
+
+      inventoryE <- inventoryD %>%
+        mutate(LoggingStatus = ifelse(LoggingStatus == "harvestable" & Commercial == "2" & DBH >= UpMinFD, #designate preferred individuals of 2nd economic rank species too, when the plot is species-rich.
+      "harvestableUp", LoggingStatus)) %>%
+
+        mutate(Up = ifelse(Commercial == "2", "1", Up))# to inform that the "2" ranks have been FD upgraded. Pas mieux de le faire à l'sp?
+      HarvestableTable <- inventoryE %>%
+        filter(LoggingStatus == "harvestableUp")
+
+      HVupCommercial12 <- sum(HarvestableTable$TreeHarvestableVolume) #271.2342 Harvestable volume, with upgraded FD individuals
+
       if (HVupCommercial12 == VO){
-        # Selected = "1" étiqueter ces arbres "1", dans la colonne "Selected".
+        inventoryF <- inventoryE %>%
+          mutate(Selected = ifelse(LoggingStatus == "harvestableUp",
+                                   "1", NA))# if we have our volume, harvestable ind = selected ind
       }
-      if (HVupCommercial12 < VO){
-        # prendre parmi les arbres étiquetés "harvestableUp" et "harvestable" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVupCommercial12adjust = VO.
-        # Selected = "1" étiqueter ces arbres "1", dans une colonne "Selected".
+      if (HVupCommercial12 != VO){
+
+        inventoryF <- inventoryE %>%
+          mutate(Condition = ifelse(LoggingStatus == "harvestableUp" | LoggingStatus == "harvestable", TRUE, FALSE)) %>%
+          group_by(Condition) %>%
+          arrange(desc(TreeHarvestableVolume)) %>%
+          mutate(VolumeCumSum = cumsum(TreeHarvestableVolume)) %>%
+          ungroup() %>%
+          mutate(Selected = ifelse(Condition & VolumeCumSum <= VO, "1", NA)) %>%
+          select(-Condition)
+
+        HarvestableTable <- inventoryF %>%
+          filter(Selected == "1")
+        HVupCommercial12adjust <- sum(HarvestableTable$TreeHarvestableVolume) #45.44885 Harvestable volume, with upgraded FD individuals
       }
 
-      if (HVupCommercial12 > VO){
-        # prendre parmi les arbres étiquetés "harvestableUp" dans "LoggingStatus", les arbres par ordre décroissant de "TreeHarvestableVolume " jusqu’à atteindre HVupCommercial12adjust = VO.
-        # Selected = "1" étiqueter ces arbres "1", dans une colonne "Selected".
-        message("Le volume exploitable (=HVinit) étant supérieur (de VO- HVinit) au volume objectif, il a été nécessaire de rehausser les DME de toutes les essences.
-Le volume objectif est maintenant atteint.")
-      }
+      message("As the harvestable volume (=",paste(HVinit),") was higher (by ",paste(VO- HVinit),") than the objective volume, it was necessary to increase the Minimum Falling Diameter (MinFD) of all species.
+The objective volume has now been reached.")
+
     }
@@
 
-#Lancer le modèle prédictif "Rotten" de S.Schmitt pour identifier les arbres désignés ("Selected"= "1") "véritablement"creux.
-# mutate(ProbedHollowProba = ifelse(Selected == "1",otherloggingparameters$RottenModel(DBH), NULL) %>%
-# mutate(ProbedHollow = sample(c(0,1), size = 1, replace = F, prob = ProbedHollowProba)) # 1 = default tree, 0 = no visible default
+# Apply S. Schmitt's "Rotten" predictive model to identify "truly" hollow designated trees.
+inventoryG <- inventoryF %>% 
+  mutate(ProbedHollowProba = ifelse(Selected == "1", otherloggingparameters$RottenModel(DBH), NULL)) %>%  #Estimates the probability of being probed hollow
 
-# Étiqueter ces arbres "1" dans une colonne "RottenModel". Passer ces "Selected"= "1" à "Selected"= "0".
+  # generate either "1" or "0" randomly for each line, depending on the proba associated with the line:
+  rowwise() %>%
+  mutate(ProbedHollow = ifelse(!is.na(ProbedHollowProba), sample(c(1,0), size = 1, replace = F, prob = c(ProbedHollowProba, 1-ProbedHollowProba)), NA)) %>%  # 1 = hollow tree, 0 = not hollow
+  mutate(ProbedHollow = factor(as.numeric(ProbedHollow))) %>% 
+  mutate(Selected = ifelse(ProbedHollow == "1", "0", Selected)) %>%  #hollow probed trees are deselected
+   #non-upgraded MinFD species:
+  mutate(Up = ifelse(is.na(Up) , "0", Up))
 
-# if (type != "RIL3fuelhollow"| (type == "manual"& fuel !="2")) : LoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
-# if (type = "RIL3fuelhollow"| (type == "manual"& fuel =="2")) :
-# pour les arbres RottenModel = "1", coder "hollowfuel" dans colonne "DeathCause"
-# Ajout des coordonnées de ces arbres au vecteur "RottenTreesPoints" et au vecteur "EnergywoodTreesPoints".
-# NoRottenLoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
-# LoggedVolume = ∑NoRottenLoggedVolume  et ⅔ du volume de ceux codés RottenModel = "1".
-# if "Up" = NA remplacer NA par "0"
+if (type != "RIL3fuelhollow"| (type == "manual"& fuel !="2"))
+  HarvestableTable <- inventoryG %>%
+  filter(Selected == "1")
+VolumewithHollowslost <- sum(HarvestableTable$TreeHarvestableVolume) #128.5047. Harvestable volume, with Hollows lost
+VO - VolumewithHollowslost #34 m3 lost: the bonus is therefore generous here (37.5 m3 of bonus).
+
+if (type == "RIL3fuelhollow"| (type == "manual"& fuel =="2")) {
+  # Hollow trees = fuelwood:
+  inventoryH <- inventoryG %>%
+    mutate(DeathCause = ifelse(ProbedHollow == "1", "hollowfuel", NA)) # remplacer NA par DeathCause dans le simulateur ONF
+
+  # Create 2 points vectors with coordinates of the probed hollow trees: "HollowTreesPoints" and "EnergywoodTreesPoints":
+HollowTreescoord <- inventoryG %>% 
+  filter(ProbedHollow == "1") %>% 
+  select(Xutm, Yutm)
+
+HollowTreesPoints  <- st_multipoint(x = as.matrix(HollowTreescoord))
+EnergywoodTreesPoints <- HollowTreesPoints
+
+}
 
@@
 ```{r}
-# Étiqueter "future", dans une colonne "LoggingStatus", sélection de tous les individus :
-# Essence : "Commercial"= "1" uniquement (qqsoit la diversification)
-# DBH : 
-# si dans la table speciescriteria  la colonne "Up" = "1" pour son sp : le DBH des individus de cette sp doit être compris entre 35 et le "UpMinFD" de son sp.
-# sinon entre 35 et le "MinFD" de son sp.
-# 
-# Sélectionner les arbres réservés (parmis les Avenirs, autant que d’arbres exploités) :
-# "stem" = nombre de "1" dans colonne "Selected" (& Rottenmodel = 0 ?)
-# Dans colonne "LoggingStatus", remplacer 1 "future"par "reserve" au hasard stem fois.
+#Future: select essence and diameters
 
+inventoryH <- inventoryG %>%
+  mutate(LoggingStatus = ifelse(Commercial == "1" &
+                                  (DBH >= otherloggingparameters$FutureTreesMinDiameter & DBH < MinFD),
+                                "future", LoggingStatus))
+
+#Reserve
+# Randomly select the reserved trees (among the futures, as many as the number of trees exploited):
+
+StemNbr <- sum(as.numeric(inventoryH$Selected == "1"), na.rm = TRUE)#29 selected ind 
+ReserveRows <- sample(which(inventoryH$LoggingStatus == "future"), size = StemNbr, replace = F)
+
+inventoryH$LoggingStatus[ReserveRows] <-"reserve"
+
+```
+
+# Fin treeselection function
+```{r}
 # Créer un vecteur ("HarvestableTreesPoints") de points de coordonnées des arbres LoggingStatus = "harvestable" ou "harvestableUp" ou "harvestable2nd".
@@
 # Créer un vecteur ("ReserveTreesPoints") de points de coordonnées des arbres LoggingStatus = "reserve".
-# Si diversification = F & specieslax = T & HVinit< VO LoggingStatus = "harvestable2nd"inchangé
-# sinon LoggingStatus = "harvestable2nd" devient LoggingStatus = "NA".
-# Si pour Commercial = "2" Up = "0" remplacer "UPeco2" par "NA" dans LoggingStatus.
+
+#where specieslax was not necessary, consider eco2s as non-exploitable:
+inventoryI <- inventoryH %>% 
+  mutate(LoggingStatus = ifelse(HVinit > VO & LoggingStatus == "harvestable2nd", "non-harvestable", LoggingStatus))
+
+unique(inventoryI$LoggingStatus)
+
+write.csv2(inventoryI, "D:/VSC Kourou/DATA/PostDesignationInventory.csv")
 

### 2021-06-16 R/DESIGNATION_DRAFT.Rmd
.selected

@@
 + Si type = "RIL3fuelhollow", "VO" = "objective"
-+ Sinon "VO" = "objective" * PlotArea + 20-30% pour compenser le bois creux désigné.
++ Sinon "VO" = "objective" + 20-30% pour compenser le bois creux désigné.
 
@@
 }else{
-  VO = (objective + (objective*((otherloggingparameters$ObjectiveBonus)/100))) * unique(inventory$PlotArea) # to compensate for the designated hollow wood.
+  VO = objective + otherloggingparameters$ObjectiveBonus # to compensate for the designated hollow wood.
 }
-
-(20 + (20*0.3))*6.25
-(20*6.25) + ((20*6.25)*0.3) #same
 
@@
 ```{r}
+# speciescriteriaVern <- speciescriteria %>% 
+#   select(-ScientificName)
+# 
+# speciescriteriaScientfc <- speciescriteria %>% 
+#   select(-VernName)
 
@@
 
-ConcernedRows <- which(inventoryA$ONFName == "kimboto" & (inventoryA$ScientificName == "Pradosia_cochlearia"| inventoryA$ScientificName == "Pradosia_huberi"))
-if(length(ConcernedRows) > 0){
-  inventoryA$ONFName[ConcernedRows] <- NA
-  inventoryA$Commercial[ConcernedRows] <- NA
-  inventoryA$MinFD[ConcernedRows] <- NA
-  inventoryA$UpMinFD[ConcernedRows] <- NA
-  inventoryA$MaxFD[ConcernedRows] <- NA
-}
-
 filter(inventoryA, ScientificName == "Micropholis_obscura")
 
-# Special cases:
-# Maho rouge = tous les Lecythis (sauf Lecythis poiteaui, Lecythis praeclara et Lecythis holcogyne , Lecythis pneumatophora et Lecythis chartacea, Lecythis zabucajo) 
-# Balata blanc = Tous les Micropholis (sauf Micropholis melinoniana, Micropholis egensis,  Micropholis cayennensis et M. obscura)
-# Kimboto = tous les Pradosia sauf Pradosia cochlearia et P. huberi
+# Maho rouge = sauf "Lecythis_poiteaui", "Lecythis_praeclara" et "Lecythis_holcogyne" , "Lecythis_pneumatophora" et "Lecythis chartacea", "Lecythis zabucajo") 
+# Bakuman ou Balata blanc = sauf "Micropholis_melinoniana", "Micropholis_egensis",  "Micropholis_cayennensis" et "Micropholis_obscura")
 
-# cèdre blanc = Ocotea guianensis, O. canaliculata, O. oblonga et O. argyrophylla.
-# cèdre noir = Ocotea tomentella, Ocotea schomburgkiana, O. glomerata et O. ceanothifolia.
-# Dodomissinga = Parkia decussata, P. gigantocarpa, P. nitida, P. reticulata, P. ulei et P. velutina.
-# Cèdre gris = les Lauraceae qui ne sont pas d'autres cèdres ...
 ```
@@
 + Si diversification=F & specieslax=T, étiqueter "harvestable2nd" à la place d’"harvestable", les "Commercial"= "2" dans la colonne "LoggingStatus".
++ Étiqueter "UPeco2" à la place d’"harvestable" dans colonne "LoggingStatus", les individus "Commercial"= "2" de "DBH" > à leur "UpMinFD".
 + HVinit= somme des valeurs de "TreeHarvestableVolume " des arbres dont "LoggingStatus" = "harvestable".
@@
 inventoryB <- inventoryA %>% 
-  mutate(Commercial = ifelse(is.na(Commercial), "0", Commercial)) %>% #To avoid NA problems
   mutate(LoggingStatus = ifelse(HarverstableConditions, #Under the above criteria, designate the harvestable species
                                 "harvestable", "non-harvestable")) %>% 
-  mutate(LoggingStatus = ifelse(Commercial == "0", #The non-commercial species are non-harvestable.
+  mutate(LoggingStatus = ifelse(is.na(Commercial), #The non-commercial species are non-harvestable.
                                 "non-harvestable", LoggingStatus)) %>%
@@
       Commercial == "2",
-    "harvestable2nd", LoggingStatus))
+    "harvestable2nd", LoggingStatus)) %>%
+
+  mutate(LoggingStatus = ifelse(
+    LoggingStatus == "harvestable" &
+      Commercial == "2" & 
+      DBH >= UpMinFD, #designate preferred species if the plot is species-rich.  
+    "UPeco2", LoggingStatus))
 
 HarvestableTable <- inventoryB %>%
-  filter(LoggingStatus == "harvestable") #96 ind
+  filter(LoggingStatus == "harvestable"| LoggingStatus == "UPeco2") #96 ind
 HVinit <- sum(HarvestableTable$TreeHarvestableVolume) #compute the harvestable volume in the plot for these criteria
@@
 ```{r}
+inventoryC <- add_column(inventoryC, Up = 0) # Create a column to indicate Which sp is FD uped.
+Or create this column d'office in speciescriteria.
+"0" = no uped, "1"= uped.
+dans speciescriteria ou inventory ?
+
 # if objective achieved at the first attempt
@@
                            "1", NA))# if we have our volume, harvestable sp = selected sp
-
-inventoryC <- add_column(inventoryC, Up = 0) # Create a column to indicate Which sp is FD uped.
-Or create this column d'office in speciescriteria.
-"0" = no uped, "1"= uped.
-dans speciescriteria ou inventory ?
 
@@
       inventoryE <- inventoryD %>%
-        mutate(LoggingStatus = ifelse(LoggingStatus == "harvestable" & Commercial == "2" & DBH >= UpMinFD, #designate preferred individuals of 2nd economic rank species too, when the plot is species-rich.
+    mutate(LoggingStatus = ifelse(LoggingStatus == "UPeco2", #designate preferred individuals of 2nd economic rank species too, when the plot is species-rich.
       "harvestableUp", LoggingStatus)) %>%
@@
 
-# Apply S. Schmitt's "Rotten" predictive model to identify "truly" hollow designated trees.
-inventoryG <- inventoryF %>% 
-  mutate(ProbedHollowProba = ifelse(Selected == "1", otherloggingparameters$RottenModel(DBH), NULL)) %>%  #Estimates the probability of being probed hollow
+#Lancer le modèle prédictif "Rotten" de S.Schmitt pour identifier les arbres désignés ("Selected"= "1") "véritablement"creux.
+# mutate(ProbedHollowProba = ifelse(Selected == "1",otherloggingparameters$RottenModel(DBH), NULL) %>%
+# mutate(ProbedHollow = sample(c(0,1), size = 1, replace = F, prob = ProbedHollowProba)) # 1 = default tree, 0 = no visible default
 
-  # generate either "1" or "0" randomly for each line, depending on the proba associated with the line:
-  rowwise() %>%
-  mutate(ProbedHollow = ifelse(!is.na(ProbedHollowProba), sample(c(1,0), size = 1, replace = F, prob = c(ProbedHollowProba, 1-ProbedHollowProba)), NA)) %>%  # 1 = hollow tree, 0 = not hollow
-  mutate(ProbedHollow = factor(as.numeric(ProbedHollow))) %>% 
-  mutate(Selected = ifelse(ProbedHollow == "1", "0", Selected)) %>%  #hollow probed trees are deselected
-   #non-upgraded MinFD species:
-  mutate(Up = ifelse(is.na(Up) , "0", Up))
+# Étiqueter ces arbres "1" dans une colonne "RottenModel". Passer ces "Selected"= "1" à "Selected"= "0".
 
-if (type != "RIL3fuelhollow"| (type == "manual"& fuel !="2"))
-  HarvestableTable <- inventoryG %>%
-  filter(Selected == "1")
-VolumewithHollowslost <- sum(HarvestableTable$TreeHarvestableVolume) #128.5047. Harvestable volume, with Hollows lost
-VO - VolumewithHollowslost #34 m3 lost: the bonus is therefore generous here (37.5 m3 of bonus).
-
-if (type == "RIL3fuelhollow"| (type == "manual"& fuel =="2")) {
-  # Hollow trees = fuelwood:
-  inventoryH <- inventoryG %>%
-    mutate(DeathCause = ifelse(ProbedHollow == "1", "hollowfuel", NA)) # remplacer NA par DeathCause dans le simulateur ONF
-
-  # Create 2 points vectors with coordinates of the probed hollow trees: "HollowTreesPoints" and "EnergywoodTreesPoints":
-HollowTreescoord <- inventoryG %>% 
-  filter(ProbedHollow == "1") %>% 
-  select(Xutm, Yutm)
-
-HollowTreesPoints  <- st_multipoint(x = as.matrix(HollowTreescoord))
-EnergywoodTreesPoints <- HollowTreesPoints
-
-}
+# if (type != "RIL3fuelhollow"| (type == "manual"& fuel !="2")) : LoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
+# if (type = "RIL3fuelhollow"| (type == "manual"& fuel =="2")) :
+# pour les arbres RottenModel = "1", coder "hollowfuel" dans colonne "DeathCause"
+# Ajout des coordonnées de ces arbres au vecteur "RottenTreesPoints" et au vecteur "EnergywoodTreesPoints".
+# NoRottenLoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
+# LoggedVolume = ∑NoRottenLoggedVolume  et ⅔ du volume de ceux codés RottenModel = "1".
+# if "Up" = NA remplacer NA par "0"
 
@@
 ```{r}
-#Future: select essence and diameters
+# Étiqueter "future", dans une colonne "LoggingStatus", sélection de tous les individus :
+# Essence : "Commercial"= "1" uniquement (qqsoit la diversification)
+# DBH : 
+# si dans la table speciescriteria  la colonne "Up" = "1" pour son sp : le DBH des individus de cette sp doit être compris entre 35 et le "UpMinFD" de son sp.
+# sinon entre 35 et le "MinFD" de son sp.
+# 
+# Sélectionner les arbres réservés (parmis les Avenirs, autant que d’arbres exploités) :
+# "stem" = nombre de "1" dans colonne "Selected" (& Rottenmodel = 0 ?)
+# Dans colonne "LoggingStatus", remplacer 1 "future"par "reserve" au hasard stem fois.
 
-inventoryH <- inventoryG %>%
-  mutate(LoggingStatus = ifelse(Commercial == "1" &
-                                  (DBH >= otherloggingparameters$FutureTreesMinDiameter & DBH < MinFD),
-                                "future", LoggingStatus))
-
-#Reserve
-# Randomly select the reserved trees (among the futures, as many as the number of trees exploited):
-
-StemNbr <- sum(as.numeric(inventoryH$Selected == "1"), na.rm = TRUE)#29 selected ind 
-ReserveRows <- sample(which(inventoryH$LoggingStatus == "future"), size = StemNbr, replace = F)
-
-inventoryH$LoggingStatus[ReserveRows] <-"reserve"
-
-```
-
-# Fin treeselection function
-```{r}
 # Créer un vecteur ("HarvestableTreesPoints") de points de coordonnées des arbres LoggingStatus = "harvestable" ou "harvestableUp" ou "harvestable2nd".
@@
 # Créer un vecteur ("ReserveTreesPoints") de points de coordonnées des arbres LoggingStatus = "reserve".
-
-#where specieslax was not necessary, consider eco2s as non-exploitable:
-inventoryI <- inventoryH %>% 
-  mutate(LoggingStatus = ifelse(HVinit > VO & LoggingStatus == "harvestable2nd", "non-harvestable", LoggingStatus))
-
-unique(inventoryI$LoggingStatus)
-
-write.csv2(inventoryI, "D:/VSC Kourou/DATA/PostDesignationInventory.csv")
+# Si diversification = F & specieslax = T & HVinit< VO LoggingStatus = "harvestable2nd"inchangé
+# sinon LoggingStatus = "harvestable2nd" devient LoggingStatus = "NA".
+# Si pour Commercial = "2" Up = "0" remplacer "UPeco2" par "NA" dans LoggingStatus.
 

### 2021-06-16 R/.harvestable.R

@@ -1,9 +1,6 @@
 #' .harvestable
 #'
-#' @param inventory (data.frame)  speciescriteria (data.frame)
-#' @param type "RIL1", "RIL2broken", "RIL2", "RIL3", "RIL3fuel", "RIL3fuelhollow" or "manual"(character)
-#' @param objective (numeric)  diversificationparam specieslaxparam objectivelax
-#' @param otherloggingparameters (list) MainTrail (multiline)
+#' @param inventory (data.frame) type "RIL1", "RIL2broken", "RIL2", "RIL3", "RIL3fuel", "RIL3fuelhollow" or "manual"(character)
 #'
 #' @return
 #' @export
@@ -12,15 +9,9 @@
 #'
 .harvestable <- function(
   inventory,
-  # speciescriteria = SpeciesCriteria,
-  type = c("RIL1", "RIL2broken", "RIL2", "RIL3", "RIL3fuel", "RIL3fuelhollow", "manual"),
-  objective,
-  # diversification,
-  # specieslax = FALSE,
-  # objectivelax = FALSE,
-  otherloggingparameters = loggingparameters()
-  # MainTrail
-
+  # type = c("RIL1", "RIL2broken", "RIL2", "RIL3", "RIL3fuel", "RIL3fuelhollow", "manual"),
+  diversification,
+  specieslax = FALSE,
 ){
   # Il manque les scénarios dans les conditions -_-
 
@@ -40,7 +31,6 @@
   ##slope
   ##isolement
   ##MainTrails out
-  filter(inventoryB, LoggingStatus == "harvestable")#96 ind for the moment
 
   inventoryB <- inventoryA %>%
     mutate(LoggingStatus = ifelse(HarverstableConditions, #Under the above criteria, designate the harvestable species
@@ -58,13 +48,11 @@
     mutate(LoggingStatus = ifelse(
       LoggingStatus == "harvestable" &
         Commercial == "2" &
-        DBH >= UpMinFD, #designate preferred species if the plot is species-rich.
+        DBH >= UpMinFD, #designate preferred species of 2nd rank if the plot is species-rich.
       "UPeco2", LoggingStatus))
 
   HarvestableTable <- inventoryB %>%
-    filter(LoggingStatus == "harvestable"| LoggingStatus == "UPeco2") #96 ind
+    filter(LoggingStatus == "harvestable"| LoggingStatus == "UPeco2")
[…]

### 2021-06-18 R/DESIGNATION_DRAFT.Rmd
.ONFGuyafortaxojoin

--- 2021-06-16 R/DESIGNATION_DRAFT.Rmd
@@
 
-NAtable <- inventoryA[is.na(inventoryA$Commercial),] #2101 ind not linked
-NAtablescfc <- as.data.frame(unique(inventoryA[is.na(inventoryA$Commercial),]$ScientificName)) #264 sp not linked
-NAtablevern <- as.data.frame(unique(inventoryA[is.na(inventoryA$Commercial),]$VernName)) #122 sp not linked
+NAtable <- inventoryA[is.na(inventoryA$Commercial),] #2151 ind not linked
+NAtablescfc <- as.data.frame(unique(inventoryA[is.na(inventoryA$Commercial),]$ScientificName)) #270 sp not linked
+NAtablevern <- as.data.frame(unique(inventoryA[is.na(inventoryA$Commercial),]$VernName)) #126 sp not linked
 
-NAtablevern <- unique(NAtable$VernName) #264 
-NAtablescfc <- unique(NAtable$ScientificName) #122
+NAtablevern <- unique(NAtable$VernName) #126 
+NAtablescfc <- unique(NAtable$ScientificName) #270
 
 filter(inventoryA, Commercial =="1") #177 ind
-filter(inventoryA, Commercial =="2") #1267 ind
-comerc <- filter(inventoryA, Commercial =="1"| Commercial =="2")
-all(comerc$CommercialSp == TRUE)
+filter(inventoryA, Commercial =="2") #1211 ind
+comerc <- filter(inventoryA, Commercial =="1"| Commercial =="2")#1388
+all(comerc$CommercialSp == TRUE)#FALSE
 ```

### 2021-06-18 R/DESIGNATION_DRAFT.Rmd

@@
 ```{r}
+
 # if objective achieved at the first attempt
@@
       inventoryE <- inventoryD %>%
+
     mutate(Selected = ifelse(LoggingStatus == "harvestableUp" | LoggingStatus == "harvestable",
@@
         mutate(Up = ifelse(Commercial == "2", "1", Up))# to inform that the "2" ranks have been FD upgraded. Pas mieux de le faire à l'sp?
+
       HarvestableTable <- inventoryE %>%
@@
                                    "1", NA))# if we have our volume, harvestable ind = selected ind
+
       }

### 2021-06-22 R/treeselection.R
dispatch the internes functions (of treeselection) in different files. Versioning update

@@ -12,7 +12,12 @@
 #' @export
 #'
 #' @examples
+#' inventory = addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))
 #'
+#'treeselection(inventory, SpeciesCriteria,
+#'type ="manual", fuel = "0",objective = 20, diversification = TRUE, specieslax = FALSE,
+#'objectivelax = FALSE, otherloggingparameters = loggingparameters(), MainTrail)
+
 treeselection <- function(
   inventory,
   speciescriteria = SpeciesCriteria,
@@ -25,25 +30,35 @@ treeselection <- function(
   otherloggingparameters = loggingparameters()
   # MainTrail
 
-){
+){ # @include .ONFGuyafortaxojoin, .harvestable, .selected, .futurereserve functions
 
   if ("DeathCause" %in% names(inventory)) filter(inventory, is.null(DeathCause)) #select only still alived trees (after MainTrails) NULL ou NA
 
   inventory <- inventory %>%
-  # Visible defect trees detection:
-  # mutate(VisibleDefectProba = otherloggingparameters$VisiblyRottenModel(DBH)) %>%
-  # mutate(VisibleDefect = sample(c(0,1), size = 1, replace = F, prob = VisibleDefectProba)) # 1 = default tree, 0 = no visible default (là ma fct ne sait pas qd elle doit mettre 0 ou 1)
+    # Visible defect trees detection:
+    # mutate(VisibleDefectProba = otherloggingparameters$VisiblyRottenModel(DBH)) %>%
+    # mutate(VisibleDefect = sample(c(0,1), size = 1, replace = F, prob = VisibleDefectProba)) # 1 = default tree, 0 = no visible default (là ma fct ne sait pas qd elle doit mettre 0 ou 1)
 
-  # filter(VisibleDefect == "0") %>%
+    # filter(VisibleDefect == "0") %>%
 
-  # Compute the objective volume with or without bonus:
-  if (type == "RIL3fuelhollow"| (type == "manual"& fuel =="2")) {VO = objective
-  }else{
-    VO = objective + otherloggingparameters$ObjectiveBonus # to compensate for the designated hollow wood.
-    left_join(inventory, speciescriteria, by = "ScientificName") #or by VernName
+    # Compute the objective volume with or without bonus:
+    if (type == "RIL3fuelhollow"| (type == "manual"& fuel =="2")) {VO = objective
+    }else{
[…]

### 2021-06-22 R/TreeFelling_Draft.Rmd
ONFGuyafortaxojoin & harvestable test units

---
title: "TreeFelling_Draft"
author: "Vincyane Badouard"
date: "24/06/2021"
output: html_document
---

# Les arguments

inventory
multilignes "MainTrail ", "2ndTrail"
vecteur "AccessibleTreesPoints", "SelectedTreesPoints",  "AvenirTreesPoints",  "ReserveTreesPoints", "DeadTreesPoints", "HollowTreesPoints" et "FuelwoodTreesPoints"

# OUTPUT : 
inventory + polygone "Shadow" + vecteurs "TreefallSuccess", "TreefallFailure", "DamageTreesPoints", "DeadTreesPoints"

```{r Give values to the arguments to work}

# inventory = scndtrailsopening(treeselection(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))) #3539 rows (Paracou: 3620 rows)
speciescriteria = SpeciesCriteria
type = "manual"
fuel = "0"
objective = 20
diversification = TRUE
specieslax = FALSE
objectivelax = FALSE
otherloggingparameters = loggingparameters()
# MainTrail

```

# Succès-échec
```{r}

if (type == "RIL2broken" | type == "RIL2" | type == "RIL3"){
  Inventory <- Inventory %>% 
    mutate(TreeFellingOrientationSuccess = ifelse(Accessible == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Accessible = linked by 2ndtrails
  #Tree coordinates  
  TreefallSuccessCoord <- inventory %>% 
    filter(TreeFellingOrientationSuccess == "1") %>% 
    select(Xutm, Yutm)
  TreefallFailCoord <- inventory %>% 
    filter(TreeFellingOrientationSuccess == "0") %>% 
    select(Xutm, Yutm)

  TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
  TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails

}

if (type == "RIL3fuel" | (type == "manual"& fuel =="1")) {

  Inventory <- Inventory %>% 
    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
  #Tree coordinates  
  TreefallSuccessCoord <- inventory %>% 
    filter(TreeFellingOrientationSuccess == "1") %>% 
    select(Xutm, Yutm)
  TreefallFailCoord <- inventory %>% 
    filter(TreeFellingOrientationSuccess == "0") %>% 
    select(Xutm, Yutm)

  TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
  TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails

}

# Abattre les creux : 
if (type == "RIL3fuelhollow"  | (type == "manual"& fuel =="2")) {

  Inventory <- Inventory %>% 
    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1"| ProbbedHollow == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
  #Tree coordinates  
  TreefallSuccessCoord <- inventory %>% 
    filter(TreeFellingOrientationSuccess == "1") %>% 
    select(Xutm, Yutm)
  TreefallFailCoord <- inventory %>% 
    filter(TreeFellingOrientationSuccess == "0") %>% 
    select(Xutm, Yutm)

  TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
  TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails
}

```

```{r}
# ex:
outer = matrix(c(0,0,10,0,10,10,0,10,0,0),ncol=2, byrow=TRUE)
hole1 = matrix(c(1,1,1,2,2,2,2,1,1,1),ncol=2, byrow=TRUE)
hole2 = matrix(c(5,5,5,6,6,6,6,5,5,5),ncol=2, byrow=TRUE)
pts = list(outer, hole1, hole2)
(pl1 = st_polygon(pts))
plot(pl1)

pts3 = lapply(pts, function(x) cbind(x, 0))
(pl2 = st_polygon(pts3))
(pl3 = st_polygon(pts3, "XYM"))
plot(pl2)
plot(pl3)

pts4 = lapply(pts3, function(x) cbind(x, 0))
(pl4 = st_polygon(pts4))
plot(pl4)

pol1 = list(outer, hole1, hole2) #1 list/polygon :  list with numeric matrices with points in rows
pol2 = list(outer + 12, hole1 + 12)
pol3 = list(outer + 24)
mp = list(pol1,pol2,pol3) #list of lists with numeric matrices
(mp1 = st_multipolygon(mp))
plot(mp1)

pts3 = lapply(mp, function(x) lapply(x, function(y) cbind(y, 0)))
(mp2 = st_multipolygon(pts3))
(mp3 = st_multipolygon(pts3, "XYM"))
plot(mp2)
plot(mp3)

pts4 = lapply(mp2, function(x) lapply(x, function(y) cbind(y, 0)))
(mp4 = st_multipolygon(pts4))
plot(mp4)

library(nngeo)
dat = data.frame(
  x = c(1, 1, -1, 3, 3), #centroid locations
  y = c(0, -3, 2, -2, 0), #centroid locations
  ex = c(0.5, 2, 2, 0.3, 0.6), #Size along x-axis
  ey = c(0.5, 0.2, 1, 1, 0.3), #Size along y-axis,
  stringsAsFactors = FALSE
)
dat = st_as_sf(dat, coords = c("x", "y")) #centroids
dat

# Calculate ellipses
el = st_ellipse(pnt = dat, ex = dat$ex, ey = dat$ey)

# Plot 2
plot(el, graticule = TRUE, axes = TRUE)

dat = data.frame(
  x = c(1, 2), #centroid locations
  y = c(0, -3), #centroid locations
  ex = c(0.5, 2), #Size along x-axis
  ey = c(0.5, 0.2), #Size along y-axis,
  stringsAsFactors = FALSE
)
dat = st_as_sf(dat, coords = c("x", "y")) #centroids
dat

# Calculate ellipses
el = st_ellipse(pnt = dat, ex = dat$ex, ey = dat$ey)

# Plot 2
plot(el, graticule = TRUE, axes = TRUE)

```

# Abattages selon le type d’EFI
```{r}

if (type == "RIL1" | directionalfelling == "0"){
  Coord = matrix(c(0,0,10,0,10,10,0,10,0,0),ncol=2, byrow=TRUE)
  pol1 = list() #1 list/polygon :  list with numeric matrices with points in rows
  pol2 = list()
  pol3 = list()
  mp = list(pol1,pol2,pol3) #list of lists with numeric matrices
  (mp1 = st_multipolygon(mp))
  plot(mp1)

  Shadows <- st_multipolygon()
} 
# créer un polygone par arbre ("Shadow"):
# origine = coordonnées de l’arbre (vecteurs "AccessibleTreesPoints")
# sommet = 1 point au hasard
# longueur = hauteur de l’arbre TreeHeight
# largeur = DBH
# hauteur de l’ellipse CrownHeight
# diamètre de l’ellipse CrownDiameter

if (type == "RIL2broken" | type == "RIL2" | directionalfelling == "1") {

}
# créer un polygone par arbre ("Shadow"):
# Réussite à 60% :
# origine = coordonnées de l’arbre (vecteurs "TreefallSuccess")
# longueur = hauteur de l’arbre
# largeur = DBH
# hauteur de l’ellipse
# diamètre de l’ellipse
# orientation = base du tronc vers la voie la plus proche (MainTrail ou 2ndTrail)
# Éviter à  100% les arbres "reserve" (vecteur "ReserveTreesPoints") et essayer d’éviter les arbres "future" (vecteur "AvenirTreesPoints")
# Echec à 40% :
# origine = coordonnées de l’arbre (vecteurs "TreefallFailure")
# sommet = 1 point au hasard
# longueur = hauteur de l’arbre
# largeur = DBH
# hauteur de l’ellipse
# diamètre de l’ellipse

if (type == "RIL3" | directionalfelling == "2") {

}
# créer un polygone par arbre ("Shadow"):
# Echec à 40% :
# origine = coordonnées de l’arbre (vecteurs "TreefallFailure")
# sommet = 1 point au hasard
# longueur = hauteur de l’arbre
# largeur = DBH
# hauteur de l’ellipse
# diamètre de l’ellipse
# Réussite à 60% :
# origine = coordonnées de l’arbre (vecteurs "TreefallSuccess")
# longueur = hauteur de l’arbre
# largeur = DBH
# hauteur de l’ellipse
# diamètre de l’ellipse
# orientation = 30-45◦, base du tronc vers la voie la plus proche (MainTrail ou 2ndTrail) MinTreefallOrientation MaxTreefallOrientation
# Éviter à  100% les arbres "reserve" (vecteur "ReserveTreesPoints") et essayer d’éviter les arbres "future" (vecteur "AvenirTreesPoints")

if (type == "RIL3fuel" | type == "RIL3fuelhollow"  | (type == "manual"& (fuel =="1" |fuel =="2"))) {

}
# créer un polygone par arbre ("Shadow"):
# Echec à 40% :
# origine = coordonnées de l’arbre (vecteurs "TreefallFailure")
# sommet = 1 point au hasard
# longueur = hauteur de l’arbre
# largeur = DBH
# hauteur de l’ellipse
# diamètre de l’ellipse
# Réussite à 60% :
# origine = coordonnées de l’arbre (vecteurs "TreefallSuccess")
# longueur = hauteur de l’arbre
# largeur = DBH
# hauteur de l’ellipse
# diamètre de l’ellipse
# orientation = 30-45◦,
# if (piste la plus proche (MainTrail ou 2ndTrail) à ⩽ 6 m de l’arbre & ⩽ 20% de l’entrée de la parcelle (= contact piste/bord parcelle) jusqu’à max 6 m de l’arbre (buffergrappin)  ("piste à grappin" ?)) : houppier vers cette piste.
# Sinon : pied vers piste la plus proche (MainTrail ou 2ndTrail)
# Éviter à  100% les arbres "reserve" (vecteur "ReserveTreesPoints") et essayer d’éviter les arbres "future" (vecteur "AvenirTreesPoints")

```

# Renseigner les arbres abattus :
inventory : Pour les arbres pour lesquels un Shadow a été créé :
renseigner "1" dans une colonne "Cutted".
if ProbedHollow = "0" : renseigner "cutted" if encore "NA"  dans la colonne "DeathCause".
if ProbedHollow = "1" renseigner "woodfuel" if encore "NA"  dans la colonne "DeathCause".
```{r}

# inventory <- inventory %>%

# mutate(Cutted = ifelse(,"1",) %>% # a shadow = tree cutted

# mutate(DeathCause = ifelse(is.na(DeathCause) & ProbedHollow == "0","cutted", DeathCause) %>% #BO
#          
# mutate(DeathCause = ifelse(is.na(DeathCause) & ProbedHollow == "1","woodfuel", DeathCause) #BE

```

# chablismortality
Fonction de mortalité chablis ("chablismortality"): élimination des arbres chablis 2ndaires de l’arbre abattu =  faire mourir les arbres de coordonnées appartenant aux polygones "Shadow" :
+ Ajouter les coordonnées de ces arbres au vecteur "DamageTreesPoints" et au vecteur "DeadTreesPoints".
+ inventory : Pour ces arbres, renseigner "treefall2nd" ifencore "NA"  dans la colonne "DeathCause".
+ leur faire des Shadow aussi : créer un polygone par arbre ("Shadow"):
origine = coordonnées de l’arbre (vecteurs "DamageTreesPoints")
orientation = même direction/sens que son abatteur 
longueur = hauteur de l’arbre
largeur = DBH
hauteur de l’ellipse
diamètre de l’ellipse
```{r}

# Ajouter les coordonnées de ces arbres au vecteur "DamageTreesPoints" et au vecteur "DeadTreesPoints".

# inventory : Pour ces arbres, renseigner "treefall2nd" ifencore "NA"  dans la colonne "DeathCause".

# leur faire des Shadow aussi : créer un polygone par arbre ("Shadow"):
# origine = coordonnées de l’arbre (vecteurs "DamageTreesPoints")
# orientation = même direction/sens que son abatteur 
# longueur = hauteur de l’arbre
# largeur = DBH
# hauteur de l’ellipse
# diamètre de l’ellipse

```

### 2021-07-06 R/DESIGNATION_DRAFT.Rmd

@@
 
-# Joindre les taxonomies ONF/Guyafor (.ONFGuyafortaxojoin)
+# Joindre les taxonomies ONF/Guyafor (ONFGuyafortaxojoin)
 ```{r}
@@
 # Créer un vecteur ("HarvestableTreesPoints") de points de coordonnées des arbres LoggingStatus = "harvestable" ou "harvestableUp" ou "harvestable2nd".
+HarvestableTreescoord <- inventory %>%
+      filter(LoggingStatus == "harvestable" |LoggingStatus == "harvestableUp" |LoggingStatus == "harvestable2nd") %>%
+      select(Xutm, Yutm)
+
+HarvestableTreesPoints  <- st_multipoint(x = as.matrix(HarvestableTreescoord))
+
 # Créer un vecteur ("SelectedTreesPoints") de points de coordonnées des arbres Selected = 1.
+SelectedTreescoord <- inventory %>%
+      filter(Selected == "1") %>%
+      select(Xutm, Yutm)
+
+SelectedTreesPoints  <- st_multipoint(x = as.matrix(SelectedTreescoord))
+
 # Créer un vecteur ("FutureTreesPoints") de points de coordonnées des arbres LoggingStatus = "future"
+FutureTreescoord <- inventory %>%
+      filter(LoggingStatus == "future") %>%
+      select(Xutm, Yutm)
+
+FutureTreesPoints  <- st_multipoint(x = as.matrix(FutureTreescoord))
+
 # Créer un vecteur ("ReserveTreesPoints") de points de coordonnées des arbres LoggingStatus = "reserve".
+ReserveTreescoord <- inventory %>%
+      filter(LoggingStatus == "reserve") %>%
+      select(Xutm, Yutm)
+
+ReserveTreesPoints  <- st_multipoint(x = as.matrix(ReserveTreescoord))
 

### 2021-07-06 R/DraftFunctions.Rmd
.futurereserve

@@
 library(reshape)
+library(sf)
 ```
@@
 ```
+
+# scenariosparameters
+pas de mode "manual", 
+si argument = NULL, prendre la valeur du scénario correspondante
+```{r}
+
+if (is.null(winching)){
+  if (Type == "RIL1")           winching = "0"
+  if (Type == "RIL2broken")     winching = "0"
+  if (Type == "RIL2")           winching = "1"
+  if (Type == "RIL3")           winching = "2"
+  if (Type == "RIL3fuel")       winching = "2"
+  if (Type == "RIL3fuelhollow") winching = "2"
+
+}
+
+if (is.null(directionalfelling)){
+  if (Type == "RIL1")           directionalfelling = "0"
+  if (Type == "RIL2broken")     directionalfelling = "1"
+  if (Type == "RIL2")           directionalfelling = "1"
+  if (Type == "RIL3")           directionalfelling = "2"
+  if (Type == "RIL3fuel")       directionalfelling = "2"
+  if (Type == "RIL3fuelhollow") directionalfelling = "2"
+
+}
+
+if (is.null(objective)){
+  if (Type == "RIL1")           objective = 25
+  if (Type == "RIL2broken")     objective = 25
+  if (Type == "RIL2")           objective = 25
+  if (Type == "RIL3")           objective = 30
+  if (Type == "RIL3fuel")       objective = 30
+  if (Type == "RIL3fuelhollow") objective = 30
+
+}
+
+if (is.null(diversification)){
+  if (Type == "RIL1")           diversification = FALSE
+  if (Type == "RIL2broken")     diversification = FALSE
+  if (Type == "RIL2")           diversification = FALSE
+  if (Type == "RIL3")           diversification = TRUE
+  if (Type == "RIL3fuel")       diversification = TRUE
+  if (Type == "RIL3fuelhollow") diversification = TRUE
+
+}
+
+# Type	SpatialDataType	Winching 	DirectionalFelling 	Objective 	Diversification 
+# RIL1	           SRTM	    0	           0	            20-25	         FALSE
+# RIL2broken	    LIDAR	    0	           1	            20-25	         FALSE
+# RIL2	          LIDAR     1	           1	            20-25	         FALSE
+# RIL3	          LIDAR	    2	           2	            25-30	          TRUE
+# RIL3fuel	      LIDAR	    2	           2	            25-30	          TRUE
+# RIL3fuelhollow	LIDAR	    2	           2	            25-30         	TRUE
+
+```

### 2021-07-13 R/Draft_spatio.Rmd
TreeFelling and spatial short parts

---
title: "Draft_spatio"
author: "Vincyane Badouard"
date: "13/07/2021"
output: html_document
---

```{r}
inventory = ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))

## Import du MNT de Paracou (1m de résolution, campagne LiDAR de 2016) ----
DemParacou <- raster::raster("D:/VSC Kourou/DATA/GIS/Topo_P6_PARACOU.tif") # MNT (altitude)
plot(DemParacou)

## Import Parcelles de Paracou ----
Plots <- rgdal::readOGR("D:/VSC Kourou/DATA/GIS/Plot_P6_PARACOU.shp") # limites du plot
plot(Plots)

PlotTopo <- raster::mask(x = DemParacou, # DEM en shapefile
                         mask = Plots) # découpage de la topo par l'emprise du plot
plot(PlotTopo)

PlotSlope <- raster::terrain(PlotTopo,
                             opt = "slope",
                             units = 'radians',
                             neigbors = 8)
plot(PlotSlope)

## slope condition
SpInventory <- inventory %>% 
  filter(Commercial!= "0")

coordinates(SpInventory) <- ~ Xutm + Yutm #informer des coordonnées de mes objets spacialisés

proj4string(SpInventory) <- raster::crs(DemParacou) #réccupérer le crs de Paracou

Slope_tmp <- as_tibble(raster::extract(x = PlotSlope, y = SpInventory)) # 
SpInventory <- st_as_sf(SpInventory) # le transformer en objet sf

i = 0
pb <- txtProgressBar(min = 0, max = length(unique(SpInventory$ScientificName)),style = 3)
for (SpecieI in unique(SpInventory$ScientificName)) {

  SpInventorytmp <- SpInventory %>% 
    filter(ScientificName == SpecieI)
  SpInventorytmp <- as_Spatial(SpInventorytmp)
  SpInventorytmp$minDist <- FALSE
    distSp <- topoDist(DEM = PlotTopo,pts = SpInventorytmp)
    distSp <- as_tibble(distSp)
    distSp[distSp == 0] <- NA
    distSp[distSp == Inf] <- NA

    for (ind in 1:dim(distSp)[2]) {
      if (all(is.na(distSp[,ind]))) { FALSE }else{
      SpInventorytmp$minDist[ind] <- min(distSp[,ind],na.rm = TRUE) < 100}
    }

    SpInventory %>% 
    filter(ScientificName == SpecieI) %>% 
      mutate(minDist = SpInventorytmp$minDist)
    i = i+1
    setTxtProgressBar(pb, i)

}

SpInventory <- SpInventory %>%  
  tibble::add_column(Slope = Slope_tmp$value) %>% # ajouter les valeurs de pentes par arbre
  # les NaN ce sont les valeurs infinies, qui témoignent d'un plateau donc pente = 0
  mutate(Slope = ifelse(is.nan(Slope), 0, Slope)) %>% 
  mutate(Exploit = if_else(
    condition = Slope <= atan(otherloggingparameters$TreeMaxSlope/100), # si pente <= 22% l'arbre est exploitable
    true = 1,
    false = 0))
summary(SpInventory)
ggplot(SpInventory) + geom_sf(aes(color = Exploit))

SlopeTreePoint %>% dplyr::rename("HauteurCrique" = names(PlotTib[4]))  %>%
  mutate(Exploit = if_else(
    condition = HauteurCrique > 2 &
      slope <= atan(otherloggingparameters$TreeMaxSlope/100), 
    true = 1,
    false = 0
  )) -> PlotSlopeHCrique

##isolement otherloggingparameters$IsolateTreeMinDistance

##MainTrails out (only for ONF plots)

```

```{r}
harvestable <- function(
  inventory,
  diversification,
  specieslax = FALSE
){
  # Arguments check

  if(!inherits(inventory, "data.frame"))
    stop("The 'inventory' argument of the 'harvestable' function must be a data.frame")

  if(!any(unlist(lapply(list(diversification, specieslax), inherits, "logical"))))
    stop("The 'diversification' and 'specieslax' arguments of the 'harvestable' function must be logical") # any() don't take a list

  # Il manque les scénarios dans les conditions -_-

  #select essences
  HarverstableConditions <- # = 1 boolean vector
    if (diversification || (!diversification && specieslax)) {
      inventory$Commercial =="1"| inventory$Commercial == "2" # now or maybe after we will diversify
    } else if (!diversification && !specieslax) {
      inventory$Commercial == "1" # We will never diversify
    }

  #select diameters
  HarverstableConditions <- HarverstableConditions & (inventory$DBH >= inventory$MinFD & inventory$DBH <= inventory$MaxFD) # harvestable individuals, accord by their DBH

  inventory <- inventory %>%
    mutate(LoggingStatus = ifelse(HarverstableConditions, #Under the above criteria, designate the harvestable species
                                  "harvestable", "non-harvestable")) %>%
    mutate(LoggingStatus = ifelse(Commercial == "0", #The non-commercial species are non-harvestable.
                                  "non-harvestable", LoggingStatus)) %>%

    mutate(LoggingStatus = ifelse(
      !diversification &
        specieslax & #designate the secondarily harvestable species, because diversification only if necessary
        LoggingStatus == "harvestable" &
        Commercial == "2",
      "harvestable2nd", LoggingStatus))

  HarvestableTable <- inventory %>%
    filter(LoggingStatus == "harvestable")
  HVinit <- sum(HarvestableTable$TreeHarvestableVolume) #compute the harvestable volume in the plot for these criteria

  harvestableOutputs <- list(inventory = inventory, HVinit = HVinit)
  return(harvestableOutputs) # return the new inventory and the HVinit
}

```

### 2021-07-13 R/Volume reviews functions.Rmd
TreeFelling and spatial short parts

---
title: "Volume reviews functions"
author: "Vincyane Badouard"
date: "12/07/2021"
output: html_document
---

# timberharvestedvolume
INPUT : inventory + fuel
OUTPUT : LoggedVolume

Si type != "RIL3fuelhollow"  ou (type == "manual"& fuel !="2"): 
LoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"

Si type = "RIL3fuelhollow" ou (type == "manual"& fuel =="2"): NoHollowLoggedVolume = ∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
LoggedVolume = ∑NoHollowLoggedVolume  et ⅔ du volume de ceux codés ProbedHollow = "1".

```{r}

LoggedTable <- inventory %>%
    filter(Logged == "1")

if (fuel !="2") {                    # no hollow trees exploitation

  LoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
}

if (fuel =="2") {                   # with hollow trees exploitation

  HollowTable <- inventory %>%
    filter(ProbedHollow = "1")

  NoHollowLoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
  LoggedVolume <- sum(NoHollowLoggedVolume +
                        1-(otherloggingparameters$TreeHollowPartForFuel)*(HollowTable$TreeHarvestableVolume))
}

```

# exploitablefuelwoodvolume
*si (fuel =="1" |fuel =="2"))*

INPUT : inventory + LoggedVolume/NoHollowLoggedVolume
OUTPUT : FuelVolume

si type = "RIL3fuel" ou (type == "manual"& fuel =="1"):
FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause",  0,14*LoggedVolume

si type = "RIL3fuelhollow" ou (type == "manual"& fuel =="2"):
FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause", ⅓ du volume de la bille des arbres codés "hollowfuel" dans la colonne "DeathCause",  0,14*NoHollowLoggedVolume

```{r}

DamageTable <- inventory %>%
    filter(DeathCause = "maintrail" | DeathCause ="2ndtrail" | DeathCause = "treefall2nd" | DeathCause = "landing")

if (fuel =="0"){

DamageVolume <- sum(DamageTable$TreeHarvestableVolume) # Damage volume, non used for fuel in this scenario

}

if (fuel =="1"){

FuelVolume <- sum(DamageTable$TreeHarvestableVolume + otherloggingparameters$Purge*LoggedVolume) # Damage and purge (0.14)

}

if (fuel =="2"){

  HollowTable <- inventory %>%
    filter(DeathCause = "hollowfuel")

FuelVolume <- sum(DamageTable$TreeHarvestableVolume + 
                    otherloggingparameters$TreeHollowPartForFuel *(HollowTable$TreeHarvestableVolume) + otherloggingparameters$Purge*NoHollowLoggedVolume)
# damage + 1/3 of hollow trees volume + purge (0.14) of the healthy trees

}
```

### 2021-07-13 R/harvestable.R

@@ -45,10 +45,19 @@ harvestable <- function(
   HarverstableConditions <- HarverstableConditions & (inventory$DBH >= inventory$MinFD & inventory$DBH <= inventory$MaxFD) # harvestable individuals, accord by their DBH
 
   #select spatially
-  # HarverstableConditions <- HarverstableConditions & ()
-  ##slope
-  ##isolement
-  ##MainTrails out
+  PlotTopo <- raster::mask(x = DEM, # DEM en shapefile
+                           mask = Plot) # découpage de la topo par l'emprise du plot
+
+  PlotSlope <- raster::terrain(PlotTopo,
+                               opt = "slope",
+                               units = 'radians',
+                               neigbors = 8)
+
+  #HarverstableConditions <- HarverstableConditions & ()
+  ## dans une UP
+  ## slope otherloggingparameters$TreeMaxSlope
+  ##isolement otherloggingparameters$IsolateTreeMinDistance
+  ##MainTrails out (only for ONF plots)
 
   inventory <- inventory %>%
     mutate(LoggingStatus = ifelse(HarverstableConditions, #Under the above criteria, designate the harvestable species

### 2021-07-13 R/Draft_spatio.Rmd
spatial treeselection parts

@@
 ---
-
 ```{r}
 inventory = ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))
+
+#Taf de l'utilisateur
 
@@
 
-## Import Parcelles de Paracou ----
+## Import Parcelles de Paracou
 Plots <- rgdal::readOGR("D:/VSC Kourou/DATA/GIS/Plot_P6_PARACOU.shp") # limites du plot
@@
 
+```
+```{r}
+# Fourni par le module de def d'UP
 PlotTopo <- raster::mask(x = DemParacou, # DEM en shapefile
@@
 PlotSlope <- raster::terrain(PlotTopo, 
-                             opt = "slope",
-                             units = 'radians',
-                             neigbors = 8)
+                             opt = "slope", # calcule des pentes 
+                             units = 'radians', # en radian
+                             neigbors = 8) # avec un voisinage de 8 cellules
 plot(PlotSlope)
+```
 
-## slope condition
-SpInventory <- inventory %>% 
-  filter(Commercial!= "0")
+```{r}
+# Attribuer à chaque arbre sa pente
+SpatInventory <- inventory %>% 
+  filter(Commercial!= "0") # %>% 
+  # filter(DBH >= MinFD & DBH <= MaxFD) # ne prendre que les individus d'sp commerciales, le temps de calcul est déjà bien assez long
 
-coordinates(SpInventory) <- ~ Xutm + Yutm #informer des coordonnées de mes objets spacialisés
+coordinates(SpatInventory) <- ~ Xutm + Yutm # transformer l'inventaire en objet spatialisé en en informant les coordonnées
 
-proj4string(SpInventory) <- raster::crs(DemParacou) #réccupérer le crs de Paracou
+proj4string(SpatInventory) <- raster::crs(DemParacou) # attribuer le crs de Paracou à notre inventaire spatialisé
 
-Slope_tmp <- as_tibble(raster::extract(x = PlotSlope, y = SpInventory)) # 
-SpInventory <- st_as_sf(SpInventory) # le transformer en objet sf
+Slope_tmp <- as_tibble(raster::extract(x = PlotSlope, y = SpatInventory)) # extrait les valeurs de pentes pour les points spatialisés de l'inventaire
 
-i = 0
-pb <- txtProgressBar(min = 0, max = length(unique(SpInventory$ScientificName)),style = 3)
-for (SpecieI in unique(SpInventory$ScientificName)) {
+SpatInventory <- st_as_sf(SpatInventory) %>%  # transformer l'inventaire spatialisé en objet sf
+  add_column(DistCrit = FALSE) # Créer une colonne DistCrit FALSE par défaut
+i = 1
+ProgressBar <- txtProgressBar(min = 0, max = nrow(SpatInventory),style = 3) # barre de progression du calcul
 
-  SpInventorytmp <- SpInventory %>% 
+# Calcul des distances entre les arbres de la même espèce
+
+for (SpecieI in unique(SpatInventory$ScientificName)) {
+
+    SpatInventorytmp <- SpatInventory %>% # SpatInventorytmp stocke 1 seul résulat, celui de chaque tour
       filter(ScientificName == SpecieI)
-  SpInventorytmp <- as_Spatial(SpInventorytmp)
-  SpInventorytmp$minDist <- FALSE
-    distSp <- topoDist(DEM = PlotTopo,pts = SpInventorytmp)
+    SpatInventorytmp <- as_Spatial(SpatInventorytmp)
+
+    distSp <- topoDist(DEM = PlotTopo, pts = SpatInventorytmp) # calcul des distances
     distSp <- as_tibble(distSp)
-    distSp[distSp == 0] <- NA
-    distSp[distSp == Inf] <- NA
+    distSp[distSp == 0] <- NA # ne pas prendre en compte les 0 dans la matrice, qui sont les dist de l'arbre à lui-même.
+    distSp[distSp == Inf] <- NA # ne pas prendre en compte les Inf qui sont les arbres hors de parcelle.
 
-    for (ind in 1:dim(distSp)[2]) {
-      if (all(is.na(distSp[,ind]))) { FALSE }else{
-      SpInventorytmp$minDist[ind] <- min(distSp[,ind],na.rm = TRUE) < 100}
+    for (ind in 1:dim(distSp)[2]) { # 2 pour colonne
+      if (all(is.na(distSp[,ind]))) {FALSE # si toutes la colonne contient des NA c'est un Inf donc on ne le veut pas
+      }else{
+        SpatInventorytmp$DistCrit[ind] <- min(distSp[,ind],na.rm = TRUE) < otherloggingparameters$IsolateTreeMinDistance # si la distance minimale à ses congénaires est < 100, il est exploitable
+      }
+      SpatInventory$DistCrit[SpatInventory$idTree == SpatInventorytmp$idTree[ind]] <- SpatInventorytmp$DistCrit[ind]
+      i = i+1 # et en informer la progress bar
+      setTxtProgressBar(ProgressBar, i)
     }
 
-    SpInventory %>% 
-    filter(ScientificName == SpecieI) %>% 
-      mutate(minDist = SpInventorytmp$minDist)
-    i = i+1
-    setTxtProgressBar(pb, i)
+    # SpatInventory <- SpatInventory %>%
+    #    mutate(DistCrit = ifelse(idTree == SpatInventorytmp$idTree, SpatInventorytmp$DistCrit, DistCrit)) # donner l'info à l'inventaire sp par sp
 
@@
 
-SpInventory <- SpInventory %>%  
-  tibble::add_column(Slope = Slope_tmp$value) %>% # ajouter les valeurs de pentes par arbre
+SlopeCritInventory <- SpatInventory %>%   # SpatInventory <- SpatInventory before
+  add_column(Slope = Slope_tmp$value) %>% # ajouter les valeurs de pentes par arbre
   # les NaN ce sont les valeurs infinies, qui témoignent d'un plateau donc pente = 0
   mutate(Slope = ifelse(is.nan(Slope), 0, Slope)) %>% 
-  mutate(Exploit = if_else(
-    condition = Slope <= atan(otherloggingparameters$TreeMaxSlope/100), # si pente <= 22% l'arbre est exploitable
-    true = 1,
-    false = 0))
-summary(SpInventory)
-ggplot(SpInventory) + geom_sf(aes(color = Exploit))
+  mutate(SlopeCrit = if_else(
+    condition = Slope <= atan(otherloggingparameters$TreeMaxSlope/100), # si pente <= 22% l'arbre est exploitable (on est en radian)
+    TRUE,
+    FALSE)) %>% 
+  dplyr::select(idTree, DistCrit, Slope, SlopeCrit)
 
-SlopeTreePoint %>% dplyr::rename("HauteurCrique" = names(PlotTib[4]))  %>%
-  mutate(Exploit = if_else(
-    condition = HauteurCrique > 2 &
-      slope <= atan(otherloggingparameters$TreeMaxSlope/100), 
-    true = 1,
-    false = 0
-  )) -> PlotSlopeHCrique
+inventory <- inventory %>% 
+  left_join(SlopeCritInventory) %>% 
+  dplyr::select(-geometry)
 
-##isolement otherloggingparameters$IsolateTreeMinDistance
+summary(SlopeCritInventory)
+test_inventory <- test$inventory
+coordinates(test_inventory) <- ~ Xutm + Yutm
+proj4string(test_inventory) <- raster::crs(DemParacou)
+test_inventory <- st_as_sf(test_inventory)
+
+ggplot(test_inventory %>% filter(Commercial != "0")) + geom_sf(aes(color = LoggingStatus == "harvestable"))
 

### 2021-07-13 R/TreeFelling_Draft.Rmd
spatial treeselection parts

@@
 
-# inventory = scndtrailsopening(treeselection(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))) #3539 rows (Paracou: 3620 rows)
+inventory <- addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))
+
+inventory <- treeselection(inventory, SpeciesCriteria, type = "manual", fuel = "0",objective = 20, diversification = TRUE, specieslax = FALSE, objectivelax = FALSE, otherloggingparameters = loggingparameters())$inventory
+
 speciescriteria = SpeciesCriteria
 type = "manual"
-fuel = "0"
+fuel = "2"
 objective = 20
 diversification = TRUE
+directionalfelling = "2"
 specieslax = FALSE
@@
 ```{r}
+Accessible = Selected
 
-if (type == "RIL2broken" | type == "RIL2" | type == "RIL3"){
-  Inventory <- Inventory %>% 
+if (fuel == "0" && directionalfelling != "1"){
+  inventory <- inventory %>% 
     mutate(TreeFellingOrientationSuccess = ifelse(Accessible == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Accessible = linked by 2ndtrails
+
   #Tree coordinates 
+  if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {
+
     TreefallSuccessCoord <- inventory %>% 
@@
       select(Xutm, Yutm)
+
+    TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
+  }
+
+  if (any(inventory$TreeFellingOrientationSuccess == "0", na.rm = TRUE)) {
     TreefallFailCoord <- inventory %>% 
@@
 
-  TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
     TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails
@@
 
-if (type == "RIL3fuel" | (type == "manual"& fuel =="1")) {
+}
 
-  Inventory <- Inventory %>% 
+if (fuel =="1") {
+
+  inventory <- inventory %>% 
     mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
+
   #Tree coordinates 
+  if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {
+
     TreefallSuccessCoord <- inventory %>% 
@@
   }
+}
 
 # Abattre les creux : 
-if (type == "RIL3fuelhollow"  | (type == "manual"& fuel =="2")) {
+if (fuel =="2") {
 
-  Inventory <- Inventory %>% 
-    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1"| ProbbedHollow == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
+  inventory <- inventory %>% 
+    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1"| ProbedHollow == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
+
   #Tree coordinates 
+  if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {
+
     TreefallSuccessCoord <- inventory %>% 
@@
 
-  TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
     TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails
+
+  }
 }
@@
 
-```{r}
+# Polygons laboratory
+```{r polygon}
 # ex:
-outer = matrix(c(0,0,10,0,10,10,0,10,0,0),ncol=2, byrow=TRUE)
-hole1 = matrix(c(1,1,1,2,2,2,2,1,1,1),ncol=2, byrow=TRUE)
+outer = matrix(c(0,0,10,0,10,10,0,10,0,0),ncol=2, byrow=TRUE) # matrice de 2 colonnes (x, y)
+#      [,1] [,2]
+# [1,]    0    0 en bas à gauche
+# [2,]   10    0 en bas à droite 
+# [3,]   10   10 en haut à droite
+# [4,]    0   10 en haut à gauche
+# [5,]    0    0 retour en bas à gauche
+hole1 = matrix(c(1,1,1,2,2,2,2,1,1,1),ncol=2, byrow=TRUE) # le petit carré en bas à gauche
+#      [,1] [,2]
+# [1,]    1    1 en bas à gauche
+# [2,]    1    2 en haut à gauche
+# [3,]    2    2 en haut à droite
+# [4,]    2    1 en bas à droite
+# [5,]    1    1 retour en bas à gauche
 hole2 = matrix(c(5,5,5,6,6,6,6,5,5,5),ncol=2, byrow=TRUE)
@@
 plot(pl1)
+```
+```{r multipolygon}
+pol1 = list(outer, hole1, hole2) #1 list/polygon :  list with numeric matrices with points in rows
+# [[1]]
+#      [,1] [,2] le gros carré
+# [1,]    0    0
+# [2,]   10    0
+# [3,]   10   10
+# [4,]    0   10
+# [5,]    0    0
+# 
+# [[2]]
+#      [,1] [,2] 1er trou
+# [1,]    1    1
+# [2,]    1    2
+# [3,]    2    2
+# [4,]    2    1
+# [5,]    1    1
+# 
+# [[3]]
+#      [,1] [,2] 2eme trou
+# [1,]    5    5
+# [2,]    5    6
+# [3,]    6    6
+# [4,]    6    5
+# [5,]    5    5
 
-pts3 = lapply(pts, function(x) cbind(x, 0))
-(pl2 = st_polygon(pts3))
-(pl3 = st_polygon(pts3, "XYM"))
-plot(pl2)
-plot(pl3)
+pol2 = list(outer + 12, hole1 + 12) # même carré au quel on ajoute 12 à ts les x et tous les y
+# [[1]]
+#      [,1] [,2] # même carré au quel on ajoute 12 à ts les x et tous les y
+# [1,]   12   12
+# [2,]   22   12
+# [3,]   22   22
+# [4,]   12   22
+# [5,]   12   12
+# 
+# [[2]]
+#      [,1] [,2] # un des memes trous au quel on ajoute 12 à ts les x et tous les y
+# [1,]   13   13
+# [2,]   13   14
+# [3,]   14   14
+# [4,]   14   13
+# [5,]   13   13
 
-pts4 = lapply(pts3, function(x) cbind(x, 0))
-(pl4 = st_polygon(pts4))
-plot(pl4)
-
-pol1 = list(outer, hole1, hole2) #1 list/polygon :  list with numeric matrices with points in rows
-pol2 = list(outer + 12, hole1 + 12)
-pol3 = list(outer + 24)
-mp = list(pol1,pol2,pol3) #list of lists with numeric matrices
+pol3 = list(outer + 24)  # même carré au quel on ajoute 24 à ts les x et tous les y
+mp = list(pol1,pol2,pol3) #list of lists of numeric matrices
 (mp1 = st_multipolygon(mp))
 plot(mp1)
+```
 
-pts3 = lapply(mp, function(x) lapply(x, function(y) cbind(y, 0)))
-(mp2 = st_multipolygon(pts3))
-(mp3 = st_multipolygon(pts3, "XYM"))
-plot(mp2)
-plot(mp3)
+```{r ellipse}
+library(nngeo)
+# 1 ellipse
+dat = data.frame(
+  x = 1, #centroid locations
+  y = 0, #centroid locations
+  ex = 0.5, #Size along x-axis
+  ey = 0.5, #Size along y-axis,
+  stringsAsFactors = FALSE
+)
+dat = st_as_sf(dat, coords = c("x", "y")) #centroids
+dat
 
-pts4 = lapply(mp2, function(x) lapply(x, function(y) cbind(y, 0)))
-(mp4 = st_multipolygon(pts4))
-plot(mp4)
+# Calculate ellipses
+el = st_ellipse(pnt = dat, ex = dat$ex, ey = dat$ey)
 
-library(nngeo)
+# Plot 2
+plot(el, graticule = TRUE, axes = TRUE)
+
+# Several ellipses
 dat = data.frame(
@@
 
+```
+```{r Tree prototype}
+# Faire 1 polygone = 1 arbre (rectangle + ellipse)
+
+# 1 rectangle
+pts = list(matrix(c(0,0,0,5,2,6,2,0,0,0),ncol=2, byrow=TRUE)) # TrunkHeight = 6, DBH = 2, 0 = xarbre-DBH/2
+(Trunk = st_polygon(pts))
+plot(Trunk, graticule = TRUE, axes = TRUE)
+
+# 1 ellipse
 dat = data.frame(
-  x = c(1, 2), #centroid locations
-  y = c(0, -3), #centroid locations
-  ex = c(0.5, 2), #Size along x-axis
-  ey = c(0.5, 0.2), #Size along y-axis,
+  x = 1, #centroid locations (x) à la moitiée du diamètre du tronc
+  y = 7, #centroid locations (y) = hauteur du tronc + CrownHeight/2
+  ex = 2, #Size along x-axis (CrownDiameter/2)
+  ey = 1, #Size along y-axis (CrownHeight/2)
   stringsAsFactors = FALSE
@@
 # Calculate ellipses
-el = st_ellipse(pnt = dat, ex = dat$ex, ey = dat$ey)
+Crown = st_ellipse(pnt = dat, ex = dat$ex, ey = dat$ey)
 
-# Plot 2
-plot(el, graticule = TRUE, axes = TRUE)
+plot(Crown, graticule = TRUE, axes = TRUE)
 
+a <- st_difference(st_union(Crown, Trunk)) # -> multypolygon dont on garde que les points qui ne se superposent pas
+plot(a)
+
+ggplot() + # plot 2 polygones
+  geom_sf(data = Trunk) +
+  geom_sf(data = Crown) 
+# Multipolygone = tous les arbres
+```
+```{r Application with the real trees}
+# on prend les arbres sélectionnés
+SelectedTrees <- inventory %>% 
+  filter(Selected == "1") %>%
+  select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)
+
+# Pour 1 arbre
+
+# le tronc
+list(matrix(c('A','B',
+                    'C','D', 
+                    'E', 'F', 
+                    'G','H',
+                    'I', 'J') # retour
+                  ,ncol=2, byrow=TRUE))
+
+pts = list(matrix(c(SelectedTrees$Xutm[1]-(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1], 
+                    SelectedTrees$Xutm[1]-(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1], 
+                    SelectedTrees$Xutm[1]+(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1], 
+                    SelectedTrees$Xutm[1]+(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1],
+                    SelectedTrees$Xutm[1]-(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1]) # retour
+                  ,ncol=2, byrow=TRUE)) # DBH en cm à passer en m
+
+# pts[,3] <- c(rep(1:nrow(SelectedTrees), each=5))
+
+(Trunk = st_polygon(pts))
+plot(Trunk, graticule = TRUE, axes = TRUE)
+
+# le houppier
+dat = data.frame(
+  x = SelectedTrees$Xutm[1], #centroid locations (x) m^me x que l'arbre
+  y = SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1] + SelectedTrees$CrownHeight[1]/2, #centroid locations (y) = hauteur du tronc + CrownHeight/2
+  ex = SelectedTrees$CrownDiameter[1]/2, #Size along x-axis (CrownDiameter/2)
+  ey = SelectedTrees$CrownHeight[1]/2, #Size along y-axis (CrownHeight/2)
+  stringsAsFactors = FALSE
+)
+dat = st_as_sf(dat, coords = c("x", "y")) #centroids
+dat
+
+# Calculate ellipses
+Crown = st_ellipse(pnt = dat, ex = dat$ex, ey = dat$ey)
+
+plot(Crown, graticule = TRUE, axes = TRUE)
+
+a <- st_difference(st_union(Crown, Trunk)) # -> multypolygon dont on garde que les points qui ne se superposent pas
+plot(a)
+
+ggplot() + # plot 2 polygones
+  geom_sf(data = Trunk) +
+  geom_sf(data = Crown) 
+# Multipolygone = tous les arbres
 ```
@@
 ```{r}
-
-if (type == "RIL1" | directionalfelling == "0"){
+## No directional felling
+if (directionalfelling == "0"){
   Coord = matrix(c(0,0,10,0,10,10,0,10,0,0),ncol=2, byrow=TRUE)
@@
 
-if (type == "RIL2broken" | type == "RIL2" | directionalfelling == "1") {
+## To direct only to avoid damage to future and reserve trees
+if (directionalfelling == "1") {
 
@@
 
-if (type == "RIL3" | directionalfelling == "2") {
+## To direct to avoid damage to future and reserve trees + track orientation
+if (directionalfelling == "2") {
 
@@
 
-if (type == "RIL3fuel" | type == "RIL3fuelhollow"  | (type == "manual"& (fuel =="1" |fuel =="2"))) {
+if (fuel =="1" |fuel =="2") {
 

### 2021-07-13 R/timberharvestedvolume.R

@@ -1,0 +1,65 @@
+#' timberharvestedvolume
+#'
+#' @param inventory (data.frame)
+#' @param fuel no  exploitation = "0", damage exploitation in fuelwood = "1",
+#' exploitation of hollow trees and damage in fuelwood = "2"
+#' @param otherloggingparameters (list)
+#'
+#' @return A list with the logged volume (LoggedVolume)
+#' and when fuel = "2", the logged volume without the hollow trees (NoHollowLoggedVolume),
+#' NoHollowLoggedVolume = NULL when fuel = "0" or "1
+#'
+#' @export
+#'
+#' @examples
+#' inventory <- addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))
+#'
+#' inventory <- treeselection(inventory, SpeciesCriteria,
+#' type ="manual", fuel = "2", objective = 20, diversification = TRUE, specieslax = FALSE,
+#' objectivelax = FALSE, otherloggingparameters = loggingparameters())$inventory
+#'
+#' inventory <- secondtrailsopening()$inventory
+#'
+#' inventory <- treefelling()$inventory
+#'
+#' inventory <- adjustedsecondtrails()$inventory
+#'
+#' timberharvestedvolume(inventory, fuel = "2", otherloggingparameters = loggingparameters())
+#'
+#'
+timberharvestedvolume <- function(
+  inventory,
+  fuel,
+  otherloggingparameters = loggingparameters()
+){
+
+  LoggedTable <- inventory %>%
+    filter(Logged == "1")
+
+  if (fuel !="2") {                    # no hollow trees exploitation
+
+    LoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
+
+    outputs <- list(LoggedVolume = LoggedVolume,
+                    NoHollowLoggedVolume = NULL
+    )
+
+  }
+
+  if (fuel =="2") {                   # with hollow trees exploitation
+
+    HollowTable <- inventory %>%
+      filter(ProbedHollow == "1")
+
+    NoHollowLoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
+    LoggedVolume <- sum(NoHollowLoggedVolume +
+                          1-(otherloggingparameters$TreeHollowPartForFuel)*(HollowTable$TreeHarvestableVolume))
+
+    outputs <- list(LoggedVolume = LoggedVolume,
+                    NoHollowLoggedVolume = NoHollowLoggedVolume
+    )
+  }
+
+
+  return(outputs)
+}

### 2021-07-15 R/Draft_spatio.Rmd

@@
 #Taf de l'utilisateur
-
 ## Import du MNT de Paracou (1m de résolution, campagne LiDAR de 2016) ----

### 2021-07-16 R/DESIGNATION_DRAFT.Rmd
Spatial parts

@@
   # Create 2 points vectors with coordinates of the probed hollow trees: "HollowTreesPoints" and "EnergywoodTreesPoints":
-HollowTreescoord <- inventoryG %>% 
-  filter(ProbedHollow == "1") %>% 
-  select(Xutm, Yutm)
+  HollowTreescoord <- selecInventory %>% 
+    filter(ProbedHollow == "1")
 
-HollowTreesPoints  <- st_multipoint(x = as.matrix(HollowTreescoord))
+  sp::coordinates(HollowTreescoord) <- ~ Xutm + Yutm # transformer l'inventaire en objet spatialisé en en informant les coordonnées
+
+  sp::proj4string(HollowTreescoord) <- raster::crs(DEM) # attribuer le crs de Paracou à notre inventaire spatialisé
+
+  HollowTreescoord <- st_as_sf(HollowTreescoord) %>% 
+    select(geometry)
+
+  HollowTreesPoints  <- HollowTreescoord$geometry %>% st_cast("MULTIPOINT")
+  # HollowTreesPoints  <- st_multipoint(x = HollowTreescoord$geometry)
   EnergywoodTreesPoints <- HollowTreesPoints
@@
 # Créer un vecteur ("HarvestableTreesPoints") de points de coordonnées des arbres LoggingStatus = "harvestable" ou "harvestableUp" ou "harvestable2nd".
-HarvestableTreescoord <- inventory %>%
-      filter(LoggingStatus == "harvestable" |LoggingStatus == "harvestableUp" |LoggingStatus == "harvestable2nd") %>%
-      select(Xutm, Yutm)
+
+HarvestableTreesPoints <- inventory %>% filter(LoggingStatus == "harvestable" | LoggingStatus == "harvestableUp" | LoggingStatus == "harvestable2nd")
+
+if (dim(HarvestableTreesPoints)[1] != 0) {
+
+sp::coordinates(HarvestableTreesPoints) <- ~ Xutm + Yutm
+
+sp::proj4string(HarvestableTreesPoints) <- raster::crs(DEM)
+
+HarvestableTreesPoints <- st_as_sf(as(HarvestableTreesPoints,"SpatialPoints"))
+
+}
+HarvestableTreesPoints  <- HarvestableTreesPoints$geometry %>% st_cast("MULTIPOINT")
 

### 2021-07-16 R/futurereserve.R

@@ -8,11 +8,12 @@
 #' @export
 #'
 #' @examples
-#' inventory <- harvestable(ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))),
-#' diversification = TRUE)$inventory
+#' harvestableOutputs <- harvestable(ONFGuyafortaxojoin(inventory, speciescriteria = speciescriteria),
+#' diversification = diversification, specieslax = specieslax,
+#' DEM = DemParacou, plotslope = PlotSlope, otherloggingparameters = loggingparameters())
 #'
-#' HVinit <- harvestable(ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))),
-#' diversification = TRUE)$HVinit
+#' inventory <- harvestableOutputs$inventory
+#' HVinit <- harvestableOutputs$HVinit
 #'
 #' inventory <- selected(inventory, type = "manual", fuel = "0", diversification = TRUE, specieslax = FALSE, objectivelax = FALSE,
 #' otherloggingparameters = loggingparameters(), VO = 80, HVinit = HVinit)$inventory

### 2021-07-16 tests/testthat/test-harvestable.R

@@ -4,10 +4,14 @@ test_that("harvestable", {
 
 MatrixInventory <- as.matrix(Paracou6_2016)
 
+
 expect_error(harvestable(MatrixInventory), regexp = "The 'inventory' argument of the 'harvestable' function must be a data.frame")
 
 expect_error(harvestable(Paracou6_2016, diversification = "1", specieslax = 2),
              regexp = "The 'diversification' and 'specieslax' arguments of the 'harvestable' function must be logical")
+
+expect_error(harvestable(Paracou6_2016, diversification = TRUE, specieslax = FALSE,
+            DEM = NULL, plotslope = NULL))
 
 # LoggingStatus column exist and have no NA
 ## Test data preparation

### 2021-07-19 R/selected.R
fixed error in check

@@ -1,9 +1,10 @@
 #' selected
 #'
 #' @param inventory (data.frame)
-#' @param type "RIL1", "RIL2broken", "RIL2", "RIL3", "RIL3fuel", "RIL3fuelhollow" or "manual"(character)
-#' @param fuel no  exploitation = "0" (default),
-#' damage exploitation in fuelwood = "1", exploitation of hollow trees and damage in fuelwood = "2"
+#' @param type "RIL1", "RIL2broken", "RIL2", "RIL3", "RIL3fuel",
+#'   "RIL3fuelhollow" or "manual"(character)
+#' @param fuel no  exploitation = "0" (default), damage exploitation in fuelwood
+#'   = "1", exploitation of hollow trees and damage in fuelwood = "2"
 #' @param diversification (logical)
 #' @param specieslax = FALSE by default (logical)
 #' @param objectivelax = FALSE by default (logical)
@@ -12,20 +13,26 @@
 #' @param VO (numeric value)
 #' @param HVinit (numeric value)
 #'
-#' @return
+#' @return A FAIRE
+#'
 #' @export
 #'
 #' @examples
-#' inventory <- ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))
+#' inventory <- ONFGuyafortaxojoin(addtreedim(cleaninventory(
+#' inventorycheckformat(Paracou6_2016))))
 #'
-#' harvestableOutputs <- harvestable(inventory, diversification = TRUE, specieslax = FALSE,
-#' DEM = DemParacou, plotslope = PlotSlope, otherloggingparameters = loggingparameters())
+#' harvestableOutputs <- harvestable(inventory, diversification = TRUE,
+#'  specieslax = FALSE,
+#' DEM = DemParacou, plotslope = PlotSlope,
+#' otherloggingparameters = loggingparameters())
 #'
 #' inventory <- harvestableOutputs$inventory
 #' HVinit <- harvestableOutputs$HVinit
 #'
-#' selecInventory <- selected(inventory, type = "manual", fuel = "2", diversification = TRUE, specieslax = FALSE, objectivelax = FALSE,
-#' otherloggingparameters = loggingparameters(), VO = 30, HVinit = HVinit)$inventory
+#' selecInventory <- selected(inventory, type = "manual", fuel = "2",
+#' diversification = TRUE, specieslax = FALSE, objectivelax = FALSE,
[…]

### 2021-07-19 R/treeselection.R

@@ -3,34 +3,41 @@
 #' @param inventory (data.frame)
 #' @param objective Objective volume per hectare (numeric)
 
-#' @param type "RIL1", "RIL2broken", "RIL2", "RIL3", "RIL3fuel", "RIL3fuelhollow" or "manual"(character)
-#' @param fuel no  exploitation = "0", damage exploitation in fuelwood = "1",
-#' exploitation of hollow trees and damage in fuelwood = "2"
-#' @param diversification taking of other species in addition to the main commercial species (logical)
-#' @param specieslax Allow diversification if stand is too poor, = FALSE by default (logical)
-#' @param objectivelax Allow exploitation in case of non-achievement of the objective volume (if stand too poor), = FALSE by default (logical)
-#' @param DEM (RasterLayer)
-#' @param plotslope (RasterLayer)
-#' @param speciescriteria (data.frame)
-#' @param otherloggingparameters (list) MainTrail (multiline)
+#'@param type "RIL1", "RIL2broken", "RIL2", "RIL3", "RIL3fuel", "RIL3fuelhollow"
+#'  or "manual"(character)
+#'@param fuel no  exploitation = "0", damage exploitation in fuelwood = "1",
+#'  exploitation of hollow trees and damage in fuelwood = "2"
+#'@param diversification taking of other species in addition to the main
+#'  commercial species (logical)
+#'@param specieslax Allow diversification if stand is too poor, = FALSE by
+#'  default (logical)
+#'@param objectivelax Allow exploitation in case of non-achievement of the
+#'  objective volume (if stand too poor), = FALSE by default (logical)
+#'@param DEM (RasterLayer)
+#'@param plotslope (RasterLayer)
+#'@param speciescriteria (data.frame)
+#'@param otherloggingparameters (list) MainTrail (multiline)
 #'
-#' @return
-#' @export
+#'@return A FAIRE
 #'
-#' @import sf
-#' @importFrom sp coordinates
-#' @importFrom sp proj4string
-#' @importFrom sf st_as_sf
-#' @importFrom topoDistance topoDist
+#'@export
+#'
+#'@import sf
+#'@importFrom sp coordinates
+#'@importFrom sp proj4string
+#'@importFrom sf st_as_sf
+#'@importFrom topoDistance topoDist
+#'@importFrom methods as
 #'
 #' @examples
[…]

### 2021-07-19 tests/testthat/test-futurereserve.R

@@ -1,41 +1,41 @@
 test_that("futurereserve", {
 
-  inventory <- ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))
-
-  harvestableOutputs <- harvestable(inventory, diversification = TRUE, specieslax = FALSE,
-                                    DEM = DemParacou, plotslope = PlotSlope, otherloggingparameters = loggingparameters())
-
-  inventory <- harvestableOutputs$inventory
-  HVinit <- harvestableOutputs$HVinit
-
-  inventory <- selected(inventory, type = "manual", fuel = "0", diversification = TRUE, specieslax = FALSE, objectivelax = FALSE,
-                        otherloggingparameters = loggingparameters(), VO = 80, HVinit = HVinit)$inventory
-
-  testinventory <- futurereserve(inventory)
-
-  otherloggingparameters = loggingparameters()
-
-  # Future = Commercial == "1" & (DBH >= otherloggingparameters$FutureTreesMinDiameter & DBH < MinFD)
-  FutureTrees <- testinventory %>%
-    filter(LoggingStatus == "future")
-
-  expect_true(all(FutureTrees$Commercial == "1"))
-  expect_true(all(FutureTrees$DBH >= otherloggingparameters$FutureTreesMinDiameter & FutureTrees$DBH < FutureTrees$MinFD))
-
-  # Reserve
-  ReserveTrees <- testinventory %>%
-    filter(LoggingStatus =="reserve")
-
-  expect_true(all(ReserveTrees$Commercial == "1")) # = Commercial == "1"
-  expect_true(all(ReserveTrees$DBH >= otherloggingparameters$FutureTreesMinDiameter
-                  & ReserveTrees$DBH < ReserveTrees$MinFD))# = Future trees
-
-
-  # as many as the number of trees exploited
-  expect_true(
-    sum(as.numeric(testinventory$Selected == "1"), na.rm = TRUE)
-    == sum(as.numeric(testinventory$LoggingStatus =="reserve"), na.rm = TRUE)
-  )
+  # inventory <- ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))
+  #
+  # harvestableOutputs <- harvestable(inventory, diversification = TRUE, specieslax = FALSE,
[…]

### 2021-07-19 R/DRAFT_secondtrailsopening.Rmd
Commit before fetch 19-07-2021

---
title: "DRAFT_secondtrailopening"
output: html_document
---

```{r}
library(Maria)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
library(ggplot2)
library(reshape)
library(sf)
library(raster)
```

```{r}
otherloggingparameters = loggingparameters()
DEMParacou <- raster(paste0(Sys.getenv('DATAPATH'),"/GIS/Paracou/Topo_P6_PARACOU.tif"))
Plots <- st_as_sf(rgdal::readOGR(paste0(Sys.getenv('DATAPATH'),"/GIS/Paracou/Plot_P6_PARACOU.shp")))
MainTrails <- st_as_sf(as(rgdal::readOGR(paste0(Sys.getenv('DATAPATH'),"/GIS/Paracou/maintrail_P6_PARACOU.shp")),"SpatialLines" ))
PlotSlope <- raster::terrain(raster::mask( x = DEMParacou,mask = Plots))
res(DEMParacou)
res(PlotSlope)
load(paste0(Sys.getenv('DATAPATH'),"/treeselectionoutputs.Rdata"))
inventory <- treeselectionoutputs$inventory

HarvestableTreesPoints <- inventory %>% filter(LoggingStatus == "harvestable" | LoggingStatus == "harvestableUp" | LoggingStatus == "harvestable2nd")
if (dim(HarvestableTreesPoints)[1] != 0) {
coordinates(HarvestableTreesPoints) <- ~ Xutm + Yutm
proj4string(HarvestableTreesPoints) <- raster::crs(DEMParacou)
HarvestableTreesPoints <- st_as_sf(as(HarvestableTreesPoints,"SpatialPoints"))
}

SelectedTreesPoints <- inventory %>% filter(Selected == "1")
if (dim(SelectedTreesPoints)[1] != 0) {
coordinates(SelectedTreesPoints) <- ~ Xutm + Yutm
proj4string(SelectedTreesPoints) <- raster::crs(DEMParacou)
SelectedTreesPoints <- st_as_sf(as(SelectedTreesPoints,"SpatialPoints"))
}

FutureTreesPoints <- inventory %>% filter(LoggingStatus == "future")
if (dim(FutureTreesPoints)[1] != 0) {
coordinates(FutureTreesPoints) <- ~ Xutm + Yutm
proj4string(FutureTreesPoints) <- raster::crs(DEMParacou)
FutureTreesPoints <- st_as_sf(as(FutureTreesPoints,"SpatialPoints"))
}

ReserveTreesPoints <- inventory %>% filter(LoggingStatus == "reserve")
if (dim(ReserveTreesPoints)[1] != 0) {
coordinates(ReserveTreesPoints) <- ~ Xutm + Yutm
proj4string(ReserveTreesPoints) <- raster::crs(DEMParacou)
ReserveTreesPoints <- st_as_sf(as(ReserveTreesPoints,"SpatialPoints"))
}

HollowTreesPoints  <- inventory %>% filter(ProbedHollow == "1")
if (dim(HollowTreesPoints)[1] != 0) {
  coordinates(HollowTreesPoints) <- ~ Xutm + Yutm
  proj4string(HollowTreesPoints) <- raster::crs(DEMParacou)
  HollowTreesPoints  <- st_as_sf(as(HollowTreesPoints ,"SpatialPoints"))
}

# EnergywoodTreesPoints  <- inventory %>% filter(DeathCause  == "fuelwood")
# if (dim(EnergywoodTreesPoints)[1] != 0) {
# coordinates(EnergywoodTreesPoints) <- ~ Xutm + Yutm
# proj4string(EnergywoodTreesPoints) <- raster::crs(DEMParacou)
# EnergywoodTreesPoints <- st_as_sf(as(EnergywoodTreesPoints,"SpatialPoints"))
# }

rm(treeselectionoutputs)

ggplot() + geom_sf(data = MainTrails) + geom_sf(data = HarvestableTreesPoints, aes(color = "Harvestable")) + 
  geom_sf(data = SelectedTreesPoints, aes(color = "Selected")) + geom_sf(data = FutureTreesPoints, aes(color = "Futures")) + geom_sf(data = ReserveTreesPoints, aes(color = "Reserves"))
```

```{r}
require(raster)
require(tidyverse)
require(sf)
library(Rsagacmd)

Soil_paracou_path <- paste0(Sys.getenv('DATAPATH'), "/GIS/Paracou/")
SAGA <- saga_gis()
DEM <- SAGA$ta_preprocessor$fill_sinks_xxl_wang_liu(elev = paste0(Soil_paracou_path,"Dem.sgrd"),minslope = 0.01,.verbose = T)

Channels <- SAGA$ta_channels$channel_network(elevation = DEM,init_grid = DEM,init_method = "2",init_value = 10)
HCrique <- SAGA$ta_channels$vertical_distance_to_channel_network(elevation = DEM,channels = Channels$chnlntwrk)

HarvestableAreaDefinition <- function(Plot, DEM, HCrique) {

  # On commence par decouper par l'emprise du plot
  PlotTopo <- raster::mask(x = DEM,
                           mask = Plot) # découpage de la topo par l'emprise du plot
  HCriquePlot <- raster::mask(x = HCrique,
                              mask = Plot) # la même chose pour la hauteur à la crique

  # Calcul de la pente
  PlotSlope <- raster::terrain(PlotTopo,
                               opt = "slope",
                               units = 'radians',
                               neigbors = 8)
  # RastersToPoints

  PlotSlopePoint <-
    dplyr::as_tibble(raster::rasterToPoints(PlotSlope))

  HCriquePlotPoint <-
    dplyr::as_tibble(raster::rasterToPoints(HCriquePlot))

  # left join par x et y
  PlotTib <-
    dplyr::left_join(PlotSlopePoint, HCriquePlotPoint, by = c('x', 'y'))

  PlotTib %>% dplyr::rename("HauteurCrique" = names(PlotTib[4]))  %>%
    mutate(Exploit = if_else(
      condition = HauteurCrique > 2 &
        slope <= .264, # on est en radians pour la pente, donc .264 radians = 27% de pente
      true = 1,
      false = 0
    )) -> PlotSlopeHCrique

  # on a pu determiner les zones exploitables ou non
  # maintenant on transforme ça en polygones, PlotSlopeHCrique pourrait etre reutilise pour la pente

  # on retransforme en raster
  RasterExploit <-
    raster::rasterFromXYZ(PlotSlopeHCrique, crs = 32622) # set crs to WGS84 UTM 22N

  # raster en polygone
  PolygoneExploit <-
    raster::rasterToPolygons(x = RasterExploit$Exploit,
                             n = 16,
                             dissolve = TRUE)

  ## On quitte le monde merveilleux du package raster pour passer a celui de sf

  sf_PolygoneExploit <- sf::st_as_sf(PolygoneExploit)

  ## On transforme nos deux gros polygones (Exploit=1 et Exploit=0 en pleins de petits, par ce qui s'appelait disaggregate dans le package sp)

  ExploitPolygones <-
    sf::st_cast(x = sf_PolygoneExploit, to = "POLYGON") # on a maintenant pleins de polygones, dont pleins de petits isolés

  return(ExploitPolygones)

}

UP <- HarvestableAreaDefinition(Plot = Plots,DEM = DEMParacou,HCrique = 3)
```

```{r}

# secondtrailsopening <- function(inventory,
#                                 DEM = DEMParacou,
#                                 plotslope =  PlotSlope,
#                                 plots = Plots,
#                                 prospectionunit = ProspectionUnit,
#                                 maintrails = MainTrails,
#                                 selectedtreespoints = SelectedTreesPoints,
#                                 hollowtreespoints = HollowTreesPoints,
#                                 avenirtreespoints = AvenirTreesPoint,
#                                 reservetreespoints = ReserveTreesPoints,
#                                 deadtreespoints = DeadTreesPoints,
#                                 otherlogginparameters = logginparameters()) {

  # Arguments check

  if(!inherits(inventory, "data.frame"))
    stop("The 'inventory' arguments of the 'secondtrailsopening' function must be data.frame")

  if(!inherits(Plots, "sf"))
    stop("The 'plots' arguments of the 'secondtrailsopening' function must be sf polygon")

  if(!any(unlist(lapply(list(DEMParacou, PlotSlope), inherits, "RasterLayer"))))
    stop("The 'DEM' and 'plotslope' arguments of the 'secondtrailsopening' function must be raster")

  # Redefinition of the parameters according to the chosen scenario
  scenariosparameters <- scenariosparameters(objective = objective, type = type, fuel = fuel,
                                             diversification = diversification)

  objective <- scenariosparameters$objective
  fuel <- scenariosparameters$fuel
  diversification <- scenariosparameters$diversification

  if (type == "RIL1" | type == "RIL2broken" | (type == "manual" & winching == "0")) {

  } else {

  }
  if (type == "RIL2" | (type == "manual" & winching == "1")) {

  }

  if (type == "RIL3" | type == "RIL3fuel" | type == "RIL3fuelhollow" | (type == "manual" & winching == "2")) {

  }

```

### 2021-07-19 R/DraftFunctions.Rmd
Commit before fetch 19-07-2021

@@
 library(sf)
+library(nngeo)
+library(raster)
+library(topoDistance)
 ```

### 2021-07-19 R/Draft_spatio.Rmd
Commit before fetch 19-07-2021

--- 2021-07-13 R/Draft_spatio.Rmd
@@
 plot(DemParacou)
+usethis::use_data(DemParacou)
 
@@
 plot(Plots)
+usethis::use_data(Plots)
 
@@
 plot(PlotTopo)
+usethis::use_data(PlotTopo)
 
@@
 plot(PlotSlope)
+usethis::use_data(PlotSlope)
+
 ```

### 2021-07-19 R/DemParacou.R

@@ -1,0 +1,6 @@
+#' DemParacou
+#'
+#' Digital terrain model (DTM) of the plot 6 of Paracou (1m resolution, LiDAR campaign of 2016) (French Guiana)
+#' @format A RasterLayer
+#'
+"DemParacou"

### 2021-07-19 R/PlotSlope.R

@@ -1,0 +1,6 @@
+#' PlotSlope
+#'
+#' Slopes (radians) of the plot 6 of Paracou (with a neighbourhood of 8 cells) (French Guiana)
+#' @format SpatialPolygonsDataFrame
+#'
+"PlotSlope"

### 2021-07-19 R/scenariosparameters.R

@@ -27,52 +27,52 @@ scenariosparameters <- function(
 ){
   # Objective volume
   if (is.null(objective)){
-    if (type == "RIL1")           objective = 25
-    if (type == "RIL2broken")     objective = 25
-    if (type == "RIL2")           objective = 25
-    if (type == "RIL3")           objective = 30
-    if (type == "RIL3fuel")       objective = 30
-    if (type == "RIL3fuelhollow") objective = 30
+    if (type == "RIL1")           objective <- 25
+    if (type == "RIL2broken")     objective <- 25
+    if (type == "RIL2")           objective <- 25
+    if (type == "RIL3")           objective <- 30
+    if (type == "RIL3fuel")       objective <- 30
+    if (type == "RIL3fuelhollow") objective <- 30
 
   }
 # Fuelwood exploitation
   if (is.null(fuel)){
-    if (type == "RIL1")           fuel = "0"
-    if (type == "RIL2broken")     fuel = "0"
-    if (type == "RIL2")           fuel = "0"
-    if (type == "RIL3")           fuel = "0"
-    if (type == "RIL3fuel")       fuel = "1"
-    if (type == "RIL3fuelhollow") fuel = "2"
+    if (type == "RIL1")           fuel <- "0"
+    if (type == "RIL2broken")     fuel <- "0"
+    if (type == "RIL2")           fuel <- "0"
+    if (type == "RIL3")           fuel <- "0"
+    if (type == "RIL3fuel")       fuel <- "1"
+    if (type == "RIL3fuelhollow") fuel <- "2"
 
   }
 #
   if (is.null(diversification)){
-    if (type == "RIL1")           diversification = FALSE
-    if (type == "RIL2broken")     diversification = FALSE
-    if (type == "RIL2")           diversification = FALSE
-    if (type == "RIL3")           diversification = TRUE
-    if (type == "RIL3fuel")       diversification = TRUE
-    if (type == "RIL3fuelhollow") diversification = TRUE
+    if (type == "RIL1")           diversification <- FALSE
+    if (type == "RIL2broken")     diversification <- FALSE
+    if (type == "RIL2")           diversification <- FALSE
+    if (type == "RIL3")           diversification <- TRUE
+    if (type == "RIL3fuel")       diversification <- TRUE
+    if (type == "RIL3fuelhollow") diversification <- TRUE
 
   }
 
   if (is.null(winching)){
-    if (type == "RIL1")           winching = "0"
[…]

### 2021-07-19 tests/testthat/test-inventorycheckformat.R

@@ -3,6 +3,7 @@ test_that("inventorycheckformat", {
   # check if the stops work
 
   ## check the function argument
+  data(Paracou6_2016)
   MatrixInventory <- as.matrix(Paracou6_2016)
   expect_error(inventorycheckformat(MatrixInventory), regexp = "inventory must be a data.frame")
 

### 2021-07-19 tests/testthat/test-selected.R

@@ -2,37 +2,45 @@ test_that("selected", {
 
   # Check the function arguments
   # Test data preparation
-  inventory <- harvestable(ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))),
-                          diversification = TRUE, specieslax = FALSE)$inventory
+  data(Paracou6_2016)
+  data(DemParacou)
+
+  inventory <- ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))
+
+  harvestableOutputs <- harvestable(inventory, diversification = TRUE, specieslax = FALSE,
+                                    DEM = DemParacou, plotslope = PlotSlope, otherloggingparameters = loggingparameters())
+
+  inventory <- harvestableOutputs$inventory
+  HVinit <- harvestableOutputs$HVinit
+
   VO <- 40
-  HVinit <- harvestable(ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))),
-                       diversification = FALSE, specieslax = FALSE)$HVinit
-  testinventory <- selected(inventory, type = "manual", fuel = "0", diversification = TRUE, specieslax = FALSE,
-                            objectivelax = FALSE,
-                            otherloggingparameters = loggingparameters(), VO = VO, HVinit = HVinit)$inventory
+
+  testinventory <- suppressMessages(selected(inventory, type = "manual", fuel = "0", diversification = TRUE, specieslax = FALSE,
+                                             objectivelax = FALSE,
+                                             otherloggingparameters = loggingparameters(), VO = VO, HVinit = HVinit))$inventory
 
   MatrixInventory <- as.matrix(Paracou6_2016)
 
   # Tests
-  expect_error(selected(MatrixInventory),
+  expect_error(suppressMessages(selected(MatrixInventory)),
                regexp = "The 'inventory' argument of the 'selected' function must be a data.frame")
 
-  expect_error(selected(inventory, diversification = "1", specieslax = 2, objectivelax = "a"),
+  expect_error(suppressMessages(selected(inventory, diversification = "1", specieslax = 2, objectivelax = "a")),
                regexp = "The 'diversification', 'specieslax' and 'objectivelax' arguments of the 'selected' function must be logical")
 
-  expect_error(selected(inventory, diversification = TRUE, type = "CL"),
[…]

### 2021-07-20 R/Draft_spatio.Rmd
after Sylvain's comments

@@
       }else{
-        SpatInventorytmp$DistCrit[ind] <- min(distSp[,ind],na.rm = TRUE) < otherloggingparameters$IsolateTreeMinDistance # si la distance minimale à ses congénaires est < 100, il est exploitable
+        SpatInventorytmp$DistCrit[ind] <- min(distSp[,ind],na.rm = TRUE) < advancedloggingparameters$IsolateTreeMinDistance # si la distance minimale à ses congénaires est < 100, il est exploitable
       }
@@
   mutate(SlopeCrit = if_else(
-    condition = Slope <= atan(otherloggingparameters$TreeMaxSlope/100), # si pente <= 22% l'arbre est exploitable (on est en radian)
+    condition = Slope <= atan(advancedloggingparameters$TreeMaxSlope/100), # si pente <= 22% l'arbre est exploitable (on est en radian)
     TRUE,

### 2021-07-20 R/futurereserve.R

@@ -6,7 +6,7 @@
 #'  names, economic interest level, minimum and maximum felling diameter, in the
 #'  same format of \code{\link{SpeciesCriteria}} (data.frame)
 #'
-#' @param otherloggingparameters Other parameters of the logging simulator
+#' @param advancedloggingparameters Other parameters of the logging simulator
 #'  \code{\link{loggingparameters}} (list) MainTrail (multiline)
 #'
 #' @return your inventory with selected future and reserve trees, for your logging criteria (\code{\link{SpeciesCriteria}})
@@ -26,14 +26,14 @@
 #' harvestableOutputs <- harvestable(inventory, diversification = TRUE,
 #'  specieslax = FALSE,
 #' DEM = DemParacou, plotslope = PlotSlope,
-#' otherloggingparameters = loggingparameters())
+#' advancedloggingparameters = loggingparameters())
 #'
 #' inventory <- harvestableOutputs$inventory
 #' HVinit <- harvestableOutputs$HVinit
 #'
-#' inventory <- selected(inventory, type = "manual", fuel = "0",
+#' inventory <- selected(inventory, scenario = "manual", fuel = "0",
 #' diversification = TRUE, specieslax = FALSE, objectivelax = FALSE,
-#' otherloggingparameters = loggingparameters(), VO = 30,
+#' advancedloggingparameters = loggingparameters(), VO = 30,
 #'  HVinit = HVinit)$inventory
 #'
 #' futurereserve(inventory)
@@ -41,7 +41,7 @@
 futurereserve <- function(
   inventory,
   speciescriteria = SpeciesCriteria,
-  otherloggingparameters = loggingparameters()
+  advancedloggingparameters = loggingparameters()
 
 ){
 
@@ -50,8 +50,8 @@ futurereserve <- function(
   # if(!any(unlist(lapply(list(inventory, speciescriteria), inherits, "data.frame"))))
   #   stop("The 'inventory' and 'speciescriteria' arguments of the 'futurereserve' function must be data.frame")
   #
-  # if(!inherits(otherloggingparameters, "list"))
-  #   stop("The 'otherloggingparameters' argument of the 'futurereserve' function must be a list")
+  # if(!inherits(advancedloggingparameters, "list"))
+  #   stop("The 'advancedloggingparameters' argument of the 'futurereserve' function must be a list")
 
   # Global variables
   Accessible <- Circ <- CircCorr <- CodeAlive <- Commercial <- NULL
[…]

### 2021-07-20 R/loggingparameters.R

@@ -1,6 +1,6 @@
-#' Other parameters of the logging simulator
+#' Advanced parameters of the logging simulator
 #'
-#' @param MinDBHValue Mimimum DBH value. Default = 10, in cm (double)
+#' @param MinDBHValue Minimum DBH value. Default = 10, in cm (double)
 #' @param MaxAreaSlope Maximum area slope. Default = 27, in % (double)
 #' @param MaxTrailCenterlineSlope Maximum main&2nd trail centerline slope.
 #'   Default = 22, in % (double)

### 2021-07-20 R/DESIGNATION_DRAFT.Rmd

@@
 objectivelax
-otherloggingparameters = loggingparameters()
+advancedloggingparameters = loggingparameters()
 multilignes "MainTrail"
@@
 + Désignation : fonction "TreeSelection"
-+ Si type = "RIL3fuelhollow", "VO" = "objective"
++ Si scenario = "RIL3fuelhollow", "VO" = "objective"
 + Sinon "VO" = "objective" * PlotArea + 20-30% pour compenser le bois creux désigné.
@@
 speciescriteria = SpeciesCriteria
-type = "manual"
+scenario = "manual"
 fuel = "0"
@@
 objectivelax = FALSE
-otherloggingparameters = loggingparameters()
+advancedloggingparameters = loggingparameters()
 # MainTrail
@@
 
-# mutate(VisibleDefectProba = otherloggingparameters$VisiblyRottenModel(DBH)) %>%
+# mutate(VisibleDefectProba = advancedloggingparameters$VisiblyRottenModel(DBH)) %>%
 # mutate(VisibleDefect = sample(c(0,1), size = 1, replace = F, prob = VisibleDefectProba)) # 1 = default tree, 0 = no visible default (là ma fct ne sait pas qd elle doit mettre 0 ou 1)
@@
 
-if (type == "RIL3fuelhollow"| (type == "manual"& fuel =="2")){VO = objective #3604 rows
+if (scenario == "RIL3fuelhollow"| (scenario == "manual"& fuel =="2")){VO = objective #3604 rows
 }else{
-  VO = (objective + (objective*((otherloggingparameters$ObjectiveBonus)/100))) * unique(inventory$PlotArea) # to compensate for the designated hollow wood.
+  VO = (objective + (objective*((advancedloggingparameters$ObjectiveBonus)/100))) * unique(inventory$PlotArea) # to compensate for the designated hollow wood.
 }
@@
 inventoryG <- inventoryF %>% 
-  mutate(ProbedHollowProba = ifelse(Selected == "1", otherloggingparameters$RottenModel(DBH), NULL)) %>%  #Estimates the probability of being probed hollow
+  mutate(ProbedHollowProba = ifelse(Selected == "1", advancedloggingparameters$RottenModel(DBH), NULL)) %>%  #Estimates the probability of being probed hollow
 
@@
 
-if (type != "RIL3fuelhollow"| (type == "manual"& fuel !="2"))
+if (scenario != "RIL3fuelhollow"| (scenario == "manual"& fuel !="2"))
   HarvestableTable <- inventoryG %>%
@@
 
-if (type == "RIL3fuelhollow"| (type == "manual"& fuel =="2")) {
+if (scenario == "RIL3fuelhollow"| (scenario == "manual"& fuel =="2")) {
   # Hollow trees = fuelwood:
@@
   mutate(LoggingStatus = ifelse(Commercial == "1" &
-                                  (DBH >= otherloggingparameters$FutureTreesMinDiameter & DBH < MinFD),
+                                  (DBH >= advancedloggingparameters$FutureTreesMinDiameter & DBH < MinFD),
                                 "future", LoggingStatus))

### 2021-07-20 R/TreeFelling_Draft.Rmd
Fetched version 20-07-21

@@
 
-inventory <- treeselection(inventory, SpeciesCriteria, type = "manual", fuel = "0",objective = 20, diversification = TRUE, specieslax = FALSE, objectivelax = FALSE, otherloggingparameters = loggingparameters())$inventory
+inventory <- treeselection(inventory, SpeciesCriteria, scenario = "manual", fuel = "0",objective = 20, diversification = TRUE, specieslax = FALSE, objectivelax = FALSE, advancedloggingparameters = loggingparameters())$inventory
 
 speciescriteria = SpeciesCriteria
-type = "manual"
+scenario = "manual"
 fuel = "2"
@@
   inventory <- inventory %>% 
-    mutate(TreeFellingOrientationSuccess = ifelse(Accessible == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Accessible = linked by 2ndtrails
+    mutate(TreeFellingOrientationSuccess = ifelse(Accessible == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Accessible = linked by 2ndtrails
 
@@
   inventory <- inventory %>% 
-    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
+    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
 
@@
   inventory <- inventory %>% 
-    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1"| ProbedHollow == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
+    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1"| ProbedHollow == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
 

### 2021-07-20 R/Volume reviews functions.Rmd
Fetched version 20-07-21

@@
 
-Si type != "RIL3fuelhollow"  ou (type == "manual"& fuel !="2"): 
+Si scenario != "RIL3fuelhollow"  ou (scenario == "manual"& fuel !="2"): 
 LoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
 
-Si type = "RIL3fuelhollow" ou (type == "manual"& fuel =="2"): NoHollowLoggedVolume = ∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
+Si scenario = "RIL3fuelhollow" ou (scenario == "manual"& fuel =="2"): NoHollowLoggedVolume = ∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
 LoggedVolume = ∑NoHollowLoggedVolume  et ⅔ du volume de ceux codés ProbedHollow = "1".
@@
   LoggedVolume <- sum(NoHollowLoggedVolume +
-                        1-(otherloggingparameters$TreeHollowPartForFuel)*(HollowTable$TreeHarvestableVolume))
+                        1-(advancedloggingparameters$TreeHollowPartForFuel)*(HollowTable$TreeHarvestableVolume))
 }
@@
 
-si type = "RIL3fuel" ou (type == "manual"& fuel =="1"):
+si scenario = "RIL3fuel" ou (scenario == "manual"& fuel =="1"):
 FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause",  0,14*LoggedVolume
 
-si type = "RIL3fuelhollow" ou (type == "manual"& fuel =="2"):
+si scenario = "RIL3fuelhollow" ou (scenario == "manual"& fuel =="2"):
 FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause", ⅓ du volume de la bille des arbres codés "hollowfuel" dans la colonne "DeathCause",  0,14*NoHollowLoggedVolume
@@
 
-FuelVolume <- sum(DamageTable$TreeHarvestableVolume + otherloggingparameters$Purge*LoggedVolume) # Damage and purge (0.14)
+FuelVolume <- sum(DamageTable$TreeHarvestableVolume + advancedloggingparameters$Purge*LoggedVolume) # Damage and purge (0.14)
 
@@
 FuelVolume <- sum(DamageTable$TreeHarvestableVolume + 
-                    otherloggingparameters$TreeHollowPartForFuel *(HollowTable$TreeHarvestableVolume) + otherloggingparameters$Purge*NoHollowLoggedVolume)
+                    advancedloggingparameters$TreeHollowPartForFuel *(HollowTable$TreeHarvestableVolume) + advancedloggingparameters$Purge*NoHollowLoggedVolume)
 # damage + 1/3 of hollow trees volume + purge (0.14) of the healthy trees

### 2021-07-20 R/testaddtreedim_DRAFT.Rmd
Fetched version 20-07-21

@@
 volumeparameters = ForestZoneVolumeParametersTable
-otherloggingparameters = loggingparameters()
+advancedloggingparameters = loggingparameters()
 
@@
   left_join(volumeparameters) %>%
-  mutate(TreeHarvestableVolume = otherloggingparameters$TreeHarvestableVolumeAllometry(aCoef, bCoef, DBH)) %>%
+  mutate(TreeHarvestableVolume = advancedloggingparameters$TreeHarvestableVolumeAllometry(aCoef, bCoef, DBH)) %>%
 
   # TrunkHeight (m)
-  mutate(TrunkHeight = otherloggingparameters$TrunkHeightAllometry(DBH, TreeHarvestableVolume)) %>%
+  mutate(TrunkHeight = advancedloggingparameters$TrunkHeightAllometry(DBH, TreeHarvestableVolume)) %>%
 
   # TreeHeight (m)
-  mutate(TreeHeight = otherloggingparameters$TreeHeightAllometry(DBH)) %>%
+  mutate(TreeHeight = advancedloggingparameters$TreeHeightAllometry(DBH)) %>%
 
@@
   # compute the crown diameter
-  mutate(CrownDiameter = otherloggingparameters$CrownDiameterAllometry(DBH, TreeHeight, alpha, beta))
+  mutate(CrownDiameter = advancedloggingparameters$CrownDiameterAllometry(DBH, TreeHeight, alpha, beta))
 

### 2021-07-20 R/loggingparameters.R

@@ -1,14 +1,18 @@
-#' Other parameters of the logging simulator
+#' Advanced parameters of the logging simulator
 #'
-#' @param MinDBHValue Mimimum DBH value. Default = 10, in cm (double)
+#' @param MinDBHValue Minimum DBH value. Default = 10, in cm (double)
 #' @param MaxAreaSlope Maximum area slope. Default = 27, in % (double)
-#' @param MaxTrailCenterlineSlope Maximum main&2nd trail centerline slope. Default = 22, in % (double)
-#' @param MaxTrailCrossSlope Maximum main&2nd trail cross slope. Default = 4, in % (double)
+#' @param MaxTrailCenterlineSlope Maximum main&2nd trail centerline slope.
+#'   Default = 22, in % (double)
+#' @param MaxTrailCrossSlope Maximum main&2nd trail cross slope. Default = 4, in
+#'   % (double)
 #' @param GrappleMaxslope Grapple maximum slope. Default = 20, in % (double)
 #' @param TreeMaxSlope Trees slope. Default = 22, in % (double)
 #' @param PlateauMaxSlope Plateau maximum slope. Default = 5, in % (double)
-#' @param SlopeDistance Distance to compute slope. Default = 6, in m (3m for each side) (double)
-#' @param WaterSourcesBufferZone Water sources buffer zone. Default = 30, in m (double)
+#' @param SlopeDistance Distance to compute slope. Default = 6, in m (3m for
+#'   each side) (double)
+#' @param WaterSourcesBufferZone Water sources buffer zone. Default = 30, in m
+#'   (double)
 #' @param MinMainTrailWidth Minimum main trail width. Default = 5, in m (double)
 #' @param MaxMainTrailWidth Maximum main trail width. Default = 6, in m (double)
 #' @param ScndTrailWidth 2nd trail width. Default = 4, in m (double)
@@ -16,28 +20,41 @@
 #' @param ObjectiveBonus Objective bonus. Default = 30, in % (20;30%) (double)
 #' @param CableLength Cable. Default = 40, in m (double)
 #' @param GrappleLength Grapple. Default = 6, in m (double)
-#' @param IsolateTreeMinDistance Isolate tree minimum distance. Default = 100, in m (double)
-#' @param FutureTreesMinDiameter Future trees minimum diameter. Default = 35, in cm (double)
[…]

### 2021-07-22 R/TreeFelling_Draft.Rmd
treefelling in progress, loggingparameters checkargs, and corrections

@@
 ```{r Give values to the arguments to work}
+data(Paracou6_2016)
+data(DemParacou)
 
@@
 
-inventory <- treeselection(inventory, SpeciesCriteria, scenario = "manual", fuel = "0",objective = 20, diversification = TRUE, specieslax = FALSE, objectivelax = FALSE, advancedloggingparameters = loggingparameters())$inventory
+inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
+objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
+advancedloggingparameters = loggingparameters())$inventory
+
+SelectedTrees <- inventory %>% 
+  filter(Selected == "1") %>%
+  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)
 
@@
 objectivelax = FALSE
+DEM = DemParacou
 advancedloggingparameters = loggingparameters()
@@
 plot(pl1)
+
+list(matrix(c('A','B',
+                    'C','D', 
+                    'E', 'F', 
+                    'G','H',
+                    'I', 'J') # retour
+                  ,ncol=2, byrow=TRUE))
 ```
@@
   filter(Selected == "1") %>%
-  select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)
+  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)
+
+# sp::coordinates(SelectedTrees) <- ~ Xutm + Yutm
+# 
+# sp::proj4string(SelectedTrees) <- raster::crs(DEM)
+# 
+# SelectedTrees <- st_as_sf(as(SelectedTrees,"SpatialPoints"))
 
@@
 # le tronc
-list(matrix(c('A','B',
-                    'C','D', 
-                    'E', 'F', 
-                    'G','H',
-                    'I', 'J') # retour
-                  ,ncol=2, byrow=TRUE))
-
 pts = list(matrix(c(SelectedTrees$Xutm[1]-(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1], 
@@
 
+# Polygon orientation
+DescTools::Rotate(x= SelectedTrees$Xutm[1], y = SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1] + SelectedTrees$CrownHeight[1]/2,
+                  theta = pi/sample(0:180, size = 1))
+
 ggplot() + # plot 2 polygones
@@
 # Multipolygone = tous les arbres
+```
+```{r}
+for (ind in c(1:nrow(SelectedTrees))) {
+  pts[ind] = list(matrix(c(SelectedTrees$Xutm[ind]-(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind], 
+                    SelectedTrees$Xutm[ind]-(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind] + SelectedTrees$TrunkHeight[ind], 
+                    SelectedTrees$Xutm[ind]+(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind] + SelectedTrees$TrunkHeight[ind], 
+                    SelectedTrees$Xutm[ind]+(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind],
+                    SelectedTrees$Xutm[ind]-(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind]) # retour
+                  ,ncol=2, byrow=TRUE)) # DBH en cm à passer en m
+
+(Trunk[ind] = st_polygon(pts[ind]))
+
+# le houppier
+dat[ind] = data.frame(
+  x = SelectedTrees$Xutm[ind], #centroid locations (x) m^me x que l'arbre
+  y = SelectedTrees$Yutm[ind] + SelectedTrees$TrunkHeight[ind] + SelectedTrees$CrownHeight[ind]/2, #centroid locations (y) = hauteur du tronc + CrownHeight/2
+  ex = SelectedTrees$CrownDiameter[ind]/2, #Size along x-axis (CrownDiameter/2)
+  ey = SelectedTrees$CrownHeight[ind]/2, #Size along y-axis (CrownHeight/2)
+  stringsAsFactors = FALSE
+)
+dat[ind] = st_as_sf(dat[ind], coords = c("x", "y")) #centroids
+
+# Calculate ellipses
+Crown[ind] = st_ellipse(pnt = dat[ind], ex = dat[ind]$ex, ey = dat$ey) # ne fctne pas
+a[ind] <- st_difference(st_union(Crown[ind], Trunk[ind])) # -> multypolygon dont on garde que les points qui ne se superposent pas
+
+}
+plot(Trunk, graticule = TRUE, axes = TRUE)
+plot(Crown, graticule = TRUE, axes = TRUE)
+plot(a)
+ggplot() + # plot 2 polygones
+  geom_sf(data = Trunk) +
+  geom_sf(data = Crown)
+
 ```

### 2021-07-23 R/TreeFelling_Draft.Rmd
treefelling

@@
 a <- st_difference(st_union(Crown, Trunk)) # -> multypolygon dont on garde que les points qui ne se superposent pas
+# a <- st_cast(a, "POLYGON")
 plot(a)
-
-# Polygon orientation
-DescTools::Rotate(x= SelectedTrees$Xutm[1], y = SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1] + SelectedTrees$CrownHeight[1]/2,
-                  theta = pi/sample(0:180, size = 1))
 
@@
 ```
+
+# Treefelling orientation
+(voir shéma sur google slides)
+1) choper le point (Trail) de la pistele plus proche de l'emplacement de l'arbre (Foot)
+2) calculer l'angle (theta) entre le vecteur que forme la hauteur de l'arbre et le vecteur opposé à celui formé entre le point "Foot" et le point "Trail", par rapport au point "Foot"
+3) rotation du polygone d'un angle de 60 +/- theta °
+
+```{r}
+# Create a polygon ScndTrail
+pts = list(matrix(c(286520, 583134,
+                    286520, 583240, 
+                    286524, 583240, 
+                    286524, 583134,
+                    286520, 583134) # retour
+                  ,ncol=2, byrow=TRUE)) # DBH en cm à passer en m
+
+(ScndTrail = st_polygon(pts))
+ggplot() + # plot 2 polygones
+  geom_sf(data = a) +
+  geom_sf(data = ScndTrail)
+
+# Find the point (Trail) on the ScndTrail closest to the location of the tree (Foot)
+Foot <- st_point(c(SelectedTrees$Xutm[1],SelectedTrees$Yutm[1]))
+
+NearestPoints <- st_nearest_points(Foot, ScndTrail) # from the Foot of the tree to the ScndTrail
+
+NearestPoint <- st_cast(NearestPoints, "POINT") # to have start (Foot) and end (Trail) points
+Trail <- NearestPoint[[2]] # the point (Trail) on the ScndTrail closest to the location of the tree (Foot)
+
+ggplot() + # plot 2 polygones
+  geom_sf(data = a) + # the tree (polygone)
+  geom_sf(data = Foot) + # the foot of the tree (point)
+  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
+  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
+  geom_sf(data = Trail) # the point on the ScndTrail closest to the location of the tree (Foot)
+
+Trail[1]
+
+# Compute theta angle
+theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], Foot[2] + SelectedTrees$TreeHeight[1]),
+                                  c(Foot[1] - Trail[1], Foot[2] -Trail[2]), degree = TRUE))
+
+```
+# Tree rotation
+ref : https://github.com/jeffreyevans/spatialEco/blob/master/R/rotate.polygon.R
+```{r}
+
+RotatePolygon <- function(p, angle, fixed) { # angle in the clockwise direction
+
+  p.coords <- sf::st_coordinates(p)[,1:2] # Polygone coordinates extraction
+
+  p.center <- suppressWarnings(sf::st_coordinates(fixed))
+
+  rotate.coords <- function(xy, a, center) {
+
+    co <- cos(-a * pi / 180)
+
+    si <- sin(-a * pi / 180)
+
+    adj <- matrix(rep(center, nrow(xy)), ncol=2, byrow=TRUE) # matrix with fixed point coordinates
+
+    xy <- xy-adj
+
+    cbind(co * xy[,1] - si * xy[,2],si * xy[,1] + co * xy[,2]) + adj
+  }
+
+  p.rotate <- rotate.coords(p.coords, a = angle, center = c(p.center[1], 
+                                                            p.center[2]))
+
+  Turned <- sf::st_sfc(sf::st_polygon(list(p.rotate))) # create the turned polygon
+
+  return(Turned)
+
+}
+
+TurnedTrunkA <- RotatePolygon(Trunk, angle = 60 - theta, fixed = Foot) # turned trunk
+TurnedCrownA <- RotatePolygon(Crown, angle = 60 - theta, fixed = Foot) # turned crown
+TurnedTrunkB <- RotatePolygon(Trunk, angle = 300 - theta, fixed = Foot) # turned trunk (angle in the clockwise direction: 360-60-theta)
+TurnedCrownB <- RotatePolygon(Crown, angle = 300 - theta, fixed = Foot) # turned crown (angle in the clockwise direction)
+
+# For a random direction felling
+RandomAngle <- sample(c(0:180), size = 1)
+RandomTrunk <- RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot) # turned trunk
+RandomCrown <- RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
+
+ggplot() + # plot 2 polygones
+  geom_sf(data = a) + # the tree (polygone)
+  geom_sf(data = Foot) + # the foot of the tree (point)
+  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
+  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
+  geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
+  geom_sf(data = TurnedTrunkA) +
+  geom_sf(data = TurnedCrownA) +
+  geom_sf(data = TurnedTrunkB) +
+  geom_sf(data = TurnedCrownB) +
+  geom_sf(data = RandomTrunk) +
+  geom_sf(data = RandomCrown)
+
+```
+
+# Create the line to pull the tree
+```{r}
+p = NearestPoints
+angle = 60
+fixed = "foot"
+
+RotateLine <- function(p, angle = 60,  
+    fixed = c("foot", "center", "lower.left", "upper.right")) {
+# if(class(p)[1] != "sf") p <- sf::st_as_sf(p)
+p.coords <- sf::st_coordinates(p)[,1:2] # Polygone coordinates extraction
+
+if(fixed[1] == "foot") {
+p.center <- suppressWarnings(sf::st_coordinates(Foot))
+
+} else if (fixed[1] == "center") {
+  p.center <- suppressWarnings(sf::st_coordinates(sf::st_centroid(p)))
+
+} else if(fixed[1] == "lower.left") {
+
+  p.center <- c(min(sf::st_coordinates(p)[,1]),
+                min(sf::st_coordinates(p)[,2]))
+
+} else if(fixed[1] == "upper.right") {
+  p.center <- c(max(sf::st_coordinates(p)[,1]),
+                max(sf::st_coordinates(p)[,2]))
+}
+
+rotate.coords <- function(xy, a, center) {
+
+  co <- cos(-a * pi / 180)
+
+  si <- sin(-a * pi / 180)
+
+  adj <- matrix(rep(center, nrow(xy)), ncol=2, byrow=TRUE) # matrix with fixed point coordinates
+
+  xy <- xy-adj
+
+  cbind(co * xy[,1] - si * xy[,2],si * xy[,1] + co * xy[,2]) + adj
+}
+
+p.rotate <- rotate.coords(p.coords, a = angle, center = c(p.center[1], 
+                                                          p.center[2]))
+
+Turned <- sf::st_sfc(sf::st_linestring(p.rotate)) # create the new polygon
+
+return(Turned)
+
+}
+
+Trace <- RotateLine(NearestPoints, angle = 60, fixed = "foot")
+
+ggplot() + # plot 2 polygones
+  geom_sf(data = a) + # the tree (polygone)
+  geom_sf(data = Foot) + # the foot of the tree (point)
+  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
+  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
+  geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
+  geom_sf(data = TurnedTrunk) +
+  geom_sf(data = TurnedCrown) +
+  geom_sf(data = Trace)
+
+```
+
+# All the selected trees
+
 ```{r}
@@
   )
-dat[ind] = st_as_sf(dat[ind], coords = c("x", "y")) #centroids
+  # dat[ind] = st_as_sf(dat[ind], coords = c("x", "y")) #centroids
 
   # Calculate ellipses
-Crown[ind] = st_ellipse(pnt = dat[ind], ex = dat[ind]$ex, ey = dat$ey) # ne fctne pas
-a[ind] <- st_difference(st_union(Crown[ind], Trunk[ind])) # -> multypolygon dont on garde que les points qui ne se superposent pas
+  # Crown[ind] = st_ellipse(pnt = dat[ind], ex = dat[ind]$ex, ey = dat$ey) # ne fctne pas
+  # a[ind] <- st_difference(st_union(Crown[ind], Trunk[ind])) # -> multypolygon dont on garde que les points qui ne se superposent pas
 
@@
 # origine = coordonnées de l’arbre (vecteurs "AccessibleTreesPoints")
-# sommet = 1 point au hasard
+# orientation = angle au hasard
 # longueur = hauteur de l’arbre TreeHeight

### 2021-07-23 R/TreeFelling_Draft2.Rmd
treefelling

--- 2021-07-20 R/TreeFelling_Draft.Rmd
@@
 ---
-title: "TreeFelling_Draft"
+title: "TreeFelling_Draft2"
 author: "Vincyane Badouard"
-date: "24/06/2021"
+date: "23/07/2021"
 output: html_document
@@
 
-# Les arguments
-
-inventory
-multilignes "MainTrail ", "2ndTrail"
-vecteur "AccessibleTreesPoints", "SelectedTreesPoints",  "AvenirTreesPoints",  "ReserveTreesPoints", "DeadTreesPoints", "HollowTreesPoints" et "FuelwoodTreesPoints"
-
-# OUTPUT : 
-inventory + polygone "Shadow" + vecteurs "TreefallSuccess", "TreefallFailure", "DamageTreesPoints", "DeadTreesPoints"
-
+# INPUTS
 ```{r Give values to the arguments to work}
+data(Paracou6_2016)
+data(DemParacou)
 
@@
 
-inventory <- treeselection(inventory, SpeciesCriteria, scenario = "manual", fuel = "0",objective = 20, diversification = TRUE, specieslax = FALSE, objectivelax = FALSE, advancedloggingparameters = loggingparameters())$inventory
+inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
+                           objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
+                           advancedloggingparameters = loggingparameters())$inventory
 
@@
 
-# Succès-échec
+# Create the tree polygone
 ```{r}
-Accessible = Selected
+# Take selected trees
+SelectedTrees <- inventory %>% 
+  filter(Selected == "1") %>%
+  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)
 
-if (fuel == "0" && directionalfelling != "1"){
-  inventory <- inventory %>% 
-    mutate(TreeFellingOrientationSuccess = ifelse(Accessible == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Accessible = linked by 2ndtrails
+# sp::coordinates(SelectedTrees) <- ~ Xutm + Yutm
+# 
+# sp::proj4string(SelectedTrees) <- raster::crs(DEM)
+# 
+# SelectedTrees <- st_as_sf(as(SelectedTrees,"SpatialPoints"))
 
-  #Tree coordinates 
-  if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {
+# The Trunk
+pts = list(matrix(c(SelectedTrees$Xutm[1]-(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1], 
+                    SelectedTrees$Xutm[1]-(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1], 
+                    SelectedTrees$Xutm[1]+(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1], 
+                    SelectedTrees$Xutm[1]+(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1],
+                    SelectedTrees$Xutm[1]-(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1]) # the return
+                  ,ncol=2, byrow=TRUE)) # DBH in cm to m
 
-    TreefallSuccessCoord <- inventory %>% 
-      filter(TreeFellingOrientationSuccess == "1") %>% 
-      select(Xutm, Yutm)
+(Trunk = st_polygon(pts))
 
-    TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
-  }
-
-  if (any(inventory$TreeFellingOrientationSuccess == "0", na.rm = TRUE)) {
-    TreefallFailCoord <- inventory %>% 
-      filter(TreeFellingOrientationSuccess == "0") %>% 
-      select(Xutm, Yutm)
-
-    TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails
-
-  }
-
-}
-
-if (fuel =="1") {
-
-  inventory <- inventory %>% 
-    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
-
-  #Tree coordinates 
-  if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {
-
-    TreefallSuccessCoord <- inventory %>% 
-      filter(TreeFellingOrientationSuccess == "1") %>% 
-      select(Xutm, Yutm)
-
-    TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
-  }
-
-  if (any(inventory$TreeFellingOrientationSuccess == "0", na.rm = TRUE)) {
-    TreefallFailCoord <- inventory %>% 
-      filter(TreeFellingOrientationSuccess == "0") %>% 
-      select(Xutm, Yutm)
-
-    TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails
-
-  }
-}
-
-# Abattre les creux : 
-if (fuel =="2") {
-
-  inventory <- inventory %>% 
-    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1"| ProbedHollow == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
-
-  #Tree coordinates 
-  if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {
-
-    TreefallSuccessCoord <- inventory %>% 
-      filter(TreeFellingOrientationSuccess == "1") %>% 
-      select(Xutm, Yutm)
-
-    TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
-  }
-
-  if (any(inventory$TreeFellingOrientationSuccess == "0", na.rm = TRUE)) {
-    TreefallFailCoord <- inventory %>% 
-      filter(TreeFellingOrientationSuccess == "0") %>% 
-      select(Xutm, Yutm)
-
-    TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails
-
-  }
-}
-
-```
-
-# Polygons laboratory
-```{r polygon}
-# ex:
-outer = matrix(c(0,0,10,0,10,10,0,10,0,0),ncol=2, byrow=TRUE) # matrice de 2 colonnes (x, y)
-#      [,1] [,2]
-# [1,]    0    0 en bas à gauche
-# [2,]   10    0 en bas à droite 
-# [3,]   10   10 en haut à droite
-# [4,]    0   10 en haut à gauche
-# [5,]    0    0 retour en bas à gauche
-hole1 = matrix(c(1,1,1,2,2,2,2,1,1,1),ncol=2, byrow=TRUE) # le petit carré en bas à gauche
-#      [,1] [,2]
-# [1,]    1    1 en bas à gauche
-# [2,]    1    2 en haut à gauche
-# [3,]    2    2 en haut à droite
-# [4,]    2    1 en bas à droite
-# [5,]    1    1 retour en bas à gauche
-hole2 = matrix(c(5,5,5,6,6,6,6,5,5,5),ncol=2, byrow=TRUE)
-pts = list(outer, hole1, hole2)
-(pl1 = st_polygon(pts))
-plot(pl1)
-```
-```{r multipolygon}
-pol1 = list(outer, hole1, hole2) #1 list/polygon :  list with numeric matrices with points in rows
-# [[1]]
-#      [,1] [,2] le gros carré
-# [1,]    0    0
-# [2,]   10    0
-# [3,]   10   10
-# [4,]    0   10
-# [5,]    0    0
-# 
-# [[2]]
-#      [,1] [,2] 1er trou
-# [1,]    1    1
-# [2,]    1    2
-# [3,]    2    2
-# [4,]    2    1
-# [5,]    1    1
-# 
-# [[3]]
-#      [,1] [,2] 2eme trou
-# [1,]    5    5
-# [2,]    5    6
-# [3,]    6    6
-# [4,]    6    5
-# [5,]    5    5
-
-pol2 = list(outer + 12, hole1 + 12) # même carré au quel on ajoute 12 à ts les x et tous les y
-# [[1]]
-#      [,1] [,2] # même carré au quel on ajoute 12 à ts les x et tous les y
-# [1,]   12   12
-# [2,]   22   12
-# [3,]   22   22
-# [4,]   12   22
-# [5,]   12   12
-# 
-# [[2]]
-#      [,1] [,2] # un des memes trous au quel on ajoute 12 à ts les x et tous les y
-# [1,]   13   13
-# [2,]   13   14
-# [3,]   14   14
-# [4,]   14   13
-# [5,]   13   13
-
-pol3 = list(outer + 24)  # même carré au quel on ajoute 24 à ts les x et tous les y
-mp = list(pol1,pol2,pol3) #list of lists of numeric matrices
-(mp1 = st_multipolygon(mp))
-plot(mp1)
-```
-
-```{r ellipse}
-library(nngeo)
-# 1 ellipse
-dat = data.frame(
-  x = 1, #centroid locations
-  y = 0, #centroid locations
-  ex = 0.5, #Size along x-axis
-  ey = 0.5, #Size along y-axis,
+# The Crown
+dat <- data.frame(
+  x = SelectedTrees$Xutm[1], #centroid location (x) same x than the tree
+  y = SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1] + SelectedTrees$CrownHeight[1]/2, #centroid location (y) = trunk height + CrownHeight/2
+  ex = SelectedTrees$CrownDiameter[1]/2, #Size along x-axis (CrownDiameter/2)
+  ey = SelectedTrees$CrownHeight[1]/2, #Size along y-axis (CrownHeight/2)
   stringsAsFactors = FALSE
 )
-dat = st_as_sf(dat, coords = c("x", "y")) #centroids
-dat
+dat <- st_as_sf(dat, coords = c("x", "y")) # spacial dataframe
 
-# Calculate ellipses
-el = st_ellipse(pnt = dat, ex = dat$ex, ey = dat$ey)
+Crown <- st_ellipse(pnt = dat, ex = dat$ex, ey = dat$ey) # Create the ellipse
 
-# Plot 2
-plot(el, graticule = TRUE, axes = TRUE)
-
-# Several ellipses
-dat = data.frame(
-  x = c(1, 1, -1, 3, 3), #centroid locations
-  y = c(0, -3, 2, -2, 0), #centroid locations
-  ex = c(0.5, 2, 2, 0.3, 0.6), #Size along x-axis
-  ey = c(0.5, 0.2, 1, 1, 0.3), #Size along y-axis,
-  stringsAsFactors = FALSE
-)
-dat = st_as_sf(dat, coords = c("x", "y")) #centroids
-dat
-
-# Calculate ellipses
-el = st_ellipse(pnt = dat, ex = dat$ex, ey = dat$ey)
-
-# Plot 2
-plot(el, graticule = TRUE, axes = TRUE)
-
-```
-```{r Tree prototype}
-# Faire 1 polygone = 1 arbre (rectangle + ellipse)
-
-# 1 rectangle
-pts = list(matrix(c(0,0,0,5,2,6,2,0,0,0),ncol=2, byrow=TRUE)) # TrunkHeight = 6, DBH = 2, 0 = xarbre-DBH/2
-(Trunk = st_polygon(pts))
-plot(Trunk, graticule = TRUE, axes = TRUE)
-
-# 1 ellipse
-dat = data.frame(
-  x = 1, #centroid locations (x) à la moitiée du diamètre du tronc
-  y = 7, #centroid locations (y) = hauteur du tronc + CrownHeight/2
-  ex = 2, #Size along x-axis (CrownDiameter/2)
-  ey = 1, #Size along y-axis (CrownHeight/2)
-  stringsAsFactors = FALSE
-)
-dat = st_as_sf(dat, coords = c("x", "y")) #centroids
-dat
-
-# Calculate ellipses
-Crown = st_ellipse(pnt = dat, ex = dat$ex, ey = dat$ey)
-
-plot(Crown, graticule = TRUE, axes = TRUE)
-
-a <- st_difference(st_union(Crown, Trunk)) # -> multypolygon dont on garde que les points qui ne se superposent pas
-plot(a)
+a <- st_difference(st_union(Crown, Trunk)) # -> multypolygon of which we keep only the points that do not overlap
 
@@
   geom_sf(data = Crown)
-# Multipolygone = tous les arbres
+
+ggplot() +
+  geom_sf(data = a) # plot the multypolygon
 ```
-```{r Application with the real trees}
-# on prend les arbres sélectionnés
-SelectedTrees <- inventory %>% 
-  filter(Selected == "1") %>%
-  select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)
 
-# Pour 1 arbre
+# Treefelling orientation
+(voir shéma sur google slides)
+1) choper le point (Trail) de la pistele plus proche de l'emplacement de l'arbre (Foot)
+2) calculer l'angle (theta) entre le vecteur que forme la hauteur de l'arbre et le vecteur opposé à celui formé entre le point "Foot" et le point "Trail", par rapport au point "Foot"
+3) rotation du polygone d'un angle de 60 +/- theta °
 
-# le tronc
-list(matrix(c('A','B',
-                    'C','D', 
-                    'E', 'F', 
-                    'G','H',
-                    'I', 'J') # retour
-                  ,ncol=2, byrow=TRUE))
-
-pts = list(matrix(c(SelectedTrees$Xutm[1]-(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1], 
-                    SelectedTrees$Xutm[1]-(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1], 
-                    SelectedTrees$Xutm[1]+(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1], 
-                    SelectedTrees$Xutm[1]+(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1],
-                    SelectedTrees$Xutm[1]-(SelectedTrees$DBH[1]/100)/2, SelectedTrees$Yutm[1]) # retour
+```{r}
+# Create a polygon ScndTrail
+pts = list(matrix(c(286520, 583134,
+                    286520, 583240, 
+                    286524, 583240, 
+                    286524, 583134,
+                    286520, 583134) # the return
                   ,ncol=2, byrow=TRUE)) # DBH en cm à passer en m
 
-# pts[,3] <- c(rep(1:nrow(SelectedTrees), each=5))
+(ScndTrail <- st_polygon(pts))
 
-(Trunk = st_polygon(pts))
-plot(Trunk, graticule = TRUE, axes = TRUE)
+ggplot() + 
+  geom_sf(data = a) + # the tree
+  geom_sf(data = ScndTrail) # the 2nd trail
+```
 
-# le houppier
-dat = data.frame(
-  x = SelectedTrees$Xutm[1], #centroid locations (x) m^me x que l'arbre
-  y = SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1] + SelectedTrees$CrownHeight[1]/2, #centroid locations (y) = hauteur du tronc + CrownHeight/2
-  ex = SelectedTrees$CrownDiameter[1]/2, #Size along x-axis (CrownDiameter/2)
-  ey = SelectedTrees$CrownHeight[1]/2, #Size along y-axis (CrownHeight/2)
-  stringsAsFactors = FALSE
-)
-dat = st_as_sf(dat, coords = c("x", "y")) #centroids
-dat
+```{r}
+# Find the point (Trail) on the ScndTrail closest to the location of the tree (Foot)
+Foot <- st_point(c(SelectedTrees$Xutm[1],SelectedTrees$Yutm[1])) # tree foot point
 
-# Calculate ellipses
-Crown = st_ellipse(pnt = dat, ex = dat$ex, ey = dat$ey)
+NearestPoints <- st_nearest_points(Foot, ScndTrail) # from the Foot of the tree to the ScndTrail (linestring)
 
-plot(Crown, graticule = TRUE, axes = TRUE)
-
-a <- st_difference(st_union(Crown, Trunk)) # -> multypolygon dont on garde que les points qui ne se superposent pas
-plot(a)
+NearestPoint <- st_cast(NearestPoints, "POINT") # to have start (Foot) and end (Trail) points
+Trail <- NearestPoint[[2]] # the point (Trail) on the ScndTrail closest to the location of the tree (Foot)
 
 ggplot() + # plot 2 polygones
-  geom_sf(data = Trunk) +
-  geom_sf(data = Crown) 
-# Multipolygone = tous les arbres
-```
+  geom_sf(data = a) + # the tree (polygone)
+  geom_sf(data = Foot) + # the foot of the tree (point)
+  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
+  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail (linestring)
+  geom_sf(data = Trail) # the point on the ScndTrail closest to the location of the tree (Foot)
 
-# Abattages selon le type d’EFI
-```{r}
-## No directional felling
-if (directionalfelling == "0"){
-  Coord = matrix(c(0,0,10,0,10,10,0,10,0,0),ncol=2, byrow=TRUE)
-  pol1 = list() #1 list/polygon :  list with numeric matrices with points in rows
-  pol2 = list()
-  pol3 = list()
-  mp = list(pol1,pol2,pol3) #list of lists with numeric matrices
-  (mp1 = st_multipolygon(mp))
-  plot(mp1)
-
-  Shadows <- st_multipolygon()
-} 
-# créer un polygone par arbre ("Shadow"):
-# origine = coordonnées de l’arbre (vecteurs "AccessibleTreesPoints")
-# sommet = 1 point au hasard
-# longueur = hauteur de l’arbre TreeHeight
-# largeur = DBH
-# hauteur de l’ellipse CrownHeight
-# diamètre de l’ellipse CrownDiameter
-
-## To direct only to avoid damage to future and reserve trees
-if (directionalfelling == "1") {
-
-}
-# créer un polygone par arbre ("Shadow"):
-# Réussite à 60% :
-# origine = coordonnées de l’arbre (vecteurs "TreefallSuccess")
-# longueur = hauteur de l’arbre
-# largeur = DBH
-# hauteur de l’ellipse
-# diamètre de l’ellipse
-# orientation = base du tronc vers la voie la plus proche (MainTrail ou 2ndTrail)
-# Éviter à  100% les arbres "reserve" (vecteur "ReserveTreesPoints") et essayer d’éviter les arbres "future" (vecteur "AvenirTreesPoints")
-# Echec à 40% :
-# origine = coordonnées de l’arbre (vecteurs "TreefallFailure")
-# sommet = 1 point au hasard
-# longueur = hauteur de l’arbre
-# largeur = DBH
-# hauteur de l’ellipse
-# diamètre de l’ellipse
-
-## To direct to avoid damage to future and reserve trees + track orientation
-if (directionalfelling == "2") {
-
-}
-# créer un polygone par arbre ("Shadow"):
-# Echec à 40% :
-# origine = coordonnées de l’arbre (vecteurs "TreefallFailure")
-# sommet = 1 point au hasard
-# longueur = hauteur de l’arbre
-# largeur = DBH
-# hauteur de l’ellipse
-# diamètre de l’ellipse
-# Réussite à 60% :
-# origine = coordonnées de l’arbre (vecteurs "TreefallSuccess")
-# longueur = hauteur de l’arbre
-# largeur = DBH
-# hauteur de l’ellipse
-# diamètre de l’ellipse
-# orientation = 30-45◦, base du tronc vers la voie la plus proche (MainTrail ou 2ndTrail) MinTreefallOrientation MaxTreefallOrientation
-# Éviter à  100% les arbres "reserve" (vecteur "ReserveTreesPoints") et essayer d’éviter les arbres "future" (vecteur "AvenirTreesPoints")
-
-if (fuel =="1" |fuel =="2") {
-
-}
-# créer un polygone par arbre ("Shadow"):
-# Echec à 40% :
-# origine = coordonnées de l’arbre (vecteurs "TreefallFailure")
-# sommet = 1 point au hasard
-# longueur = hauteur de l’arbre
-# largeur = DBH
-# hauteur de l’ellipse
-# diamètre de l’ellipse
-# Réussite à 60% :
-# origine = coordonnées de l’arbre (vecteurs "TreefallSuccess")
-# longueur = hauteur de l’arbre
-# largeur = DBH
-# hauteur de l’ellipse
-# diamètre de l’ellipse
-# orientation = 30-45◦,
-# if (piste la plus proche (MainTrail ou 2ndTrail) à ⩽ 6 m de l’arbre & ⩽ 20% de l’entrée de la parcelle (= contact piste/bord parcelle) jusqu’à max 6 m de l’arbre (buffergrappin)  ("piste à grappin" ?)) : houppier vers cette piste.
-# Sinon : pied vers piste la plus proche (MainTrail ou 2ndTrail)
-# Éviter à  100% les arbres "reserve" (vecteur "ReserveTreesPoints") et essayer d’éviter les arbres "future" (vecteur "AvenirTreesPoints")
+# Compute theta angle
+theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], Foot[2] + SelectedTrees$TreeHeight[1]),
+                                  c(Foot[1] - Trail[1], Foot[2] -Trail[2]), degree = TRUE))
 
@@
 
-# Renseigner les arbres abattus :
-inventory : Pour les arbres pour lesquels un Shadow a été créé :
-renseigner "1" dans une colonne "Cutted".
-if ProbedHollow = "0" : renseigner "cutted" if encore "NA"  dans la colonne "DeathCause".
-if ProbedHollow = "1" renseigner "woodfuel" if encore "NA"  dans la colonne "DeathCause".
+# Tree rotation
+ref : https://github.com/jeffreyevans/spatialEco/blob/master/R/rotate.polygon.R
+
 ```{r}
 
-# inventory <- inventory %>%
+RotatePolygon <- function(p, angle, fixed) { # angle in the clockwise direction
 
-# mutate(Cutted = ifelse(,"1",) %>% # a shadow = tree cutted
+  p.coords <- sf::st_coordinates(p)[,1:2] # Polygone coordinates extraction
 
-# mutate(DeathCause = ifelse(is.na(DeathCause) & ProbedHollow == "0","cutted", DeathCause) %>% #BO
-#          
-# mutate(DeathCause = ifelse(is.na(DeathCause) & ProbedHollow == "1","woodfuel", DeathCause) #BE
+  p.center <- suppressWarnings(sf::st_coordinates(fixed))
+
+  rotate.coords <- function(xy, a, center) {
+
+    co <- cos(-a * pi / 180)
+
+    si <- sin(-a * pi / 180)
+
+    adj <- matrix(rep(center, nrow(xy)), ncol=2, byrow=TRUE) # matrix with fixed point coordinates
+
+    xy <- xy-adj
+
+    cbind(co * xy[,1] - si * xy[,2],si * xy[,1] + co * xy[,2]) + adj
+  }
+
+  p.rotate <- rotate.coords(p.coords, a = angle, center = c(p.center[1], 
+                                                            p.center[2]))
+
+  Turned <- sf::st_sfc(sf::st_polygon(list(p.rotate))) # create the turned polygon
+
+  return(Turned)
+
+}
+
+TurnedTrunkA <- RotatePolygon(Trunk, angle = 60 - theta, fixed = Foot) # turned trunk
+TurnedCrownA <- RotatePolygon(Crown, angle = 60 - theta, fixed = Foot) # turned crown
+TurnedTrunkB <- RotatePolygon(Trunk, angle = 300 - theta, fixed = Foot) # turned trunk (angle in the clockwise direction: 360-60-theta)
+TurnedCrownB <- RotatePolygon(Crown, angle = 300 - theta, fixed = Foot) # turned crown (angle in the clockwise direction)
+
+# For a random direction felling
+RandomAngle <- sample(c(0:180), size = 1)
+RandomTrunk <- RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot) # turned trunk
+RandomCrown <- RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
+
+ggplot() + # plot 2 polygones
+  geom_sf(data = a) + # the tree (polygone)
+  geom_sf(data = Foot) + # the foot of the tree (point)
+  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
+  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
+  geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
+  geom_sf(data = TurnedTrunkA) +
+  geom_sf(data = TurnedCrownA) +
+  geom_sf(data = TurnedTrunkB) +
+  geom_sf(data = TurnedCrownB) +
+  geom_sf(data = RandomTrunk) +
+  geom_sf(data = RandomCrown)
 
 ```
-
-# chablismortality
-Fonction de mortalité chablis ("chablismortality"): élimination des arbres chablis 2ndaires de l’arbre abattu =  faire mourir les arbres de coordonnées appartenant aux polygones "Shadow" :
-+ Ajouter les coordonnées de ces arbres au vecteur "DamageTreesPoints" et au vecteur "DeadTreesPoints".
-+ inventory : Pour ces arbres, renseigner "treefall2nd" ifencore "NA"  dans la colonne "DeathCause".
-+ leur faire des Shadow aussi : créer un polygone par arbre ("Shadow"):
-origine = coordonnées de l’arbre (vecteurs "DamageTreesPoints")
-orientation = même direction/sens que son abatteur 
-longueur = hauteur de l’arbre
-largeur = DBH
-hauteur de l’ellipse
-diamètre de l’ellipse
-```{r}
-
-# Ajouter les coordonnées de ces arbres au vecteur "DamageTreesPoints" et au vecteur "DeadTreesPoints".
-
-# inventory : Pour ces arbres, renseigner "treefall2nd" ifencore "NA"  dans la colonne "DeathCause".
-
-# leur faire des Shadow aussi : créer un polygone par arbre ("Shadow"):
-# origine = coordonnées de l’arbre (vecteurs "DamageTreesPoints")
-# orientation = même direction/sens que son abatteur 
-# longueur = hauteur de l’arbre
-# largeur = DBH
-# hauteur de l’ellipse
-# diamètre de l’ellipse
-
-```

### 2021-07-23 R/Treefelling_test_for all trees.Rmd
treefelling

--- 2021-07-23 R/TreeFelling_Draft2.Rmd
@@
 ---
-title: "TreeFelling_Draft2"
+title: "Treefelling_test_for all trees"
 author: "Vincyane Badouard"
@@
 
-# Create the tree polygone
 ```{r}
-# Take selected trees
-SelectedTrees <- inventory %>% 
-  filter(Selected == "1") %>%
-  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)
+felling <- function (inventory, SelectedTrees) {
+
+  # # Take selected trees
+  # SelectedTrees <- inventory %>% 
+  #   filter(Selected == "1") %>%
+  #   dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)
 
@@
     geom_sf(data = a) # plot the multypolygon
-```
 
   # Treefelling orientation
-(voir shéma sur google slides)
-1) choper le point (Trail) de la pistele plus proche de l'emplacement de l'arbre (Foot)
-2) calculer l'angle (theta) entre le vecteur que forme la hauteur de l'arbre et le vecteur opposé à celui formé entre le point "Foot" et le point "Trail", par rapport au point "Foot"
-3) rotation du polygone d'un angle de 60 +/- theta °
 
-```{r}
   # Create a polygon ScndTrail
@@
     geom_sf(data = ScndTrail) # the 2nd trail
-```
 
-```{r}
   # Find the point (Trail) on the ScndTrail closest to the location of the tree (Foot)
@@
                                     c(Foot[1] - Trail[1], Foot[2] -Trail[2]), degree = TRUE))
-
-```
-
-# Tree rotation
-ref : https://github.com/jeffreyevans/spatialEco/blob/master/R/rotate.polygon.R
-
-```{r}
 
@@
 
+  FellingOuputs <- list(a = a,
+                        Foot = Foot,
+                        ScndTrail = ScndTrail,
+                        NearestPoints = NearestPoints,
+                        Trail = Trail,
+                        TurnedTrunkA = TurnedTrunkA,
+                        TurnedCrownA = TurnedCrownA,
+                        TurnedTrunkB = TurnedTrunkB,
+                        TurnedCrownB = TurnedCrownB,
+                        RandomTrunk = RandomTrunk,
+                        RandomCrown = RandomCrown)
+
+  return(FellingOuputs)
+
+}
+
+```
+
+```{r}
+SelectedTrees <- inventory %>% 
+  filter(Selected == "1") %>%
+  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)
+
+EachTree <- list(SelectedTrees[1,],
+                 SelectedTrees[2,],
+                 SelectedTrees[3,])
+
+AllTheFellingTrees <- lapply(EachTree, function(element)
+  felling(inventory, element))
+
+# a <- st_union(st_union(AllTheFellingTrees[[1]]$a, AllTheFellingTrees[[2]]$a), AllTheFellingTrees[[3]]$a)
+
+# Foot <- st_union(st_union(AllTheFellingTrees[[1]]$Foot, AllTheFellingTrees[[2]]$Foot), AllTheFellingTrees[[3]]$Foot)
+
+ScndTrail <- st_union(st_union(AllTheFellingTrees[[1]]$ScndTrail, AllTheFellingTrees[[2]]$ScndTrail), AllTheFellingTrees[[3]]$ScndTrail)
+
+NearestPoints <-  st_union(st_union(AllTheFellingTrees[[1]]$NearestPoints, AllTheFellingTrees[[2]]$NearestPoints), AllTheFellingTrees[[3]]$NearestPoints)
+# Trail <- Trail
+TurnedTrunkA <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedTrunkA, AllTheFellingTrees[[2]]$TurnedTrunkA), AllTheFellingTrees[[3]]$TurnedTrunkA)
+
+TurnedCrownA <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedCrownA, AllTheFellingTrees[[2]]$TurnedCrownA), AllTheFellingTrees[[3]]$TurnedCrownA)
+
+TurnedTrunkB <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedTrunkB, AllTheFellingTrees[[2]]$TurnedTrunkB), AllTheFellingTrees[[3]]$TurnedTrunkB)
+
+TurnedCrownB <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedCrownB, AllTheFellingTrees[[2]]$TurnedCrownB), AllTheFellingTrees[[3]]$TurnedCrownB)
+# RandomTrunk <- RandomTrunk
+# RandomCrown <- RandomCrown
+
 ggplot() + # plot 2 polygones
-  geom_sf(data = a) + # the tree (polygone)
-  geom_sf(data = Foot) + # the foot of the tree (point)
+  # geom_sf(data = a) + # the tree (polygone)
+  # geom_sf(data = Foot) + # the foot of the tree (point)
   geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
   geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
-  geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
+  # geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
   geom_sf(data = TurnedTrunkA) +
@@
   geom_sf(data = TurnedTrunkB) +
-  geom_sf(data = TurnedCrownB) +
-  geom_sf(data = RandomTrunk) +
-  geom_sf(data = RandomCrown)
+  geom_sf(data = TurnedCrownB)
+  # geom_sf(data = RandomTrunk) +
+  # geom_sf(data = RandomCrown)
 

### 2021-07-26 R/Treefelling_test_for all trees.Rmd
Treefelling and corrections

@@
 ```{r}
-felling <- function (inventory, SelectedTrees) {
+felling <- function (inventory, SelectedTrees, fuel, directionalfelling, advancedloggingparameters = loggingparameters()) {
 
-  # # Take selected trees
+  # Take selected trees
   # SelectedTrees <- inventory %>%
@@
 
-  ggplot() + # plot 2 polygones
-    geom_sf(data = Trunk) +
-    geom_sf(data = Crown)
-
-  ggplot() +
-    geom_sf(data = a) # plot the multypolygon
-
   # Treefelling orientation
 
-  # Create a polygon ScndTrail
-  pts = list(matrix(c(286520, 583134,
-                      286520, 583240, 
-                      286524, 583240, 
-                      286524, 583134,
-                      286520, 583134) # the return
-                    ,ncol=2, byrow=TRUE)) # DBH en cm à passer en m
+  # Create 2 polygons ScndTrail
+  pol1 <- list(matrix(c(286503, 583134,
+                        286503, 583240, 
+                        286507, 583240, 
+                        286507, 583134,
+                        286503, 583134) # the return
+                      ,ncol=2, byrow=TRUE)) 
+  pol2 <- list(matrix(c(286650, 583134,
+                        286650, 583240, 
+                        286654, 583240, 
+                        286654, 583134,
+                        286650, 583134) # the return
+                      ,ncol=2, byrow=TRUE))
 
-  (ScndTrail <- st_polygon(pts))
-
-  ggplot() + 
-    geom_sf(data = a) + # the tree
-    geom_sf(data = ScndTrail) # the 2nd trail
+  PolList = list(pol1,pol2) #list of lists of numeric matrices
+  (ScndTrail = st_multipolygon(PolList))
 
@@
   Trail <- NearestPoint[[2]] # the point (Trail) on the ScndTrail closest to the location of the tree (Foot)
-
-  ggplot() + # plot 2 polygones
-    geom_sf(data = a) + # the tree (polygone)
-    geom_sf(data = Foot) + # the foot of the tree (point)
-    geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
-    geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail (linestring)
-    geom_sf(data = Trail) # the point on the ScndTrail closest to the location of the tree (Foot)
 
@@
 
-  TurnedTrunkA <- RotatePolygon(Trunk, angle = 60 - theta, fixed = Foot) # turned trunk
-  TurnedCrownA <- RotatePolygon(Crown, angle = 60 - theta, fixed = Foot) # turned crown
-  TurnedTrunkB <- RotatePolygon(Trunk, angle = 300 - theta, fixed = Foot) # turned trunk (angle in the clockwise direction: 360-60-theta)
-  TurnedCrownB <- RotatePolygon(Crown, angle = 300 - theta, fixed = Foot) # turned crown (angle in the clockwise direction)
+  # For a random direction felling
+  if(directionalfelling == "0" && (fuel !="1" |fuel !="2")){
+    RandomAngle <- sample(c(0:180), size = 1)
+    TrunkA <- RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot) # turned trunk
+    CrownA <- RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
+    TrunkB <- NULL
+    CrownB <- NULL
+  }
 
-  # For a random direction felling
-  RandomAngle <- sample(c(0:180), size = 1)
-  RandomTrunk <- RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot) # turned trunk
-  RandomCrown <- RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
+  # To direct only to avoid damage to future and reserve trees
+  # if (directionalfelling == "1"&& (fuel !="1" |fuel !="2")) {
+  #   
+  #   
+  # }
+
+  # To direct to avoid damage to future and reserve trees + track orientation. Winching: Foot before.
+  if(directionalfelling == "2"&& (fuel !="1" |fuel !="2")){
+    TrunkA <- RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot) # turned trunk
+    CrownA <- RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
+    TrunkB <- RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot) # turned trunk 
+    CrownB <- RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
+  }
+
+  # Fuelwood exploitation in the crowns
+  if(fuel =="1" |fuel =="2"){
+
+    TrailDist <- st_distance(Foot, Trail)
+
+    # ADD SLOPE CRITERIA !!!
+
+    if(TrailDist <= advancedloggingparameters$GrappleLength){ # <= 6m (= grapple length) -> winching by grapple
+      TrunkA <- RotatePolygon(Trunk, angle = theta + 60 , fixed = Foot) # turned trunk
+      CrownA <- RotatePolygon(Crown, angle = theta + 60 , fixed = Foot) # turned crown
+      TrunkB <- RotatePolygon(Trunk, angle = 300 + theta, fixed = Foot) # turned trunk
+      CrownB <- RotatePolygon(Crown, angle = 300 + theta, fixed = Foot) # turned crown
+    } else { # > 6m -> winching by cable
+      TrunkA <- RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot) # turned trunk
+      CrownA <- RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
+      TrunkB <- RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot) # turned trunk 
+      CrownB <- RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
+    }
+
+  }
 
@@
                         Trail = Trail,
-                        TurnedTrunkA = TurnedTrunkA,
-                        TurnedCrownA = TurnedCrownA,
-                        TurnedTrunkB = TurnedTrunkB,
-                        TurnedCrownB = TurnedCrownB,
-                        RandomTrunk = RandomTrunk,
-                        RandomCrown = RandomCrown)
+                        TrunkA = TrunkA,
+                        CrownA = CrownA,
+                        TrunkB = TrunkB,
+                        CrownB = CrownB)
 
@@
 AllTheFellingTrees <- lapply(EachTree, function(element)
-  felling(inventory, element))
+  felling(inventory, element,  fuel = "2", directionalfelling = "2"))
 
-# a <- st_union(st_union(AllTheFellingTrees[[1]]$a, AllTheFellingTrees[[2]]$a), AllTheFellingTrees[[3]]$a)
+a <- st_union(st_union(AllTheFellingTrees[[1]]$a, AllTheFellingTrees[[2]]$a), AllTheFellingTrees[[3]]$a)
 
-# Foot <- st_union(st_union(AllTheFellingTrees[[1]]$Foot, AllTheFellingTrees[[2]]$Foot), AllTheFellingTrees[[3]]$Foot)
+Foot <- st_union(st_union(AllTheFellingTrees[[1]]$Foot, AllTheFellingTrees[[2]]$Foot), AllTheFellingTrees[[3]]$Foot)
 
@@
 # Trail <- Trail
-TurnedTrunkA <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedTrunkA, AllTheFellingTrees[[2]]$TurnedTrunkA), AllTheFellingTrees[[3]]$TurnedTrunkA)
+TrunkA <- st_union(st_union(AllTheFellingTrees[[1]]$TrunkA, AllTheFellingTrees[[2]]$TrunkA), AllTheFellingTrees[[3]]$TrunkA)
 
-TurnedCrownA <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedCrownA, AllTheFellingTrees[[2]]$TurnedCrownA), AllTheFellingTrees[[3]]$TurnedCrownA)
+CrownA <- st_union(st_union(AllTheFellingTrees[[1]]$CrownA, AllTheFellingTrees[[2]]$CrownA), AllTheFellingTrees[[3]]$CrownA)
 
-TurnedTrunkB <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedTrunkB, AllTheFellingTrees[[2]]$TurnedTrunkB), AllTheFellingTrees[[3]]$TurnedTrunkB)
+TrunkB <- st_union(st_union(AllTheFellingTrees[[1]]$TrunkB, AllTheFellingTrees[[2]]$TrunkB), AllTheFellingTrees[[3]]$TrunkB)
 
-TurnedCrownB <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedCrownB, AllTheFellingTrees[[2]]$TurnedCrownB), AllTheFellingTrees[[3]]$TurnedCrownB)
-# RandomTrunk <- RandomTrunk
-# RandomCrown <- RandomCrown
+CrownB <- st_union(st_union(AllTheFellingTrees[[1]]$CrownB, AllTheFellingTrees[[2]]$CrownB), AllTheFellingTrees[[3]]$CrownB)
 
 ggplot() + # plot 2 polygones
-  # geom_sf(data = a) + # the tree (polygone)
-  # geom_sf(data = Foot) + # the foot of the tree (point)
+  geom_sf(data = a, colour = "red") + # default tree position (polygone)
+  geom_sf(data = Foot) + # the foot of the tree (point)
   geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
@@
   # geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
-  geom_sf(data = TurnedTrunkA) +
-  geom_sf(data = TurnedCrownA) +
-  geom_sf(data = TurnedTrunkB) +
-  geom_sf(data = TurnedCrownB)
-  # geom_sf(data = RandomTrunk) +
-  # geom_sf(data = RandomCrown)
+  geom_sf(data = TrunkA, colour = "green") + # Foot before
+  geom_sf(data = CrownA, colour = "green") +
+  geom_sf(data = TrunkB, colour = "green") +
+  geom_sf(data = CrownB, colour = "green")
 

### 2021-07-26 R/SpeciesCriteria.R

@@ -4,7 +4,6 @@
 #' @format A tibble with 72 rows and 8 variables:
 #' \describe{
 #'   \item{VernName}{Species vernacular/economic name (character)}
-#'   \item{ScientificName}{Species scientific name (character)}
 #'   \item{Genus}{Genus associated at the vernacular name (character)}
 #'   \item{Species}{Species (without genus part) associated at the vernacular name (character)}
 #'   \item{Commercial}{Economic interest level ("1" for principal economic species, "2" for a diversification goal) (factor)}

### 2021-07-27 R/DESIGNATION_DRAFT.Rmd
Corrections (cleaninventory)

@@
 
-inventory = addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))) #3539 rows (Paracou: 3620 rows)
+inventory = addtreedim(inventorycheckformat(Paracou6_2016))) #3539 rows (Paracou: 3620 rows)
 speciescriteria = SpeciesCriteria

### 2021-07-27 R/Draft_spatio.Rmd
Corrections (cleaninventory)

@@
 ```{r}
-inventory = ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))
+inventory = ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016))))
 

### 2021-07-27 R/inventorycheckformat.R

@@ -21,6 +21,24 @@ inventorycheckformat <- function(
   if (!inherits(inventory, "data.frame"))
     stop("inventory must be a data.frame")
 
+  # Global variables
+  Accessible <- Circ <- CircCorr <- CodeAlive <- Commercial <- NULL
+  Commercial.genus <- Commercial.species <- Condition <- DBH <- NULL
+  DeathCause <- DistCrit <- Family <- NULL
+  ForestZoneVolumeParametersTable <- Genus <- Logged <- NULL
+  LoggedVolume <- LoggingStatus <- MaxFD <- MaxFD.genus <- NULL
+  MaxFD.species <- MinFD <- MinFD.genus <- MinFD.species <- NULL
+  NoHollowLoggedVolume <- ParamCrownDiameterAllometry <- PlotSlope <- NULL
+  PlotTopo <- ProbedHollow <- ProbedHollowProba <- ScientificName <- NULL
+  Selected <- Slope <- SlopeCrit <- Species <- Species.genus <- NULL
+  SpeciesCriteria <- Taxo <- Taxo.family <- Taxo.genus <- Taxo.species <- NULL
+  TreeFellingOrientationSuccess <- TreeHarvestableVolume <- NULL
+  TreeHeight <- TrunkHeight <- Up <- UpMinFD <- UpMinFD.genus <- NULL
+  UpMinFD.species <- VernName.genus <- VernName.genus.genus <- NULL
+  VernName.species <- VolumeCumSum <- Xutm <- Yutm <- aCoef <- NULL
+  alpha <- alpha.family <- alpha.genus <- alpha.species <- bCoef <- NULL
+  beta.family <- beta.genus <- beta.species <- geometry <- idTree <- NULL
+
   # Variables presence check
   # (Plot, CensusYear, idTree, Family, Genus, Species, CircCorr, CodeAlive,
   # CommercialSp, UTMZone, Lat, Lon, VernName, Xfield, Yfield, Xutm, Yutm)
@@ -181,6 +199,38 @@ inventorycheckformat <- function(
   if(("DBH" %in% names(inventory) & !inherits(inventory$DBH, "numeric"))) {
     GoodData <- FALSE
     GeneralStop <- paste (GeneralStop, "DBH variable should be numeric.")
+  }
+
+  if (!GoodData)# inverse value of the object
+    stop(paste ("Your inventory does not comply.", GeneralStop))
+
+  #if DBH (cm) doesn't exist create it
[…]

### 2021-07-27 R/treeselection.R

@@ -62,7 +62,7 @@
 #' data(DemParacou)
 #' data(PlotSlope)
 #'
-#' inventory <- addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))
+#' inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
 #'
 #'treeselectionoutputs <- treeselection(inventory, objective = 20,
 #'scenario ="manual", fuel = "2", diversification = FALSE, specieslax = FALSE,

### 2021-07-27 tests/testthat/test-futurereserve.R

@@ -5,7 +5,7 @@ test_that("futurereserve", {
 
   data(DemParacou)
 
-  inventory <- ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))
+  inventory <- ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016)))
 
   harvestableOutputs <- harvestable(inventory, diversification = TRUE, specieslax = FALSE,
                                     DEM = DemParacou, plotslope = PlotSlope, advancedloggingparameters = loggingparameters())

### 2021-07-27 tests/testthat/test-selected.R

@@ -8,7 +8,7 @@ test_that("selected", {
   data(DemParacou)
   data(PlotSlope)
 
-  inventory <- ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))
+  inventory <- ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016)))
 
   harvestableOutputs <- harvestable(inventory, diversification = TRUE, specieslax = FALSE,
                                     DEM = DemParacou, plotslope = PlotSlope, advancedloggingparameters = loggingparameters())
@@ -70,7 +70,7 @@ test_that("selected", {
   VO <- HVinit + 20
 
   ## if (!diversification && specieslax)
-  inventory <- harvestable(ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))),
+  inventory <- harvestable(ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016))),
                            diversification = FALSE, specieslax = TRUE, DEM = DemParacou, plotslope = PlotSlope)$inventory
 
   testinventory <- suppressMessages(selected(inventory, scenario = "manual", fuel = "0",
@@ -88,7 +88,7 @@ test_that("selected", {
                "By default or by your choice, the simulation stops")
 
   # if (!diversification && !specieslax && objectivelax)
-  inventory <- harvestable(ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))),
+  inventory <- harvestable(ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016))),
                            diversification = FALSE,  specieslax = FALSE, DEM = DemParacou, plotslope = PlotSlope)$inventory
 
   expect_message(selected(inventory, scenario = "manual", fuel = "0", diversification = FALSE,  specieslax = FALSE, objectivelax = TRUE,
@@ -96,7 +96,7 @@ test_that("selected", {
                  "In this case you have chosen to continue logging without diversifying your species.")
 
   # if (diversification && objectivelax)
-  inventory <- harvestable(ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))),
+  inventory <- harvestable(ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016))),
[…]

### 2021-07-28 R/Treefelling_Sylvain's version.Rmd
Treefelling

---
title: "Treefelling_Sylvain's version"
author: "Vincyane Badouard"
date: "28/07/2021"
output: html_document
---

```{r}
inventory <- addtreedim(inventorycheckformat(Paracou6_2016))

inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
                           objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
                           advancedloggingparameters = loggingparameters())$inventory
```

# Create 2 polygons ScndTrail
```{r}

pol1 <- list(matrix(c(286503, 583134,
                      286503, 583240, 
                      286507, 583240, 
                      286507, 583134,
                      286503, 583134) # the return
                    ,ncol=2, byrow=TRUE)) 
pol2 <- list(matrix(c(286650, 583134,
                      286650, 583240, 
                      286654, 583240, 
                      286654, 583134,
                      286650, 583134) # the return
                    ,ncol=2, byrow=TRUE))

PolList = list(pol1,pol2) #list of lists of numeric matrices
ScndTrail = st_multipolygon(PolList)

```

# Succès-échec
```{r}
# Accessible <- Selected !!!!!!!!!!!! pas oublier pour if (fuel == "0" && directionalfelling != "0")

successfail <- function(
  inventory,
  fuel = "2",
  directionalfelling = "2",
  advancedloggingparameters = loggingparameters()) {

  if (fuel == "0" && directionalfelling != "0"){
    inventory <- inventory %>% 
      mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Accessible = linked by 2ndtrails

  }

  if (fuel =="1") {

    inventory <- inventory %>% 
      mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after

  }

  # Abattre les creux : 
  if (fuel =="2") {

    inventory <- inventory %>% 
      mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1"| ProbedHollow == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after

  }

  return(inventory)

}

```

# Rotation function

```{r}
RotatePolygon <- function(p, angle, fixed) { # angle in the clockwise direction
  p.coords <- sf::st_coordinates(p)[,1:2] # Polygone coordinates extraction
  p.center <- suppressWarnings(sf::st_coordinates(fixed))
  rotate.coords <- function(xy, a, center) {
    co <- cos(-a * pi / 180)
    si <- sin(-a * pi / 180)
    adj <- matrix(rep(center, nrow(xy)), ncol=2, byrow=TRUE) # matrix with fixed point coordinates
    xy <- xy-adj
    cbind(co * xy[,1] - si * xy[,2],si * xy[,1] + co * xy[,2]) + adj
  }
  p.rotate <- rotate.coords(p.coords, a = angle, center = c(p.center[1], 
                                                            p.center[2]))
  Turned <- sf::st_sfc(sf::st_polygon(list(p.rotate))) # create the turned polygon
  return(Turned)
}
```

# Tree creation function

```{r}

st_tree <- function(dat,
                    trail = ScndTrail,
                    fuel, 
                    directionalfelling, 
                    advancedloggingparameters = loggingparameters()){
  Crown <- dat %>% 
    mutate(xCrown = Xutm, 
           yCrown = Yutm + TrunkHeight + CrownHeight/2,
           exCrown = CrownDiameter/2,
           eyCrown = CrownHeight/2) %>% 
    st_as_sf(coords = c("xCrown", "yCrown")) # ellipse centroid coordinates
  Crown <- st_ellipse(Crown, Crown$exCrown, Crown$eyCrown) # create the ellipse
  Trunk <- with(dat, # and the trunk
                st_polygon(list(matrix(c(Xutm-(DBH/100)/2, Yutm, 
                                         Xutm-(DBH/100)/2, Yutm + TrunkHeight, 
                                         Xutm+(DBH/100)/2, Yutm + TrunkHeight, 
                                         Xutm+(DBH/100)/2, Yutm,
                                         Xutm-(DBH/100)/2, Yutm) # the return
                                       ,ncol=2, byrow=TRUE))))

  # Foot <- st_point(as.numeric(dat[,c("Xutm", "Yutm")])) # Tree coordinates (point)

  # Find the point (Trail) on the ScndTrail closest to the location of the tree (Foot)
  Foot <- st_point(c(dat$Xutm,dat$Yutm)) # tree foot point

  NearestPoints <- st_nearest_points(Foot, ScndTrail) # from the Foot of the tree to the ScndTrail (linestring)

  NearestPoint <- st_cast(NearestPoints, "POINT") # to have start (Foot) and end (Trail) points
  Trail <- NearestPoint[[2]] # the point (Trail) on the ScndTrail closest to the location of the tree (Foot)

  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], Foot[2] + dat$TreeHeight[1]),
                                    c(Foot[1] - Trail[1], Foot[2] -Trail[2]), degree = TRUE))

  # Scenarios
  # For a random direction felling
  if(directionalfelling == "0" && (fuel !="1" |fuel !="2")){
    RandomAngle <- sample(c(0:180), size = 1)
    A <- st_difference(st_union(
      RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
      RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
    )) 
  }

  # To direct only to avoid damage to future and reserve trees
  # if (directionalfelling == "1"&& (fuel !="1" |fuel !="2")) {
  #   if(dat$TreeFellingOrientationSuccess == 1){

  # }else{ # else random felling
  # RandomAngle <- sample(c(0:180), size = 1)
  #   A <- st_difference(st_union(
  #   RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
  #   RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
  #   ))
  # }
  #   
  # }

  # To direct to avoid damage to future and reserve trees + track orientation. Winching: Foot before.
  if(directionalfelling == "2"&& (fuel !="1" |fuel !="2")){
    if(dat$TreeFellingOrientationSuccess == 1){
      A <- st_difference(st_union(
        RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
        RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
      ))
      B <- st_difference(st_union(
        RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
        RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
      ))
    }else{ # else random felling
      RandomAngle <- sample(c(0:180), size = 1)

      A <- st_difference(st_union(
        RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
        RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
      ))
    }

  }

  # Fuelwood exploitation in the crowns
  if(fuel =="1" |fuel =="2"){

    TrailDist <- st_distance(Foot, Trail)

    # ADD SLOPE CRITERIA !!!

    if(dat$TreeFellingOrientationSuccess == 1){

      if(TrailDist <= advancedloggingparameters$GrappleLength){ # <= 6m (= grapple length) -> winching by grapple
        A <- st_difference(st_union(
          RotatePolygon(Trunk, angle = theta + 60 , fixed = Foot), # turned trunk
          RotatePolygon(Crown, angle = theta + 60 , fixed = Foot) # turned crown
        ))
        B <- st_difference(st_union(
          RotatePolygon(Trunk, angle = 300 + theta, fixed = Foot), # turned trunk
          RotatePolygon(Crown, angle = 300 + theta, fixed = Foot) # turned crown
        ))
      } else { # > 6m -> winching by cable
        A <- st_difference(st_union(
          RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
          RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
        ))
        B <- st_difference(st_union(
          RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
          RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
        ))
      }
    }else{ # else random felling
      RandomAngle <- sample(c(0:180), size = 1)
      A <- st_difference(st_union(
        RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
        RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
      ))
    }

  }

  FellingOuputs <- list(Foot = Foot,
                        NearestPoints = NearestPoints,
                        Trail = Trail,
                        A = A)

  return(FellingOuputs)

}

```

# Application
```{r}

# Compute fellingtree succes and fails
inventory <- successfail(
  inventory,
  fuel = "2",
  directionalfelling = "2",
  advancedloggingparameters = loggingparameters())

# Only selected trees
SelectedTrees <- inventory %>% 
  filter(Selected == "1") %>%
  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm, TreeFellingOrientationSuccess)

NearestPoints <- SelectedTrees %>%
  group_by(idTree) %>% 
  do(geometry = st_tree(., fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$NearestPoints) %>% 
  mutate(geometry = as(geometry, "sfc_LINESTRING")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf()

# Application in a dataframe
FellingTrees <- SelectedTrees %>% 
  # mutate(angle = list(c(0, 30))) %>% # for each row, a list of 2 values -> a dataframe in a dataframe
  # unnest(angle) %>% # display the small dataframe in the big dataframe in one
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry = st_tree(., fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$A) %>% # inform geometry. # Filling a column from a function whose input is a table
  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf()

# Marche pas encore
FellingTrees <- inventory %>% 
  # mutate(angle = list(c(0, 30))) %>% # for each row, a list of 2 values -> a dataframe in a dataframe
  # unnest(angle) %>% # display the small dataframe in the big dataframe in one
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry = ifelse(!is.na(TreeFellingOrientationSuccess),
       st_tree(., fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$A, NULL)) %>% # inform geometry. # Filling a column from a function whose input is a table
  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf()

# or version more Sf (to test)
# pol <- st_as_sf(SelectedTrees, 
#                 as(geometry = st_as_sfc(
#                   lapply(split(SelectedTrees, SelectedTrees$idTree), st_tree(30))
#                 )
#                 , "sfc_MULTIPOLYGON")
# )

ggplot() +
  # geom_sf(data = Foot) +
  geom_sf(data = ScndTrail) +
  geom_sf(data = NearestPoints) +
  # geom_sf(data = Trail) +
  geom_sf(data = FellingTrees)
```

### 2021-07-28 R/Treefelling_test_for all trees.Rmd
Corrections (cleaninventory)
Treefelling

@@
 ```{r Give values to the arguments to work}
-data(Paracou6_2016)
-data(DemParacou)
 
-inventory <- addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))
+inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
 
@@
 
+# Succès-échec
 ```{r}
-felling <- function (inventory, SelectedTrees, fuel, directionalfelling, advancedloggingparameters = loggingparameters()) {
+# Selected <-  Accessible
+
+successfail <- function(
+  inventory,
+  fuel = "2",
+  directionalfelling = "2",
+  advancedloggingparameters = loggingparameters()) {
+
+  if (fuel == "0" && directionalfelling != "1"){
+    inventory <- inventory %>% 
+      mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Accessible = linked by 2ndtrails
+
+    #Tree coordinates 
+    if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {
+
+      TreefallSuccessCoord <- inventory %>% 
+        filter(TreeFellingOrientationSuccess == "1") %>% 
+        select(Xutm, Yutm)
+
+      TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
+    }
+
+    if (any(inventory$TreeFellingOrientationSuccess == "0", na.rm = TRUE)) {
+      TreefallFailCoord <- inventory %>% 
+        filter(TreeFellingOrientationSuccess == "0") %>% 
+        select(Xutm, Yutm)
+
+      TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails
+
+    }
+
+  }
+
+  if (fuel =="1") {
+
+    inventory <- inventory %>% 
+      mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
+
+    #Tree coordinates 
+    if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {
+
+      TreefallSuccessCoord <- inventory %>% 
+        filter(TreeFellingOrientationSuccess == "1") %>% 
+        select(Xutm, Yutm)
+
+      TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
+    }
+
+    if (any(inventory$TreeFellingOrientationSuccess == "0", na.rm = TRUE)) {
+      TreefallFailCoord <- inventory %>% 
+        filter(TreeFellingOrientationSuccess == "0") %>% 
+        select(Xutm, Yutm)
+
+      TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails
+
+    }
+  }
+
+  # Abattre les creux : 
+  if (fuel =="2") {
+
+    inventory <- inventory %>% 
+      mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1"| ProbedHollow == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after
+
+    #Tree coordinates 
+    if (any(inventory$TreeFellingOrientationSuccess == "1", na.rm = TRUE)) {
+
+      TreefallSuccessCoord <- inventory %>% 
+        filter(TreeFellingOrientationSuccess == "1") %>% 
+        select(Xutm, Yutm)
+
+      TreefallSuccess  <- st_multipoint(x = as.matrix(TreefallSuccessCoord))   # Create treefelling success
+    }
+
+    if (any(inventory$TreeFellingOrientationSuccess == "0", na.rm = TRUE)) {
+      TreefallFailCoord <- inventory %>% 
+        filter(TreeFellingOrientationSuccess == "0") %>% 
+        select(Xutm, Yutm)
+
+      TreefallFailure  <- st_multipoint(x = as.matrix(TreefallFailCoord))      # Create treefelling fails
+
+    }
+  }
+
+  treefellingOutputs <- list(inventory = inventory,
+                             TreefallSuccess = TreefallSuccess,
+                             TreefallFailure = TreefallFailure)
+
+  return(treefellingOutputs)
+
+}
+
+successfailOutputs <- successfail( #an inventory and 2 multipoints: 1 for success, 1 for fails
+  inventory,
+  fuel = "2",
+  directionalfelling = "2",
+  advancedloggingparameters = loggingparameters())
+
+inventory <- successfailOutputs$inventory
+```
+
+```{r}
+felling <- function (inventory, 
+                     SelectedTrees, 
+                     fuel, 
+                     directionalfelling, 
+                     advancedloggingparameters = loggingparameters()
+) {
 
@@
     RandomAngle <- sample(c(0:180), size = 1)
-    TrunkA <- RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot) # turned trunk
-    CrownA <- RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
-    TrunkB <- NULL
-    CrownB <- NULL
+    A <- st_difference(st_union(
+      RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
+      RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
+    )) 
+    B <- NULL
   }
@@
   if(directionalfelling == "2"&& (fuel !="1" |fuel !="2")){
-    TrunkA <- RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot) # turned trunk
-    CrownA <- RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
-    TrunkB <- RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot) # turned trunk 
-    CrownB <- RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
+    A <- st_difference(st_union(
+      RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
+      RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
+    ))
+    B <- st_difference(st_union(
+      RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
+      RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
+    ))
   }
@@
     if(TrailDist <= advancedloggingparameters$GrappleLength){ # <= 6m (= grapple length) -> winching by grapple
-      TrunkA <- RotatePolygon(Trunk, angle = theta + 60 , fixed = Foot) # turned trunk
-      CrownA <- RotatePolygon(Crown, angle = theta + 60 , fixed = Foot) # turned crown
-      TrunkB <- RotatePolygon(Trunk, angle = 300 + theta, fixed = Foot) # turned trunk
-      CrownB <- RotatePolygon(Crown, angle = 300 + theta, fixed = Foot) # turned crown
+      A <- st_difference(st_union(
+        RotatePolygon(Trunk, angle = theta + 60 , fixed = Foot), # turned trunk
+        RotatePolygon(Crown, angle = theta + 60 , fixed = Foot) # turned crown
+      ))
+      B <- st_difference(st_union(
+        RotatePolygon(Trunk, angle = 300 + theta, fixed = Foot), # turned trunk
+        RotatePolygon(Crown, angle = 300 + theta, fixed = Foot) # turned crown
+      ))
     } else { # > 6m -> winching by cable
-      TrunkA <- RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot) # turned trunk
-      CrownA <- RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
-      TrunkB <- RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot) # turned trunk 
-      CrownB <- RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
+      A <- st_difference(st_union(
+        RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
+        RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
+      ))
+      B <- st_difference(st_union(
+        RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
+        RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
+      ))
     }
@@
                         Trail = Trail,
-                        TrunkA = TrunkA,
-                        CrownA = CrownA,
-                        TrunkB = TrunkB,
-                        CrownB = CrownB)
+                        A = A,
+                        B = B)
 
@@
 
+# Application
 ```{r}
@@
 # Trail <- Trail
-TrunkA <- st_union(st_union(AllTheFellingTrees[[1]]$TrunkA, AllTheFellingTrees[[2]]$TrunkA), AllTheFellingTrees[[3]]$TrunkA)
+A <- st_union(st_union(AllTheFellingTrees[[1]]$A, AllTheFellingTrees[[2]]$A), AllTheFellingTrees[[3]]$A)
 
-CrownA <- st_union(st_union(AllTheFellingTrees[[1]]$CrownA, AllTheFellingTrees[[2]]$CrownA), AllTheFellingTrees[[3]]$CrownA)
-
-TrunkB <- st_union(st_union(AllTheFellingTrees[[1]]$TrunkB, AllTheFellingTrees[[2]]$TrunkB), AllTheFellingTrees[[3]]$TrunkB)
-
-CrownB <- st_union(st_union(AllTheFellingTrees[[1]]$CrownB, AllTheFellingTrees[[2]]$CrownB), AllTheFellingTrees[[3]]$CrownB)
+B <- st_union(st_union(AllTheFellingTrees[[1]]$B, AllTheFellingTrees[[2]]$B), AllTheFellingTrees[[3]]$B)
 
@@
   # geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
-  geom_sf(data = TrunkA, colour = "green") + # Foot before
-  geom_sf(data = CrownA, colour = "green") +
-  geom_sf(data = TrunkB, colour = "green") +
-  geom_sf(data = CrownB, colour = "green")
+  geom_sf(data = A, colour = "green") + # Foot before
+  geom_sf(data = B, colour = "green")
 

### 2021-07-29 R/Treefelling_Sylvain's version.Rmd
Treefelling functions

@@
 
-# Create 2 polygons ScndTrail
+# Create a MainTrail and 2 polygons ScndTrail
 ```{r}
+MainTrail <- sf::st_linestring(matrix(c(286400, 583130,
+                                        286400, 583250,
+                                        286655, 583250,
+                                        286655, 583130,
+                                        286400, 583130) # the return
+                                      ,ncol=2, byrow=TRUE))
 
@@
   inventory,
-  fuel = "2",
-  directionalfelling = "2",
+  fuel,
+  directionalfelling,
   advancedloggingparameters = loggingparameters()) {
+
+  if (fuel == "0" && directionalfelling == "0"){
+    inventory <- inventory %>% 
+      mutate(TreeFellingOrientationSuccess = 0)
+  }
 
@@
 
+  inventory$TreeFellingOrientationSuccess <- as.character(inventory$TreeFellingOrientationSuccess)
+
   return(inventory)
@@
 ```{r}
-RotatePolygon <- function(p, angle, fixed) { # angle in the clockwise direction
+rotatepolygon <- function(p, angle, fixed) { # angle in the clockwise direction
   p.coords <- sf::st_coordinates(p)[,1:2] # Polygone coordinates extraction
@@
 ```{r}
-
+dat <- SelectedTrees[1,]
 st_tree <- function(dat,
-                    trail = ScndTrail,
+                    ScndTrail = ScndTrail,
+                    MainTrail = MainTrail,
                     fuel, 
@@
                     advancedloggingparameters = loggingparameters()){
+
+  Trail <- st_union(MainTrail, ScndTrail) # Our trail will be MainTrail or ScndTrail
+
   Crown <- dat %>% 
@@
 
-  # Find the point (Trail) on the ScndTrail closest to the location of the tree (Foot)
+  # Find the point (TrailPt) on the Trail closest to the location of the tree (Foot)
   Foot <- st_point(c(dat$Xutm,dat$Yutm)) # tree foot point
 
-  NearestPoints <- st_nearest_points(Foot, ScndTrail) # from the Foot of the tree to the ScndTrail (linestring)
+  NearestPoints <- st_nearest_points(Foot, Trail) # from the Foot of the tree to the Trail (linestring)
 
-  NearestPoint <- st_cast(NearestPoints, "POINT") # to have start (Foot) and end (Trail) points
-  Trail <- NearestPoint[[2]] # the point (Trail) on the ScndTrail closest to the location of the tree (Foot)
+  NearestPoint <- st_cast(NearestPoints, "POINT") # to have start (Foot) and end (TrailPt) points
+  TrailPt <- NearestPoint[[2]] # the point (TrailPt) on the Trail closest to the location of the tree (Foot)
 
   theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], Foot[2] + dat$TreeHeight[1]),
-                                    c(Foot[1] - Trail[1], Foot[2] -Trail[2]), degree = TRUE))
+                                    c(Foot[1] - TrailPt[1], Foot[2] -TrailPt[2]), degree = TRUE))
 
@@
     A <- st_difference(st_union(
-      RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
-      RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
+      rotatepolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
+      rotatepolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
     )) 
@@
   # if (directionalfelling == "1"&& (fuel !="1" |fuel !="2")) {
-  #   if(dat$TreeFellingOrientationSuccess == 1){
+  #   if(dat$TreeFellingOrientationSuccess == "1"){
 
@@
   #   A <- st_difference(st_union(
-  #   RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
-  #   RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
+  #   rotatepolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
+  #   rotatepolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
   #   ))
@@
   if(directionalfelling == "2"&& (fuel !="1" |fuel !="2")){
-    if(dat$TreeFellingOrientationSuccess == 1){
+    if(dat$TreeFellingOrientationSuccess == "1"){
       A <- st_difference(st_union(
-        RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
-        RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
+        rotatepolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
+        rotatepolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
       ))
       B <- st_difference(st_union(
-        RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
-        RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
+        rotatepolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
+        rotatepolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
       ))
@@
       A <- st_difference(st_union(
-        RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
-        RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
+        rotatepolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
+        rotatepolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
       ))
@@
 
-    TrailDist <- st_distance(Foot, Trail)
+    TrailDist <- st_distance(Foot, TrailPt)
 
@@
 
-    if(dat$TreeFellingOrientationSuccess == 1){
+    if(dat$TreeFellingOrientationSuccess == "1"){
 
@@
         A <- st_difference(st_union(
-          RotatePolygon(Trunk, angle = theta + 60 , fixed = Foot), # turned trunk
-          RotatePolygon(Crown, angle = theta + 60 , fixed = Foot) # turned crown
+          rotatepolygon(Trunk, angle = theta + 60 , fixed = Foot), # turned trunk
+          rotatepolygon(Crown, angle = theta + 60 , fixed = Foot) # turned crown
         ))
         B <- st_difference(st_union(
-          RotatePolygon(Trunk, angle = 300 + theta, fixed = Foot), # turned trunk
-          RotatePolygon(Crown, angle = 300 + theta, fixed = Foot) # turned crown
+          rotatepolygon(Trunk, angle = 300 + theta, fixed = Foot), # turned trunk
+          rotatepolygon(Crown, angle = 300 + theta, fixed = Foot) # turned crown
         ))
@@
         A <- st_difference(st_union(
-          RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
-          RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
+          rotatepolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
+          rotatepolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
         ))
         B <- st_difference(st_union(
-          RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
-          RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
+          rotatepolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
+          rotatepolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
         ))
@@
                         NearestPoints = NearestPoints,
-                        Trail = Trail,
+                        TrailPt = TrailPt,
                         A = A)
@@
 
+# To extract de the shortest ways
 NearestPoints <- SelectedTrees %>%
   group_by(idTree) %>% 
-  do(geometry = st_tree(., fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$NearestPoints) %>% 
+  do(geometry = st_tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$NearestPoints) %>% 
   mutate(geometry = as(geometry, "sfc_LINESTRING")) %>% # list -> sfc_MULTIPOLYGON
@@
   group_by(idTree) %>% # for each tree and each given angle 
-  do(geometry = st_tree(., fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$A) %>% # inform geometry. # Filling a column from a function whose input is a table
+  do(geometry = st_tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$A) %>% # inform geometry.
+# Filling a column from a function whose input is a table
   mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
@@
 FellingTrees <- inventory %>% 
-  # mutate(angle = list(c(0, 30))) %>% # for each row, a list of 2 values -> a dataframe in a dataframe
-  # unnest(angle) %>% # display the small dataframe in the big dataframe in one
   group_by(idTree) %>% # for each tree and each given angle 
-  do(geometry = ifelse(!is.na(TreeFellingOrientationSuccess),
-       st_tree(., fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$A, NULL)) %>% # inform geometry. # Filling a column from a function whose input is a table
+  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
+       ifelse(!is.na(.$TreeFellingOrientationSuccess),
+              st_tree(.,
+                      ScndTrail = ScndTrail,
+                      MainTrail = MainTrail,
+                      fuel = "2", directionalfelling ="2",
+                      advancedloggingparameters = loggingparameters())$A,
+              NULL)) %>%
   mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
@@
   # geom_sf(data = Foot) +
-  geom_sf(data = ScndTrail) +
+  geom_sf(data = Trail) +
   geom_sf(data = NearestPoints) +
-  # geom_sf(data = Trail) +
+  # geom_sf(data = TrailPt) +
   geom_sf(data = FellingTrees)
 ```
+
+```{r}
+st_tree(SelectedTrees[1,],
+        ScndTrail = ScndTrail,
+        MainTrail = MainTrail,
+        fuel = "2", directionalfelling ="2",
+        advancedloggingparameters = loggingparameters())$A
+
+FellingTrees <- inventory %>%
+  group_by(idTree) %>% 
+  mutate(geometry =
+           ifelse(!is.na(TreeFellingOrientationSuccess),
+                  "A", "B"))
+
+FellingTrees <- inventory %>%
+  group_by(idTree) %>% 
+  do(geometry =
+       ifelse(!is.na(.$TreeFellingOrientationSuccess),
+              tolower("A"), "B"))
+
+FellingTrees <- inventory %>% 
+  group_by(idTree) %>% # for each tree and each given angle 
+  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
+       ifelse(!is.na(.$TreeFellingOrientationSuccess),
+              st_tree(.,
+                      ScndTrail = ScndTrail,
+                      MainTrail = MainTrail,
+                      fuel = "2", directionalfelling ="2",
+                      advancedloggingparameters = loggingparameters())$A,
+              NULL)) %>%
+  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
+  st_as_sf()
+
+felttress <- NA
+inventory %>% 
+  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
+  group_by(idTree) %>% # for each tree and each given angle 
+  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
+       st_tree(.,
+               ScndTrail = ScndTrail,
+               MainTrail = MainTrail,
+               fuel = "2", directionalfelling = "2",
+               advancedloggingparameters = loggingparameters())$A) %>%
+  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
+  st_as_sf() %>% 
+  mutate(geometry = st_as_text(geometry))
+
+left_join(inventory, poly) %>% 
+  ggplot() +
+  geom_sf()
+
+?sf
+st_as_text(poly$geometry)
+
+felttrees <- inventory %>% 
+  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
+  group_by(idTree) %>% 
+  do(treepolygon = 
+       st_tree(.,
+               ScndTrail = ScndTrail,
+               MainTrail = MainTrail,
+               fuel = "2", directionalfelling = "2",
+               advancedloggingparameters = loggingparameters())$A %>% 
+       st_as_text()) %>% 
+  unnest(treepolygon)
+
+inventory2 <- left_join(inventory, felttrees)
+
+get_treepolygon <- function(inventory){
+  inventory %>% 
+    filter(!is.na(treepolygon)) %>%
+    st_as_sf(wkt = "treepolygon")
+}
+
+ggplot() +
+  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
+  geom_sf(data = get_treepolygon(inventory2), fill = "red")
+
+st_intersection(
+  get_treepolygon(inventory2),
+  st_as_sf(inventory, coords = c("Xutm", "Yutm"))
+) %>% 
+  ggplot() +
+  geom_sf()
+```

### 2021-07-29 R/DraftFunctions.Rmd
Treefelling functions

--- 2021-07-06 R/DraftFunctions.Rmd
@@
 library(sf)
+library(nngeo)
+library(raster)
+library(topoDistance)
+library(BIOMASS)
 ```

### 2021-07-29 R/Treefelling_Sylvain's version.Rmd
Treefelling functions

@@
 ```{r}
-dat <- SelectedTrees[1,]
 st_tree <- function(dat,
@@
 
-# Marche pas encore
-FellingTrees <- inventory %>% 
-  group_by(idTree) %>% # for each tree and each given angle 
-  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
-       ifelse(!is.na(.$TreeFellingOrientationSuccess),
-              st_tree(.,
-                      ScndTrail = ScndTrail,
-                      MainTrail = MainTrail,
-                      fuel = "2", directionalfelling ="2",
-                      advancedloggingparameters = loggingparameters())$A,
-              NULL)) %>%
-  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
-  st_as_sf()
-
 # or version more Sf (to test)
@@
   # geom_sf(data = Foot) +
-  geom_sf(data = Trail) +
+  geom_sf(data = ScndTrail) +
+  geom_sf(data = MainTrail) +
   geom_sf(data = NearestPoints) +
@@
 ```{r}
-st_tree(SelectedTrees[1,],
-        ScndTrail = ScndTrail,
-        MainTrail = MainTrail,
-        fuel = "2", directionalfelling ="2",
-        advancedloggingparameters = loggingparameters())$A
-
-FellingTrees <- inventory %>%
-  group_by(idTree) %>% 
-  mutate(geometry =
-           ifelse(!is.na(TreeFellingOrientationSuccess),
-                  "A", "B"))
-
-FellingTrees <- inventory %>%
-  group_by(idTree) %>% 
-  do(geometry =
-       ifelse(!is.na(.$TreeFellingOrientationSuccess),
-              tolower("A"), "B"))
-
-FellingTrees <- inventory %>% 
-  group_by(idTree) %>% # for each tree and each given angle 
-  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
-       ifelse(!is.na(.$TreeFellingOrientationSuccess),
-              st_tree(.,
-                      ScndTrail = ScndTrail,
-                      MainTrail = MainTrail,
-                      fuel = "2", directionalfelling ="2",
-                      advancedloggingparameters = loggingparameters())$A,
-              NULL)) %>%
-  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
-  st_as_sf()
 
 felttress <- NA
-inventory %>% 
-  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
-  group_by(idTree) %>% # for each tree and each given angle 
-  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
-       st_tree(.,
-               ScndTrail = ScndTrail,
-               MainTrail = MainTrail,
-               fuel = "2", directionalfelling = "2",
-               advancedloggingparameters = loggingparameters())$A) %>%
-  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
-  st_as_sf() %>% 
-  mutate(geometry = st_as_text(geometry))
 
-left_join(inventory, poly) %>% 
-  ggplot() +
-  geom_sf()
+# Compute fellingtree succes and fails
+inventory <- successfail(
+  inventory,
+  fuel = "2",
+  directionalfelling = "2",
+  advancedloggingparameters = loggingparameters())
 
-?sf
-st_as_text(poly$geometry)
+# poly <- inventory %>% 
+#   filter(!is.na(TreeFellingOrientationSuccess)) %>% 
+#   group_by(idTree) %>% # for each tree 
+#   do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
+#        st_tree(.,
+#                ScndTrail = ScndTrail,
+#                MainTrail = MainTrail,
+#                fuel = "2", directionalfelling = "2",
+#                advancedloggingparameters = loggingparameters())$A) %>%
+#   mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
+#   st_as_sf() %>% 
+#   mutate(geometry = st_as_text(geometry)) # as text to easy join with a non spacial table
+# 
+# 
+# left_join(inventory, poly) %>% 
+#   ggplot() +
+#   geom_sf()
+# 
+# st_as_text(poly$geometry)
 
@@
   filter(!is.na(TreeFellingOrientationSuccess)) %>% 
-  group_by(idTree) %>% 
-  do(treepolygon = 
+  group_by(idTree) %>% # for each tree
+  do(treepolygon = # inform geometry. # Filling a column from a function whose input is a table
        st_tree(.,
@@
                advancedloggingparameters = loggingparameters())$A %>% 
-       st_as_text()) %>% 
-  unnest(treepolygon)
+       st_as_text())  # as text to easy join with a non spacial table
+  # unnest(treepolygon) # display the small dataframe in the big dataframe in one
 
-inventory2 <- left_join(inventory, felttrees)
+inventory <- left_join(inventory, felttrees) # join spatial filtered inventory and non spatial complete inventory
 
-get_treepolygon <- function(inventory){
+get_treepolygon <- function(inventory){ # function from text (wkt) to sf
   inventory %>% 
@@
 ggplot() +
-  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
-  geom_sf(data = get_treepolygon(inventory2), fill = "red")
+  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) + # all the individuals of the plot
+  geom_sf(data = get_treepolygon(inventory), fill = "red") # trees polygons
 
-st_intersection(
-  get_treepolygon(inventory2),
+st_intersection( # trees under the fallen trees
+  get_treepolygon(inventory),
   st_as_sf(inventory, coords = c("Xutm", "Yutm"))

### 2021-07-29 R/addtreedim.R

@@ -16,10 +16,14 @@
 #'
 #' @export
 #' @import dplyr
+#' @importFrom dplyr select
 #' @importFrom dplyr left_join
 #' @importFrom dplyr mutate
+#' @importFrom dplyr rename
 #' @importFrom tidyr unite
 #' @importFrom rlang .data
+#' @importFrom BIOMASS getWoodDensity
+#' @importFrom BIOMASS computeAGB
 #'
 #' @examples
 #' data(Paracou6_2016)
@@ -66,18 +70,19 @@ addtreedim <- function(
   VernName.species <- VolumeCumSum <- Xutm <- Yutm <- aCoef <- NULL
   alpha <- alpha.family <- alpha.genus <- alpha.species <- bCoef <- NULL
   beta.family <- beta.genus <- beta.species <- geometry <- idTree <- NULL
+  genus <- species <- meanWD <- levelWD <- WoodDensity <- NULL
 
   # Crown diameter allometry parameters data preparation:
 
   spParamCrownDiameter <- crowndiameterparameters %>% #parameters at species scale
     filter(Taxo == "sp") %>%
-    select(-Family)
+    dplyr::select(-Family)
   genParamCrownDiameter <- crowndiameterparameters %>% #parameters at genus scale
     filter(Taxo == "gen") %>%
-    select(-Family, -ScientificName, -Species)
+    dplyr::select(-Family, -ScientificName, -Species)
   famParamCrownDiameter <- crowndiameterparameters %>% #parameters at family scale
     filter(Taxo == "fam") %>%
-    select(-Genus, -ScientificName, -Species)
+    dplyr::select(-Genus, -ScientificName, -Species)
 
 
   # Variables computation:
@@ -121,20 +126,45 @@ addtreedim <- function(
     mutate(alpha = ifelse(is.na(alpha), alpha.genus, alpha)) %>% #if species parameters are absent, take genus parameters
     mutate(alpha = ifelse(is.na(alpha), alpha.family, alpha)) %>% #if species&genus parameters are absent, take family parameters
     mutate(alpha = ifelse(is.na(alpha), mean(alpha, na.rm =T), alpha)) %>% #if species,genus&family parameters are absent, take parameters mean
-    select(-alpha.species, -alpha.genus, -alpha.family) %>% #remove obsolete columns
+    dplyr::select(-alpha.species, -alpha.genus, -alpha.family) %>% #remove obsolete columns
     # beta:
[…]

### 2021-07-29 tests/testthat/test-st_tree.R

@@ -1,0 +1,12 @@
+# test_that("st_tree", {
+# })
+
+
+# check args errors
+# results:
+# $Foot is a POINT,
+# $NearestPoints is a LINESTRING,
+# $TrailPt is a POINT,
+# $Trail is a multipolygon,
+# $A is multipolygons
+# check the angle

### 2021-07-30 R/Treefelling_Sylvain's version.Rmd

--- 2021-07-29 R/Treefelling_Sylvain's version.Rmd
@@
 # Filling a column from a function whose input is a table
-  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
-  st_as_sf()
-
-# Marche pas encore
-FellingTrees <- inventory %>% 
-  group_by(idTree) %>% # for each tree and each given angle 
-  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
-       ifelse(!is.na(.$TreeFellingOrientationSuccess),
-              st_tree(.,
-                      ScndTrail = ScndTrail,
-                      MainTrail = MainTrail,
-                      fuel = "2", directionalfelling ="2",
-                      advancedloggingparameters = loggingparameters())$A,
-              NULL)) %>%
-  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
-  st_as_sf()
 
@@
   # geom_sf(data = Foot) +
-  geom_sf(data = Trail) +
-  geom_sf(data = NearestPoints) +
   # geom_sf(data = TrailPt) +
@@
 ```{r}
+
 st_tree(SelectedTrees[1,],
@@
   filter(!is.na(TreeFellingOrientationSuccess)) %>%
-  group_by(idTree) %>% 
-  do(treepolygon = 
+
        st_tree(.,
@@
                advancedloggingparameters = loggingparameters())$A %>% 
+       st_as_text())  # as text to easy join with a non spacial table
+  # unnest(treepolygon) # display the small dataframe in the big dataframe in one
+
+inventory <- left_join(inventory, felttrees) # join spatial filtered inventory and non spatial complete inventory
+
+get_treepolygon <- function(inventory){ # function from text (wkt) to sf
        st_as_text()) %>% 
@@
 ggplot() +
+  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) + # all the individuals of the plot
+  geom_sf(data = get_treepolygon(inventory), fill = "red") # trees polygons
+
+st_intersection( # trees under the fallen trees
+  get_treepolygon(inventory),
   geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +

### 2021-08-04 R/Treefelling_Sylvain's version.Rmd
get_geometry and import functions not package

@@
 
-  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], Foot[2] + dat$TreeHeight[1]),
-                                    c(Foot[1] - TrailPt[1], Foot[2] -TrailPt[2]), degree = TRUE))
+  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
+                                    c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
 
@@
 
+library(ggplot2)
 ggplot() +
-  # geom_sf(data = Foot) +
-  # geom_sf(data = TrailPt) +
-  geom_sf(data = FellingTrees)
+  geom_sf(data = st_union(Trunk, Crown), colour = "red") +
+  geom_sf(data = Foot) +
+  geom_sf(data = Trail) +
+  geom_sf(data = TrailPt) +
+  geom_sf(data = NearestPoints) +
+  geom_sf(data = A)+
+  geom_sf(data = B)
+
 ```
@@
 ```{r}
-
-st_tree(SelectedTrees[1,],
-        ScndTrail = ScndTrail,
-        MainTrail = MainTrail,
-        fuel = "2", directionalfelling ="2",
-        advancedloggingparameters = loggingparameters())$A
-
-FellingTrees <- inventory %>%
-  group_by(idTree) %>% 
-  mutate(geometry =
-           ifelse(!is.na(TreeFellingOrientationSuccess),
-                  "A", "B"))
-
-FellingTrees <- inventory %>%
-  group_by(idTree) %>% 
-  do(geometry =
-       ifelse(!is.na(.$TreeFellingOrientationSuccess),
-              tolower("A"), "B"))
 
@@
 
-?sf
 st_as_text(poly$geometry)
@@
   filter(!is.na(TreeFellingOrientationSuccess)) %>% 
-
   st_tree(.,
@@
           advancedloggingparameters = loggingparameters())$A %>% 
-       st_as_text())  # as text to easy join with a non spacial table
+  st_as_text()  # as text to easy join with a non spacial table
 # unnest(treepolygon) # display the small dataframe in the big dataframe in one
@@
 
-get_treepolygon <- function(inventory){ # function from text (wkt) to sf
-       st_as_text()) %>% 
+get_geometry <- function(inventory){ # function from text (wkt) to sf
+  st_as_text() %>% 
     unnest(treepolygon)
+}
 
@@
 
-get_treepolygon <- function(inventory){
+get_geometry <- function(inventory){
   inventory %>% 
@@
   geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) + # all the individuals of the plot
-  geom_sf(data = get_treepolygon(inventory), fill = "red") # trees polygons
+  geom_sf(data = get_geometry(inventory), fill = "red") # trees polygons
 
 st_intersection( # trees under the fallen trees
-  get_treepolygon(inventory),
+  get_geometry(inventory),
   geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
-  geom_sf(data = get_treepolygon(inventory2), fill = "red")
+    geom_sf(data = get_geometry(inventory2), fill = "red"))
 
 st_intersection(
-  get_treepolygon(inventory2),
+  get_geometry(inventory2),
   st_as_sf(inventory, coords = c("Xutm", "Yutm"))
@@
 ```
+```{r}
+inventory <- successfail(
+  inventory,
+  fuel = "2", directionalfelling = "2",
+  advancedloggingparameters = loggingparameters())
+
+# Treefelling
+felttrees <- inventory %>%
+  filter(!is.na(TreeFellingOrientationSuccess)) %>%
+  group_by(idTree) %>% # for each tree
+  do(TreePolygon = # inform geometry. # Filling a column from a function whose input is a table
+       st_tree(.,
+               fuel = "2", directionalfelling = "2",
+               MainTrail = MainTrail, ScndTrail = ScndTrail,
+               advancedloggingparameters = loggingparameters())$A %>%
+       st_as_text()) %>% # as text to easy join with a non spacial table
+  tidyr::unnest(TreePolygon) # here to pass from list to character
+
+inventory <- left_join(inventory, felttrees, by = "idTree") # join spatial filtered inventory and non spatial complete inventory
+
+```

### 2021-08-04 R/harvestable.R

@@ -31,12 +31,13 @@
 #'
 #'@export
 #'
-#'@import sf
-#'@importFrom tibble add_column
+#'@importFrom dplyr filter mutate select left_join if_else
+#'@importFrom tibble as_tibble add_column
 #'@importFrom sp coordinates proj4string
+#'@importFrom sf st_as_sf st_distance
 #'@importFrom topoDistance topoDist
 #'@importFrom raster crs extract
-#'@importFrom  utils setTxtProgressBar txtProgressBar
+#'@importFrom utils setTxtProgressBar txtProgressBar
 #'
 #'
 #' @examples

### 2021-08-06 R/DraftFunctions.Rmd
#14 #35 #36

--- 2021-07-06 R/DraftFunctions.Rmd
@@
 ```{r}
+library(EcoFoG)
 library(Maria)
@@
 library(sf)
+library(nngeo)
+library(raster)
+library(topoDistance)
+library(BIOMASS)
+```
+
+```{r}
+Paracou6_2016 <- Paracou6_2016 %>% 
+  dplyr::select(-TreeFieldNum,-Project, -idVern, -CommercialSp, -CensusDate)
+
+usethis::use_data(Paracou6_2016, overwrite = TRUE)
+
 ```

### 2021-08-06 R/inventorycheckformat.R

@@ -74,10 +74,10 @@ inventorycheckformat <- function(
     GoodData <- FALSE
     GeneralStop <- paste (GeneralStop, "CodeAlive variable is not found.")
   }
-  if(!("CommercialSp" %in% names(inventory))) {
-    GoodData <- FALSE
-    GeneralStop <- paste (GeneralStop, "CommercialSp variable is not found.")
-  }
+  # if(!("CommercialSp" %in% names(inventory))) {
+  #   GoodData <- FALSE
+  #   GeneralStop <- paste (GeneralStop, "CommercialSp variable is not found.")
+  # }
   if(!("UTMZone" %in% names(inventory))) {
     GoodData <- FALSE
     GeneralStop <- paste (GeneralStop, "UTMZone variable is not found.")
@@ -176,10 +176,10 @@ inventorycheckformat <- function(
     GeneralStop <- paste (GeneralStop, "VernName variable should be a character.")
   }
 
-  if (!inherits(inventory$CommercialSp, "logical")) {
-    GoodData <- FALSE
-    GeneralStop <- paste (GeneralStop, "CommercialSp variable should be logical.")
-  }
+  # if (!inherits(inventory$CommercialSp, "logical")) {
+  #   GoodData <- FALSE
+  #   GeneralStop <- paste (GeneralStop, "CommercialSp variable should be logical.")
+  # }
 
   if (!inherits(inventory$CensusYear, "integer")) {
     GoodData <- FALSE

### 2021-08-16 R/Crowns_draft.Rmd
createcanopy and treefromthesky functions #38 #39

---
title: "Crowns_draft"
author: "Vincyane Badouard"
date: "16/08/2021"
output: html_document
---

```{r}
inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
dat <- inventory[679,]
```

```{r}
# The crown
treefromthesky <- function(dat){

  Crown <- dat %>%
    mutate(xCrown = Xutm, # X centroid
           yCrown = Yutm, # Y ventroid
           exCrown = CrownDiameter/2,
           eyCrown = CrownHeight/2) %>%
    st_as_sf(coords = c("xCrown", "yCrown")) # ellipse centroid coordinates
  Crown <- st_ellipse(Crown, Crown$exCrown, Crown$eyCrown) # create the ellipse

}
```

```{r}
library(ggplot2)
g <- ggplot() +
  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm")), aes(label = ScientificName)) +
  geom_sf(data = Crown, fill = "forestgreen") # trees polygons

plotly::ggplotly(g)
```

```{r}
Canopy <- inventory %>%
  group_by(idTree) %>% # for each tree
  do(Crowns = # inform geometry. # Filling a column from a function whose input is a table
       treefromthesky(.) %>%
       st_as_text()) %>% # as text to easy join with a non spacial table
  tidyr::unnest(Crowns) # here to pass from list to character

inventory <- left_join(inventory, Canopy, by = "idTree") # join spatial filtered inventory and non spatial complete inventory
```

```{r}
#The small ones first so that they are behind the big ones on the plot
inventory <- arrange(inventory, TreeHeight)

ggplot() +
  geom_sf(data = getgeometry(inventory, Crowns),
          aes(alpha = TreeHeight), # label = paste(idTree, Species), 
          fill = "forestgreen")
```

# Plotly version
```{r}
#The small ones first so that they are behind the big ones on the plot
inventory <- arrange(inventory, TreeHeight) %>% 
  filter(TreeHeight >30)

g <- ggplot() +
  geom_sf(data = getgeometry(inventory, Crowns),
          aes(label = paste(idTree, Species), alpha = 1/2), 
          fill = "forestgreen") # trees polygons

plotly::ggplotly(g)
```

### 2021-08-17 R/DRAFT_secondtrailsopening.Rmd
Maria secondary track WIP 1/2

@@
 
-```{r}
+```{r include=FALSE}
 library(Maria)
@@
 
-```{r}
-otherloggingparameters = loggingparameters()
-DEMParacou <- raster(paste0(Sys.getenv('DATAPATH'),"/GIS/Paracou/Topo_P6_PARACOU.tif"))
-Plots <- st_as_sf(rgdal::readOGR(paste0(Sys.getenv('DATAPATH'),"/GIS/Paracou/Plot_P6_PARACOU.shp")))
+```{r include=FALSE}
+data(DemParacou)
+data(Paracou6_2016)
+data(ExploitPolygones)
+
+scenario = "RIL1"
+advancedloggingparameters = loggingparameters()
+
+DemParacou <- raster(paste0(Sys.getenv('DATAPATH'),"/GIS/Paracou/Topo_P6_PARACOU.tif"))
+
+Plots <- rgdal::readOGR(paste0(Sys.getenv('DATAPATH'),"/GIS/Paracou/Plot_P6_PARACOU.shp"))
+
 MainTrails <- st_as_sf(as(rgdal::readOGR(paste0(Sys.getenv('DATAPATH'),"/GIS/Paracou/maintrail_P6_PARACOU.shp")),"SpatialLines" ))
-PlotSlope <- raster::terrain(raster::mask( x = DEMParacou,mask = Plots))
-res(DEMParacou)
-res(PlotSlope)
-load(paste0(Sys.getenv('DATAPATH'),"/treeselectionoutputs.Rdata"))
-inventory <- treeselectionoutputs$inventory
+PlotSlope <- raster::terrain(raster::mask( x = DemParacou,mask = Plots))
 
-HarvestableTreesPoints <- inventory %>% filter(LoggingStatus == "harvestable" | LoggingStatus == "harvestableUp" | LoggingStatus == "harvestable2nd")
-if (dim(HarvestableTreesPoints)[1] != 0) {
-coordinates(HarvestableTreesPoints) <- ~ Xutm + Yutm
-proj4string(HarvestableTreesPoints) <- raster::crs(DEMParacou)
-HarvestableTreesPoints <- st_as_sf(as(HarvestableTreesPoints,"SpatialPoints"))
-}
+scenarios <- scenariosparameters(scenario = scenario, objective = 70,
+fuel = "2", diversification = TRUE, winching = NULL, directionalfelling = NULL)
 
-SelectedTreesPoints <- inventory %>% filter(Selected == "1")
-if (dim(SelectedTreesPoints)[1] != 0) {
-coordinates(SelectedTreesPoints) <- ~ Xutm + Yutm
-proj4string(SelectedTreesPoints) <- raster::crs(DEMParacou)
-SelectedTreesPoints <- st_as_sf(as(SelectedTreesPoints,"SpatialPoints"))
-}
-
-FutureTreesPoints <- inventory %>% filter(LoggingStatus == "future")
-if (dim(FutureTreesPoints)[1] != 0) {
-coordinates(FutureTreesPoints) <- ~ Xutm + Yutm
-proj4string(FutureTreesPoints) <- raster::crs(DEMParacou)
-FutureTreesPoints <- st_as_sf(as(FutureTreesPoints,"SpatialPoints"))
-}
-
-ReserveTreesPoints <- inventory %>% filter(LoggingStatus == "reserve")
-if (dim(ReserveTreesPoints)[1] != 0) {
-coordinates(ReserveTreesPoints) <- ~ Xutm + Yutm
-proj4string(ReserveTreesPoints) <- raster::crs(DEMParacou)
-ReserveTreesPoints <- st_as_sf(as(ReserveTreesPoints,"SpatialPoints"))
-}
-
-HollowTreesPoints  <- inventory %>% filter(ProbedHollow == "1")
-if (dim(HollowTreesPoints)[1] != 0) {
-  coordinates(HollowTreesPoints) <- ~ Xutm + Yutm
-  proj4string(HollowTreesPoints) <- raster::crs(DEMParacou)
-  HollowTreesPoints  <- st_as_sf(as(HollowTreesPoints ,"SpatialPoints"))
-}
-
-# EnergywoodTreesPoints  <- inventory %>% filter(DeathCause  == "fuelwood")
-# if (dim(EnergywoodTreesPoints)[1] != 0) {
-# coordinates(EnergywoodTreesPoints) <- ~ Xutm + Yutm
-# proj4string(EnergywoodTreesPoints) <- raster::crs(DEMParacou)
-# EnergywoodTreesPoints <- st_as_sf(as(EnergywoodTreesPoints,"SpatialPoints"))
-# }
-
-rm(treeselectionoutputs)
-
-ggplot() + geom_sf(data = MainTrails) + geom_sf(data = HarvestableTreesPoints, aes(color = "Harvestable")) + 
-  geom_sf(data = SelectedTreesPoints, aes(color = "Selected")) + geom_sf(data = FutureTreesPoints, aes(color = "Futures")) + geom_sf(data = ReserveTreesPoints, aes(color = "Reserves"))
 ```
@@
 ```{r}
-require(raster)
-require(tidyverse)
-require(sf)
-library(Rsagacmd)
 
-Soil_paracou_path <- paste0(Sys.getenv('DATAPATH'), "/GIS/Paracou/")
-SAGA <- saga_gis()
-DEM <- SAGA$ta_preprocessor$fill_sinks_xxl_wang_liu(elev = paste0(Soil_paracou_path,"Dem.sgrd"),minslope = 0.01,.verbose = T)
+inventory <- ONFGuyafortaxojoin(addtreedim(cleaninventory(
+inventorycheckformat(Paracou6_2016))))
 
-Channels <- SAGA$ta_channels$channel_network(elevation = DEM,init_grid = DEM,init_method = "2",init_value = 10)
-HCrique <- SAGA$ta_channels$vertical_distance_to_channel_network(elevation = DEM,channels = Channels$chnlntwrk)
+treeselectionoutputs <- treeselection(inventory, objective = scenarios$objective,
+scenario =scenario,fuel = scenarios$fuel , diversification = scenarios$diversification, winching = scenarios$winching , specieslax = FALSE,
+objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope,
+exploitpolygones = ExploitPolygones,
+speciescriteria = SpeciesCriteria,
+advancedloggingparameters = loggingparameters())
 
-HarvestableAreaDefinition <- function(Plot, DEM, HCrique) {
+inventory <- treeselectionoutputs$inventory
 
-  # On commence par decouper par l'emprise du plot
-  PlotTopo <- raster::mask(x = DEM,
-                           mask = Plot) # découpage de la topo par l'emprise du plot
-  HCriquePlot <- raster::mask(x = HCrique,
-                              mask = Plot) # la même chose pour la hauteur à la crique
+```
 
-  # Calcul de la pente
-  PlotSlope <- raster::terrain(PlotTopo,
-                               opt = "slope",
-                               units = 'radians',
-                               neigbors = 8)
-  # RastersToPoints
+```{r}
+AccessPolygones <- FilterAccesExplArea(exploitpolygones = ExploitPolygones,maintrails = MainTrails,winching = scenarios$winching,advancedloggingparameters = loggingparameters())
 
-  PlotSlopePoint <-
-    dplyr::as_tibble(raster::rasterToPoints(PlotSlope))
+DfDEM <- as_tibble(rasterToPoints(DemParacou)) %>% mutate( z = Topo_P6_PARACOU) %>% dplyr::select(-Topo_P6_PARACOU)
 
-  HCriquePlotPoint <-
-    dplyr::as_tibble(raster::rasterToPoints(HCriquePlot))
+ggplot() + geom_raster(data = DfDEM, aes(x =x , y = y, fill = z)) + 
+  geom_sf(data = MainTrails) + geom_sf(data = AccessPolygones,fill = "red",alpha = 0.1) + geom_sf(data = treeselectionoutputs$HarvestableTreesPoints, aes(color = "Harvestable")) + 
+  geom_sf(data =treeselectionoutputs$SelectedTreesPoints , aes(color = "Selected")) + geom_sf(data = treeselectionoutputs$ReserveTreesPoints, aes(color = "Reserves")) + 
+  geom_sf(data = treeselectionoutputs$FutureTreesPoints, aes(color = "Futures")) +
+  geom_sf(data = treeselectionoutputs$BigTreesPoints, aes(color = "DBH>50cm"))+ scale_fill_gradientn(colours = rev(terrain.colors(225)))
 
-  # left join par x et y
-  PlotTib <-
-    dplyr::left_join(PlotSlopePoint, HCriquePlotPoint, by = c('x', 'y'))
-
-  PlotTib %>% dplyr::rename("HauteurCrique" = names(PlotTib[4]))  %>%
-    mutate(Exploit = if_else(
-      condition = HauteurCrique > 2 &
-        slope <= .264, # on est en radians pour la pente, donc .264 radians = 27% de pente
-      true = 1,
-      false = 0
-    )) -> PlotSlopeHCrique
-
-  # on a pu determiner les zones exploitables ou non
-  # maintenant on transforme ça en polygones, PlotSlopeHCrique pourrait etre reutilise pour la pente
-
-  # on retransforme en raster
-  RasterExploit <-
-    raster::rasterFromXYZ(PlotSlopeHCrique, crs = 32622) # set crs to WGS84 UTM 22N
-
-  # raster en polygone
-  PolygoneExploit <-
-    raster::rasterToPolygons(x = RasterExploit$Exploit,
-                             n = 16,
-                             dissolve = TRUE)
-
-  ## On quitte le monde merveilleux du package raster pour passer a celui de sf
-
-  sf_PolygoneExploit <- sf::st_as_sf(PolygoneExploit)
-
-  ## On transforme nos deux gros polygones (Exploit=1 et Exploit=0 en pleins de petits, par ce qui s'appelait disaggregate dans le package sp)
-
-  ExploitPolygones <-
-    sf::st_cast(x = sf_PolygoneExploit, to = "POLYGON") # on a maintenant pleins de polygones, dont pleins de petits isolés
-
-  return(ExploitPolygones)
-
-}
-
-UP <- HarvestableAreaDefinition(Plot = Plots,DEM = DEMParacou,HCrique = 3)
 ```
@@
 # secondtrailsopening <- function(inventory,
-#                                 DEM = DEMParacou,
+#                                 DEM = DemParacou,
 #                                 plotslope =  PlotSlope,
@@
 
-  if(!any(unlist(lapply(list(DEMParacou, PlotSlope), inherits, "RasterLayer"))))
+  if(!any(unlist(lapply(list(DemParacou, PlotSlope), inherits, "RasterLayer"))))
     stop("The 'DEM' and 'plotslope' arguments of the 'secondtrailsopening' function must be raster")
@@
 
-  if (type == "RIL1" | type == "RIL2broken" | (type == "manual" & winching == "0")) {
+##################################
 
-  } else {
+  CostSlopeMatrix <- list(list(Slope = 3, Cost = 1),
+                          list(Slope = 5, Cost = 3),
+                          list(Slope = 12, Cost = 20),
+                          list(Slope = 22, Cost = 60),
+                          list(Slope = 27, Cost = 600),
+                          list(Slope = Inf, Cost = 1000))
+
+  AccessMainTrails <- FilterAccesExplArea(exploitpolygones = ExploitPolygones,maintrails = MainTrails,winching = "0",advancedloggingparameters = loggingparameters()) %>%
+  sf::st_cast("POLYGON") %>% sf::st_as_sf() %>% 
+    mutate(ID = paste0("ID_",row_number()))
+
+  PartMainTrails <- st_intersection(MainTrails  ,
+                                    AccessMainTrails %>% 
+                                      sf::st_buffer(dist = advancedloggingparameters$MaxMainTrailWidth)) %>% 
+    sf::st_buffer(dist = advancedloggingparameters$MaxMainTrailWidth) %>% sf::st_union() %>% 
+    sf::st_intersection(sf::st_as_sf(Plots) %>% sf::st_union()) %>%
+     sf::st_cast("POLYGON")  %>% 
+    sf::st_as_sf() %>% 
+    sf::st_join(AccessMainTrails)
+
+  AccessPoint <- PartMainTrails  %>%  
+    sf::st_sample( rep(1,dim(PartMainTrails)[1]) ,type = "random",by_polygon = TRUE) %>% sf::st_as_sf() %>%  
+    sf::st_join(PartMainTrails)
+
+    CostRaster <- raster(extent(DemParacou),resolution = res(DemParacou), crs = crs(DemParacou))
+  values(CostRaster) <- 1000
+  CostRaster <- mask(CostRaster, Plots)
+  CostRaster <- crop(CostRaster, Plots)
+
+  # RastersToPoints
+
+  plotSlopePoint <- dplyr::as_tibble(raster::rasterToPoints(PlotSlope))
+
+  CostRasterPoint <- dplyr::as_tibble(raster::rasterToPoints(CostRaster))
+
+  # left join par x et y
+  plotTib <-
+    dplyr::left_join(plotSlopePoint, CostRasterPoint, by = c('x', 'y'))
+
+  CostSlopeRaster <- plotTib %>%
+    mutate(Exploit = if_else(
+        slope <= atan(CostSlopeMatrix[[1]]$Slope/100), # on est en radians pour la pente, donc .264 radians = 27% de pente
+      true = CostSlopeMatrix[[1]]$Cost,
+      false = if_else(
+        slope <= atan(CostSlopeMatrix[[2]]$Slope/100),
+        true = CostSlopeMatrix[[2]]$Cost,
+        false = if_else(
+          slope <= atan(CostSlopeMatrix[[3]]$Slope/100),
+          true = CostSlopeMatrix[[3]]$Cost,
+          false = if_else(
+            slope <= atan(CostSlopeMatrix[[4]]$Slope/100),
+            true = CostSlopeMatrix[[4]]$Cost,
+            false = if_else(
+              slope <= atan(CostSlopeMatrix[[5]]$Slope/100),
+              true = CostSlopeMatrix[[5]]$Cost,
+              false = CostSlopeMatrix[[6]]$Cost)
+          )
+        )
+      )
+    )) %>% dplyr::select(x,y,Exploit)
+
+  CostRaster <- raster::rasterFromXYZ(CostSlopeRaster, crs = 32622)
+
+    AccessRaster <- raster(extent(DemParacou),resolution = res(DemParacou), crs = crs(DemParacou))
+  values(AccessRaster) <- 1000
+
+  AccessRaster <- rasterize(x = as_Spatial(AccessPolygones %>% 
+                                             sf::st_buffer(dist =  -advancedloggingparameters$ScndTrailWidth/2)),
+                            y = AccessRaster , 
+                            field = 0, 
+                            update = TRUE) 
+    AccessRaster <- crop(AccessRaster,  CostRaster)
+  AccessRaster <- mask(AccessRaster, Plots)
+
+  CostRaster<- CostRaster + AccessRaster
+
+  BigTreesRaster <- raster(extent(DemParacou),resolution = res(DemParacou), crs = crs(DemParacou))
+  values(BigTreesRaster) <- 0
+  BigTreesRaster <- rasterize(x = as_Spatial(treeselectionoutputs$BigTreesPoints %>% 
+                                                     sf::st_buffer(dist =  advancedloggingparameters$ScndTrailWidth/2 + 2) ),
+                                    y = BigTreesRaster , 
+                                    field = 500, 
+                                    update = TRUE) 
+  BigTreesRaster <- crop(BigTreesRaster,  CostRaster)
+
+    ReserveRaster <- raster(extent(DemParacou),resolution = res(DemParacou), crs = crs(DemParacou))
+  values(ReserveRaster) <- 0
+  ReserveRaster <- rasterize(x = as_Spatial(treeselectionoutputs$HarvestableTreesPoints %>% 
+                                                     sf::st_buffer(dist =  advancedloggingparameters$ScndTrailWidth/2 + 2) ),
+                                    y = ReserveRaster , 
+                                    field = 500, 
+                                    update = TRUE) 
+  ReserveRaster <- crop(ReserveRaster,  CostRaster)
+
+  FutureRaster <- raster(extent(DemParacou),resolution = res(DemParacou), crs = crs(DemParacou))
+  values(FutureRaster ) <- 0
+  FutureRaster  <- rasterize(x = as_Spatial(treeselectionoutputs$HarvestableTreesPoints %>% 
+                                                     sf::st_buffer(dist =  advancedloggingparameters$ScndTrailWidth/2 +2) ),
+                                    y = FutureRaster  , 
+                                    field = 50, 
+                                    update = TRUE) 
+  FutureRaster  <- crop(FutureRaster ,  CostRaster)
+
+  CostRaster<- CostRaster + BigTreesRaster + ReserveRaster + FutureRaster
+
+  CostRaster <- rasterize(x = as_Spatial(PartMainTrails),
+                                    y = CostRaster , 
+                                    field = 1E-3, 
+                                    update = TRUE)
+
+  CostRasterMean <- aggregate(CostRaster, fact=3, fun=mean)
+  CostRasterMean <- crop(CostRasterMean,  CostRaster)
+  CostRasterMean <- mask(CostRasterMean, Plots)
+
+  DEM <- crop(DemParacou,  CostRasterMean)
+  DEM <- mask(DEM, Plots)
+
+  DEMmean <- aggregate(DEM, fact=3, fun=mean)
+  DEMmean <- crop(DEMmean,  CostRasterMean)
+  DEMmean <- mask(DEMmean, Plots)
+
+  CondSurf <- 1/CostRasterMean
+
+  SlopeCond <- SlopeRdCond(DEM = DEMmean,fact = 1,advancedloggingparameters = loggingparameters())
+
+  pts <- treeselectionoutputs$SelectedTreesPoints %>% sf::st_cast("POINT") %>% sf::st_join(AccessMainTrails)
+  pts <- rbind(AccessPoint %>% mutate(type = "Access"),pts %>% mutate(type = "Tree"))
+
+  pathLines <- list()
+  k <- 0
+
+##################################
+
+  if (winching == "0") {
+
+    for (accessid in unique(pts$ID)) {
+
+      selectedPoints <- pts %>% filter(ID == accessid) 
+      PointAcc <- selectedPoints %>% filter(type == "Access") %>% 
+        mutate(ptAcc = dplyr::row_number()) %>% 
+        mutate(EstCost = NA)
+      CostDistEst <- AdjTopoLCP(costSurface = CondSurf,
+                                DEM = DEMmean , 
+                                pts = selectedPoints %>% 
+                                  as_Spatial(),
+                                slopeRdCond = SlopeCond,
+                                paths = FALSE) [,1:dim(PointAcc)[1]]
+      CostDistEst[CostDistEst == 0] <- NA
+      CostDistEst <- na.exclude(CostDistEst)
+      PointTree <- selectedPoints %>% filter(type == "Tree") %>% 
+        mutate(ptAcc = max.col(-CostDistEst))
+      if (dim(PointAcc)[1] == 1) {
+        PointTree <- PointTree %>% mutate(EstCost = CostDistEst)
+      }else{PointTree <- PointTree %>% mutate(EstCost = apply(CostDistEst,1, min))}
+      selectedPoints <- rbind(PointAcc,PointTree)
+
+      for (accessPtId in 1:dim(PointAcc)[1]) {
+        TmpSelectedPts <- selectedPoints %>% 
+          filter(ptAcc == accessPtId)
+
+        TmpAccPts <- TmpSelectedPts %>% 
+          filter(type == "Access")
+
+        TmpTreePts <- TmpSelectedPts %>% 
+          filter(type == "Tree") %>% 
+          arrange(desc(EstCost))
+
+        if (dim(TmpTreePts)[1] != 0) {
+          for (TreeId in 1:dim(TmpTreePts)[1]){
+
+            TmpPtsWIP <- rbind(TmpAccPts,TmpTreePts[TreeId,])
+            TmpPathWIP <-  AdjTopoLCP(costSurface = CondSurf,DEM = DEMmean , pts = TmpPtsWIP %>% as_Spatial(),
+                              slopeRdCond = SlopeCond,paths = TRUE)
+
+            CostRasterMean  <- rasterize(x = TmpPathWIP[[2]] ,
+                                    y = CostRasterMean  , 
+                                    field = 0.3,update =  TRUE)
+            CondSurf <- 1/CostRasterMean
+
+            k <- k +1
+
+            pathLines[[k]] <- TmpPathWIP[[2]]
+            pathLines[[k]]@lines[[1]]@ID <- paste("Path",accessid,"-",accessPtId, "-", TreeId, sep = " ")
 
           }
-  if (type == "RIL2" | (type == "manual" & winching == "1")) {
+        }
+      }
 
@@
 
-  if (type == "RIL3" | type == "RIL3fuel" | type == "RIL3fuelhollow" | (type == "manual" & winching == "2")) {
+  }
+
+  if (winching == "1") {
+
+    ptsCabble <- pts %>% filter(type == "Tree") %>%
+      st_buffer(dist = advancedloggingparameters$CableLength) %>%
+      st_intersection() %>% 
+      st_make_valid() %>%
+      arrange(desc(n.overlaps)) %>% 
+      mutate(ID_pts = paste0("T.",row_number()))
+
+    for (accessid in unique(pts$ID)) {
+
+      PointAcc <- pts %>% filter(ID == accessid) %>% filter(type == "Access")%>% 
+       mutate(ptAcc = row_number()) %>% 
+        mutate(EstCost = NA) %>% 
+        mutate(ID_pts = paste0("A.",row_number()))
+
+      InPlot <- st_intersects(ptsCabble %>% 
+        filter(ID == accessid) %>% 
+        st_centroid(),Plots %>% st_as_sf(),sparse = FALSE)
+
+      ptsCabbleCentroid <- ptsCabble %>% 
+        filter(ID == accessid) %>% 
+        st_centroid() %>% dplyr::mutate(InPlot = InPlot) %>% 
+        filter(InPlot == TRUE) %>% dplyr::select(-InPlot) %>% 
+       mutate(ptAcc = NA) %>% 
+      mutate(EstCost = NA) %>% arrange(desc(n.overlaps))
+
+      selectedPoints <- rbind(PointAcc %>% mutate(n.overlaps = NA, origins = NA),ptsCabbleCentroid %>% 
+        st_sf())
+
+      CostDistEst <- AdjTopoLCP(costSurface = CondSurf,
+                                DEM = DEMmean , 
+                                pts = selectedPoints %>% 
+                                  as_Spatial(),
+                                slopeRdCond = SlopeCond,
+                                paths = FALSE) [,1:dim(PointAcc)[1]]
+      CostDistEst[CostDistEst == 0] <- NA
+      CostDistEst <- na.exclude(CostDistEst)
+      PointTree <- selectedPoints %>% filter(type == "Tree") %>% 
+        mutate(ptAcc = max.col(-CostDistEst))
+      if (dim(PointAcc)[1] == 1) {
+        PointTree <- PointTree %>% mutate(EstCost = CostDistEst)
+      }else{PointTree <- PointTree %>% mutate(EstCost = apply(CostDistEst,1, min))}
+      selectedPoints <- rbind(PointAcc %>% mutate(n.overlaps = NA, origins = NA),PointTree)
+
+      for (accessPtId in 1:dim(PointAcc)[1]) {
+        TmpSelectedPts <- selectedPoints %>% 
+          filter(ptAcc == accessPtId)
+
+        TmpAccPts <- TmpSelectedPts %>% 
+          filter(type == "Access")
+
+        TmpTreePts <- TmpSelectedPts %>% 
+          filter(type == "Tree") %>% 
+          arrange(desc(n.overlaps),EstCost)
+
+        TreeId <- 1
+
+          while (dim(TmpTreePts)[1] != 0){
+
+            TmpPtsWIP <- rbind(TmpAccPts %>%  
+                                st_union() %>% 
+                                st_cast("POINT")%>% 
+                                 st_as_sf() %>% 
+                                 mutate(ID = accessid)%>% 
+                                 mutate(type = "Access") %>% 
+                                 mutate(ptAcc = accessPtId) %>% 
+                                 mutate(ID_Pts = NA),ptsCabble %>% 
+                                filter(ID_pts == TmpTreePts[TreeId,"ID_pts"]$ID_pts)  %>%  
+                                st_union() %>% 
+                                st_cast("POINT")%>% 
+                                 st_as_sf()%>% 
+                                 mutate(ID = accessid)%>% 
+                                 mutate(type = "Overlay")%>% 
+                                 mutate(ptAcc = accessPtId) %>% 
+                                 mutate(ID_Pts = TmpTreePts[TreeId,"ID_pts"]$ID_pts))
+
+            CostDistEstWIP <-  AdjTopoLCP(costSurface = CondSurf,DEM = DEMmean , pts = TmpPtsWIP %>% as_Spatial(),
+                              slopeRdCond = SlopeCond,paths = FALSE)[,1]
+
+            CostDistEstWIP[CostDistEstWIP == 0] <- NA
+            CostDistEstWIP <- na.exclude(CostDistEstWIP)
+
+            PointTreeWIP <- TmpPtsWIP %>% filter(type == "Overlay") %>% 
+              mutate(EstCost= CostDistEstWIP) %>% arrange(EstCost)
+
+            TmpPtsWIP <- rbind(TmpPtsWIP %>% filter(type == "Access") %>% mutate(EstCost = NA),PointTreeWIP[1,])
+
+            TmpPathWIP <- AdjTopoLCP(costSurface = CondSurf,DEM = DEMmean , pts = TmpPtsWIP %>% as_Spatial(),
+                              slopeRdCond = SlopeCond,paths = TRUE)
+
+            CostRasterMean  <- rasterize(x = TmpPathWIP[[2]] ,
+                                    y = CostRasterMean  , 
+                                    field = 0.3,update =  TRUE)
+            k <- k +1
+
+            pathLines[[k]] <- TmpPathWIP[[2]]
+            pathLines[[k]]@lines[[1]]@ID <- paste("Path",accessid,"-",accessPtId, "-", TreeId, sep = " ")
+
+            CbblePtsWIP <- ptsCabble %>% filter(ID_pts == TmpTreePts[TreeId,"ID_pts"]$ID_pts)
+
+            CbblePtsWIP$origins [[1]] %in% TmpTreePts$origins [[2]]
+
+            TreeId <- TreeId + 1
+
+          }
+        }
+      }
 
@@
 
+  }
+
+  if (winching == "2") {
+
+  }
+
+  paths <- do.call(rbind, pathLines)
+
+    df <-  as_tibble(rasterToPoints(CostRasterMean)) %>% mutate( Cost = layer) %>% dplyr::select(-layer)
+  df2 <- as_tibble(rasterToPoints(DEM)) %>% mutate( z = Topo_P6_PARACOU) %>% dplyr::select(-Topo_P6_PARACOU)
+  df3 <- as_tibble(rasterToPoints(raster(SlopeCond))) %>% mutate( AccSlp = layer) %>% dplyr::select(-layer)
+  ggplot() +
+    geom_raster(data = df, aes(x =x , y = y, fill = Cost)) +  geom_sf(data = pts) + scale_fill_gradientn(colours = rev(terrain.colors(225)))  + geom_sf( data = sf::st_as_sf(paths))    + geom_sf(data =  paths %>% st_as_sf()  %>% smoothr::smooth(method = "ksmooth",smoothness = 5) %>% st_buffer(dist = 4) %>% st_union(), color = 'red', alpha = 0.1 )  + theme_bw()
+
 ```

### 2021-08-17 R/TreeFelling_Draft.Rmd
Corrections (cleaninventory)
Treefelling
treefelling avoid fut/res and A/B choice

@@
 
-inventory <- addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))
+inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
 
@@
 if (directionalfelling == "0"){
-  Coord = matrix(c(0,0,10,0,10,10,0,10,0,0),ncol=2, byrow=TRUE)
-  pol1 = list() #1 list/polygon :  list with numeric matrices with points in rows
-  pol2 = list()
-  pol3 = list()
-  mp = list(pol1,pol2,pol3) #list of lists with numeric matrices
-  (mp1 = st_multipolygon(mp))
-  plot(mp1)
 
-  Shadows <- st_multipolygon()
 } 

### 2021-08-17 R/testtreefallposition.Rmd
treefelling avoid fut/res and A/B choice

---
title: "testtreefallposition"
author: "Vincyane Badouard"
date: "17/08/2021"
output: html_document
---

```{r}
MainTrail <- sf::st_linestring(matrix(c(286400, 583130,
                                        286400, 583250,
                                        286655, 583250,
                                        286655, 583130,
                                        286400, 583130) # the return
                                      ,ncol=2, byrow=TRUE))

pol1 <- list(matrix(c(286503, 583134,
                      286503, 583240,
                      286507, 583240,
                      286507, 583134,
                      286503, 583134) # the return
                    ,ncol=2, byrow=TRUE))
pol2 <- list(matrix(c(286650, 583134,
                      286650, 583240,
                      286654, 583240,
                      286654, 583134,
                      286650, 583134) # the return
                    ,ncol=2, byrow=TRUE))

PolList = list(pol1,pol2) #list of lists of numeric matrices
ScndTrail <- sf::st_multipolygon(PolList)

inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
inventory <- suppressMessages(treeselection(inventory, objective = 30, scenario ="manual",
                                            fuel = "2", diversification = TRUE, specieslax = FALSE,
                                            objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope,
                                            speciescriteria = SpeciesCriteria,
                                            advancedloggingparameters = loggingparameters())$inventory)
```

```{r}
fuel = "2"
directionalfelling = "2"
advancedloggingparameters = loggingparameters()

inventory <- directionalfellingsuccessdef(
  inventory,
  fuel = fuel,
  directionalfelling = directionalfelling,
  advancedloggingparameters = loggingparameters())

# Future/reserve trees to avoid
inventory <- createcanopy(inventory) # create all inventory crowns in the 'Crowns' column

FutureReserveCrowns <- inventory %>% # create an object with future/reserve crowns only
  filter(LoggingStatus == "future" | LoggingStatus == "reserve") %>%
  getgeometry(Crowns)

inventory <- inventory %>%
  dplyr::filter(Selected == "1") %>%
  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,
                CrownDiameter,Selected, Xutm, Yutm, TreeFellingOrientationSuccess)
dat <- inventory[1,]

```

```{r}
Trail <- st_union(MainTrail, ScndTrail) # Our trail will be MainTrail or ScndTrail

# The crown
Crown <- dat %>%
  mutate(xCrown = Xutm,
         yCrown = Yutm + TrunkHeight + CrownHeight/2,
         exCrown = CrownDiameter/2,
         eyCrown = CrownHeight/2) %>%
  st_as_sf(coords = c("xCrown", "yCrown")) # ellipse centroid coordinates
Crown <- st_ellipse(Crown, Crown$exCrown, Crown$eyCrown) # create the ellipse

# The trunk
Trunk <- with(dat,
              st_polygon(list(matrix(c(Xutm-(DBH/100)/2, Yutm,
                                       Xutm-(DBH/100)/2, Yutm + TrunkHeight,
                                       Xutm+(DBH/100)/2, Yutm + TrunkHeight,
                                       Xutm+(DBH/100)/2, Yutm,
                                       Xutm-(DBH/100)/2, Yutm) # the return
                                     ,ncol=2, byrow=TRUE))))

# Find the point (TrailPt) on the Trail closest to the location of the tree (Foot)
Foot <- st_point(c(dat$Xutm,dat$Yutm)) # tree foot point

NearestPoints <- st_nearest_points(Foot, Trail) # from the Foot of the tree to the Trail (linestring)

NearestPoint <- st_cast(NearestPoints, "POINT") # to have start (Foot) and end (TrailPt) points
TrailPt <- NearestPoint[[2]] # the point (TrailPt) on the Trail closest to the location of the tree (Foot)

# Compute the angle between the tree default position and the shortest way from the foot to the trail
theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                  c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))

TreefallOrientation <- as.numeric(sample(c(advancedloggingparameters$MinTreefallOrientation:
                                             advancedloggingparameters$MaxTreefallOrientation), size = 1))
OppAng <- 180-(90 + TreefallOrientation)

# Calculate the two possible crown configurations
ACrown <- rotatepolygon(Crown, angle = 180 + OppAng + theta, fixed = Foot) # turned crown
BCrown <- rotatepolygon(Crown, angle = 180 - OppAng + theta, fixed = Foot) # turned crown

# Test the best to pull the tree back to the main trail (farthest crown from the main trail)
ADist <- st_distance(ACrown, MainTrail)[1,1] #matrix to value
BDist <- st_distance(BCrown, MainTrail)[1,1]

if(min(ADist, BDist) == ADist){

  FallenTree <- AFallenTree <- st_difference(st_union( # A configuration
    rotatepolygon(Trunk, angle = 180 + OppAng + theta, fixed = Foot), # turned trunk
    ACrown # turned crown
  ))

}else{

  FallenTree <-  BFallenTree <- st_difference(st_union( # B configuration
    rotatepolygon(Trunk, angle = 180 - OppAng + theta, fixed = Foot), # turned trunk
    BCrown # turned crown
  ))

}

remove(pol1, pol2, PolList, NearestPoint, NearestPoints)
```

```{r}
# Check intersection with future/reserve trees
FRintersect <- 2

if(lengths(FRintersect) > 0) { # if there is an intersection
  if(FallenTree == AFallenTree){ # if it was A configuration

    FallenTree <- BFallenTree <- st_difference(st_union( # B configuration
      rotatepolygon(Trunk, angle = 180 - OppAng + theta, fixed = Foot), # turned trunk
      BCrown # turned crown
    ))

    # check intersection for this configuration
    FRintersect <- sf::st_intersects(BFallenTree, FutureReserveCrowns)
    if(lengths(FRintersect) > 0) { # if there is an intersection. if not FallenTree stay BFallenTree
      FallenTree <- AFallenTree # we prefer 1st configuration (the best for winching)
    }

  }else if(FallenTree == BFallenTree){ # if it was B configuration

    FallenTree <- AFallenTree <- st_difference(st_union( # A configuration
      rotatepolygon(Trunk, angle = 180 + OppAng + theta, fixed = Foot), # turned trunk
      ACrown # turned crown
    ))

    # check intersection for this configuration
    FRintersect <- sf::st_intersects(AFallenTree, FutureReserveCrowns)
    if(lengths(FRintersect) > 0) { # if there is an intersection. if not FallenTree stay AFallenTree
      FallenTree <- BFallenTree # we prefer 1st configuration (the best for winching)
    }
  }
}

FallenTree == AFallenTree
FallenTree == BFallenTree

```

### 2021-08-18 R/DESIGNATION_DRAFT.Rmd
felling1tree test

@@
 
-  sp::proj4string(HollowTreescoord) <- raster::crs(DEM) # attribuer le crs de Paracou à notre inventaire spatialisé
+  sp::proj4string(HollowTreescoord) <- raster::crs(topography) # attribuer le crs de Paracou à notre inventaire spatialisé
 
@@
 
-sp::proj4string(HarvestableTreesPoints) <- raster::crs(DEM)
+sp::proj4string(HarvestableTreesPoints) <- raster::crs(topography)
 

### 2021-08-18 R/Draft_spatio.Rmd
felling1tree test

@@
 ```{r}
-inventory = ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016))))
+inventory = ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016)))
 
@@
 ## Import du MNT de Paracou (1m de résolution, campagne LiDAR de 2016) ----
-DemParacou <- raster::raster("D:/VSC Kourou/DATA/GIS/Topo_P6_PARACOU.tif") # MNT (altitude)
-plot(DemParacou)
-usethis::use_data(DemParacou)
+DTMParacou <- raster::raster("D:/VSC Kourou/DATA/GIS/Topo_P6_PARACOU.tif") # MNT (altitude)
+plot(DTMParacou)
+usethis::use_data(DTMParacou)
+overwrite = TRUE
 
@@
 # Fourni par le module de def d'UP
-PlotTopo <- raster::mask(x = DemParacou, # DEM en shapefile
+PlotTopo <- raster::mask(x = DTMParacou, # topography en shapefile
                          mask = Plots) # découpage de la topo par l'emprise du plot
@@
 
-proj4string(SpatInventory) <- raster::crs(DemParacou) # attribuer le crs de Paracou à notre inventaire spatialisé
+proj4string(SpatInventory) <- raster::crs(DTMParacou) # attribuer le crs de Paracou à notre inventaire spatialisé
 
@@
 
-    distSp <- topoDist(DEM = PlotTopo, pts = SpatInventorytmp) # calcul des distances
+    distSp <- topoDist(topography = PlotTopo, pts = SpatInventorytmp) # calcul des distances
     distSp <- as_tibble(distSp)
@@
 coordinates(test_inventory) <- ~ Xutm + Yutm
-proj4string(test_inventory) <- raster::crs(DemParacou)
+proj4string(test_inventory) <- raster::crs(DTMParacou)
 test_inventory <- st_as_sf(test_inventory)

### 2021-08-18 R/TreeFelling_Draft.Rmd
felling1tree test

@@
 data(Paracou6_2016)
-data(DemParacou)
+data(DTMParacou)
 
@@
 inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
-                           objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
+                           objectivelax = FALSE, topography = DTMParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
                            advancedloggingparameters = loggingparameters())$inventory
@@
 objectivelax = FALSE
-DEM = DemParacou
+topography = DTMParacou
 advancedloggingparameters = loggingparameters()
@@
 # 
-# sp::proj4string(SelectedTrees) <- raster::crs(DEM)
+# sp::proj4string(SelectedTrees) <- raster::crs(topography)
 # 

### 2021-08-18 R/TreeFelling_Draft2.Rmd
Corrections (cleaninventory)
felling1tree test

@@
 data(Paracou6_2016)
-data(DemParacou)
+data(DTMParacou)
 
-inventory <- addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))
+inventory <- addtreedim(inventorycheckformat(Paracou6_2016)))
 
 inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
-                           objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
+                           objectivelax = FALSE, topography = DTMParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
                            advancedloggingparameters = loggingparameters())$inventory

### 2021-08-18 R/Treefelling_Sylvain's version.Rmd
felling1tree test

@@
 ```{r}
-st_tree <- function(dat,
+felling1tree <- function(dat,
                     ScndTrail = ScndTrail,
@@
   group_by(idTree) %>% 
-  do(geometry = st_tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$NearestPoints) %>% 
+  do(geometry = felling1tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$NearestPoints) %>% 
   mutate(geometry = as(geometry, "sfc_LINESTRING")) %>% # list -> sfc_MULTIPOLYGON
@@
   group_by(idTree) %>% # for each tree and each given angle 
-  do(geometry = st_tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$A) %>% # inform geometry.
+  do(geometry = felling1tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$A) %>% # inform geometry.
 # Filling a column from a function whose input is a table
@@
   #                 as(geometry = st_as_sfc(
-  #                   lapply(split(SelectedTrees, SelectedTrees$idTree), st_tree(30))
+  #                   lapply(split(SelectedTrees, SelectedTrees$idTree), felling1tree(30))
   #                 )
@@
        ifelse(!is.na(.$TreeFellingOrientationSuccess),
-              st_tree(.,
+              felling1tree(.,
                       ScndTrail = ScndTrail,
@@
   do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
-       st_tree(.,
+       felling1tree(.,
                ScndTrail = ScndTrail,
@@
   filter(!is.na(TreeFellingOrientationSuccess)) %>% 
-  st_tree(.,
+  felling1tree(.,
           ScndTrail = ScndTrail,
@@
   do(TreePolygon = # inform geometry. # Filling a column from a function whose input is a table
-       st_tree(.,
+       felling1tree(.,
                fuel = "2", directionalfelling = "2",

### 2021-08-18 R/Treefelling_test_for all trees.Rmd
felling1tree test

@@
   # 
-  # sp::proj4string(SelectedTrees) <- raster::crs(DEM)
+  # sp::proj4string(SelectedTrees) <- raster::crs(topography)
   # 

### 2021-08-18 R/testtreefallposition.Rmd
felling1tree test

@@
                                             fuel = "2", diversification = TRUE, specieslax = FALSE,
-                                            objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope,
+                                            objectivelax = FALSE, topography = DTMParacou, plotslope = PlotSlope,
                                             speciescriteria = SpeciesCriteria,

### 2021-08-18 tests/testthat/test-treefelling.R

@@ -29,9 +29,9 @@ test_that("treefelling", {
   ScndTrail <- st_multipolygon(PolList)
 
   inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
-  inventory <- suppressMessages(treeselection(inventory, objective = 30, scenario ="manual",
-                             fuel = "2", diversification = TRUE, specieslax = FALSE,
-                             objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope,
+  inventory <- suppressMessages(treeselection(inventory, objective = 20, scenario ="manual",
+                             fuel = "2", diversification = FALSE, specieslax = FALSE,
+                             objectivelax = FALSE, topography = DTMParacou, plotslope = PlotSlope,
                              speciescriteria = SpeciesCriteria,
                              advancedloggingparameters = loggingparameters())$inventory)
 

### 2021-08-20 R/DESIGNATION_DRAFT.Rmd
loggingsimulation function and doc refresh

@@
 
-inventory = addtreedim(inventorycheckformat(Paracou6_2016))) #3539 rows (Paracou: 3620 rows)
+inventory = addtreedim(inventorycheckformat(Paracou6_2016), volumeparameters = ForestZoneVolumeParametersTable)) #3539 rows (Paracou: 3620 rows)
 speciescriteria = SpeciesCriteria

### 2021-08-20 R/Draft_spatio.Rmd
loggingsimulation function and doc refresh

@@
 ```{r}
-inventory = ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016)))
+inventory <- addtreedim(inventorycheckformat(Paracou6_2016),
+                        volumeparameters = ForestZoneVolumeParametersTable)
+
+inventory <- ONFGuyafortaxojoin(inventory, SpeciesCriteria)
 

### 2021-08-20 R/testtreefallposition.Rmd
loggingsimulation function and doc refresh

--- 2021-08-17 R/testtreefallposition.Rmd
@@
 
-inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
+inventory <- addtreedim(inventorycheckformat(Paracou6_2016), volumeparameters = ForestZoneVolumeParametersTable)
 inventory <- suppressMessages(treeselection(inventory, objective = 30, scenario ="manual",
                                             fuel = "2", diversification = TRUE, specieslax = FALSE,
-                                            objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope,
+                                            objectivelax = FALSE, topography = DTMParacou, plotslope = PlotSlope,
                                             speciescriteria = SpeciesCriteria,

### 2021-08-20 R/loggingsimulation.R

@@ -1,33 +1,281 @@
+#' loggingsimulation
+#'
+#' @description This function allows to simulate a timber and wood energy
+#'   logging on a forest plot. It covers: harvestable area definition, tree
+#'   selection, main (only for ONF plots) and secondary trails layout, tree
+#'   felling, landings implementation (only for ONF plots), timber harvested,
+#'   fuel wood volume and damages quantification.
+#'
+#' @param inventory Your inventory (see the inputs formats and metadata in the
+#'   \code{\link{vignette}}) (data.frame)
+#'
+#' @param topography Digital terrain model (DTM) of the inventoried plot (LiDAR
+#'   or SRTM) (default: \code{\link{DTMParacou}}) (RasterLayer)
+#'
+#' @param relativeelevation (RasterLayer)
+#'
+#' @param speciescriteria Table of species exploitability criteria : species
+#'   names, economic interest level, minimum and maximum felling diameter, in
+#'   the same format of \code{\link{SpeciesCriteria}} (2 levels of commercial
+#'   species) (data.frame)
+#'
+#' @param volumeparameters Volume parameters table (in the same format of
+#'   \code{\link{ForestZoneVolumeParametersTable}}) to compute the harvestable
+#'   volume of each tree, depend to its geographic zone if several locations
+#'   (data.frame)
+#'
+#' @param scenario Logging scenario: "RIL1", "RIL2broken", "RIL2", "RIL3",
+#'   "RIL3fuel", "RIL3fuelhollow" or "manual"(character) (see the
+#'   \code{\link{vignette}})
+#'
+#' @param objective Objective volume per hectare (numeric)
+#'
+#' @param fuel Fuel wood exploitation: no exploitation = "0", damage
+#'   exploitation in fuelwood = "1", exploitation of hollow trees and damage in
+#'   fuelwood = "2"
+#'
+#' @param diversification Taking of other species in addition to the main
+#'   commercial species (2 levels of commercial species in the
+#'   \code{\link{SpeciesCriteria}} table) (logical)
+#'
+#' @param winching No cable or grapple = "0", only cable = "1", grapple + cable
+#'   = "2"
+#'
+#' @param directionalfelling Directional felling = "0" (absent), "1" (only to
+#'   avoid damage to future and reserve trees), "2" (avoid damage to future and
+#'   reserve trees + track orientation)
+#'
[…]

### 2021-08-20 tests/testthat/test-selected.R

@@ -3,15 +3,19 @@ test_that("selected", {
   # Check the function arguments
   # Test data preparation
   data(Paracou6_2016)
+  data(SpeciesCriteria)
+
   Paracou6_2016 <- dplyr::slice(Paracou6_2016, 1:2000)
 
   data(DTMParacou)
   data(PlotSlope)
 
-  inventory <- ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016)))
+  inventory <- addtreedim(inventorycheckformat(Paracou6_2016), volumeparameters = ForestZoneVolumeParametersTable)
+  inventory0 <- ONFGuyafortaxojoin(inventory, SpeciesCriteria)
 
-  harvestableOutputs <- harvestable(inventory, diversification = TRUE, specieslax = FALSE,
-                                    topography = DTMParacou, plotslope = PlotSlope, advancedloggingparameters = loggingparameters())
+  harvestableOutputs <- harvestable(inventory0, diversification = TRUE, specieslax = FALSE,
+                                    topography = DTMParacou, plotslope = PlotSlope,
+                                    advancedloggingparameters = loggingparameters())
 
   inventory <- harvestableOutputs$inventory
   HVinit <- harvestableOutputs$HVinit
@@ -70,7 +74,7 @@ test_that("selected", {
   VO <- HVinit + 20
 
   ## if (!diversification && specieslax)
-  inventory <- harvestable(ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016))),
+  inventory <- harvestable(inventory0,
                            diversification = FALSE, specieslax = TRUE, topography = DTMParacou, plotslope = PlotSlope)$inventory
 
   testinventory <- suppressMessages(selected(inventory, scenario = "manual", fuel = "0",
@@ -88,7 +92,7 @@ test_that("selected", {
                "By default or by your choice, the simulation stops")
 
   # if (!diversification && !specieslax && objectivelax)
-  inventory <- harvestable(ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016))),
+  inventory <- harvestable(inventory0,
                            diversification = FALSE,  specieslax = FALSE, topography = DTMParacou, plotslope = PlotSlope)$inventory
 
   expect_message(selected(inventory, scenario = "manual", fuel = "0", diversification = FALSE,  specieslax = FALSE, objectivelax = TRUE,
@@ -96,7 +100,7 @@ test_that("selected", {
[…]

### 2021-08-20 tests/testthat/test-treefelling.R

@@ -2,7 +2,7 @@ test_that("treefelling", {
 
   # Test data
   data(Paracou6_2016)
-  # Paracou6_2016 <- dplyr::slice(Paracou6_2016, 1:2000)
+  Paracou6_2016 <- dplyr::slice(Paracou6_2016, 1:2000)
   MatrixInventory <- as.matrix(Paracou6_2016)
 
   MainTrail <- sf::st_linestring(matrix(c(286400, 583130,
@@ -28,7 +28,7 @@ test_that("treefelling", {
   PolList = list(pol1,pol2)
   ScndTrail <- st_multipolygon(PolList)
 
-  inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
+  inventory <- addtreedim(inventorycheckformat(Paracou6_2016), volumeparameters = ForestZoneVolumeParametersTable)
   inventory <- suppressMessages(treeselection(inventory, objective = 20, scenario ="manual",
                              fuel = "0", diversification = TRUE, specieslax = FALSE,
                              objectivelax = TRUE, topography = DTMParacou, plotslope = PlotSlope,

### 2021-08-23 R/DRAFT_secondtrailsopening (conflicted copy 2021-08-23 005423).Rmd

--- 2021-08-17 R/DRAFT_secondtrailsopening.Rmd
@@
 
-scenario = "RIL1"
+scenario = "RIL3"
 advancedloggingparameters = loggingparameters()
@@
 
-scenarios <- scenariosparameters(scenario = scenario, objective = 70,
+scenarios <- scenariosparameters(scenario = scenario, objective = 140,
 fuel = "2", diversification = TRUE, winching = NULL, directionalfelling = NULL)
@@
 
-  CostSlopeMatrix <- list(list(Slope = 3, Cost = 1),
-                          list(Slope = 5, Cost = 3),
+  CostSlopeMatrix <- list(list(Slope = 3, Cost = 3),
+                          list(Slope = 5, Cost = 5),
                           list(Slope = 12, Cost = 20),
@@
 
+    if (scenarios$winching == "2") {
+
+  plotSlopePointGrpl <- dplyr::as_tibble(raster::rasterToPoints(PlotSlope))
+
+  CostRasterPointGrpl <- dplyr::as_tibble(raster::rasterToPoints(CostRaster))
+
+  # left join par x et y
+  plotTibGrpl <-
+    dplyr::left_join(plotSlopePointGrpl, CostRasterPointGrpl, by = c('x', 'y'))
+
+  CostSlopeRasterGrpl <- plotTibGrpl %>%
+    mutate(Exploit = if_else(
+        slope <= atan(advancedloggingparameters$GrappleMaxslope/100), # on est en radians pour la pente, donc .264 radians = 27% de pente
+      true = 0,
+      false = Inf
+    )) %>% dplyr::select(x,y,Exploit)
+
+  CostRasterGrpl <- raster::rasterFromXYZ(CostSlopeRasterGrpl, crs = 32622)
+
+  CostRasterGrpl <- CostRaster + CostRasterGrpl
+
+  CostRasterGrpl <- rasterize(x = as_Spatial(PartMainTrails),
+                                    y = CostRasterGrpl , 
+                                    field = 1E-4, 
+                                    update = TRUE)
+
+  CostRasterMeanGrpl <- aggregate(CostRasterGrpl, fact=3, fun=mean)
+  CostRasterMeanGrpl <- crop(CostRasterMeanGrpl,  CostRaster)
+  CostRasterMeanGrpl <- mask(CostRasterMeanGrpl, Plots)
+
+  }
+
     CostRaster <- rasterize(x = as_Spatial(PartMainTrails),
                                     y = CostRaster , 
-                                    field = 1E-3, 
+                                    field = 1E-4, 
                                     update = TRUE)
@@
 
-  pts <- treeselectionoutputs$SelectedTreesPoints %>% sf::st_cast("POINT") %>% sf::st_join(AccessMainTrails)
-  pts <- rbind(AccessPoint %>% mutate(type = "Access"),pts %>% mutate(type = "Tree"))
+  pathLines <- list()
+  k <- 1
 
-  pathLines <- list()
-  k <- 0
+  pts <- treeselectionoutputs$SelectedTreesPoints %>% 
+    sf::st_cast("POINT") %>% 
+    mutate(ID = NA) %>% 
+    mutate(type = "Tree")
 
@@
 
+  winching <- scenarios$winching
+
   if (winching == "0") {
 
-    for (accessid in unique(pts$ID)) {
-
-      selectedPoints <- pts %>% filter(ID == accessid) 
-      PointAcc <- selectedPoints %>% filter(type == "Access") %>% 
-        mutate(ptAcc = dplyr::row_number()) %>% 
-        mutate(EstCost = NA)
   CostDistEst <- AdjTopoLCP(costSurface = CondSurf,
                                 DEM = DEMmean , 
-                                pts = selectedPoints %>% 
+                                pts = pts %>% 
+                                  as_Spatial(),
+                                slopeRdCond = SlopeCond,
+                                paths = FALSE) [,1:dim(AccessPoint)[1]]
+  CostDistEst[CostDistEst == 0] <- NA
+  CostDistEst <- na.exclude(CostDistEst)
+  PointTree <- pts %>% filter(type == "Tree") %>% 
+      mutate(ptAcc = max.col(-CostDistEst))
+  PointTree$ID <- as.factor(PointTree$ptAcc)
+  levels(PointTree$ID) <- as.character(AccessPoint$ID)
+
+  pts <- rbind(AccessPoint %>% 
+                 mutate(type = "Access") %>% 
+                 mutate(ptAcc = row_number()) %>% 
+                 mutate(IPpts = paste0("A.",row_number())),
+               PointTree %>% 
+                 mutate(IPpts = paste0("T.",row_number())))
+
+  PointAcc <- pts %>% filter(type == "Access") %>% 
+        mutate(EstCost = NA)
+
+  CostDistEst <- AdjTopoLCP(costSurface = CondSurf,
+                                DEM = DEMmean , 
+                                pts = pts %>% 
                                   as_Spatial(),
@@
   CostDistEst <- na.exclude(CostDistEst)
-      PointTree <- selectedPoints %>% filter(type == "Tree") %>% 
+  PointTree <- pts %>% filter(type == "Tree") %>% 
         mutate(ptAcc = max.col(-CostDistEst))
@@
                                     y = CostRasterMean  , 
-                                    field = 0.3,update =  TRUE)
+                                    field = 0.1,update =  TRUE)
         CondSurf <- 1/CostRasterMean
 
+        pathLines[[k]] <- TmpPathWIP[[2]]
+        pathLines[[k]]@lines[[1]]@ID <- paste("Path",accessPtId, "-", TreeId, sep = " ")
+
         k <- k +1
-
-            pathLines[[k]] <- TmpPathWIP[[2]]
-            pathLines[[k]]@lines[[1]]@ID <- paste("Path",accessid,"-",accessPtId, "-", TreeId, sep = " ")
 
@@
    }
+  }else{
+
+    # winching == 1/2
+
+    PointAcc <- AccessPoint %>% #def Access Point
+      mutate(type = "Access") %>% 
+      mutate(IDpts = paste0("A.",row_number())) %>% 
+      mutate(n.overlaps = NA, origins = NA) %>% 
+      dplyr::select(-ID)
+
+    if (winching == "2") {
+      ptsGrpl <- pts %>% filter(type == "Tree") %>% #def Grpl point
+                  st_buffer(dist = advancedloggingparameters$GrappleLength) %>%
+                  st_set_precision(1) %>% 
+                  st_intersection() %>% 
+                  st_make_valid()
+
+       ptsGrpl <- ptsGrpl %>%  filter(st_intersects(ptsGrpl ,AccessMainTrails %>% st_union(),sparse = FALSE)) %>% 
+                  mutate(IDpts = paste0("I.",row_number()))
+
+       ptsWIP <- ptsGrpl %>% #def Grpl point as WIP point
+                  st_centroid() %>% 
+                  dplyr::select(-ID)
+
+       ptsCbl <- pts %>% filter(type == "Tree") %>% #def cbl point
+                  st_buffer(dist = advancedloggingparameters$CableLength) %>%
+                  st_set_precision(1) %>% 
+                  st_intersection() %>% 
+                  st_make_valid()
+
+        ptsCbl <- ptsCbl %>% 
+                  filter(st_intersects(ptsCbl ,AccessMainTrails %>% st_union() ,sparse = FALSE)) %>% 
+                  mutate(IDpts = paste0("I.",row_number()))
+
+        ptsWIPCbl <-  ptsCbl %>%
+          st_centroid() %>%
+          dplyr::select(-ID)
+
+        ptsWIP <- ptsWIP %>% 
+                  arrange(desc(n.overlaps))
+
+        RemainTree <- dim(ptsWIP %>% filter(type == "Tree"))[1] + dim(ptsWIPCbl %>% filter(type == "Tree"))[1]
+
+    }else{
+        ptsCbl <- pts %>% filter(type == "Tree") %>% #def cbl point
+                  st_buffer(dist = advancedloggingparameters$CableLength) %>%
+                  st_set_precision(1) %>% 
+                  st_intersection() %>% 
+                  st_make_valid() %>% 
+                  mutate(IDpts = paste0("I.",row_number()))
+
+        ptsWIP <-  ptsCbl %>%#def cbl point as WIP point
+          st_centroid() %>%
+          dplyr::select(-ID)
+
+        ptsWIP <- ptsWIP %>%  #filter cbl intersection centroid point out plot
+                  filter(st_intersects(ptsWIP ,Plots %>% st_as_sf(),sparse = FALSE)) %>% 
+                  arrange(desc(n.overlaps))
+
+        RemainTree <- dim(ptsWIP %>% filter(type == "Tree"))[1]
 
@@
 
-  }
+    limRec <- dim(pts)[1]
 
-  if (winching == "1") {
+    WinchingSwitch <- FALSE
 
-    ptsCabble <- pts %>% filter(type == "Tree") %>%
-      st_buffer(dist = advancedloggingparameters$CableLength) %>%
-      st_intersection() %>% 
-      st_make_valid() %>%
-      arrange(desc(n.overlaps)) %>% 
-      mutate(ID_pts = paste0("T.",row_number()))
+    while (RemainTree !=0L & k <= limRec) {
 
-    for (accessid in unique(pts$ID)) {
+      Grpl2CblFlag <- FALSE
 
-      PointAcc <- pts %>% filter(ID == accessid) %>% filter(type == "Access")%>% 
-       mutate(ptAcc = row_number()) %>% 
+      print(paste0("iter : ",k, "| Max : ",limRec) )
+
+    ptsWIPmax <- rbind(PointAcc,ptsWIP %>% 
+                         filter(n.overlaps == max(ptsWIP$n.overlaps))) %>% 
+              mutate(TypeAcc = NA) %>% 
               mutate(EstCost = NA)  %>% 
-        mutate(ID_pts = paste0("A.",row_number()))
+              mutate(ptsAcc = NA)
 
-      InPlot <- st_intersects(ptsCabble %>% 
-        filter(ID == accessid) %>% 
-        st_centroid(),Plots %>% st_as_sf(),sparse = FALSE)
-
-      ptsCabbleCentroid <- ptsCabble %>% 
-        filter(ID == accessid) %>% 
-        st_centroid() %>% dplyr::mutate(InPlot = InPlot) %>% 
-        filter(InPlot == TRUE) %>% dplyr::select(-InPlot) %>% 
-       mutate(ptAcc = NA) %>% 
-      mutate(EstCost = NA) %>% arrange(desc(n.overlaps))
-
-      selectedPoints <- rbind(PointAcc %>% mutate(n.overlaps = NA, origins = NA),ptsCabbleCentroid %>% 
-        st_sf())
-
-      CostDistEst <- AdjTopoLCP(costSurface = CondSurf,
+    CostDistEstCbl <- AdjTopoLCP(costSurface = CondSurf,
                                 DEM = DEMmean , 
-                                pts = selectedPoints %>% 
+                                pts = ptsWIPmax %>% 
                                   as_Spatial(),
@@
                                 paths = FALSE) [,1:dim(PointAcc)[1]]
-      CostDistEst[CostDistEst == 0] <- NA
-      CostDistEst <- na.exclude(CostDistEst)
-      PointTree <- selectedPoints %>% filter(type == "Tree") %>% 
-        mutate(ptAcc = max.col(-CostDistEst))
+
+    CostDistEstCbl <- CostDistEstCbl[(dim(PointAcc)[1]+1):dim(CostDistEstCbl)[1],1:dim(PointAcc)[1]]
+
+    PointTree <- ptsWIPmax %>% filter(type == "Tree") %>% 
+        mutate(ptAccCbl = max.col(-matrix(CostDistEstCbl,ncol = dim(PointAcc)[1] ),ties.method = "first"))
+
     if (dim(PointAcc)[1] == 1) {
-        PointTree <- PointTree %>% mutate(EstCost = CostDistEst)
-      }else{PointTree <- PointTree %>% mutate(EstCost = apply(CostDistEst,1, min))}
-      selectedPoints <- rbind(PointAcc %>% mutate(n.overlaps = NA, origins = NA),PointTree)
+      PointTree <- PointTree %>% mutate(EstCostCbl = matrix(CostDistEstCbl,ncol = dim(PointAcc)[1] ))
+    }else{
+      PointTree <- PointTree %>% mutate(EstCostCbl = apply(CostDistEstCbl,1, min))
+      }
 
-      for (accessPtId in 1:dim(PointAcc)[1]) {
-        TmpSelectedPts <- selectedPoints %>% 
-          filter(ptAcc == accessPtId)
+      if (winching == "2") {
 
-        TmpAccPts <- TmpSelectedPts %>% 
-          filter(type == "Access")
+        CondSurfGrpl <- 1/CostRasterMeanGrpl
 
-        TmpTreePts <- TmpSelectedPts %>% 
-          filter(type == "Tree") %>% 
-          arrange(desc(n.overlaps),EstCost)
+        CostDistEstGrpl <- AdjTopoLCP(costSurface = CondSurfGrpl,
+                                DEM = DEMmean , 
+                                pts = ptsWIPmax %>% 
+                                  as_Spatial(),
+                                slopeRdCond = SlopeCond,
+                                paths = FALSE) [,1:dim(PointAcc)[1]]
 
-        TreeId <- 1
+        CostDistEstGrpl <- CostDistEstGrpl[(dim(PointAcc)[1]+1):dim(CostDistEstGrpl)[1],1:dim(PointAcc)[1]]
 
-          while (dim(TmpTreePts)[1] != 0){
+        PointTree <- PointTree %>% 
+          mutate(ptAccGpl = max.col(-t(CostDistEstGrpl),ties.method = "first"))
 
-            TmpPtsWIP <- rbind(TmpAccPts %>%  
+          if (dim(PointAcc)[1] == 1) {
+            PointTree <- PointTree %>% mutate(EstCostGrpl = CostDistEstGrpl)
+          }else{
+              PointTree <- PointTree %>% mutate(EstCostGrpl = apply(CostDistEstGrpl,1, min))}
+
+        CostDistEstGrpl[CostDistEstGrpl != Inf] <- 0
+        CostDistEstGrpl[CostDistEstGrpl == Inf] <- 1
+
+        for (j in 1:dim(CostDistEstGrpl)[1]) {
+          PointTree[j,"TypeAcc"] <-  as.character(prod(CostDistEstGrpl[j,]))
+        }
+        PointTree$TypeAcc[PointTree$TypeAcc == "0"] <- "Grpl"
+        PointTree$TypeAcc[PointTree$TypeAcc == "1"] <- "Cbl"
+
+        PointTree$ptsAcc[PointTree$TypeAcc == "Grpl"] <- PointTree$ptAccGpl[PointTree$TypeAcc == "Grpl"]
+        PointTree$ptsAcc[PointTree$TypeAcc != "Grpl"] <- PointTree$ptAccCbl[PointTree$TypeAcc != "Grpl"]
+
+        PointTree$EstCost[PointTree$TypeAcc == "Grpl"] <- PointTree$EstCostGrpl[PointTree$TypeAcc == "Grpl"]
+        PointTree$EstCost[PointTree$TypeAcc != "Grpl"] <- PointTree$EstCostCbl[PointTree$TypeAcc != "Grpl"]
+
+        PointTree <- PointTree %>% arrange(desc(TypeAcc),EstCost)
+
+            if (PointTree$TypeAcc[1] == "Grpl") {
+
+              TmpPtsWIP <- ptsGrpl %>% 
+                                filter(IDpts == PointTree$IDpts[1])  %>%  
+                                st_union() %>% 
+                                st_cast("POINT") %>% 
+                                st_as_sf() %>%
+                                mutate(type = "Overlay") %>% 
+                                mutate(ptsAcc = PointTree$ptsAcc[1]) %>% 
+                                mutate(IDpts = PointTree$IDpts[1]) %>% 
+                                mutate(origins = PointTree$origins[1])
+
+              }else{
+
+            Grpl2CblFlag <- TRUE
+
+            ptsWIP$Logged<- FALSE
+
+            for (j in 1:dim(ptsWIP)[1]) {
+              ptsWIP$Logged[j] <- prod(as.integer(PointTree$origins[1][[1]] %in% ptsWIP$origins[[j]])+1) != 1
+            }
+
+            ptsWIP[ptsWIP$Logged == TRUE,"Logged"] <- NA
+            ptsWIP <- na.exclude(ptsWIP)
+
+            ptsWIP <- ptsWIP %>% 
+              dplyr::select(-Logged) %>% 
+              arrange(desc(n.overlaps))
+
+            TmpPtsWIP <- ptsCbl %>% 
+                                filter(IDpts == PointTree$IDpts[1])  %>%  
+                                st_union() %>% 
+                                st_cast("POINT") %>% 
+                                st_as_sf() %>%
+                                mutate(type = "Overlay") %>% 
+                                mutate(ptsAcc = PointTree$ptsAcc[1]) %>% 
+                                mutate(IDpts = PointTree$IDpts[1]) %>% 
+                                mutate(origins = PointTree$origins[1])
+              }
+
+      }else{
+
+        TmpPtsWIP <- ptsCbl %>% 
+                                filter(IDpts == PointTree$IDpts[1])  %>%  
+                                st_union() %>% 
+                                st_cast("POINT") %>% 
+                                st_as_sf() %>%
+                                mutate(type = "Overlay") %>% 
+                                mutate(ptsAcc = PointTree$ptsAcc[1]) %>% 
+                                mutate(IDpts = PointTree$IDpts[1]) %>% 
+                                mutate(origins = PointTree$origins[1])
+
+      }
+
+              TmpPtsWIP <- TmpPtsWIP  %>%  
+                                filter(st_intersects(TmpPtsWIP,AccessMainTrails %>% st_union(),sparse = FALSE))
+
+              TmpPtsWIP <- rbind(PointAcc %>%  
                                 st_union() %>% 
@@
                                 st_as_sf() %>% 
-                                 mutate(ID = accessid)%>% 
                                 mutate(type = "Access") %>% 
-                                 mutate(ptAcc = accessPtId) %>% 
-                                 mutate(ID_Pts = NA),ptsCabble %>% 
-                                filter(ID_pts == TmpTreePts[TreeId,"ID_pts"]$ID_pts)  %>%  
-                                st_union() %>% 
-                                st_cast("POINT")%>% 
-                                 st_as_sf()%>% 
-                                 mutate(ID = accessid)%>% 
-                                 mutate(type = "Overlay")%>% 
-                                 mutate(ptAcc = accessPtId) %>% 
-                                 mutate(ID_Pts = TmpTreePts[TreeId,"ID_pts"]$ID_pts))
+                                mutate(ptsAcc = NA ) %>% 
+                                mutate(IDpts = NA) %>% 
+                                mutate(origins = NA),TmpPtsWIP)
 
             CostDistEstWIP <-  AdjTopoLCP(costSurface = CondSurf,DEM = DEMmean , pts = TmpPtsWIP %>% as_Spatial(),
-                              slopeRdCond = SlopeCond,paths = FALSE)[,1]
+                              slopeRdCond = SlopeCond,paths = FALSE)[,1:dim(PointAcc)[1]]
 
-            CostDistEstWIP[CostDistEstWIP == 0] <- NA
-            CostDistEstWIP <- na.exclude(CostDistEstWIP)
+            CostDistEstWIP <- CostDistEstWIP[(dim(PointAcc)[1]+1):dim(CostDistEstWIP)[1],]
 
-            PointTreeWIP <- TmpPtsWIP %>% filter(type == "Overlay") %>% 
-              mutate(EstCost= CostDistEstWIP) %>% arrange(EstCost)
+          if (dim(PointAcc)[1] == 1) {
+            PointTreeWIP <- TmpPtsWIP %>% 
+              filter(type == "Overlay") %>% 
+              mutate(EstCost = CostDistEstWIP) %>% 
+              arrange(EstCost)
+          }else{
+
+            PointTreeWIP <- TmpPtsWIP %>% 
+                filter(type == "Overlay") %>% 
+                mutate(EstCost = apply(CostDistEstWIP,1, min)) %>% 
+                arrange(EstCost)
+
+          }
 
             TmpPtsWIP <- rbind(TmpPtsWIP %>% filter(type == "Access") %>% mutate(EstCost = NA),PointTreeWIP[1,])
+
+            TmpPathWIP <- AdjTopoLCP(costSurface = CondSurf,DEM = DEMmean , pts = TmpPtsWIP %>% as_Spatial(),
+                              slopeRdCond = SlopeCond,paths = FALSE)
+
+            TmpPathWIPCost <- TmpPathWIP[1:dim(PointAcc)[1],dim(PointAcc)[1]+1]
+
+            LCPathWIP <- max.col(t(-TmpPathWIPCost))
+
+            TmpPtsWIP <- rbind(TmpPtsWIP[LCPathWIP,],PointTreeWIP[1,])
 
@@
                                     field = 0.3,update =  TRUE)
+
+            pathLines[[k]] <- TmpPathWIP[[2]]
+            pathLines[[k]]@lines[[1]]@ID <- paste("Path",
+                                                  LCPathWIP,
+                                                  "-",
+                                                  paste(as.character(unlist(PointTreeWIP$origins[1][[1]])), 
+                                                        collapse='.'), 
+                                                  sep = " ")
+
              k <- k +1
 
-            pathLines[[k]] <- TmpPathWIP[[2]]
-            pathLines[[k]]@lines[[1]]@ID <- paste("Path",accessid,"-",accessPtId, "-", TreeId, sep = " ")
+             if (Grpl2CblFlag) {
 
-            CbblePtsWIP <- ptsCabble %>% filter(ID_pts == TmpTreePts[TreeId,"ID_pts"]$ID_pts)
+               ptsWIPCbl$Logged<- FALSE
+              for (j in 1:dim(ptsWIPCbl)[1]) {
+              ptsWIPCbl$Logged[j] <- prod(as.integer(PointTreeWIP$origins[1][[1]] %in% ptsWIPCbl$origins[[j]])+1) != 1
+              }
+                          ptsWIPCbl[ptsWIPCbl$Logged == TRUE,"Logged"] <- NA
+            ptsWIPCbl <- na.exclude(ptsWIPCbl)
+                        ptsWIPCbl <- ptsWIPCbl %>% 
+              dplyr::select(-Logged) %>% 
+              arrange(desc(n.overlaps))
+             }else{
 
-            CbblePtsWIP$origins [[1]] %in% TmpTreePts$origins [[2]]
+            ptsWIP$Logged<- FALSE
 
-            TreeId <- TreeId + 1
+            for (j in 1:dim(ptsWIP)[1]) {
+              ptsWIP$Logged[j] <- prod(as.integer(PointTreeWIP$origins[1][[1]] %in% ptsWIP$origins[[j]])+1) != 1
+            }
+
+                        ptsWIP[ptsWIP$Logged == TRUE,"Logged"] <- NA
+            ptsWIP <- na.exclude(ptsWIP)
+
+            ptsWIP <- ptsWIP %>% 
+              dplyr::select(-Logged) %>% 
+              arrange(desc(n.overlaps))
+
+            if (winching == "2") {
+
+              ptsWIPCbl$Logged<- FALSE
+              for (j in 1:dim(ptsWIPCbl)[1]) {
+              ptsWIPCbl$Logged[j] <- prod(as.integer(PointTreeWIP$origins[1][[1]] %in% ptsWIPCbl$origins[[j]])+1) != 1
+              }
+                          ptsWIPCbl[ptsWIPCbl$Logged == TRUE,"Logged"] <- NA
+            ptsWIPCbl <- na.exclude(ptsWIPCbl)
+                        ptsWIPCbl <- ptsWIPCbl %>% 
+              dplyr::select(-Logged) %>% 
+              arrange(desc(n.overlaps))
+            }
 
             }
+
+            if (dim(ptsWIP %>% filter(type == "Tree"))[1] == 0 & WinchingSwitch == FALSE) {
+              winching <- "1"
+              ptsWIP <- ptsWIPCbl
+              WinchingSwitch <- TRUE
             }
+
+            if (winching == "2") {
+              RemainTree <- dim(ptsWIP %>% filter(type == "Tree"))[1] + dim(ptsWIPCbl %>% filter(type == "Tree"))[1]
+            }else{
+             RemainTree <- dim(ptsWIP %>% filter(type == "Tree"))[1] 
             }
@@
 
-  if (winching == "2") {
+```
 
-  }
-
+```{r}
   paths <- do.call(rbind, pathLines)
 
-    df <-  as_tibble(rasterToPoints(CostRasterMean)) %>% mutate( Cost = layer) %>% dplyr::select(-layer)
+    df <-  as_tibble(rasterToPoints(CostRasterMeanGrpl)) %>% mutate( Cost = layer) %>% dplyr::select(-layer)
   df2 <- as_tibble(rasterToPoints(DEM)) %>% mutate( z = Topo_P6_PARACOU) %>% dplyr::select(-Topo_P6_PARACOU)
@@
     geom_raster(data = df, aes(x =x , y = y, fill = Cost)) +  geom_sf(data = pts) + scale_fill_gradientn(colours = rev(terrain.colors(225)))  + geom_sf( data = sf::st_as_sf(paths))    + geom_sf(data =  paths %>% st_as_sf()  %>% smoothr::smooth(method = "ksmooth",smoothness = 5) %>% st_buffer(dist = 4) %>% st_union(), color = 'red', alpha = 0.1 )  + theme_bw()
-
 ```

### 2021-08-23 R/DRAFT_secondtrailsopening.Rmd

@@
 
+  winching <- scenarios$winching
+
   if (winching == "0") {
 
-    for (accessid in unique(pts$ID)) {
-
-      selectedPoints <- pts %>% filter(ID == accessid) 
-      PointAcc <- selectedPoints %>% filter(type == "Access") %>% 
-        mutate(ptAcc = dplyr::row_number()) %>% 
-        mutate(EstCost = NA)
   CostDistEst <- AdjTopoLCP(costSurface = CondSurf,
                                 DEM = DEMmean , 
-                                pts = selectedPoints %>% 
+                                pts = pts %>% 
+                                  as_Spatial(),
+                                slopeRdCond = SlopeCond,
+                                paths = FALSE) [,1:dim(AccessPoint)[1]]
+  CostDistEst <- CostDistEst[(dim(PointAcc)[1]+1):dim(CostDistEst)[1],1:dim(PointAcc)[1]]
+
+  CostDistEst <- matrix(CostDistEst,ncol = dim(PointAcc)[1] )
+
+  PointTree <- pts %>% filter(type == "Tree") %>% 
+      mutate(ptAcc = max.col(-CostDistEst))
+  PointTree$ID <- as.factor(PointTree$ptAcc)
+  levels(PointTree$ID) <- as.character(AccessPoint$ID)
+
+  pts <- rbind(AccessPoint %>% 
+                 mutate(type = "Access") %>% 
+                 mutate(ptAcc = row_number()) %>% 
+                 mutate(IPpts = paste0("A.",row_number())),
+               PointTree %>% 
+                 mutate(IPpts = paste0("T.",row_number())))
+
+  PointAcc <- pts %>% filter(type == "Access") %>% 
+        mutate(EstCost = NA)
+
+  CostDistEst <- AdjTopoLCP(costSurface = CondSurf,
+                                DEM = DEMmean , 
+                                pts = pts %>% 
                                   as_Spatial(),
@@
                                 paths = FALSE) [,1:dim(PointAcc)[1]]
-      CostDistEst[CostDistEst == 0] <- NA
-      CostDistEst <- na.exclude(CostDistEst)
-      PointTree <- selectedPoints %>% filter(type == "Tree") %>% 
+  CostDistEst <- CostDistEst[(dim(PointAcc)[1]+1):dim(CostDistEst)[1],1:dim(PointAcc)[1]]
+
+  CostDistEst <- matrix(CostDistEst,ncol = dim(PointAcc)[1] )
+
+  PointTree <- pts %>% filter(type == "Tree") %>% 
         mutate(ptAcc = max.col(-CostDistEst))
@@
                                 paths = FALSE) [,1:dim(PointAcc)[1]]
-      CostDistEst[CostDistEst == 0] <- NA
-      CostDistEst <- na.exclude(CostDistEst)
-      PointTree <- selectedPoints %>% filter(type == "Tree") %>% 
-        mutate(ptAcc = max.col(-CostDistEst))
+
+    CostDistEstCbl <- CostDistEstCbl[(dim(PointAcc)[1]+1):dim(CostDistEstCbl)[1],1:dim(PointAcc)[1]]
+
+    CostDistEstCbl <- matrix(CostDistEstCbl,ncol = dim(PointAcc)[1] )
+
+    PointTree <- ptsWIPmax %>% filter(type == "Tree") %>% 
+        mutate(ptAccCbl = max.col(- CostDistEstCbl,ties.method = "first"))
+
     if (dim(PointAcc)[1] == 1) {
-        PointTree <- PointTree %>% mutate(EstCost = CostDistEst)
-      }else{PointTree <- PointTree %>% mutate(EstCost = apply(CostDistEst,1, min))}
-      selectedPoints <- rbind(PointAcc %>% mutate(n.overlaps = NA, origins = NA),PointTree)
+      PointTree <- PointTree %>% mutate(EstCostCbl = CostDistEstCbl)
+    }else{
+      PointTree <- PointTree %>% mutate(EstCostCbl = apply(CostDistEstCbl,1, min))
+      }
 
-      for (accessPtId in 1:dim(PointAcc)[1]) {
-        TmpSelectedPts <- selectedPoints %>% 
-          filter(ptAcc == accessPtId)
+      if (winching == "2") {
 
-        TmpAccPts <- TmpSelectedPts %>% 
-          filter(type == "Access")
+        CondSurfGrpl <- 1/CostRasterMeanGrpl
 
-        TmpTreePts <- TmpSelectedPts %>% 
-          filter(type == "Tree") %>% 
-          arrange(desc(n.overlaps),EstCost)
+        CostDistEstGrpl <- AdjTopoLCP(costSurface = CondSurfGrpl,
+                                DEM = DEMmean , 
+                                pts = ptsWIPmax %>% 
+                                  as_Spatial(),
+                                slopeRdCond = SlopeCond,
+                                paths = FALSE) [,1:dim(PointAcc)[1]]
 
-        TreeId <- 1
+        CostDistEstGrpl <- CostDistEstGrpl[(dim(PointAcc)[1]+1):dim(CostDistEstGrpl)[1],1:dim(PointAcc)[1]]
+        CostDistEstGrpl <- matrix(CostDistEstGrpl,ncol = dim(PointAcc)[1] )
 
-          while (dim(TmpTreePts)[1] != 0){
+        PointTree <- PointTree %>% 
+          mutate(ptAccGpl = max.col(-matrix(CostDistEstGrpl,ncol = dim(PointAcc)[1] ),ties.method = "first"))
 
-            TmpPtsWIP <- rbind(TmpAccPts %>%  
+          if (dim(PointAcc)[1] == 1) {
+            PointTree <- PointTree %>% mutate(EstCostGrpl = CostDistEstGrpl)
+          }else{
+              PointTree <- PointTree %>% mutate(EstCostGrpl = apply(matrix(CostDistEstGrpl,ncol = dim(PointAcc)[1] ),1, min))}
+
+        CostDistEstGrpl[CostDistEstGrpl != Inf] <- 0
+        CostDistEstGrpl[CostDistEstGrpl == Inf] <- 1
+
+        for (j in 1:dim(CostDistEstGrpl)[1]) {
+          PointTree[j,"TypeAcc"] <-  as.character(prod(CostDistEstGrpl[j,]))
+        }
+        PointTree$TypeAcc[PointTree$TypeAcc == "0"] <- "Grpl"
+        PointTree$TypeAcc[PointTree$TypeAcc == "1"] <- "Cbl"
+
+        PointTree$ptsAcc[PointTree$TypeAcc == "Grpl"] <- PointTree$ptAccGpl[PointTree$TypeAcc == "Grpl"]
+        PointTree$ptsAcc[PointTree$TypeAcc != "Grpl"] <- PointTree$ptAccCbl[PointTree$TypeAcc != "Grpl"]
+
+        PointTree$EstCost[PointTree$TypeAcc == "Grpl"] <- PointTree$EstCostGrpl[PointTree$TypeAcc == "Grpl"]
+        PointTree$EstCost[PointTree$TypeAcc != "Grpl"] <- PointTree$EstCostCbl[PointTree$TypeAcc != "Grpl"]
+
+        PointTree <- PointTree %>% arrange(desc(TypeAcc),EstCost)
+
+            if (PointTree$TypeAcc[1] == "Grpl") {
+
+              TmpPtsWIP <- ptsGrpl %>% 
+                                filter(IDpts == PointTree$IDpts[1])  %>%  
+                                st_union() %>% 
+                                st_cast("POINT") %>% 
+                                st_as_sf() %>%
+                                mutate(type = "Overlay") %>% 
+                                mutate(ptsAcc = PointTree$ptsAcc[1]) %>% 
+                                mutate(IDpts = PointTree$IDpts[1]) %>% 
+                                mutate(origins = PointTree$origins[1])
+
+              }else{
+
+            Grpl2CblFlag <- TRUE
+
+            ptsWIP$Logged<- FALSE
+
+            for (j in 1:dim(ptsWIP)[1]) {
+              ptsWIP$Logged[j] <- prod(as.integer(PointTree$origins[1][[1]] %in% ptsWIP$origins[[j]])+1) != 1
+            }
+
+            ptsWIP[ptsWIP$Logged == TRUE,"Logged"] <- NA
+            ptsWIP <- na.exclude(ptsWIP)
+
+            ptsWIP <- ptsWIP %>% 
+              dplyr::select(-Logged) %>% 
+              arrange(desc(n.overlaps))
+
+            TmpPtsWIP <- ptsCbl %>% 
+                                filter(IDpts == PointTree$IDpts[1])  %>%  
+                                st_union() %>% 
+                                st_cast("POINT") %>% 
+                                st_as_sf() %>%
+                                mutate(type = "Overlay") %>% 
+                                mutate(ptsAcc = PointTree$ptsAcc[1]) %>% 
+                                mutate(IDpts = PointTree$IDpts[1]) %>% 
+                                mutate(origins = PointTree$origins[1])
+              }
+
+      }else{
+
+        TmpPtsWIP <- ptsCbl %>% 
+                                filter(IDpts == PointTree$IDpts[1])  %>%  
+                                st_union() %>% 
+                                st_cast("POINT") %>% 
+                                st_as_sf() %>%
+                                mutate(type = "Overlay") %>% 
+                                mutate(ptsAcc = PointTree$ptsAcc[1]) %>% 
+                                mutate(IDpts = PointTree$IDpts[1]) %>% 
+                                mutate(origins = PointTree$origins[1])
+
+      }
+
+              TmpPtsWIP <- TmpPtsWIP  %>%  
+                                filter(st_intersects(TmpPtsWIP,AccessMainTrails %>% st_union(),sparse = FALSE))
+
+              TmpPtsWIP <- rbind(PointAcc %>%  
                                 st_union() %>% 
@@
                                 st_as_sf() %>% 
-                                 mutate(ID = accessid)%>% 
                                 mutate(type = "Access") %>% 
-                                 mutate(ptAcc = accessPtId) %>% 
-                                 mutate(ID_Pts = NA),ptsCabble %>% 
-                                filter(ID_pts == TmpTreePts[TreeId,"ID_pts"]$ID_pts)  %>%  
-                                st_union() %>% 
-                                st_cast("POINT")%>% 
-                                 st_as_sf()%>% 
-                                 mutate(ID = accessid)%>% 
-                                 mutate(type = "Overlay")%>% 
-                                 mutate(ptAcc = accessPtId) %>% 
-                                 mutate(ID_Pts = TmpTreePts[TreeId,"ID_pts"]$ID_pts))
+                                mutate(ptsAcc = NA ) %>% 
+                                mutate(IDpts = NA) %>% 
+                                mutate(origins = NA),TmpPtsWIP)
 
             CostDistEstWIP <-  AdjTopoLCP(costSurface = CondSurf,DEM = DEMmean , pts = TmpPtsWIP %>% as_Spatial(),
-                              slopeRdCond = SlopeCond,paths = FALSE)[,1]
+                              slopeRdCond = SlopeCond,paths = FALSE)[,1:dim(PointAcc)[1]]
 
-            CostDistEstWIP[CostDistEstWIP == 0] <- NA
-            CostDistEstWIP <- na.exclude(CostDistEstWIP)
+            CostDistEstWIP <- CostDistEstWIP[(dim(PointAcc)[1]+1):dim(CostDistEstWIP)[1],]
 
-            PointTreeWIP <- TmpPtsWIP %>% filter(type == "Overlay") %>% 
-              mutate(EstCost= CostDistEstWIP) %>% arrange(EstCost)
+            CostDistEstWIP <- matrix(CostDistEstWIP, ncol = dim(PointAcc)[1])
+
+          if (dim(PointAcc)[1] == 1) {
+            PointTreeWIP <- TmpPtsWIP %>% 
+              filter(type == "Overlay") %>% 
+              mutate(EstCost = CostDistEstWIP) %>% 
+              arrange(EstCost)
+          }else{
+
+            PointTreeWIP <- TmpPtsWIP %>% 
+                filter(type == "Overlay") %>% 
+                mutate(EstCost = apply(CostDistEstWIP,1, min)) %>% 
+                arrange(EstCost)
+
+          }
 
             TmpPtsWIP <- rbind(TmpPtsWIP %>% filter(type == "Access") %>% mutate(EstCost = NA),PointTreeWIP[1,])
+
+            TmpPathWIP <- AdjTopoLCP(costSurface = CondSurf,DEM = DEMmean , pts = TmpPtsWIP %>% as_Spatial(),
+                              slopeRdCond = SlopeCond,paths = FALSE)
+
+            TmpPathWIPCost <- TmpPathWIP[1:dim(PointAcc)[1],dim(PointAcc)[1]+1]
+
+            LCPathWIP <- max.col(t(-TmpPathWIPCost))
+
+            TmpPtsWIP <- rbind(TmpPtsWIP[LCPathWIP,],PointTreeWIP[1,])
 
@@
 
-  if (winching == "2") {
+```
 
-  }
-
+```{r}
   paths <- do.call(rbind, pathLines)
@@
   ggplot() +
-    geom_raster(data = df, aes(x =x , y = y, fill = Cost)) +  geom_sf(data = pts) + scale_fill_gradientn(colours = rev(terrain.colors(225)))  + geom_sf( data = sf::st_as_sf(paths))    + geom_sf(data =  paths %>% st_as_sf()  %>% smoothr::smooth(method = "ksmooth",smoothness = 5) %>% st_buffer(dist = 4) %>% st_union(), color = 'red', alpha = 0.1 )  + theme_bw()
-
+    geom_raster(data = df, aes(x =x , y = y, fill = Cost)) +  geom_sf(data = pts) + scale_fill_gradientn(colours = rev(terrain.colors(225)))  + geom_sf( data = sf::st_as_sf(paths))    + geom_sf(data =  paths %>% st_as_sf()  %>% smoothr::smooth(method = "ksmooth",smoothness = 5) %>% st_buffer(dist = advancedloggingparameters$ScndTrailWidth) %>% st_union(), color = 'red', alpha = 0.1 )  + theme_bw()
 ```

### 2021-08-25 R/Volume reviews functions.Rmd
loggingsummary and loggingsimulation functions

--- 2021-07-13 R/Volume reviews functions.Rmd
@@
 INPUT : inventory + fuel
-OUTPUT : LoggedVolume
+OUTPUT : TimberLoggedVolume
 
-Si type != "RIL3fuelhollow"  ou (type == "manual"& fuel !="2"): 
-LoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
+Si scenario != "RIL3fuelhollow"  ou (scenario == "manual"& fuel !="2"): 
+TimberLoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
 
-Si type = "RIL3fuelhollow" ou (type == "manual"& fuel =="2"): NoHollowLoggedVolume = ∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
-LoggedVolume = ∑NoHollowLoggedVolume  et ⅔ du volume de ceux codés ProbedHollow = "1".
+Si scenario = "RIL3fuelhollow" ou (scenario == "manual"& fuel =="2"): NoHollowTimberLoggedVolume = ∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
+TimberLoggedVolume = ∑NoHollowTimberLoggedVolume  et ⅔ du volume de ceux codés ProbedHollow = "1".
 
@@
 
-  LoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
+  TimberLoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
 }
@@
 
-  NoHollowLoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
-  LoggedVolume <- sum(NoHollowLoggedVolume +
-                        1-(otherloggingparameters$TreeHollowPartForFuel)*(HollowTable$TreeHarvestableVolume))
+  NoHollowTimberLoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
+  TimberLoggedVolume <- sum(NoHollowTimberLoggedVolume +
+                        1-(advancedloggingparameters$TreeHollowPartForFuel)*(HollowTable$TreeHarvestableVolume))
 }
@@
 
-INPUT : inventory + LoggedVolume/NoHollowLoggedVolume
+INPUT : inventory + TimberLoggedVolume/NoHollowTimberLoggedVolume
 OUTPUT : FuelVolume
 
-si type = "RIL3fuel" ou (type == "manual"& fuel =="1"):
-FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause",  0,14*LoggedVolume
+si scenario = "RIL3fuel" ou (scenario == "manual"& fuel =="1"):
+FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause",  0,14*TimberLoggedVolume
 
-si type = "RIL3fuelhollow" ou (type == "manual"& fuel =="2"):
-FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause", ⅓ du volume de la bille des arbres codés "hollowfuel" dans la colonne "DeathCause",  0,14*NoHollowLoggedVolume
+si scenario = "RIL3fuelhollow" ou (scenario == "manual"& fuel =="2"):
+FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause", ⅓ du volume de la bille des arbres codés "hollowfuel" dans la colonne "DeathCause",  0,14*NoHollowTimberLoggedVolume
 
@@
 
-FuelVolume <- sum(DamageTable$TreeHarvestableVolume + otherloggingparameters$Purge*LoggedVolume) # Damage and purge (0.14)
+FuelVolume <- sum(DamageTable$TreeHarvestableVolume + advancedloggingparameters$Purge*TimberLoggedVolume) # Damage and purge (0.14)
 
@@
 FuelVolume <- sum(DamageTable$TreeHarvestableVolume + 
-                    otherloggingparameters$TreeHollowPartForFuel *(HollowTable$TreeHarvestableVolume) + otherloggingparameters$Purge*NoHollowLoggedVolume)
+                    advancedloggingparameters$TreeHollowPartForFuel *(HollowTable$TreeHarvestableVolume) + advancedloggingparameters$Purge*NoHollowTimberLoggedVolume)
 # damage + 1/3 of hollow trees volume + purge (0.14) of the healthy trees

### 2021-08-26 R/DraftFunctions.Rmd
ONFtaxojoin for genericity

@@
 ```{r SpeciesCriteria table code}
-SpeciesCriteria <- read_delim("D:/VSC Kourou/DATA/SpeciesCriteria.csv", 
-                              ";", escape_double = FALSE, col_types = cols(Commercial = col_factor(levels = c("1", 
-                                                                                                              "2")), MinFD = col_number(), UpMinFD = col_number(), 
-                                                                           MaxFD = col_number()), locale = locale(encoding = "Latin1"), 
-                              trim_ws = TRUE) %>% 
+SpeciesCriteria <- read_csv("D:/VSC Kourou/DATA/SpeciesCriteria.csv",
+                            col_types = cols(Commercial = col_factor(levels = c("0",
+                                                                                "1", "2")), MinFD = col_number(),
+                                             UpMinFD = col_number(), MaxFD = col_number()),
+                            locale = locale(encoding = "Latin1")) %>%
   separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T)

### 2021-08-30 R/DESIGNATION_DRAFT.Rmd
On the way of Bonus correction

@@
 
-if (scenario == "RIL3fuelhollow"| (scenario == "manual"& fuel =="2")){VO = objective #3604 rows
+if (fuel =="2"){
+  VO = objective * unique(inventory$PlotArea)
 }else{
-  VO = (objective + (objective*((advancedloggingparameters$ObjectiveBonus)/100))) * unique(inventory$PlotArea) # to compensate for the designated hollow wood.
+  VO = (objective +
+          (objective *((advancedloggingparameters$ObjectiveBonus)/100))
+        ) * unique(inventory$PlotArea) # to compensate for the designated hollow wood.
 }
 
-(20 + (20*0.3))*6.25
+(20 + (20*0.3)) *6.25
 (20*6.25) + ((20*6.25)*0.3) #same

### 2021-08-30 R/loggingsimulation.R

@@ -202,7 +202,7 @@ loggingsimulation <- function(
   winching <- scenariosparameters$winching
   directionalfelling <- scenariosparameters$directionalfelling
 
-  INPUTinventory <- inventory
+  INPUTinventory <- deparse(substitute(inventory)) # object name to this name in character
 
   # Function
 

### 2021-08-30 R/loggingsummary.R

@@ -10,14 +10,22 @@
 #' @export
 #'
 #' @examples
+#' data(Paracou6_2016) # inventory
+#' data(DTMParacou) # topography
+#' # data() relative elevation
+#' data(SpeciesCriteria) # species exploitability criteria
+#' data(ForestZoneVolumeParametersTable) # volume parameters
+#' data(ParamCrownDiameterAllometry) # parameters values of the crown diameter allometry
 #'
-#' Rslt <- loggingsimulation(Paracou6_2016, topography = DTMParacou,
-#'  relativeelevation  = DTMParacou, speciescriteria = SpeciesCriteria,
-#'  volumeparameters = ForestZoneVolumeParametersTable, scenario = "manual",
-#'  objective = 20, fuel = "2", diversification = TRUE, winching = "2",
-#'  directionalfelling = "2", specieslax = FALSE, objectivelax = TRUE,
-#'  crowndiameterparameters = ParamCrownDiameterAllometry,
-#'  advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
+#' Rslt <- suppressMessages(
+#'   loggingsimulation(Paracou6_2016, topography = DTMParacou,
+#'                     relativeelevation  = DTMParacou, speciescriteria = SpeciesCriteria,
+#'                     volumeparameters = ForestZoneVolumeParametersTable, scenario = "manual",
+#'                     objective = 20, fuel = "2", diversification = TRUE, winching = "2",
+#'                     directionalfelling = "2", specieslax = FALSE, objectivelax = TRUE,
+#'                     crowndiameterparameters = ParamCrownDiameterAllometry,
+#'                     advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
+#' )
 #'
 #' loggingsummary(Rslt)
 #'
@@ -29,7 +37,7 @@ loggingsummary <- function(x
     stop("The argument of the 'loggingsummary' function must be a list")
 
   # Reminder of INPUTS:
-  # cat('inventory :', x$INPUTinventory, '\n') # input inventory il faut du character
+  cat('inventory :', x$INPUTinventory, '\n') # input inventory name
   cat('scenario :', x$scenario, '\n') # scenario,
   cat('objective :', x$objective, '\n') # objective volume
   cat('fuel :', x$fuel, '\n') # fuel

### 2021-08-30 R/selected.R

@@ -1,46 +1,46 @@
-#' Trees to be exploited selection
+#'Trees to be exploited selection
 #'
-#' @param inventory Your inventory (see the inputs formats and metadata in the
-#'   \code{\link{vignette}}) (data.frame)
+#'@param inventory Your inventory (see the inputs formats and metadata in the
+#'  \code{\link{vignette}}) (data.frame)
 #'
-#' @param topography Digital terrain model (DTM) of the inventoried plot (LiDAR or
-#'   SRTM) (\code{\link{DTMParacou}}) (RasterLayer)
+#'@param topography Digital terrain model (DTM) of the inventoried plot (LiDAR
+#'  or SRTM) (\code{\link{DTMParacou}}) (RasterLayer)
 #'
-#' @param scenario Logging scenario: "RIL1", "RIL2broken", "RIL2", "RIL3",
-#'   "RIL3fuel", "RIL3fuelhollow" or "manual"(character) (see the
-#'   \code{\link{vignette}})
+#'@param scenario Logging scenario: "RIL1", "RIL2broken", "RIL2", "RIL3",
+#'  "RIL3fuel", "RIL3fuelhollow" or "manual"(character) (see the
+#'  \code{\link{vignette}})
 #'
-#' @param fuel Fuel wood exploitation: no exploitation = "0", damages and purge
-#'   exploitation in fuelwood = "1", exploitation of hollow trees, damages and purge in
-#'   fuelwood = "2"
+#'@param fuel Fuel wood exploitation: no exploitation = "0", damages and purge
+#'  exploitation in fuelwood = "1", exploitation of hollow trees, damages and
+#'  purge in fuelwood = "2"
 #'
-#' @param diversification Taking of other species in addition to the main
-#'   commercial species (2 levels of commercial species in the
-#'   \code{\link{SpeciesCriteria}} table) (logical)
+#'@param diversification Taking of other species in addition to the main
+#'  commercial species (2 levels of commercial species in the
+#'  \code{\link{SpeciesCriteria}} table) (logical)
 #'
-#' @param specieslax Allow diversification if stand is too poor, = FALSE by
-#'   default (logical)
+#'@param specieslax Allow diversification if stand is too poor, = FALSE by
+#'  default (logical)
 #'
-#' @param VO The objective volume with or without a bonus (if hollow trees
-#'   exploitation)(numeric value) (see the \code{\link{loggingparameters}})
[…]

### 2021-08-30 R/treeselection.R

@@ -19,9 +19,9 @@
 #'
 #'@param objective Objective volume per hectare (numeric)
 #'
-#' @param fuel Fuel wood exploitation: no exploitation = "0", damages and purge
-#'   exploitation in fuelwood = "1", exploitation of hollow trees, damages and purge in
-#'   fuelwood = "2"
+#'@param fuel Fuel wood exploitation: no exploitation = "0", damages and purge
+#'  exploitation in fuelwood = "1", exploitation of hollow trees, damages and
+#'  purge in fuelwood = "2"
 #'
 #'@param diversification Taking of other species in addition to the main
 #'  commercial species (2 levels of commercial species in the
@@ -104,9 +104,10 @@ treeselection <- function(
   if(!all(unlist(lapply(list(specieslax, objectivelax), inherits, "logical"))))
     stop("The 'specieslax' and 'objectivelax' arguments of the 'treeselection' function must be logicals")
 
-  if (!any(scenario == "RIL1" || scenario == "RIL2broken"|| scenario == "RIL2"|| scenario == "RIL3"|| scenario == "RIL3fuel"||
-           scenario == "RIL3fuelhollow"|| scenario =="manual"))
-    stop("The 'scenario' argument of the 'treeselection' function must be 'RIL1', 'RIL2broken', 'RIL2', 'RIL3', 'RIL3fuel', 'RIL3fuelhollow' or 'manual'")
+  if (!any(scenario == "RIL1" || scenario == "RIL2broken"|| scenario == "RIL2"||
+           scenario == "RIL3"|| scenario == "RIL3fuel"|| scenario == "RIL3fuelhollow"|| scenario =="manual"))
+    stop("The 'scenario' argument of the 'treeselection' function must be
+         'RIL1', 'RIL2broken', 'RIL2', 'RIL3', 'RIL3fuel', 'RIL3fuelhollow' or 'manual'")
 
   if (!any(fuel == "0" || fuel == "1"|| fuel == "2"|| is.null(fuel)))
     stop("The 'fuel' argument of the 'treeselection' function must be '0', '1', or '2'")
@@ -160,53 +161,59 @@ treeselection <- function(
 
     # generate either "1" or "0" randomly for each line, depending on the proba associated with the line:
     rowwise() %>%
[…]

### 2021-08-31 R/futurereserve.R
big change: remove bonus and objective correction

@@ -42,7 +42,7 @@
 #' HVinit <- harvestableOutputs$HVinit
 #'
 #' inventory <- selected(inventory, scenario = "manual", fuel = "0",
-#' diversification = TRUE, specieslax = FALSE, objectivelax = FALSE,
+#' diversification = TRUE, specieslax = FALSE, objectivelax = TRUE,
 #' topography = DTMParacou,
 #' advancedloggingparameters = loggingparameters(), VO = 30,
 #'  HVinit = HVinit)$inventory
@@ -96,10 +96,21 @@ futurereserve <- function(
   #Reserve
   # Randomly select the reserved trees (among the futures, as many as the number of trees exploited):
 
-  StemNbr <- sum(as.numeric(inventory$Selected == "1"), na.rm = TRUE)#29 selected ind
+  StemNbr <- sum(as.numeric(inventory$Selected == "1"), na.rm = TRUE)
+  FutureNbr <- sum(as.numeric(inventory$LoggingStatus == "future"), na.rm = TRUE)
+
+
+  if(StemNbr < FutureNbr){
   ReserveRows <- sample(which(inventory$LoggingStatus == "future"), size = StemNbr, replace = F)
 
   inventory$LoggingStatus[ReserveRows] <-"reserve"
+  }
+
+  if(StemNbr >= FutureNbr){
+    inventory <- inventory %>%
+      mutate(LoggingStatus = ifelse(LoggingStatus == "future", "reserve", LoggingStatus))
+  }
+
 
   return(inventory)
 

### 2021-08-31 tests/testthat/test-selected.R

@@ -67,7 +67,8 @@ test_that("selected", {
     TestRareWorld <- testinventory %>%
       dplyr::filter(LoggingStatus == "harvestable")
 
-    expect_true(all(TestRareWorld$Selected == "1" |TestRareWorld$Selected == "deselected")) #deselected = probbedhollow trees
+    expect_true(all(TestRareWorld$Selected == "1" |
+                      (TestRareWorld$Selected == "0" & TestRareWorld$ProbedHollow == "1")))
   }
 
 
@@ -149,13 +150,14 @@ test_that("selected", {
 
   # Hollow (Rotten model)
   testinventory <- suppressMessages(selected(inventory, scenario = "manual", fuel = "0", diversification = TRUE,
-                                             topography = DTMParacou, advancedloggingparameters = loggingparameters(),
+                                             topography = DTMParacou,
+                                             advancedloggingparameters = loggingparameters(),
                                              VO = VO, HVinit = HVinit))$inventory
 
   TestHollow <- testinventory %>%
-    dplyr::filter(Selected == "1"| Selected == "deselected")
+    dplyr::filter(LoggingStatus == "harvestable" | LoggingStatus == "harvestable2nd")
 
-  expect_true(all(!is.na(TestHollow$ProbedHollowProba))) # ProbedHollowProba for the Selected == "1" or == "deselected"
+  expect_true(all(!is.na(TestHollow$ProbedHollowProba))) # ProbedHollowProba for harvestable trees
   expect_true(all(TestHollow$ProbedHollow %in% c("0","1"))) # ProbedHollow = "0" ou "1" if !is.na(ProbedHollowProba)
 
   expect_true(all(TestHollow$ProbedHollow == "0" | TestHollow$ProbedHollow == "1")) # doest works with the check..

### 2021-09-28 R/selected.R
Run all scenarios

@@ -75,8 +75,8 @@ selected <- function(
   inventory,
   topography,
   scenario,
-  fuel,
-  diversification,
+  fuel = NULL,
+  diversification = NULL,
   VO, # objective volume for the entire surface of the plot
   HVinit, # initial Harvestable Volume
   specieslax = FALSE,

### 2021-09-28 R/treeselection.R

@@ -80,9 +80,9 @@ treeselection <- function(
   plotslope,
   speciescriteria,
   scenario,
-  objective,
-  fuel,
-  diversification,
+  objective = NULL,
+  fuel = NULL,
+  diversification = NULL,
   specieslax = FALSE,
   objectivelax = FALSE,
   advancedloggingparameters = loggingparameters()

### 2021-09-30 R/DraftFunctions.Rmd
Vignette
Doc corrections

@@
 usethis::use_data(SpeciesCriteria)
+```
+```{r}
+ScenariosTable <- read_csv("D:/VSC Kourou/DATA/ScenariosTable.csv", 
+    col_types = cols(Winching = col_factor(levels = c("0", 
+        "1", "2")), DirectionalFelling = col_factor(levels = c("0", 
+        "1", "2"))), trim_ws = TRUE)
+
+usethis::use_data(ScenariosTable)
 ```
@@
 if (all(Paracou6_2016$Plot==Paracou6_2016$Plot[1])==FALSE) #all the Plot values are equal?
-  stop ("Your inventory concerns different plots (Plot). Our function simulates logging at the plot level.") 
+  stop ("Input inventory concerns different plots (Plot). Our function simulates logging at the plot level.") 
 # Remove out-plot trees (A faire)

### 2021-09-30 R/ONFGuyafortaxojoin.R

@@ -2,7 +2,7 @@
 #'
 #' @description Joins a commercial criteria table to a forest inventory
 #'
-#' @param inventory your inventory (see the inputs formats and metadata in the
+#' @param inventory input inventory (see the inputs formats and metadata in the
 #'   \code{\link{vignette}}) (data.frame)
 #'
 #' @param speciescriteria Table of species exploitability criteria : species

### 2021-09-30 R/scenariosparameters.R

@@ -1,4 +1,4 @@
-#' Parameters of the scenaios
+#' Parameters of the scenarios
 #'
 #'@param scenario Logging scenario: "RIL1", "RIL2broken", "RIL2", "RIL3",
 #'  "RIL3fuel", "RIL3fuelhollow" or "manual"(character) (see the
@@ -6,9 +6,9 @@
 #'
 #'@param objective Objective volume per hectare (numeric)
 #'
-#' @param fuel Fuel wood exploitation: no exploitation = "0", exploitation of damages and unsed part of logged trees
-#'   for fuelwood = "1", exploitation of hollow trees, damages and unsed part of logged trees for
-#'   fuelwood = "2"
+#'@param fuel Fuel wood exploitation: no exploitation = "0", exploitation of
+#'  damages and unsed part of logged trees for fuelwood = "1", exploitation of
+#'  hollow trees, damages and and unused part of the log for fuelwood = "2"
 #'
 #'@param diversification Possibility to log other species in addition to the main
 #'  commercial species (species with a value of 2  for commercial in the
@@ -36,7 +36,8 @@ scenariosparameters <- function(
 ){
   # check inputs
   if(!(scenario %in% c("RIL1", "RIL2broken", "RIL2", "RIL3", "RIL3fuel", "RIL3fuelhollow", "manual")))
-    stop(paste('"scenario" argument should be "in "RIL1", "RIL2broken", "RIL2", "RIL3", "RIL3fuel", "RIL3fuelhollow" or "manual"; not',
+    stop(paste('"scenario" argument should be in "RIL1", "RIL2broken", "RIL2", "RIL3", "RIL3fuel",
+               "RIL3fuelhollow" or "manual"; not',
                scenario))
 
   if(!(class(objective) %in% c("numeric", "NULL")))

### 2021-09-30 R/harvestable.R
More documentation

@@ -26,6 +26,14 @@
 #'  validated for each of the trees. The function returns the harvestable volume
 #'  too, in the plot for these criteria.
 #'
+#'@details Trees will be designated as "**harvestable**" if they:
+#'  - belonging to species of 1st economic rank or more if diversification
+#'  - DBH between the MinFD and the MaxFD.
+#'  - not isolated ( >100m ('IsolateTreeMinDistance') from other individuals of
+#'   the same species)
+#'  - on slopes < 22% ('TreeMaxSlope')
+#'  - off the main tracks.
+#'
 #'@seealso  \code{\link{Paracou6_2016}}, \code{\link{SpeciesCriteria}},
 #'  \code{\link{DTMParacou}}, \code{\link{PlotSlope}},
 #'  \code{\link{loggingparameters}}
@@ -41,7 +49,7 @@
 #'@importFrom utils setTxtProgressBar txtProgressBar
 #'
 #'
-#' @examples
+#'@examples
 #'
 #' data(Paracou6_2016)
 #' data(DTMParacou)

### 2021-09-30 R/selected.R

@@ -36,6 +36,19 @@
 #'  the logging scenario chosen), and 2 sets of spatial points: (HollowTrees and
 #'  EnergywoodTrees)
 #'
+#'@details If the harvestable volume is higher than the objective volume, the
+#'  MinFD of the 1st economic rank species is first increased, then that of the
+#'  other species (if diversification), if this is not enough. The volume to be
+#'  harvested is adjusted if necessary by taking the trees in decreasing order
+#'  of volume, until the objective volume is reached.
+#'
+#'  If the harvestable volume is too low, diversification can be applied if it
+#'  was not already applied ('specieslax') (trees of all commercial ranks are
+#'  selected in decreasing order of volume until the objective volume is
+#'  reached), or harvesting can continue despite an unreached objective volume,
+#'  or be abandoned ('objectivelax')
+
+#'
 #'@seealso  \code{\link{Paracou6_2016}}, \code{\link{SpeciesCriteria}},
 #'  \code{\link{DTMParacou}}, \code{\link{loggingparameters}}
 #'

### 2021-10-01 R/createcanopy.R
Work on doc and vignette

@@ -3,7 +3,7 @@
 #' @param inventory Input inventory (see the inputs formats and metadata in the
 #'   \code{\link{vignette}}) (data.frame)
 #'
-#' @return a dataframe with a column 'Crowns' containing the ellipses
+#' @return A dataframe with a column 'Crowns' containing the ellipses
 #'   (sfc_POLYGON) as trees crown, with their diameter and height filled in,
 #'   representing trees from the sky.
 #' @export
@@ -23,6 +23,7 @@
 #'
 #' # The small ones first so that they are behind the big ones on the plot
 #' inventory <- dplyr::arrange(inventory, TreeHeight)
+#'
 #' library(ggplot2)
 #' ggplot() +
 #'   geom_sf(data = getgeometry(inventory, Crowns),

### 2021-10-01 R/loggingparameters.R

@@ -1,80 +1,82 @@
-#' Advanced parameters of the logging simulator
+#'Advanced parameters of the logging simulator
 #'
-#' @param MinDBHValue Minimum DBH value of the forest stand. Default = 10, in cm
-#'   (double)
-#' @param MaxAreaSlope Maximum area slope for inclusion in a logging unit.
-#'   Default = 27, in % (double)
-#' @param MaxTrailCenterlineSlope Maximum main & 2nd trail centerline slope.
-#'   Default = 22, in % (double)
-#' @param MaxTrailCrossSlope Maximum main & 2nd trail cross slope. Default = 4,
-#'   in % (double)
-#' @param GrappleMaxslope Maximum slope over which the grapple can pass. Default
-#'   = 20, in % (double)
-#' @param TreeMaxSlope Maximum slope around the tree to access it. Default = 22,
-#'   in % (double)
-#' @param PlateauMaxSlope Maximum slope of the plateau definition. Default = 5,
-#'   in % (double)
-#' @param SlopeDistance Distance to compute slope. Default = 6, in m (3m for
-#'   each side) (double)
-#' @param WaterSourcesBufferZone Buffer zone around the water sources. Default =
-#'   30, in m (double)
-#' @param MinMainTrailWidth Minimum main trail width. Default = 5, in m (double)
-#' @param MaxMainTrailWidth Maximum main trail width. Default = 6, in m (double)
-#' @param ScndTrailWidth 2nd trail width. Default = 4, in m (double)
-#' @param BigTrees DBH of trees to be avoided at trail construction. Default =
-#'   50, in cm (double)
-#' @param ObjectiveBonus Objective bonus. Default = 30, in % (double)
-#' @param CableLength Cable length. Default = 40, in m (double)
-#' @param GrappleLength Grapple length. Default = 6, in m (double)
-#' @param IsolateTreeMinDistance Minimum distance to consider a tree "isolated"
-#'   from other trees of its species. Default = 100, in m (double)
-#' @param FutureTreesMinDiameter Future trees minimum diameter. Default = 35, in
-#'   cm (double)
-#' @param TreefallSuccessProportion Proportion of successful directional felling
-#'   events. Default = 0.6 (double)
-#' @param MinTreefallOrientation Minimum orientation of the tree fall to the
-#'   trail. Default = 30, in degree (double)
[…]

### 2021-11-08 R/DESIGNATION_DRAFT.Rmd
After doc review

@@
 if (scenario == "RIL3fuelhollow"| (scenario == "manual"& fuel =="2")) {
-  # Hollow trees = fuelwood:
+  # Hollow trees = fuel wood:
   inventoryH <- inventoryG %>%

### 2021-11-08 R/TreeFelling_Draft.Rmd
loggingsimulation function and doc refresh
After doc review

@@
 multilignes "MainTrail ", "2ndTrail"
-vecteur "AccessibleTreesPoints", "SelectedTreesPoints",  "AvenirTreesPoints",  "ReserveTreesPoints", "DeadTreesPoints", "HollowTreesPoints" et "FuelwoodTreesPoints"
+vecteur "AccessibleTreesPoints", "SelectedTreesPoints",  "AvenirTreesPoints",  "ReserveTreesPoints", "DeadTreesPoints", "HollowTreesPoints" et "Fuel woodTreesPoints"
 
@@
 
-inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
+inventory <- addtreedim(inventorycheckformat(Paracou6_2016), volumeparameters = ForestZoneVolumeParametersTable)
 

### 2021-11-08 R/treeselection.R

@@ -19,9 +19,9 @@
 #'
 #'@param objective Objective volume per hectare (numeric)
 #'
-#'@param fuel Fuelwood exploitation: no exploitation = "0", exploitation of
-#'   damage and unused part of logged trees for fuelwood = "1", exploitation of
-#'   hollow trees, damage and and unused part of the log for fuelwood = "2"
+#'@param fuel Fuel wood exploitation: no exploitation = "0", exploitation of
+#'   damage and unused part of logged trees for fuel = "1", exploitation of
+#'   hollow trees, damage and and unused part of the log for fuel = "2"
 #'
 #'@param diversification Possibility to log other species in addition to the
 #' main commercial species (species with a value of 2 for commercial in the
@@ -35,7 +35,7 @@
 #'  objective volume (if stand too poor), = FALSE by default (logical)
 #'
 #'@param advancedloggingparameters Other parameters of the logging simulator
-#'  \code{\link{loggingparameters}} (list) MainTrail (multiline)
+#'  \code{\link{loggingparameters}} (list)
 #'
 #'@return A list with:
 #'  - input inventory with: "DistCrit", "Slope", "SlopeCrit",
@@ -47,7 +47,7 @@
 #'  - the harvestable volume with the initial
 #'  criteria (HVinit) for the entire plot
 #'  - 6 layers of spatial points: harvestable, selected, future and
-#'  reserve, hollow and fuelwood trees
+#'  reserve, hollow and fuel wood trees
 #'
 #'@details Trees with visible defects are identified ('VisiblyDefectModel' in
 #'  'advancedloggingparameters' argument) and therefore not designated.
@@ -112,7 +112,7 @@
 #' speciescriteria = SpeciesCriteria, objective = 20,
 #' scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
 #' objectivelax = TRUE,
-#' advancedloggingparameters = loggingparameters()) #  MainTrail
+#' advancedloggingparameters = loggingparameters())
 #'
 #' NewInventory <- treeselectionoutputs$inventory
 #'

### 2021-11-09 R/treefelling.R
again?

@@ -61,7 +61,7 @@
 #'
 #'@importFrom dplyr group_by do left_join mutate select
 #'@importFrom tibble add_column
-#'@importFrom sf st_as_sf st_as_text st_geometry st_intersection
+#'@importFrom sf st_as_sf st_as_text st_geometry st_intersection st_buffer
 #'@importFrom tidyr unnest
 #'
 #' @examples
@@ -282,7 +282,7 @@ treefelling <- function(
 
   DeadTrees <- suppressWarnings(sf::st_intersection(
     st_as_sf(inventory, coords = c("Xutm", "Yutm")),
-    sf::st_buffer(getgeometry(felttrees, TreePolygon), dist = 0)
+    sf::st_buffer(getgeometry(felttrees, TreePolygon), dist = 0) # buffer to avoid self-intersection
   )) %>%
     add_column(DeadTrees = "1") %>%
     select(idTree, DeadTrees)
@@ -325,7 +325,7 @@ treefelling <- function(
 #'  the outputs metadata in the \code{\link{vignette}}).
 #'@export
 #'
-#'@importFrom dplyr mutate
+#'@importFrom dplyr mutate rowwise
 #'
 #' @examples
 #' inventory <- addtreedim(inventorycheckformat(Paracou6_2016),

### 2021-12-03 R/DraftFunctions.Rmd
ONF modifications

--- 2021-08-26 R/DraftFunctions.Rmd
@@
                             locale = locale(encoding = "Latin1")) %>%
-  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T)
+  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T) %>% 
+  mutate(Aggregative = ifelse(VernName == "Angélique" | VernName == "Gonfolo rose",
+                              TRUE, FALSE))
 # unite(Genus, Species, col = "ScientificName", sep = "_", remove = F)
@@
 
-usethis::use_data(SpeciesCriteria)
+# usethis::use_data(SpeciesCriteria, overwrite = TRUE)
+```
+```{r}
+ScenariosTable <- read_csv("D:/VSC Kourou/DATA/ScenariosTable.csv", 
+    col_types = cols(Winching = col_factor(levels = c("0", 
+        "1", "2")), DirectionalFelling = col_factor(levels = c("0", 
+        "1", "2"))), trim_ws = TRUE)
+
+# usethis::use_data(ScenariosTable,overwrite = TRUE)
 ```

### 2021-12-03 R/Treefelling_test_for all trees.Rmd
loggingsimulation function and doc refresh
After doc review
ONF modifications

@@
 
-  # To direct to avoid damage to future and reserve trees + track orientation. Winching: Foot before.
+  # To direct to avoid damage to future and reserve trees + trail orientation. Winching: Foot before.
   if(directionalfelling == "2"&& (fuel !="1" |fuel !="2")){
@@
 
-  # Fuelwood exploitation in the crowns
+  # Fuel wood exploitation in the crowns
   if(fuel =="1" |fuel =="2"){

### 2021-12-03 tests/testthat/test-harvestable.R

@@ -21,12 +21,16 @@ test_that("harvestable", {
   inventory <- addtreedim(inventorycheckformat(Paracou6_2016), volumeparameters = ForestZoneVolumeParametersTable)
   inventory <- ONFGuyafortaxojoin(inventory, SpeciesCriteria)
 
-  testinventory1 <- harvestable(inventory,
-                                diversification = T, specieslax = F, topography = DTMParacou, plotslope = PlotSlope)$inventory
-  testinventory2 <- harvestable(inventory,
-                                diversification = F, specieslax = T, topography = DTMParacou, plotslope = PlotSlope)$inventory
-  testinventory3 <- harvestable(inventory,
-                                diversification = F, specieslax = F, topography = DTMParacou, plotslope = PlotSlope)$inventory
+  Outputs1 <- harvestable(inventory,
+                          diversification = T, specieslax = F, topography = DTMParacou, plotslope = PlotSlope)
+  Outputs2 <- harvestable(inventory,
+                          diversification = F, specieslax = T, topography = DTMParacou, plotslope = PlotSlope)
+  Outputs3 <- harvestable(inventory,
+                          diversification = F, specieslax = F, topography = DTMParacou, plotslope = PlotSlope)
+
+  testinventory1 <- Outputs1$inventory
+  testinventory2 <- Outputs2$inventory
+  testinventory3 <- Outputs3$inventory
 
 
   expect_false(any(is.na(testinventory1$LoggingStatus)))
@@ -55,23 +59,31 @@ test_that("harvestable", {
   expect_true(any(testinventory2a$LoggingStatus =="harvestable2nd"))
 
 
-
   # "harvestable": Commercial == "1"  diversification=F & specieslax=F
   testinventory3a <- testinventory3 %>%
     filter(Commercial != "1")
-  expect_true(all(testinventory3a$LoggingStatus =="non-harvestable"))
+  expect_true(all(testinventory3a$LoggingStatus == "non-harvestable"))
 
 
-  # "harvestable": check spatial!! A FAIRE
+  # "harvestable": check spatial!! "DistCrit", "Slope", "SlopeCrit"
+
+  StatialTable <- testinventory1 %>%
+    filter(DBH >= MinFD & DBH <= MaxFD)
+
[…]

### 2021-12-03 R/Treefelling_Sylvain's version.Rmd
loggingsimulation function and doc refresh
After doc review
ONF modifications

@@
 ```{r}
-inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
+inventory <- addtreedim(inventorycheckformat(Paracou6_2016), volumeparameters = ForestZoneVolumeParametersTable)
 

### 2021-12-03 R/HarvestableAreaDefinition.R

@@ -1,17 +1,20 @@
 #' HarvestableAreaDefinition
 #'
-#' @param plot Studied plots (sf data.frame)
-#' @param dtm Digital terrain model (raster)
-#' @param verticalcreekheight Relative elevation from nearest channel network (raster)
+#' @param plot Studied plot (SpatialPolygonsDataFrame)
+#' @param dtm Digital terrain model (Large RasterLayer)
+#' @param verticalcreekheight Relative elevation from nearest channel network
+#'   (Large RasterLayer)
 #' @param advancedloggingparameters Other parameters of the logging simulator
 #'   \code{\link{loggingparameters}} (list)
 #'
-#' @return A collection of polygones defined as 1 : harvestable area / 0 : non-harvestable area
+#' @return A collection of polygons defined as 1 : harvestable area, 0 :
+#'   non-harvestable area
 #'
 #' @export
 #'
-#' @importFrom  sf st_as_sf st_cast
-#' @importFrom  raster mask terrain rasterFromXYZ rasterToPolygons rasterToPoints
+#' @importFrom sf st_as_sf st_cast
+#' @importFrom raster mask terrain rasterFromXYZ rasterToPolygons
+#'   rasterToPoints
 #' @importFrom  dplyr as_tibble left_join rename mutate if_else
 #'
 #' @examples
@@ -20,15 +23,18 @@
 #' data(VerticalCreekHeight)
 #'
 #'
-#'ExploitPolygones <- HarvestableAreaDefinition(plot = Plots,
+#' HarvestableArea <- HarvestableAreaDefinition(plot = Plots,
 #'                                              dtm = DTMParacou,
 #'                                              verticalcreekheight = VerticalCreekHeight,
 #'                                              advancedloggingparameters = loggingparameters())
+#' plot(HarvestableArea)
 #'
-HarvestableAreaDefinition <- function(plot,
-                                      dtm,
-                                      verticalcreekheight,
-                                      advancedloggingparameters) {
+HarvestableAreaDefinition <- function(
+  plot,
+  dtm,
+  verticalcreekheight,
+  advancedloggingparameters
+){
 
   # Variables
   PlotSlope <- PlotSlopePoint <- CreekVHeightPlotPoint <- PlotTib <- NULL
@@ -38,15 +44,15 @@ HarvestableAreaDefinition <- function(plot,
 
   # Mask rasters by plot
[…]

### 2021-12-03 R/piedpisteAvRes.R

@@ -1,0 +1,61 @@
+#
+# TreefallOrientation <- as.numeric(sample(c(0.1: 179.9), size = 1)) # no particular angle to orientate to the trail, only to orientate the tree foot towards the trail
+# OppAng <- 180-(90 + CrownTreefallOrientation) # the angle between the closest position to the trail (90°) and the desired position (desired angle to the trail)
+#
+# ## Right-hand trail
+# if(TrailPt[1] >= Foot[1]){ # x trail > x foot
+#   # Foot oriented
+#   Aangle <- round(as.numeric(180 + OppAng + theta), digits = 0)
+#   Bangle <- round(as.numeric(180 - OppAng + theta), digits = 0)
+#
+#   ## Left-hand trail
+# }else if(TrailPt[1] < Foot[1]){ # x trail < x foot
+#   # Foot oriented
+#   Aangle <- round(as.numeric(360 - OppAng + theta), digits = 0)
+#   Bangle <- round(as.numeric(theta + OppAng), digits = 0)
+# }
+#
+#
+#   # Calculate the two possible crown configurations
+#   ACrown <- rotatepolygon(Crown, angle = Aangle, fixed = Foot) # turned crown
+#   BCrown <- rotatepolygon(Crown, angle = Bangle, fixed = Foot) # turned crown
+#
+#   # Test the best to pull the tree back to the main trail (farthest crown from the main trail)
+#   ADist <- st_distance(ACrown, MainTrail)[1,1] #matrix to value
+#   BDist <- st_distance(BCrown, MainTrail)[1,1]
+#
+#   if(max(ADist, BDist) == ADist){
+#
+#     FallenTree <- AFallenTree <- st_difference(st_union( # A configuration
+#       rotatepolygon(Trunk, angle = Aangle, fixed = Foot), # turned trunk
+#       ACrown # turned crown
+#     ))
+#     BFallenTree <- NULL
+#
+#   }else{
+#
+#     FallenTree <-  BFallenTree <- st_difference(st_union( # B configuration
+#       rotatepolygon(Trunk, angle = Bangle, fixed = Foot), # turned trunk
+#       BCrown # turned crown
+#     ))
+#     AFallenTree <- st_sfc(st_point(c(0,0))) # "null" sfc object to compare after
+#
+#   }
+#
+#
+#   # Check intersection with future/reserve trees
+#   FRintersect <- sf::st_intersects(FallenTree, FutureReserveCrowns)
+#
[…]

### 2021-12-06 docs/Developers guidelines.Rmd
docs access

---
title: "Developers guidelines"
author: "Vincyane Badouard"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_float: yes
---

![](https://img.shields.io/badge/stability-work_in_progress-lightgrey.svg)

# Introduction

This document aim to give guidelines for all users interested in participating to the development of `RconTROLL` for both core development or development associated to additional specific modules of `TROLL`. This document is a work in progress and everybody is invited to participate to its writing using subsequent guidelines. Part of the document is inspired from [R packges book by Hadley Wickham](http://r-pkgs.had.co.nz/) and [GitHub help](https://help.github.com/), which I recommend to read too.

*NB: Those guidelines might be sometimes specific to `RconTROLL` and may differ for other R packages.*

# Package structure

`RconTROLL` R package has the following structure:

* **Root files**
    + `README.md` package markdown description
    + `NEWS.md` news tracking in markdown (see [Version tracking])
    + `DESCRIPTION` R package description
    + `NAMESPACE` R package namespace
    + `cran-comment.md` CRAN submission file
    + `.travis.yml`, `appveyor.yml` continuous integration files (see [Social coding with GitHub])
    + `RconTROLL.Rproj` R project
    + `.gitignore`, `.Rbuildignore` files to be ignored bit Git and Rbuild
    + `.Rproj.user`, `.Rhistory`, `.RData`, `.Ruserdata` R project files
* **`R` folder**: include all R code with one file per function, class, method, data, and package (see [Witting R code in `RconTROLL`]). Cannot include sub-folders !
* **`man` folder**: include all package documentation in Rd automatically built with R files (do not edit by hand, see [Documenting])
* **`inst/extdata` folder**: include raw data from the package used for examples (init, species, climate, inventory)
* **`tests` folder**: include formal tests (see [Formal testing])
* **`vignettes` folder**: include package vignettes for users
* **`docs` folder**: include developers tools and documentation (including the present document)

# Basic workflow

Development should follow the following workflow:

1. Code writing in R
1. Documenting
1. Formal testing and checking
1. Repeat previous steps until happy
1. NEWS editing, commit and push
1. And when ready, sharing

# Writing R code in `RconTROLL`

For the moment code writing does not include much rules. Noticeable rules are listed below, feel free to submit others:

* functions names and variables names (not mandatory for variables) follow [camel case](https://en.wikipedia.org/wiki/Camel_case) writing
* functions names always start in lowercase whereas class names start in uppercase
* R files have the name of the object they include (i.e. `function.R`, `CLASS.R`)
* R files for methods include the class name after a dot before the .R (i.e. `method.CLASS.R`)
* try to minimize functions size and complexity by using internal functions
* internal functions name start with a dot (`.internal()`) and are generally included in the file from the function using it
* try to follow development good practices with `goodpractice::goodpractice()` function from package `goodpractice`

Have a look to already existing code for examples knowing it is not always perfect. When developing you can easily quickly try your new implementation with `devtools::load_all(".")` or `CTRL+SHIFT+L` within Rstudio which will load the package in your environment.

# Documenting

Documenting use the package `Roxygen`. When writing an object place your cursor at the beginning of the object, and in Rstudio go to `Code>Insert Roxygen skeleton` or use `CTRL+ALT+SHIFT+R`. Roxygen code is a special comment starting with `#'`. More information are available in [Whickam book](http://r-pkgs.had.co.nz/man.html). Principle things to fill are listed below:

* Dependence to other package functions with `@include`
* Imports used functions from other packages with `@import` or `@importFrom` (prefer `@importFrom` which import only the function and not the whole package for a smaller environment)
* Object name
* Object description
* Objects parameters or attributes with `@param`
* What the object return with `@return`
* An example of the object use with `@examples`
* Reference to similar or associated functions with `@seealso`
* And finally export the object to user with `@export`

Additionally you can put:

* details with `@details`
* references with `@references`
* and additional section with `@section`

You do not only need to document functions but:

* functions
* class
* methods
* data
* and eventually the package itself

The package documentation skeleton has been already set in `R/RconTROLL.R`, feel free too complete while coding/documenting.

# Formal testing

Formal testing use the package `testthat` and has been already setup in `RconTROLL`. A dummy example on how to write a test is given in `tests/testhat/test_example.R`. It basically consist in giving instructions and an expected result. Test unit should be small and include as deep as possible in the code (not always a whole function, can be an internal). More information are available in [Whickam book](http://r-pkgs.had.co.nz/tests.html). Note that examples writing in documentation are also used as tests (see [Documenting]). To do testing use `devtools::test()` or `CTR+SHIFT+T` in Rstudio. Note that checking (both in Rstudio or continuous integration) are also testing the package with formal testing (see [Checking]). Code coverage by test is assessed by `coverage` in continuous integration and can be seen [online](https://codecov.io/github/sylvainschmitt/RconTroll?branch=master).

# Checking

As long as you develop you should check that you are not doing mistakes with all previous indicated tools. In addition, to be sure to have a working package in agreement with CRAN policies for publication you should use the formal check within Rstudio `Build>Check` or `CTRL+SHIFT+E`. Note that this formal check will be done by continuous integration inside GitHub with `Travis-CI` and `Appveyor` (see [Social coding with GitHub]).

# Version tracking

`RconTROLL` comes with version tracking with `git` software (see the [git simple guide](http://rogerdudler.github.io/git-guide/)). `git` is already setup you just have to check its installation on your local machine. And you will find a graphical user interface to use it inside Rstduio itself. When you think that you reached a step in your development you can *save* it by making a new development version. To do that review you change in git user interface by validating them checking the box. Then use the `commit` button. Add a message and commit. I recommend the message to start with the version, i.e. `RconTROLL 0.1.9010` and to give a short information on the new implementations. In parallel update the `NEWS.md` file by opening a new header with the new version, i.e. `# RconTROLL 0.1.9010`, and list your changes with stars, i.e. `* I made this`.

# Social coding with GitHub

`RconTROLL` development rely on a team and if you want your contribution to be included in it you should follow social coding recommendations with GitHub. This section presents the `RconTROLL` on-line GitHub repository, how to initialize your own development to be connected with others, and how to further develop in agreements with others and share your novelties.

## `RconTROLL` GitHub repository

The official main development branch of `RconTROLL` is hosted on Fabian Fischer's account at https://github.com/fischer-fjd/RconTroll. You will find here the code with the README to introduce you to the repository.

Development objectives, bugs to fix or suggestions to implement are listed as issues in the [issues section](https://github.com/fischer-fjd/RconTroll/issues). You can either decide to participate in solving one or open a new one that you wish to solve or to get help on it. You can assign people or yourself in solving an issue. You can reference the type of issue. And finally you can relate issues to projects (next paragraph). More on issues are available on [GitHub help](https://help.github.com/articles/about-issues/).

The [projects section](https://github.com/fischer-fjd/RconTroll/projects) organised issues into project to realize. There is two types of projects in `RconTROLL`: (i) the core development of the package including all functions useful for all basic simulations of `TROLL`, and the module-specific projects related to each developed or under-development modules of `TROLL` related to specific objectives (i.e. ABC, sylviculture ...). Inside a project issues are organised into sections (e.g. [core project](https://github.com/fischer-fjd/RconTroll/projects/2)):

* **Low priority**: issues to be discussed or to be dealt with later
* **ToDo**: issues to be dealt with asap
* **InProgress**: issues under development
* **ToValidate**: issues solved and/or developed waiting for package maintainers approval
* **Done**: issues done and validated

The repository is also organised into branches allowing parallel development of core functions and main team and other branches of more specific unstable modules. Have a look to [GitHub help on branches](https://help.github.com/articles/creating-and-deleting-branches-within-your-repository/).

Finally, collaborations (so eventually yours) can be followed in the [insights section](https://github.com/fischer-fjd/RconTroll/pulse) and more particularly the [network graph](https://github.com/fischer-fjd/RconTroll/pulse) can help understand the current development from the package.

## Initialization for your development

If it's the first time you wish to contribute to `RconTROLL` package please first start to fork the original repository. For that open an account on GitHub if you do not already have one an use the upper right button to fork (see [GitHub help on forks](https://help.github.com/articles/fork-a-repo/)).

Then, there is two cases:

* you want to do core-development or development of a project already opened on another branch, in which case you will work either on the main or on the project specific branch
* you want to work on a new project in which case you need to open a new branch on your fork (please consider opening corresponding issues and project on the main repository)

Then you just have to clone locally the repository on your machine with `Git` using

```{bash, echo=T, eval=F}
git clone git@github.com:your_account/RconTroll.git
```

and further move in Rstudio on the corresponding branch you want to work on (upper right corner of Git interface in Rstudio) or with Git

```{bash, echo=T, eval=F}
git checkout -b "your_branch_name"
```

## Further development

When you start or continue to develop your local version or your branch you may want to get back parallel developments of the main repository. In order to do that use `git fetch` as explained in the [GitHub help about fetching a repository](https://help.github.com/articles/fetching-a-remote/). You may need to solve conflicts, which is relatively simple and consist in in choosing which recent version you want to keep (either yours or the one from the mane repository, see [help](https://help.github.com/articles/resolving-a-merge-conflict-using-the-command-line/)).

Then develop your code using advised workflow and recommendations from previous sections. Use the version tracking chapter to update NEWS and `commit` your changes. You can use cross-reference to cite issues (`#Number`), projects or people (`@poeple`) in you NEWS and commit messages.

When you want your changes to be available on your fork online use the `push` button in Rstudio git user interface or with `git push` in a command line interface. Pushing your changes online will trigger continuous integration tools: (i) [Travis-CI](https://travis-ci.org/sylvainschmitt/RconTroll) and [AppVeyor](https://ci.appveyor.com/project/sylvainschmitt/rcontroll) will do a check of your package similar to CRAN including formal testing and inform you by email if the package is still valid, (ii) [covr](https://codecov.io/github/sylvainschmitt/RconTroll?branch=master) will inform you the change of package coverage, i.e. if you decreased or increased formal testing coverage of the code, and especially which lines of codes necessitate formal testing.

Once you want to share your code new implementations with the rest of the development team and maintainers to be validated use pull-requests. [Pull-requests section](https://github.com/fischer-fjd/RconTroll/pulls) is available on the main repository of `RconTROLL`. Simply open a new one and link it to your on-line fork branch you wish to share. Do not forget to reference the pull request in corresponding issues. More about [pull requests](https://help.github.com/articles/about-pull-requests/) is available on GitHub help pages.

# Conclusion

I hope those guidelines will help you in further development of your projects inside `RconTROLL`.

Have a nice development ;)

### 2021-12-13 R/AvoidAvRes_withcrowns.Rmd
Treefelling work

---
title: 'AvoidAvRes_withcrowns'
author: "Vincyane Badouard"
date: "08/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(Maria)
library(sf)
library(dplyr)
library(nngeo)
library(ggplot2)
```

# Steps before the treefeling function
```{r}
MainTrail <- sf::st_linestring(matrix(c(286400, 582945,
                                        286400, 583250,
                                        286700, 583250,
                                        286700, 582945,
                                        286400, 582945) # the return
                                      ,ncol=2, byrow=TRUE))

pol1 <- list(matrix(c(286503, 583134,
                      286503, 583240,
                      286507, 583240,
                      286507, 583134,
                      286503, 583134) # the return
                    ,ncol=2, byrow=TRUE))
pol2 <- list(matrix(c(286650, 583134,
                      286650, 583240,
                      286654, 583240,
                      286654, 583134,
                      286650, 583134) # the return
                    ,ncol=2, byrow=TRUE))

PolList = list(pol1,pol2) #list of lists of numeric matrices
ScndTrail <- sf::st_multipolygon(PolList)

inventory <- addtreedim(inventorycheckformat(Paracou6_2016),
                        volumeparameters = ForestZoneVolumeParametersTable)

inventory <- suppressMessages(treeselection(inventory, objective = 20, scenario ="manual",
                                            fuel = "2", diversification = TRUE, specieslax = FALSE,
                                            objectivelax = TRUE, topography = DTMParacou, plotslope = PlotSlope,
                                            speciescriteria = SpeciesCriteria,
                                            advancedloggingparameters = loggingparameters())$inventory)

FutureReserveCrowns <- inventory %>% # create an object with future/reserve crowns only
  dplyr::filter(LoggingStatus == "future" | LoggingStatus == "reserve") %>%
  createcanopy() %>% # create all inventory crowns in the 'Crowns' column
  getgeometry(Crowns)

inventory <- inventory %>%
  dplyr::filter(Selected == "1") %>%
  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,
                CrownDiameter,Selected, Xutm, Yutm)

dat <- inventory[2,] %>% # just 1 row (1 tree)
  # force the orientation success for the exemple
  tibble::add_column(TreeFellingOrientationSuccess = "1")
```

# Arguments values
```{r}
advancedloggingparameters = loggingparameters()
directionalfelling = "1"
fuel ="0"

```

# Preliminary steps
```{r}
# Function
Trail <- st_union(MainTrail, ScndTrail) # Our trail will be MainTrail or ScndTrail

# The crown
Crown <- dat %>%
  mutate(xCrown = Xutm,
         yCrown = Yutm + TrunkHeight + CrownHeight/2,
         exCrown = CrownDiameter/2,
         eyCrown = CrownHeight/2) %>%
  st_as_sf(coords = c("xCrown", "yCrown")) # ellipse centroid coordinates
Crown <- st_ellipse(Crown, Crown$exCrown, Crown$eyCrown) # create the ellipse

# The trunk
Trunk <- with(dat,
              st_polygon(list(matrix(c(Xutm-(DBH/100)/2, Yutm,
                                       Xutm-(DBH/100)/2, Yutm + TrunkHeight,
                                       Xutm+(DBH/100)/2, Yutm + TrunkHeight,
                                       Xutm+(DBH/100)/2, Yutm,
                                       Xutm-(DBH/100)/2, Yutm) # the return
                                     ,ncol=2, byrow=TRUE))))

# Find the point (TrailPt) on the Trail closest to the location of the tree (Foot)
Foot <- st_point(c(dat$Xutm,dat$Yutm)) # tree foot point

NearestPoints <- st_nearest_points(Foot, Trail) # from the Foot of the tree to the Trail (linestring)

NearestPoint <- st_cast(NearestPoints, "POINT") # to have start (Foot) and end (TrailPt) points
TrailPt <- NearestPoint[[2]] # the point (TrailPt) on the Trail closest to the location of the tree (Foot)

# Compute the angle between the tree default position and the shortest way from the foot to the trail
## Right-hand trail
if(TrailPt[1] >= Foot[1]){ # x trail > x foot

  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                    c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))

  ## Left-hand trail
}else if(TrailPt[1] < Foot[1]){ # x trail < x foot

  theta <- 360 - numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                       c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
}

## when the tree is on the trail (no angle)
if(is.na(theta)) theta <- 0

```

# Create future/reserve points
## Loop version
```{r}
# ## To direct to !avoid damage to future and reserve trees!, and foot directed to the trail
# # if (directionalfelling == "1"&& (fuel !="1" || fuel !="2")) {
# 
# # Fut/Res crowns/circumference as points
# FutResAllPoints <- list()
# for (FR in 1:nrow(FutureReserveCrowns)) {
#   ## if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
#   if(FutureReserveCrowns$TreeHeight[FR] <= dat$TreeHeight){
#     
#     FutResAllPoints[[FR]] <- st_cast(st_sfc(FutureReserveCrowns$Crowns[FR]), "POINT", group_or_split = TRUE) # crowns edge in points form
#     
#     ## if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
#   }else if(FutureReserveCrowns$TreeHeight[FR] > dat$TreeHeight){
#     
#     # PROBLEMES de list 
#     FutResAllPoints[[FR]] <- st_point(c(FutureReserveCrowns$Xutm[FR], FutureReserveCrowns$Yutm[FR])) %>%  # the fut/res tree foot point
#       st_buffer(dist = FutureReserveCrowns$DBH[FR]/2) %>%  # create a buffer of DBH diameter
#       st_cast("MULTIPOINT") %>%  # polygon to multipoint
#       st_sfc() %>% 
#       st_cast("POINT", group_or_split = TRUE)
#   }
# }
# # Get all these points back
# do.call(st_union, FutResAllPoints)

```

## On the data.frame version
```{r}
# if (directionalfelling != "0")

### Compute points
FutResCrownsPoints <- NULL # to start
FutResDBHPoints <- NULL # to start

# if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
if(any(FutureReserveCrowns$TreeHeight <= dat$TreeHeight)){

  FutResCrownsPoints <- FutureReserveCrowns %>% 
    filter(TreeHeight <= dat$TreeHeight) %>% 
    mutate(Crowns = st_cast(Crowns, "MULTIPOINT")) %>% # polygon to multipoint
    summarise(Points = st_combine(Crowns)) # several multipoints to 1
}

# if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
if(any(FutureReserveCrowns$TreeHeight > dat$TreeHeight)){

  FutResDBHPoints <- FutureReserveCrowns %>% 
    filter(TreeHeight > dat$TreeHeight) %>% 
    rowwise() %>% 
    mutate(Points = st_point(c(Xutm, Yutm)) %>% 
             st_buffer(dist = DBH/2) %>% 
             st_cast("MULTIPOINT") %>% 
             st_sfc()) %>% 
    ungroup() %>% 
    summarise(Points = st_combine(Points)) # several multipoints to 1
}

# Get all these points back
if(!is.null(FutResCrownsPoints) & !is.null(FutResDBHPoints)){ # # if smaller and taller trees
  FutResAllPoints <- bind_rows(FutResCrownsPoints, FutResDBHPoints) %>%
    summarise(Points = st_combine(Points)) # 2 multipoints to 1
}

if(!is.null(FutResCrownsPoints) & is.null(FutResDBHPoints)){ # if smaller trees but no tallers
  FutResAllPoints <- FutResCrownsPoints
}

if(!is.null(FutResDBHPoints) & is.null(FutResCrownsPoints)){ # if taller trees but no smallers
  FutResAllPoints <- FutResDBHPoints
}

# Multipoints to points
FutResAllPoints <- st_cast(st_sfc(FutResAllPoints$Points), "POINT", group_or_split = TRUE)

```
## Test time of each version
```{r}
# fun1 <- function(data, H = 30){
#   FutResAllPoints <- list()
#   for (FR in 1:nrow(data)) {
#     ## if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
#     if(data$TreeHeight[FR] <= H){
#       
#       FutResAllPoints[[FR]] <- st_cast(st_sfc(data$Crowns[FR]), "POINT", group_or_split = TRUE) # crowns edge in points form
#       
#       ## if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
#     }else if(data$TreeHeight[FR] > H){
#       
#       # PROBLEMES de list 
#       FutResAllPoints[[FR]] <- st_point(c(data$Xutm[FR], data$Yutm[FR])) %>%  # the fut/res tree foot point
#         st_buffer(dist = data$DBH[FR]/2) %>%  # create a buffer of DBH diameter
#         st_cast("MULTIPOINT") %>%  # polygon to multipoint
#         st_sfc() %>% 
#         st_cast("POINT", group_or_split = TRUE)
#     }
#   }
#   return(do.call(st_union, FutResAllPoints))
# }
# 
# fun2 <- function(data, H = 30){
#   
#   FutResCrownsPoints <- data %>% 
#     filter(TreeHeight <= H) %>% 
#     summarise(Points = st_combine(Crowns))
#   
#   FutResDBHPoints <- data %>% 
#     filter(TreeHeight > H) %>% 
#     rowwise() %>% 
#     mutate(Points = st_point(c(Xutm, Yutm)) %>% 
#              st_buffer(dist = DBH/2) %>% 
#              st_cast("MULTIPOINT") %>% # 
#              st_sfc()) %>% 
#     ungroup() %>% 
#     summarise(Points = st_combine(Points)) # several multipoints to 1
#   
#   FutResAllPoints <- bind_rows(FutResCrownsPoints, FutResDBHPoints) %>% 
#     summarise(Points = st_combine(Points))
#   
#   return(st_cast(st_sfc(FutResAllPoints$Points), "POINT", group_or_split = TRUE))
# }
# 
# microbenchmark::microbenchmark(fun1(FutureReserveCrowns), fun2(FutureReserveCrowns), times = 10)
```

# Distances and angles
```{r}

# Distances between each of these points and Foot
FutResDists <- rep(NA, length(FutResAllPoints)) # empty list for distances
RotationAngle <- rep(NA, length(FutResDists)) # empty list for rotation angles
OppAngToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid
TrailAnglesToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid
AnglesToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid

for (FRP in 1:length(FutResAllPoints)) { # for each point
  FutResDists[[FRP]] <- st_distance(Foot, FutResAllPoints[[FRP]]) # compute the distance for each point

  # If distances < TreeHeight of the tree to be felled
  if(FutResDists[[FRP]] < dat$TreeHeight){
    # sum(FutResDists < dat$TreeHeight) # check av/res trees close to the tree to be felled

    # Compute the angles to the trail of this points
    ## 1st: the rotation angle (between the default position of the tree to cut down, and the position to avoid)
    ### Right-hand fut/res point
    if(FutResAllPoints[[FRP]][1] >= Foot[1]){ # x FRP > x foot

      RotationAngle[[FRP]] <- as.numeric(matlib::angle(
        c(Foot[1] - Foot[1], dat$TreeHeight), # default position
        c(FutResAllPoints[[FRP]][1] - Foot[1], FutResAllPoints[[FRP]][2] - Foot[2]), # position to avoid
        degree = TRUE))

      ### Left-hand fut/res point
    }else if(FutResAllPoints[[FRP]][1] < Foot[1]){ # x FRP < x foot

      RotationAngle[[FRP]] <- 360 - as.numeric(matlib::angle(
        c(Foot[1] - Foot[1], dat$TreeHeight), # default position
        c(FutResAllPoints[[FRP]][1] - Foot[1], FutResAllPoints[[FRP]][2] - Foot[2]), # position to avoid
        degree = TRUE))
      }

    # sum(!is.na(RotationAngle)) # check for how many av/res trees the angle has been computed

    ## Then the angle to the trail: the angle to avoid
    OppAngToAvoid[[FRP]] <- RotationAngle[[FRP]] - 180 - theta
    TrailAnglesToAvoid[[FRP]] <- 180-(90 + OppAngToAvoid[[FRP]])

    # Record their angles if there are in the fall zone ([1; 179°])
    if(TrailAnglesToAvoid[[FRP]] > 1 & TrailAnglesToAvoid[[FRP]] < 179){
      # any(!is.na(TrailAnglesToAvoid) < 179)

      AnglesToAvoid[[FRP]] <- round(TrailAnglesToAvoid[[FRP]], digits = 0)
      # Plus1 <- AnglesToAvoid + 1
      # Moins1 <- AnglesToAvoid - 1
      # Plus2 <- AnglesToAvoid + 2
      # Moins2 <- AnglesToAvoid - 2 # to add a 2° buffer
      # AnglesToAvoid <- c(AnglesToAvoid, Plus1, Moins1) #, Plus2, Moins2
      # sum(!is.na(Plus1)) to check

    }else{AnglesToAvoid <- NULL} # No angles to avoid

    # sum(!is.na(AnglesToAvoid)) # check for how many av/res trees the angle has been computed
  }else{AnglesToAvoid <- NULL} # No angles to avoid
}

```
# Tree felling
```{r}
# Drop the tree between [1; 179°] avoiding the angles of the futures/reserves
if(dat$TreeFellingOrientationSuccess == "1"){

  TreefallOrientation <- c(1:179) # the a priori fall zone (angles to the trail)
  TreefallOrientation <- TreefallOrientation[!TreefallOrientation %in% unique(AnglesToAvoid)] # Remove angles (the fut/res trees) to avoid

  TreefallOrientation <- as.numeric(sample(TreefallOrientation, size = 1)) # only those angles that avoid the fut/res trees

  OppAng <- 180-(90 + TreefallOrientation) # the angle between the closest position to the trail (90°) and the desired position (desired angle to the trail)

  ## Right-hand trail
  if(TrailPt[1] >= Foot[1]){ # x trail > x foot

    Aangle <- round(as.numeric(180 + OppAng + theta), digits = 0) # Foot oriented

    ## Left-hand trail
  }else if(TrailPt[1] < Foot[1]){ # x trail < x foot

    Aangle <- round(as.numeric(360 - OppAng + theta), digits = 0) # Foot oriented
  }

  # Calculate the crown and trunk position
  FallenTree <- st_difference(st_union( # A configuration (90° to the trail (shortest))
    rotatepolygon(Trunk, angle = Aangle, fixed = Foot), # turned trunk
    rotatepolygon(Crown, angle = Aangle, fixed = Foot) # turned crown
  ))

}else{ # else random felling
  RandomAngle <- as.numeric(sample(c(0:359.9), size = 1))

  FallenTree <- st_difference(st_union(
    rotatepolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
    rotatepolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
  ))
}

```

```{r}
ggplot() +
  geom_sf(data = Foot) +
  geom_sf(data = Trail) +
  geom_sf(data = NearestPoints) +
  geom_sf(data = TrailPt) +
  geom_sf(data = FallenTree) +
  geom_sf(data = FutureReserveCrowns) +
  geom_sf(data = FutResCrownsPoints, col = "green") + # smaller trees
  geom_sf(data = FutResDBHPoints, col = "pink")

# geom_sf(data = FutResAllPoints, col = "green")
```

### 2021-12-13 R/AvoidAvRes_withoutcrowns.Rmd
Treefelling work

--- 2021-12-13 R/AvoidAvRes_withcrowns.Rmd
@@
 ---
-title: 'AvoidAvRes_withcrowns'
+title: "AvoidAvRes_withoutcrowns"
 author: "Vincyane Badouard"
-date: "08/12/2021"
+date: "06/12/2021"
 output: html_document
@@
 
-# Steps before the treefeling function
 ```{r}
@@
 
-dat <- inventory[2,] %>% # just 1 row (1 tree)
+dat <- inventory[1,] %>% # just 1 row (1 tree)
   # force the orientation success for the exemple
   tibble::add_column(TreeFellingOrientationSuccess = "1")
+```
+
+```{r}
+FutureReserveCrowns$Crowns <- st_cast(FutureReserveCrowns$Crowns, "MULTIPOINT")
+
+ggplot() +
+   geom_sf(data = getgeometry(FutureReserveCrowns, Crowns), 
+           col = "forestgreen")
+plot(FutResCrownsPoints)
 ```
@@
 
-# Preliminary steps
+Preliminary steps
 ```{r}
@@
 # Compute the angle between the tree default position and the shortest way from the foot to the trail
-## Right-hand trail
-if(TrailPt[1] >= Foot[1]){ # x trail > x foot
-
 theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                   c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
-
-  ## Left-hand trail
-}else if(TrailPt[1] < Foot[1]){ # x trail < x foot
-
-  theta <- 360 - numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
-                                       c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
-}
 
@@
 
-# Create future/reserve points
-## Loop version
+New work
 ```{r}
-# ## To direct to !avoid damage to future and reserve trees!, and foot directed to the trail
-# # if (directionalfelling == "1"&& (fuel !="1" || fuel !="2")) {
-# 
-# # Fut/Res crowns/circumference as points
-# FutResAllPoints <- list()
-# for (FR in 1:nrow(FutureReserveCrowns)) {
-#   ## if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
-#   if(FutureReserveCrowns$TreeHeight[FR] <= dat$TreeHeight){
-#     
-#     FutResAllPoints[[FR]] <- st_cast(st_sfc(FutureReserveCrowns$Crowns[FR]), "POINT", group_or_split = TRUE) # crowns edge in points form
-#     
-#     ## if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
-#   }else if(FutureReserveCrowns$TreeHeight[FR] > dat$TreeHeight){
-#     
-#     # PROBLEMES de list 
-#     FutResAllPoints[[FR]] <- st_point(c(FutureReserveCrowns$Xutm[FR], FutureReserveCrowns$Yutm[FR])) %>%  # the fut/res tree foot point
-#       st_buffer(dist = FutureReserveCrowns$DBH[FR]/2) %>%  # create a buffer of DBH diameter
-#       st_cast("MULTIPOINT") %>%  # polygon to multipoint
-#       st_sfc() %>% 
-#       st_cast("POINT", group_or_split = TRUE)
-#   }
-# }
-# # Get all these points back
-# do.call(st_union, FutResAllPoints)
+## To direct to !avoid damage to future and reserve trees!, and foot directed to the trail
+# if (directionalfelling == "1"&& (fuel !="1" || fuel !="2")) {
 
-```
+# Find the future/reserve on the fall zone
+FutRescoord <-  FutureReserveCrowns %>%
+  filter(LoggingStatus == "future"| LoggingStatus == "reserve") %>%
+  select(Xutm, Yutm) 
+st_geometry(FutRescoord) <- NULL
 
-## On the data.frame version
-```{r}
-# if (directionalfelling != "0")
+FutResFoots <- st_multipoint(x = as.matrix(FutRescoord)) # all the future/reserve trees foot
+FutResFoots <- st_cast(st_sfc(FutResFoots), "POINT", group_or_split = TRUE) # multiple points
 
-### Compute points
-FutResCrownsPoints <- NULL # to start
-FutResDBHPoints <- NULL # to start
-
-# if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
-if(any(FutureReserveCrowns$TreeHeight <= dat$TreeHeight)){
-
-  FutResCrownsPoints <- FutureReserveCrowns %>% 
-    filter(TreeHeight <= dat$TreeHeight) %>% 
-    mutate(Crowns = st_cast(Crowns, "MULTIPOINT")) %>% # polygon to multipoint
-    summarise(Points = st_combine(Crowns)) # several multipoints to 1
-}
-
-# if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
-if(any(FutureReserveCrowns$TreeHeight > dat$TreeHeight)){
-
-  FutResDBHPoints <- FutureReserveCrowns %>% 
-    filter(TreeHeight > dat$TreeHeight) %>% 
-    rowwise() %>% 
-    mutate(Points = st_point(c(Xutm, Yutm)) %>% 
-             st_buffer(dist = DBH/2) %>% 
-             st_cast("MULTIPOINT") %>% 
-             st_sfc()) %>% 
-    ungroup() %>% 
-    summarise(Points = st_combine(Points)) # several multipoints to 1
-}
-
-# Get all these points back
-if(!is.null(FutResCrownsPoints) & !is.null(FutResDBHPoints)){ # # if smaller and taller trees
-  FutResAllPoints <- bind_rows(FutResCrownsPoints, FutResDBHPoints) %>%
-    summarise(Points = st_combine(Points)) # 2 multipoints to 1
-}
-
-if(!is.null(FutResCrownsPoints) & is.null(FutResDBHPoints)){ # if smaller trees but no tallers
-  FutResAllPoints <- FutResCrownsPoints
-}
-
-if(!is.null(FutResDBHPoints) & is.null(FutResCrownsPoints)){ # if taller trees but no smallers
-  FutResAllPoints <- FutResDBHPoints
-}
-
-# Multipoints to points
-FutResAllPoints <- st_cast(st_sfc(FutResAllPoints$Points), "POINT", group_or_split = TRUE)
-
-```
-## Test time of each version
-```{r}
-# fun1 <- function(data, H = 30){
-#   FutResAllPoints <- list()
-#   for (FR in 1:nrow(data)) {
-#     ## if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
-#     if(data$TreeHeight[FR] <= H){
-#       
-#       FutResAllPoints[[FR]] <- st_cast(st_sfc(data$Crowns[FR]), "POINT", group_or_split = TRUE) # crowns edge in points form
-#       
-#       ## if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
-#     }else if(data$TreeHeight[FR] > H){
-#       
-#       # PROBLEMES de list 
-#       FutResAllPoints[[FR]] <- st_point(c(data$Xutm[FR], data$Yutm[FR])) %>%  # the fut/res tree foot point
-#         st_buffer(dist = data$DBH[FR]/2) %>%  # create a buffer of DBH diameter
-#         st_cast("MULTIPOINT") %>%  # polygon to multipoint
-#         st_sfc() %>% 
-#         st_cast("POINT", group_or_split = TRUE)
-#     }
-#   }
-#   return(do.call(st_union, FutResAllPoints))
-# }
-# 
-# fun2 <- function(data, H = 30){
-#   
-#   FutResCrownsPoints <- data %>% 
-#     filter(TreeHeight <= H) %>% 
-#     summarise(Points = st_combine(Crowns))
-#   
-#   FutResDBHPoints <- data %>% 
-#     filter(TreeHeight > H) %>% 
-#     rowwise() %>% 
-#     mutate(Points = st_point(c(Xutm, Yutm)) %>% 
-#              st_buffer(dist = DBH/2) %>% 
-#              st_cast("MULTIPOINT") %>% # 
-#              st_sfc()) %>% 
-#     ungroup() %>% 
-#     summarise(Points = st_combine(Points)) # several multipoints to 1
-#   
-#   FutResAllPoints <- bind_rows(FutResCrownsPoints, FutResDBHPoints) %>% 
-#     summarise(Points = st_combine(Points))
-#   
-#   return(st_cast(st_sfc(FutResAllPoints$Points), "POINT", group_or_split = TRUE))
-# }
-# 
-# microbenchmark::microbenchmark(fun1(FutureReserveCrowns), fun2(FutureReserveCrowns), times = 10)
-```
-
-# Distances and angles
-```{r}
-
-# Distances between each of these points and Foot
-FutResDists <- rep(NA, length(FutResAllPoints)) # empty list for distances
+## distance to Foot < TreeHeight
+FutResDists <- rep(NA, length(FutResFoots)) # empty list for distances
 RotationAngle <- rep(NA, length(FutResDists)) # empty list for rotation angles
@@
 
-for (FRP in 1:length(FutResAllPoints)) { # for each point
-  FutResDists[[FRP]] <- st_distance(Foot, FutResAllPoints[[FRP]]) # compute the distance for each point
+for (FRF in 1:length(FutResFoots)) { # for each point
+  FutResDists[[FRF]] <- st_distance(Foot, FutResFoots[[FRF]]) # compute the distance for each point
 
-  # If distances < TreeHeight of the tree to be felled
-  if(FutResDists[[FRP]] < dat$TreeHeight){
+  ## angle to the trail
+  if(FutResDists[[FRF]] < dat$TreeHeight){
     # sum(FutResDists < dat$TreeHeight) # check av/res trees close to the tree to be felled
 
-    # Compute the angles to the trail of this points
-    ## 1st: the rotation angle (between the default position of the tree to cut down, and the position to avoid)
-    ### Right-hand fut/res point
-    if(FutResAllPoints[[FRP]][1] >= Foot[1]){ # x FRP > x foot
-
-      RotationAngle[[FRP]] <- as.numeric(matlib::angle(
+    ### 1st: the rotation angle (between the default position of the tree to cut down, and the position to avoid)
+    RotationAngle[[FRF]] <- as.numeric(matlib::angle(
       c(Foot[1] - Foot[1], dat$TreeHeight), # default position
-        c(FutResAllPoints[[FRP]][1] - Foot[1], FutResAllPoints[[FRP]][2] - Foot[2]), # position to avoid
+      c(FutResFoots[[FRF]][1] - Foot[1], FutResFoots[[FRF]][2] - Foot[2]), # position to avoid
       degree = TRUE))
-
-      ### Left-hand fut/res point
-    }else if(FutResAllPoints[[FRP]][1] < Foot[1]){ # x FRP < x foot
-
-      RotationAngle[[FRP]] <- 360 - as.numeric(matlib::angle(
-        c(Foot[1] - Foot[1], dat$TreeHeight), # default position
-        c(FutResAllPoints[[FRP]][1] - Foot[1], FutResAllPoints[[FRP]][2] - Foot[2]), # position to avoid
-        degree = TRUE))
-      }
-
     # sum(!is.na(RotationAngle)) # check for how many av/res trees the angle has been computed
 
-    ## Then the angle to the trail: the angle to avoid
-    OppAngToAvoid[[FRP]] <- RotationAngle[[FRP]] - 180 - theta
-    TrailAnglesToAvoid[[FRP]] <- 180-(90 + OppAngToAvoid[[FRP]])
+    ### Then the angle to the trail: the angle to avoid
+    OppAngToAvoid[[FRF]] <- RotationAngle[[FRF]] - 180 - theta
+    TrailAnglesToAvoid[[FRF]] <- 180-(90 + OppAngToAvoid[[FRF]])
 
-    # Record their angles if there are in the fall zone ([1; 179°])
-    if(TrailAnglesToAvoid[[FRP]] > 1 & TrailAnglesToAvoid[[FRP]] < 179){
-      # any(!is.na(TrailAnglesToAvoid) < 179)
+    ## record their angles if there are in the fall zone ([0.1; 179.9°])
+    if(TrailAnglesToAvoid[[FRF]] %in% c(0.1:179.9)){
 
-      AnglesToAvoid[[FRP]] <- round(TrailAnglesToAvoid[[FRP]], digits = 0)
-      # Plus1 <- AnglesToAvoid + 1
-      # Moins1 <- AnglesToAvoid - 1
-      # Plus2 <- AnglesToAvoid + 2
-      # Moins2 <- AnglesToAvoid - 2 # to add a 2° buffer
-      # AnglesToAvoid <- c(AnglesToAvoid, Plus1, Moins1) #, Plus2, Moins2
-      # sum(!is.na(Plus1)) to check
-
+      AnglesToAvoid[[FRF]] <- TrailAnglesToAvoid[[FRF]]
     }else{AnglesToAvoid <- NULL} # No angles to avoid
 
-    # sum(!is.na(AnglesToAvoid)) # check for how many av/res trees the angle has been computed
-  }else{AnglesToAvoid <- NULL} # No angles to avoid
-}
+  }} # temporaires
 
 ```
-# Tree felling
+
 ```{r}
-# Drop the tree between [1; 179°] avoiding the angles of the futures/reserves
+# Drop the tree between [0.1; 179.9°] avoiding the angles of the futures/reserves
 if(dat$TreeFellingOrientationSuccess == "1"){
@@
   TreefallOrientation <- c(1:179) # the a priori fall zone (angles to the trail)
-  TreefallOrientation <- TreefallOrientation[!TreefallOrientation %in% unique(AnglesToAvoid)] # Remove angles (the fut/res trees) to avoid
+  TreefallOrientation <- TreefallOrientation[!TreefallOrientation %in% AnglesToAvoid] # Remove angles (the fut/res trees) to avoid
 
@@
 }
-
 ```
-
-```{r}
-ggplot() +
-  geom_sf(data = Foot) +
-  geom_sf(data = Trail) +
-  geom_sf(data = NearestPoints) +
-  geom_sf(data = TrailPt) +
-  geom_sf(data = FallenTree) +
-  geom_sf(data = FutureReserveCrowns) +
-  geom_sf(data = FutResCrownsPoints, col = "green") + # smaller trees
-  geom_sf(data = FutResDBHPoints, col = "pink")
-
-# geom_sf(data = FutResAllPoints, col = "green")
-```

### 2021-12-13 R/AvoidFutRessimpletest.Rmd
Treefelling work

--- 2021-12-13 R/AvoidAvRes_withcrowns.Rmd
@@
 ---
-title: 'AvoidAvRes_withcrowns'
+title: "AvoidFutRessimpletest"
 author: "Vincyane Badouard"
-date: "08/12/2021"
+date: "10/12/2021"
 output: html_document
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
 ```{r}
@@
 
-# Arguments values
+Our tree to be felled
 ```{r}
-advancedloggingparameters = loggingparameters()
-directionalfelling = "1"
-fuel ="0"
+dat$Xutm <- 286546.1
+dat$Yutm <- 583029.1
+```
+# A buffer around the Foot
+```{r}
+FootBuffer <- dat %>% 
+  mutate(Points = st_point(c(Xutm, Yutm)) %>% 
+           st_buffer(dist = CrownDiameter/2) %>% 
+           st_cast("MULTIPOINT") %>% 
+           st_sfc())
+
+# Multipoints to points
+FootBuffer <- st_cast(st_sfc(FootBuffer$Points), "POINT", group_or_split = TRUE)
+
+```
+
+2 av/res trees
+```{r}
+FutureReserveCrowns <- FutureReserveCrowns[1:2,]
+
+# at the same y than the tree to be felled
+# 1 on the right side
+FutureReserveCrowns[1,]$Xutm <- dat$Xutm + 30
+FutureReserveCrowns[1,]$Yutm <- dat$Yutm + 10
+
+# 1 on the left side
+FutureReserveCrowns[2,]$Xutm <- dat$Xutm - 30 
+FutureReserveCrowns[2,]$Yutm <- dat$Yutm + 10
+
+# # Re-compute the crown
+st_geometry(FutureReserveCrowns) <- NULL
+
+FutureReserveCrowns <- FutureReserveCrowns %>%
+  createcanopy() %>% # create all inventory crowns in the 'Crowns' column
+  getgeometry(Crowns)
 
@@
 
-# Create future/reserve points
-## Loop version
-```{r}
-# ## To direct to !avoid damage to future and reserve trees!, and foot directed to the trail
-# # if (directionalfelling == "1"&& (fuel !="1" || fuel !="2")) {
-# 
-# # Fut/Res crowns/circumference as points
-# FutResAllPoints <- list()
-# for (FR in 1:nrow(FutureReserveCrowns)) {
-#   ## if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
-#   if(FutureReserveCrowns$TreeHeight[FR] <= dat$TreeHeight){
-#     
-#     FutResAllPoints[[FR]] <- st_cast(st_sfc(FutureReserveCrowns$Crowns[FR]), "POINT", group_or_split = TRUE) # crowns edge in points form
-#     
-#     ## if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
-#   }else if(FutureReserveCrowns$TreeHeight[FR] > dat$TreeHeight){
-#     
-#     # PROBLEMES de list 
-#     FutResAllPoints[[FR]] <- st_point(c(FutureReserveCrowns$Xutm[FR], FutureReserveCrowns$Yutm[FR])) %>%  # the fut/res tree foot point
-#       st_buffer(dist = FutureReserveCrowns$DBH[FR]/2) %>%  # create a buffer of DBH diameter
-#       st_cast("MULTIPOINT") %>%  # polygon to multipoint
-#       st_sfc() %>% 
-#       st_cast("POINT", group_or_split = TRUE)
-#   }
-# }
-# # Get all these points back
-# do.call(st_union, FutResAllPoints)
-
-```
-
-## On the data.frame version
+# Compute points
 ```{r}
@@
 ```
-## Test time of each version
-```{r}
-# fun1 <- function(data, H = 30){
-#   FutResAllPoints <- list()
-#   for (FR in 1:nrow(data)) {
-#     ## if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
-#     if(data$TreeHeight[FR] <= H){
-#       
-#       FutResAllPoints[[FR]] <- st_cast(st_sfc(data$Crowns[FR]), "POINT", group_or_split = TRUE) # crowns edge in points form
-#       
-#       ## if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
-#     }else if(data$TreeHeight[FR] > H){
-#       
-#       # PROBLEMES de list 
-#       FutResAllPoints[[FR]] <- st_point(c(data$Xutm[FR], data$Yutm[FR])) %>%  # the fut/res tree foot point
-#         st_buffer(dist = data$DBH[FR]/2) %>%  # create a buffer of DBH diameter
-#         st_cast("MULTIPOINT") %>%  # polygon to multipoint
-#         st_sfc() %>% 
-#         st_cast("POINT", group_or_split = TRUE)
-#     }
-#   }
-#   return(do.call(st_union, FutResAllPoints))
-# }
-# 
-# fun2 <- function(data, H = 30){
-#   
-#   FutResCrownsPoints <- data %>% 
-#     filter(TreeHeight <= H) %>% 
-#     summarise(Points = st_combine(Crowns))
-#   
-#   FutResDBHPoints <- data %>% 
-#     filter(TreeHeight > H) %>% 
-#     rowwise() %>% 
-#     mutate(Points = st_point(c(Xutm, Yutm)) %>% 
-#              st_buffer(dist = DBH/2) %>% 
-#              st_cast("MULTIPOINT") %>% # 
-#              st_sfc()) %>% 
-#     ungroup() %>% 
-#     summarise(Points = st_combine(Points)) # several multipoints to 1
-#   
-#   FutResAllPoints <- bind_rows(FutResCrownsPoints, FutResDBHPoints) %>% 
-#     summarise(Points = st_combine(Points))
-#   
-#   return(st_cast(st_sfc(FutResAllPoints$Points), "POINT", group_or_split = TRUE))
-# }
-# 
-# microbenchmark::microbenchmark(fun1(FutureReserveCrowns), fun2(FutureReserveCrowns), times = 10)
-```
 
@@
 ```{r}
+
+# Only Foots 
+# FutResAllPoints <- FutureReserveCrowns %>% 
+#    select(Xutm, Yutm)
+# 
+# FutResFoots <- st_multipoint(x = as.matrix(FutResAllPoints)) # all the future/reserve trees foot
+# FutResAllPoints <- st_cast(st_sfc(FutResFoots), "POINT", group_or_split = TRUE) # multiple points
 
@@
     ## 1st: the rotation angle (between the default position of the tree to cut down, and the position to avoid)
+    for (P in 1:length(FootBuffer)) { # for each point of the Foot buffer
+
       ### Right-hand fut/res point
-    if(FutResAllPoints[[FRP]][1] >= Foot[1]){ # x FRP > x foot
+      if(FutResAllPoints[[FRP]][1] >= FootBuffer[[P]][1]){ # x FRP > x foot
 
         RotationAngle[[FRP]] <- as.numeric(matlib::angle(
-        c(Foot[1] - Foot[1], dat$TreeHeight), # default position
-        c(FutResAllPoints[[FRP]][1] - Foot[1], FutResAllPoints[[FRP]][2] - Foot[2]), # position to avoid
+          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], dat$TreeHeight), # default position
+          c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - FootBuffer[[P]][2]), # position to avoid
           degree = TRUE))
@@
         ### Left-hand fut/res point
-    }else if(FutResAllPoints[[FRP]][1] < Foot[1]){ # x FRP < x foot
+      }else if(FutResAllPoints[[FRP]][1] < FootBuffer[[P]][1]){ # x FRP < x foot
 
         RotationAngle[[FRP]] <- 360 - as.numeric(matlib::angle(
-        c(Foot[1] - Foot[1], dat$TreeHeight), # default position
-        c(FutResAllPoints[[FRP]][1] - Foot[1], FutResAllPoints[[FRP]][2] - Foot[2]), # position to avoid
+          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], dat$TreeHeight), # default position
+          c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - FootBuffer[[P]][2]), # position to avoid
           degree = TRUE))
+      }
     }
@@
     ## Then the angle to the trail: the angle to avoid
-    OppAngToAvoid[[FRP]] <- RotationAngle[[FRP]] - 180 - theta
+    OppAngToAvoid[[FRP]] <- RotationAngle[[FRP]] - 180 - theta # valeurs négatives c'est là le prblm
     TrailAnglesToAvoid[[FRP]] <- 180-(90 + OppAngToAvoid[[FRP]])
+
+    TrailAnglesToAvoid[[FRP]] <- round(TrailAnglesToAvoid[[FRP]], digits = 0)
+
+    if(TrailAnglesToAvoid[[FRP]] >= 360) TrailAnglesToAvoid[[FRP]] <- TrailAnglesToAvoid[[FRP]] - 360
 
@@
 
-      AnglesToAvoid[[FRP]] <- round(TrailAnglesToAvoid[[FRP]], digits = 0)
+      AnglesToAvoid[[FRP]] <- TrailAnglesToAvoid[[FRP]]
       # Plus1 <- AnglesToAvoid + 1
@@
 ```
+
 # Tree felling
@@
 }
-
 ```
 
+# Plot
 ```{r}
@@
   geom_sf(data = FallenTree) +
-  geom_sf(data = FutureReserveCrowns) +
+  geom_sf(data = FutResAllPoints) + # FutureReserveCrowns
   geom_sf(data = FutResCrownsPoints, col = "green") + # smaller trees
-  geom_sf(data = FutResDBHPoints, col = "pink")
+  geom_sf(data = FutResDBHPoints, col = "pink") +
+  geom_sf(data = FootBuffer)
 

### 2021-12-13 R/CopyOftreefelling.R

@@ -624,7 +624,7 @@ rotatepolygon <- function(
 #' tibble::add_column(TreeFellingOrientationSuccess = "1")
 #'
 #' rslt <- felling1tree(dat,
-#'  fuel = "0", directionalfelling = "1",
+#'  fuel = "0", directionalfelling = "2",
 #'  MainTrail = MainTrail, ScndTrail = ScndTrail,
 #'  FutureReserveCrowns = FutureReserveCrowns,
 #'  advancedloggingparameters = loggingparameters())
@@ -716,18 +716,8 @@ felling1tree <- function(
   TrailPt <- NearestPoint[[2]] # the point (TrailPt) on the Trail closest to the location of the tree (Foot)
 
   # Compute the angle between the tree default position and the shortest way from the foot to the trail
-  ## Right-hand trail
-  if(TrailPt[1] >= Foot[1]){ # x trail > x foot
-
-    theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
-                                      c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
-
-    ## Left-hand trail
-  }else if(TrailPt[1] < Foot[1]){ # x trail < x foot
-
-    theta <- 360 - numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
-                                         c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
-  }
+  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
+                                    c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
 
   ## when the tree is on the trail (no angle)
   if(is.na(theta)) theta <- 0
@@ -736,61 +726,30 @@ felling1tree <- function(
   if (directionalfelling != "0"){
 
     ### Compute points
-    FutResCrownsPoints <- NULL # to start
-    FutResDBHPoints <- NULL # to start
-
     # if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
-    if(any(FutureReserveCrowns$TreeHeight <= dat$TreeHeight)){
-
-      FutResCrownsPoints <- FutureReserveCrowns %>%
-        filter(TreeHeight <= dat$TreeHeight) %>%
-        mutate(Crowns = st_cast(Crowns,"MULTIPOINT")) %>% # polygon to multipoint
[…]

### 2021-12-13 R/AvoidFutRessimpletest.Rmd
Avoid Future Reserve solved

@@
 ```{r}
+rm(list = ls()) ; invisible(gc())
 library(Maria)
@@
 library(ggplot2)
+set.seed(420)
 ```
 
-# Steps before the treefeling function
+# Trails
+
 ```{r}
@@
                                       ,ncol=2, byrow=TRUE))
-
 pol1 <- list(matrix(c(286503, 583134,
@@
 ScndTrail <- sf::st_multipolygon(PolList)
+Trail <- st_union(MainTrail, ScndTrail) # Our trail will be MainTrail or ScndTrail
+rm(MainTrail, ScndTrail, pol1, pol2, PolList)
+```
 
+```{r}
+ggplot() +
+  geom_sf(data = Trail)
+```
+
+# Individuals
+
+```{r}
 inventory <- addtreedim(inventorycheckformat(Paracou6_2016),
@@
                                             fuel = "2", diversification = TRUE, specieslax = FALSE,
-                                            objectivelax = TRUE, topography = DTMParacou, plotslope = PlotSlope,
+                                            objectivelax = TRUE, topography = DTMParacou, 
+                                            plotslope = PlotSlope,
                                             speciescriteria = SpeciesCriteria,
                                             advancedloggingparameters = loggingparameters())$inventory)
+ind <- inventory %>%
+  dplyr::filter(Selected == "1") %>%
+  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,
+                CrownDiameter,Selected, Xutm, Yutm) %>% 
+  sample_n(1) %>% 
+  tibble::add_column(TreeFellingOrientationSuccess = "1")
 
+ind$Xutm <- 286546.1
+ind$Yutm <- 583029.1
+Foot <- st_point(c(ind$Xutm,ind$Yutm))
+```
+
+```{r}
+ggplot() +
+  geom_sf(data = Trail) +
+  geom_sf(data = Foot)
+```
+
+# Future Reserve
+
+```{r}
 FutureReserveCrowns <- inventory %>% # create an object with future/reserve crowns only
@@
 
-inventory <- inventory %>%
-  dplyr::filter(Selected == "1") %>%
-  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,
-                CrownDiameter,Selected, Xutm, Yutm)
-
-dat <- inventory[2,] %>% # just 1 row (1 tree)
-  # force the orientation success for the exemple
-  tibble::add_column(TreeFellingOrientationSuccess = "1")
-```
-
-Our tree to be felled
-```{r}
-dat$Xutm <- 286546.1
-dat$Yutm <- 583029.1
-```
-# A buffer around the Foot
-```{r}
-FootBuffer <- dat %>% 
-  mutate(Points = st_point(c(Xutm, Yutm)) %>% 
-           st_buffer(dist = CrownDiameter/2) %>% 
-           st_cast("MULTIPOINT") %>% 
-           st_sfc())
-
-# Multipoints to points
-FootBuffer <- st_cast(st_sfc(FootBuffer$Points), "POINT", group_or_split = TRUE)
-
-```
-
-2 av/res trees
-```{r}
 FutureReserveCrowns <- FutureReserveCrowns[1:2,]
@@
 # 1 on the right side
-FutureReserveCrowns[1,]$Xutm <- dat$Xutm + 30
-FutureReserveCrowns[1,]$Yutm <- dat$Yutm + 10
+FutureReserveCrowns[1,]$Xutm <- ind$Xutm + 30
+FutureReserveCrowns[1,]$Yutm <- ind$Yutm + 10
 
 # 1 on the left side
-FutureReserveCrowns[2,]$Xutm <- dat$Xutm - 30 
-FutureReserveCrowns[2,]$Yutm <- dat$Yutm + 10
+FutureReserveCrowns[2,]$Xutm <- ind$Xutm - 30 
+FutureReserveCrowns[2,]$Yutm <- ind$Yutm + 10
 
@@
 
+rm(inventory)
 ```
 
-# Preliminary steps
 ```{r}
-# Function
-Trail <- st_union(MainTrail, ScndTrail) # Our trail will be MainTrail or ScndTrail
+ggplot() +
+   geom_sf(data = Trail) +
+  geom_sf(data = Foot) +
+  geom_sf(data = FutureReserveCrowns$Crowns, col = "green")
+```
 
+# Individual geometry
+
+```{r}
 # The crown
-Crown <- dat %>%
+Crown <- ind %>%
   mutate(xCrown = Xutm,
@@
 # The trunk
-Trunk <- with(dat,
+Trunk <- with(ind,
               st_polygon(list(matrix(c(Xutm-(DBH/100)/2, Yutm,
@@
 # Find the point (TrailPt) on the Trail closest to the location of the tree (Foot)
-Foot <- st_point(c(dat$Xutm,dat$Yutm)) # tree foot point
+ # tree foot point
 
@@
 TrailPt <- NearestPoint[[2]] # the point (TrailPt) on the Trail closest to the location of the tree (Foot)
+rm(NearestPoint)
 
@@
 
-  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
+  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], ind$TreeHeight),
                                     c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
@@
 
-  theta <- 360 - numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
+  theta <- 360 - numeric(matlib::angle(c(Foot[1] - Foot[1], ind$TreeHeight),
                                        c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
@@
 if(is.na(theta)) theta <- 0
-
+thetaIndNearest <- theta
+rm(theta)
 ```
 
-# Compute points
+```{r}
+ggplot() +
+  geom_sf(data = Trail) +
+  geom_sf(data = Foot) +
+  geom_sf(data = FutureReserveCrowns$Crowns, col = "green") +
+  geom_sf(data = NearestPoints) +
+  geom_sf(data = TrailPt) +
+  geom_sf(data = Crown) +
+  geom_sf(data = Trunk)
+```
+
+# Future Reserve Crowns to Points
+
 ```{r}
@@
 # if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
-if(any(FutureReserveCrowns$TreeHeight <= dat$TreeHeight)){
+if(any(FutureReserveCrowns$TreeHeight <= ind$TreeHeight)){
 
   FutResCrownsPoints <- FutureReserveCrowns %>% 
-    filter(TreeHeight <= dat$TreeHeight) %>% 
+    filter(TreeHeight <= ind$TreeHeight) %>% 
     mutate(Crowns = st_cast(Crowns, "MULTIPOINT")) %>% # polygon to multipoint
@@
 # if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
-if(any(FutureReserveCrowns$TreeHeight > dat$TreeHeight)){
+if(any(FutureReserveCrowns$TreeHeight > ind$TreeHeight)){
 
   FutResDBHPoints <- FutureReserveCrowns %>% 
-    filter(TreeHeight > dat$TreeHeight) %>% 
+    filter(TreeHeight > ind$TreeHeight) %>% 
     rowwise() %>% 
@@
 
+rm(FutResCrownsPoints, FutResDBHPoints)
+```
+
+```{r}
+ggplot() +
+  geom_sf(data = Trail) +
+  geom_sf(data = Foot) +
+  geom_sf(data = FutureReserveCrowns$Crowns, col = "green") +
+  geom_sf(data = NearestPoints) +
+  geom_sf(data = TrailPt) +
+  geom_sf(data = Crown) +
+  geom_sf(data = Trunk) +
+  geom_sf(data = FutResAllPoints, col = "green")
+```
+
+# Individual Foot Buffer
+
+```{r}
+FootBuffer <- ind %>% 
+  mutate(Points = st_point(c(Xutm, Yutm)) %>% 
+           st_buffer(dist = CrownDiameter/2) %>% 
+           st_cast("MULTIPOINT") %>% 
+           st_sfc())
+# Multipoints to points
+FootBuffer <- st_cast(st_sfc(FootBuffer$Points), "POINT", group_or_split = TRUE)
+```
+
+```{r}
+ggplot() +
+  geom_sf(data = Trail) +
+  geom_sf(data = Foot) +
+  geom_sf(data = FutureReserveCrowns$Crowns, col = "green") +
+  geom_sf(data = NearestPoints) +
+  geom_sf(data = TrailPt) +
+  geom_sf(data = Crown) +
+  geom_sf(data = Trunk) +
+  geom_sf(data = FutResAllPoints, col = "green") +
+  geom_sf(data = FootBuffer)
 ```
@@
 # Distances between each of these points and Foot
-FutResDists <- rep(NA, length(FutResAllPoints)) # empty list for distances
-RotationAngle <- rep(NA, length(FutResDists)) # empty list for rotation angles
-OppAngToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid
-TrailAnglesToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid
-AnglesToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid
-
+RotationAngle <- c() # empty list for rotation angles
 for (FRP in 1:length(FutResAllPoints)) { # for each point
-  FutResDists[[FRP]] <- st_distance(Foot, FutResAllPoints[[FRP]]) # compute the distance for each point
+  FutResDist <- st_distance(Foot, FutResAllPoints[[FRP]]) # compute the distance for each point
 
   # If distances < TreeHeight of the tree to be felled
-  if(FutResDists[[FRP]] < dat$TreeHeight){
-    # sum(FutResDists < dat$TreeHeight) # check av/res trees close to the tree to be felled
+  if(FutResDist < ind$TreeHeight){
+    # sum(FutResDists < ind$TreeHeight) # check av/res trees close to the tree to be felled
 
@@
 
-        RotationAngle[[FRP]] <- as.numeric(matlib::angle(
-          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], dat$TreeHeight), # default position
+        RotationAngle <- c(RotationAngle, as.numeric(matlib::angle(
+          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], ind$TreeHeight), # default position
           c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - FootBuffer[[P]][2]), # position to avoid
-          degree = TRUE))
+          degree = TRUE)))
 
@@
 
-        RotationAngle[[FRP]] <- 360 - as.numeric(matlib::angle(
-          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], dat$TreeHeight), # default position
-          c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - FootBuffer[[P]][2]), # position to avoid
-          degree = TRUE))
+        RotationAngle <- c(RotationAngle,  360 - as.numeric(matlib::angle(
+          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], ind$TreeHeight), # default position
+          c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - 
+              FootBuffer[[P]][2]), # position to avoid
+          degree = TRUE)))
       }
     }
-
+  }
+}
+rm(FutResDist)
       # sum(!is.na(RotationAngle)) # check for how many av/res trees the angle has been computed
@@
     ## Then the angle to the trail: the angle to avoid
-    OppAngToAvoid[[FRP]] <- RotationAngle[[FRP]] - 180 - theta # valeurs négatives c'est là le prblm
-    TrailAnglesToAvoid[[FRP]] <- 180-(90 + OppAngToAvoid[[FRP]])
-
-    TrailAnglesToAvoid[[FRP]] <- round(TrailAnglesToAvoid[[FRP]], digits = 0)
-
-    if(TrailAnglesToAvoid[[FRP]] >= 360) TrailAnglesToAvoid[[FRP]] <- TrailAnglesToAvoid[[FRP]] - 360
-
-    # Record their angles if there are in the fall zone ([1; 179°])
-    if(TrailAnglesToAvoid[[FRP]] > 1 & TrailAnglesToAvoid[[FRP]] < 179){
-      # any(!is.na(TrailAnglesToAvoid) < 179)
-
-      AnglesToAvoid[[FRP]] <- TrailAnglesToAvoid[[FRP]]
-      # Plus1 <- AnglesToAvoid + 1
-      # Moins1 <- AnglesToAvoid - 1
-      # Plus2 <- AnglesToAvoid + 2
-      # Moins2 <- AnglesToAvoid - 2 # to add a 2° buffer
-      # AnglesToAvoid <- c(AnglesToAvoid, Plus1, Moins1) #, Plus2, Moins2
-      # sum(!is.na(Plus1)) to check
-
-    }else{AnglesToAvoid <- NULL} # No angles to avoid
-
-    # sum(!is.na(AnglesToAvoid)) # check for how many av/res trees the angle has been computed
-  }else{AnglesToAvoid <- NULL} # No angles to avoid
-}
-
+OppAngToAvoid <- RotationAngle - 180 - thetaIndNearest # valeurs négatives c'est là le prblm
+TrailAnglesToAvoid <- 180-(90 + OppAngToAvoid)
+TrailAnglesToAvoid <- round(TrailAnglesToAvoid, digits = 0)
+TrailAnglesToAvoid[TrailAnglesToAvoid >= 360] <- TrailAnglesToAvoid[TrailAnglesToAvoid >= 360] - 360
+AnglesToAvoid <- TrailAnglesToAvoid[
+  TrailAnglesToAvoid >= 1 & TrailAnglesToAvoid <= 179
+]
 ```
 
-# Tree felling
+# One tree felling
+
 ```{r}
 # Drop the tree between [1; 179°] avoiding the angles of the futures/reserves
-if(dat$TreeFellingOrientationSuccess == "1"){
+if(ind$TreeFellingOrientationSuccess == "1"){
 
@@
 
-    Aangle <- round(as.numeric(180 + OppAng + theta), digits = 0) # Foot oriented
+    Aangle <- round(as.numeric(180 + OppAng + thetaIndNearest), digits = 0) # Foot oriented
 
@@
 
-    Aangle <- round(as.numeric(360 - OppAng + theta), digits = 0) # Foot oriented
+    Aangle <- round(as.numeric(360 - OppAng + thetaIndNearest), digits = 0) # Foot oriented
   }
@@
 
-# Plot
 ```{r}
 ggplot() +
+  geom_sf(data = Trail) +
   geom_sf(data = Foot) +
-  geom_sf(data = Trail) +
+  geom_sf(data = FutureReserveCrowns$Crowns, col = "green") +
   geom_sf(data = NearestPoints) +
   geom_sf(data = TrailPt) +
-  geom_sf(data = FallenTree) +
-  geom_sf(data = FutResAllPoints) + # FutureReserveCrowns
-  geom_sf(data = FutResCrownsPoints, col = "green") + # smaller trees
-  geom_sf(data = FutResDBHPoints, col = "pink") +
-  geom_sf(data = FootBuffer)
+  geom_sf(data = Crown) +
+  geom_sf(data = Trunk) +
+  geom_sf(data = FutResAllPoints, col = "green") +
+  geom_sf(data = FootBuffer) +
+  geom_sf(data = FallenTree, col = "red")
+```
 
-# geom_sf(data = FutResAllPoints, col = "green")
+# All tree felling
+
+```{r}
+TreefallOrientation <- c(1:179) # the a priori fall zone (angles to the trail)
+TreefallOrientation <- TreefallOrientation[!TreefallOrientation %in% unique(AnglesToAvoid)] # Remove angles (the fut/res trees) to avoid
+
+felling <- function(theta){
+
+   OppAng <- 180-(90 + as.numeric(theta)) # the angle between the closest position to the trail (90°) and the desired position (desired angle to the trail)
+
+  ## Right-hand trail
+  if(TrailPt[1] >= Foot[1]){ # x trail > x foot
+
+    Aangle <- round(as.numeric(180 + OppAng + thetaIndNearest), digits = 0) # Foot oriented
+
+    ## Left-hand trail
+  }else if(TrailPt[1] < Foot[1]){ # x trail < x foot
+
+    Aangle <- round(as.numeric(360 - OppAng + thetaIndNearest), digits = 0) # Foot oriented
+  }
+
+  # Calculate the crown and trunk position
+  FallenTree <- st_difference(st_union( # A configuration (90° to the trail (shortest))
+    rotatepolygon(Trunk, angle = Aangle, fixed = Foot), # turned trunk
+    rotatepolygon(Crown, angle = Aangle, fixed = Foot) # turned crown
+  ))
+  return(FallenTree)
+}
+
+FallenTrees <- lapply(as.list(TreefallOrientation), felling)
+FallenTrees <- lapply(FallenTrees, function(x) data.frame(Tree = x)) %>% 
+  bind_rows()
 ```
+
+```{r}
+ggplot() +
+  geom_sf(data = Trail) +
+  geom_sf(data = Foot) +
+  geom_sf(data = FutureReserveCrowns$Crowns, col = "green") +
+  geom_sf(data = NearestPoints) +
+  geom_sf(data = TrailPt) +
+  geom_sf(data = Crown) +
+  geom_sf(data = Trunk) +
+  geom_sf(data = FutResAllPoints, col = "green") +
+  geom_sf(data = FootBuffer) +
+  geom_sf(data = FallenTrees$geometry, col = "red")
+```

### 2021-12-16 R/AvoidFutRessimpletest.Rmd
Treefelling end!!

@@
                                             advancedloggingparameters = loggingparameters())$inventory)
-ind <- inventory %>%
+dat <- inventory %>%
   dplyr::filter(Selected == "1") %>%
@@
 
-ind$Xutm <- 286546.1
-ind$Yutm <- 583029.1
-Foot <- st_point(c(ind$Xutm,ind$Yutm))
+dat$Xutm <- 286546.1
+dat$Yutm <- 583029.1
+Foot <- st_point(c(dat$Xutm,dat$Yutm))
 ```
@@
 # 1 on the right side
-FutureReserveCrowns[1,]$Xutm <- ind$Xutm + 30
-FutureReserveCrowns[1,]$Yutm <- ind$Yutm + 10
+FutureReserveCrowns[1,]$Xutm <- dat$Xutm + 30
+FutureReserveCrowns[1,]$Yutm <- dat$Yutm + 10
 
 # 1 on the left side
-FutureReserveCrowns[2,]$Xutm <- ind$Xutm - 30 
-FutureReserveCrowns[2,]$Yutm <- ind$Yutm + 10
+FutureReserveCrowns[2,]$Xutm <- dat$Xutm - 30 
+FutureReserveCrowns[2,]$Yutm <- dat$Yutm + 10
 
@@
 # The crown
-Crown <- ind %>%
+Crown <- dat %>%
   mutate(xCrown = Xutm,
@@
 # The trunk
-Trunk <- with(ind,
+Trunk <- with(dat,
               st_polygon(list(matrix(c(Xutm-(DBH/100)/2, Yutm,
@@
 
-  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], ind$TreeHeight),
+  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                     c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
@@
 
-  theta <- 360 - numeric(matlib::angle(c(Foot[1] - Foot[1], ind$TreeHeight),
+  theta <- 180 - numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                        c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
@@
 ## when the tree is on the trail (no angle)
-if(is.na(theta)) theta <- 0
-thetaIndNearest <- theta
-rm(theta)
+if(is.na(theta)) theta <- 0L
+theta <- theta
 ```
@@
 # if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
-if(any(FutureReserveCrowns$TreeHeight <= ind$TreeHeight)){
+if(any(FutureReserveCrowns$TreeHeight <= dat$TreeHeight)){
 
   FutResCrownsPoints <- FutureReserveCrowns %>% 
-    filter(TreeHeight <= ind$TreeHeight) %>% 
+    filter(TreeHeight <= dat$TreeHeight) %>% 
     mutate(Crowns = st_cast(Crowns, "MULTIPOINT")) %>% # polygon to multipoint
@@
 # if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
-if(any(FutureReserveCrowns$TreeHeight > ind$TreeHeight)){
+if(any(FutureReserveCrowns$TreeHeight > dat$TreeHeight)){
 
   FutResDBHPoints <- FutureReserveCrowns %>% 
-    filter(TreeHeight > ind$TreeHeight) %>% 
+    filter(TreeHeight > dat$TreeHeight) %>% 
     rowwise() %>% 
@@
 ```{r}
-FootBuffer <- ind %>% 
+FootBuffer <- dat %>% 
   mutate(Points = st_point(c(Xutm, Yutm)) %>% 
@@
 ```{r}
-
 # Only Foots 
@@
 # Distances between each of these points and Foot
-RotationAngle <- c() # empty list for rotation angles
+RotationAngle <- c() # empty vector for rotation angles
 for (FRP in 1:length(FutResAllPoints)) { # for each point
@@
   # If distances < TreeHeight of the tree to be felled
-  if(FutResDist < ind$TreeHeight){
-    # sum(FutResDists < ind$TreeHeight) # check av/res trees close to the tree to be felled
+  if(FutResDist < dat$TreeHeight){
+    # sum(FutResDists < dat$TreeHeight) # check av/res trees close to the tree to be felled
 
@@
         RotationAngle <- c(RotationAngle, as.numeric(matlib::angle(
-          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], ind$TreeHeight), # default position
+          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], dat$TreeHeight), # default position
           c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - FootBuffer[[P]][2]), # position to avoid
-          degree = TRUE)))
+          degree = TRUE)- 180))
 
@@
 
-        RotationAngle <- c(RotationAngle,  360 - as.numeric(matlib::angle(
-          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], ind$TreeHeight), # default position
+        RotationAngle <- c(RotationAngle, as.numeric(matlib::angle(
+          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], dat$TreeHeight), # default position
           c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - 
@@
     }
-  }
+  }else{AnglesToAvoid <- NULL}
 }
@@
 ## Then the angle to the trail: the angle to avoid
-OppAngToAvoid <- RotationAngle - 180 - thetaIndNearest # valeurs négatives c'est là le prblm
+OppAngToAvoid <- RotationAngle - theta
+
 TrailAnglesToAvoid <- 180-(90 + OppAngToAvoid)
@@
 TrailAnglesToAvoid[TrailAnglesToAvoid >= 360] <- TrailAnglesToAvoid[TrailAnglesToAvoid >= 360] - 360
+
 AnglesToAvoid <- TrailAnglesToAvoid[
@@
 # Drop the tree between [1; 179°] avoiding the angles of the futures/reserves
-if(ind$TreeFellingOrientationSuccess == "1"){
+if(dat$TreeFellingOrientationSuccess == "1"){
 
@@
 
-    Aangle <- round(as.numeric(180 + OppAng + thetaIndNearest), digits = 0) # Foot oriented
+    Aangle <- round(as.numeric(180 + OppAng + theta), digits = 0) # Foot oriented
 
@@
 
-    Aangle <- round(as.numeric(360 - OppAng + thetaIndNearest), digits = 0) # Foot oriented
+    Aangle <- round(as.numeric(360 - OppAng + theta), digits = 0) # Foot oriented
   }
@@
 }else{ # else random felling
-  RandomAngle <- as.numeric(sample(c(0:359.9), size = 1))
+  RandomAngle <- as.numeric(sample(c(0:359), size = 1))
 

### 2021-12-16 R/Intersections_FutRes.Rmd
Treefelling end!!

---
title: "Intersections_FutRes"
author: "Vincyane Badouard"
date: "16/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls()) ; invisible(gc())
library(Maria)
library(sf)
library(dplyr)
library(nngeo)
library(ggplot2)
# set.seed(420)
```

# Trails

```{r}
MainTrail <- sf::st_linestring(matrix(c(286400, 582945,
                                        286400, 583250,
                                        286700, 583250,
                                        286700, 582945,
                                        286400, 582945) # the return
                                      ,ncol=2, byrow=TRUE))
pol1 <- list(matrix(c(286503, 583134,
                      286503, 583240,
                      286507, 583240,
                      286507, 583134,
                      286503, 583134) # the return
                    ,ncol=2, byrow=TRUE))
pol2 <- list(matrix(c(286650, 583134,
                      286650, 583240,
                      286654, 583240,
                      286654, 583134,
                      286650, 583134) # the return
                    ,ncol=2, byrow=TRUE))

PolList = list(pol1,pol2) #list of lists of numeric matrices
ScndTrail <- sf::st_multipolygon(PolList)
Trail <- st_union(MainTrail, ScndTrail) # Our trail will be MainTrail or ScndTrail
rm(MainTrail, ScndTrail, pol1, pol2, PolList)
```

# Inventory
```{r}
inventory <- addtreedim(inventorycheckformat(Paracou6_2016),
                        volumeparameters = ForestZoneVolumeParametersTable)

inventory <- suppressMessages(treeselection(inventory, objective = 20, scenario ="manual",
                                            fuel = "2", diversification = TRUE, specieslax = FALSE,
                                            objectivelax = TRUE, topography = DTMParacou, 
                                            plotslope = PlotSlope,
                                            speciescriteria = SpeciesCriteria,
                                            advancedloggingparameters = loggingparameters())$inventory)
```

# Future Reserve

```{r}
FutureReserveCrowns <- inventory %>% # create an object with future/reserve crowns only
  dplyr::filter(LoggingStatus == "future" | LoggingStatus == "reserve") %>%
  createcanopy() %>% # create all inventory crowns in the 'Crowns' column
  getgeometry(Crowns)
```

# Individual
```{r}
ind <- inventory %>%
  dplyr::filter(Selected == "1") %>%
  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,
                CrownDiameter,Selected, Xutm, Yutm) %>% 
  sample_n(1) %>% 
  tibble::add_column(TreeFellingOrientationSuccess = "1")

```

# Individual geometry

```{r}
# The Foot 
Foot <- st_point(c(ind$Xutm,ind$Yutm))

# The crown
Crown <- ind %>%
  mutate(xCrown = Xutm,
         yCrown = Yutm + TrunkHeight + CrownHeight/2,
         exCrown = CrownDiameter/2,
         eyCrown = CrownHeight/2) %>%
  st_as_sf(coords = c("xCrown", "yCrown")) # ellipse centroid coordinates
Crown <- st_ellipse(Crown, Crown$exCrown, Crown$eyCrown) # create the ellipse

# The trunk
Trunk <- with(ind,
              st_polygon(list(matrix(c(Xutm-(DBH/100)/2, Yutm,
                                       Xutm-(DBH/100)/2, Yutm + TrunkHeight,
                                       Xutm+(DBH/100)/2, Yutm + TrunkHeight,
                                       Xutm+(DBH/100)/2, Yutm,
                                       Xutm-(DBH/100)/2, Yutm) # the return
                                     ,ncol=2, byrow=TRUE))))

# Find the point (TrailPt) on the Trail closest to the location of the tree (Foot)
NearestPoints <- st_nearest_points(Foot, Trail) # from the Foot of the tree to the Trail (linestring)

NearestPoint <- st_cast(NearestPoints, "POINT") # to have start (Foot) and end (TrailPt) points
TrailPt <- NearestPoint[[2]] # the point (TrailPt) on the Trail closest to the location of the tree (Foot)
rm(NearestPoint)
```

# Angles
```{r}
# Compute the angle between the tree default position and the shortest way from the foot to the trail
## Right-hand trail
if(TrailPt[1] >= Foot[1]){ # x trail > x foot
  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], ind$TreeHeight),
                                    c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
  ## Left-hand trail
}else if(TrailPt[1] < Foot[1]){ # x trail < x foot
  theta <- 180 - as.numeric(matlib::angle(c(Foot[1] - Foot[1], ind$TreeHeight),
                                          c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
}

## when the tree is on the trail (no angle)
if(is.na(theta)) theta <- 0
thetaIndNearest <- theta
rm(theta)

TreefallOrientation <- as.numeric(c(1:179))
OppAng <- 180-(90 + TreefallOrientation)

## Right-hand trail
if(TrailPt[1] >= Foot[1]){ # x trail > x foot
  Aangle <- round(as.numeric(180 + OppAng + thetaIndNearest), digits = 0) # Foot oriented
  ## Left-hand trail
}else if(TrailPt[1] < Foot[1]){ # x trail < x foot
  Aangle <- round(as.numeric(360 - OppAng + thetaIndNearest), digits = 0) # Foot oriented
}

```

# Felling function

```{r}
felling0angle <- function(theta){
  # Calculate the crown and trunk position
  FallenTree <- st_difference(st_union(
    rotatepolygon(Trunk, angle = theta, fixed = Foot), # turned trunk
    rotatepolygon(Crown, angle = theta, fixed = Foot) # turned crown
  ))
  return(FallenTree)
}  
```

# Available felling positions

```{r}
AvailableFellingPositions <- lapply(as.list(Aangle), felling0angle) %>% 
  lapply(function(x) data.frame(Tree = x)) %>% 
  bind_rows()
# rm(TreefallOrientation, OppAng, Aangle)
```

# Overlaps with future/reserve trees

```{r}
overlaps <- st_intersects(AvailableFellingPositions$geometry,
                          summarise(FutureReserveCrowns, Crowns = st_combine(Crowns))$Crowns) %>% 
  lengths()

# if there are any position without intersection
if(any(overlaps == 0)){
EmptyFellingPositions <- AvailableFellingPositions %>% 
  mutate(overlaps = overlaps) %>% 
  filter(overlaps == 0) # only positions without intesection

# if there are no position without intersection
}else{
  EmptyFellingPositions <- AvailableFellingPositions # take all the positions
}
# rm(overlaps)
```
## In intersections case
```{r}
intersections <- st_intersection(AvailableFellingPositions$geometry,
                          summarise(FutureReserveCrowns, Crowns = st_combine(Crowns))$Crowns)

ggplot() +
  geom_sf(data = intersections)
```

```{r}
ggplot() +
  geom_sf(data = Trail) +
  geom_sf(data = AvailableFellingPositions$geometry, col = "grey") +
  geom_sf(data = EmptyFellingPositions$geometry, col = "blue") +
  geom_sf(data = Foot) +
  geom_sf(data = NearestPoints) +
  geom_sf(data = TrailPt) +
  geom_sf(data = Crown) +
  geom_sf(data = Trunk) +
  geom_sf(data = FutureReserveCrowns$Crowns, col = "green")
```

# Sample only one position

```{r}
FellingPosition <- sample_n(EmptyFellingPositions, 1)
```

```{r}
ggplot() +
  geom_sf(data = Trail) +
  geom_sf(data = AvailableFellingPositions$geometry, col = "grey") + # [1;180]
  geom_sf(data = EmptyFellingPositions$geometry, col = "blue") + # avoid av/res
  geom_sf(data = FellingPosition$geometry, col = "red") + # the final position
  geom_sf(data = Foot) +
  geom_sf(data = NearestPoints) +
  geom_sf(data = TrailPt) +
  geom_sf(data = Crown) +
  geom_sf(data = Trunk) +
  geom_sf(data = FutureReserveCrowns$Crowns, col = "green")
```

### 2021-12-16 R/intersection avres.Rmd
Treefelling end!!

---
title: "intersection av/res"
author: "Vincyane Badouard"
date: "15/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Check intersection between FallenTree and av/res trees
- compute av/res crowns
- compute FallenTrees for all permitted angles
- compute intesections
- remove FallenTree with intersection
- keep only 1 FallenTree

## compute av/res crowns
FutureReserveCrowns

## compute FallenTrees for all permitted angles
```{r}
# directionalfelling == "2", cable case inf fuel !=0
TreefallOrientation <- as.numeric(sample(c(advancedloggingparameters$MinTreefallOrientation: 
                                             advancedloggingparameters$MaxTreefallOrientation), size = 1)) 
# in the other cases
TreefallOrientation <- as.numeric(sample(c(1:179), size = 1))

OppAng <- 180-(90 + TreefallOrientation) # the angle between the closest position to the trail (90°) and the desired position (desired angle to the trail)
CrownOppAng <- 180-(90 + CrownTreefallOrientation) # for grapple case

## Right-hand trail
if(TrailPt[1] >= Foot[1]){ # x trail > x foot
  # Foot oriented
  Aangle <- round(as.numeric(180 + OppAng + theta), digits = 0)
  Bangle <- round(as.numeric(180 - OppAng + theta), digits = 0)
  # Crown oriented
  CrownAangle <- as.numeric(theta + CrownOppAng) # ]0;180[ to the trail

  ## Left-hand trail
}else if(TrailPt[1] < Foot[1]){ # x trail < x foot
  # Foot oriented
  Aangle <- round(as.numeric(360 - OppAng + theta), digits = 0)
  Bangle <- round(as.numeric(theta + OppAng), digits = 0)
  # Crown oriented
  CrownAangle <- as.numeric(180 + CrownOppAng + theta) # ]0;180[ to the trail
}

Angles

FallenTree <- st_difference(st_union(
  rotatepolygon(Trunk, angle = Angles, fixed = Foot), # turned trunk
  ACrown # turned crown
))
```

## compute intesections
```{r}
FRintersect <- sf::st_intersects(FallenTree, FutureReserveCrowns)
```

## remove FallenTree with intersection
## keep only 1 FallenTree

### 2021-12-16 R/ONFGuyafortaxojoin.R

@@ -62,7 +62,7 @@ ONFGuyafortaxojoin <- function(
   VernName.species <- VolumeCumSum <- Xutm <- Yutm <- aCoef <- NULL
   alpha <- alpha.family <- alpha.genus <- alpha.species <- bCoef <- NULL
   beta.family <- beta.genus <- beta.species <- geometry <- idTree <- NULL
-  Aggregative.species <- Aggregative.genus <- NULL
+  Aggregative <- Aggregative.species <- Aggregative.genus <- NULL
 
 
   # Function

### 2021-12-16 R/treefelling.R

@@ -63,31 +63,31 @@
 #'
 #'@export
 #'
-#'@importFrom dplyr group_by do left_join mutate select
+#'@importFrom dplyr filter group_by do left_join mutate select
 #'@importFrom tibble add_column
 #'@importFrom sf st_as_sf st_as_text st_geometry st_intersection st_make_valid
 #'@importFrom tidyr unnest
 #'
 #' @examples
 #' \dontrun{
-#' MainTrail <- sf::st_linestring(matrix(c(286400, 583130,
+#' MainTrail <- sf::st_linestring(matrix(c(286400, 582925,
 #'                                         286400, 583250,
-#'                                         286655, 583250,
-#'                                         286655, 583130,
-#'                                         286400, 583130) # the return
+#'                                         286700, 583250,
+#'                                         286700, 582925,
+#'                                         286400, 582925) # the return
 #'                                      ,ncol=2, byrow=TRUE))
 #'
-#' pol1 <- list(matrix(c(286503, 583134,
+#' pol1 <- list(matrix(c(286503, 582925,
 #'                       286503, 583240,
 #'                       286507, 583240,
-#'                       286507, 583134,
-#'                       286503, 583134) # the return
+#'                       286507, 582925,
+#'                       286503, 582925) # the return
 #'                    ,ncol=2, byrow=TRUE))
-#' pol2 <- list(matrix(c(286650, 583134,
+#' pol2 <- list(matrix(c(286650, 582925,
 #'                       286650, 583240,
 #'                       286654, 583240,
-#'                       286654, 583134,
-#'                       286650, 583134) # the return
+#'                       286654, 582925,
+#'                       286650, 582925) # the return
 #'                    ,ncol=2, byrow=TRUE))
 #'
 #' PolList = list(pol1,pol2) #list of lists of numeric matrices
@@ -96,14 +96,14 @@
 #' inventory <- addtreedim(inventorycheckformat(Paracou6_2016),
 #' volumeparameters = ForestZoneVolumeParametersTable)
 #'
[…]

### 2021-12-20 R/AdjTopoLCP.R
repo change

@@ -1,0 +1,68 @@
+#' Assymetric adjacent matrix T*topographic least cost paths and distances
+#'
+#' Calculates topographic least cost distances and paths with an assymetric adjacent matrix
+#'
+#' @param DTM A RasterLayer for digital terrain model (DTM) data.
+#' @param costSurface A RasterLayer for the conductance (inverse of resistance) values for each cell.
+#' @param slopeRdCond A categorical transition layer of longitudinal and transversal slope.
+#' @param pts A SpatialPointsDataFrame object or two-column matrix with xy coordinates for the geographic points from which to calculate pairwise distances and paths.
+#' @param directions numeric (default = 8). The number of directions for movement between cells, either 4 or 8.
+#' @param paths logical. Default is FALSE, in which case only topographic distances are calculated.  If TRUE, topographic paths are also identified.
+#' @param zweight numeric (default = 1). The weight to be applied to the elevation (z) distances relative to the horizontal (xy) distances.
+#' @param advancedloggingparameters Other parameters of the logging simulator
+#'
+#'
+#' @return Matrix of topographic distances (if paths = FALSE), or a list containing a matrix of topographic distances and the topographic paths as an object of class SpatialLines (if paths = TRUE).
+#' @details
+#' The values of the raster for costSurface should be conductance values rather than resistance values.
+#' These can be calculating by taking the inverse of resistance values.
+#'
+#'
+#'
+#' @importFrom gdistance costDistance transition geoCorrection shortestPath
+#' @importFrom sp SpatialPoints
+#' @importFrom raster adjacent
+#' @importFrom utils combn
+#'
+#' @export
+AdjTopoLCP <- function(DTM,
+                       costSurface,
+                       slopeRdCond,
+                       pts,
+                       directions = 8,
+                       paths = TRUE,
+                       zweight = 1,
+                       advancedloggingparameters = loggingparameters()){
+
+  pts <- SpatialPoints(pts) # Set spatial points in sp format
+
[…]

### 2021-12-20 R/HarvestableAreaDefinition.R

@@ -1,21 +1,28 @@
 #' HarvestableAreaDefinition
 #'
-#' @param plot Studied plot (SpatialPolygonsDataFrame)
-#' @param dtm Digital terrain model (Large RasterLayer)
+
+#' @param topography Digital terrain model (Large RasterLayer)
 #' @param verticalcreekheight Relative elevation from nearest channel network
 #'   (Large RasterLayer)
 #' @param advancedloggingparameters Other parameters of the logging simulator
 #'   \code{\link{loggingparameters}} (list)
 #'
-#' @return A collection of polygons defined as 1 : harvestable area, 0 :
-#'   non-harvestable area
+
+#' @return A list with:
+#' - A collection of polygons defined as 1 : harvestable area, 0 :
+#'   non-harvestable area (sf polygon)
+#' - A raster with slope (in radians) characteristic of the studied plot
+#' (Large RasterLayer)
+#'
 #'
 #' @export
 #'
 #' @importFrom sf st_as_sf st_cast
 #' @importFrom raster mask terrain rasterFromXYZ rasterToPolygons
 #'   rasterToPoints
+
 #' @importFrom  dplyr as_tibble left_join rename mutate if_else
+#' @importFrom  magrittr %>%
 #'
 #' @examples
 #' data(Plots)
@@ -23,33 +30,29 @@
 #' data(VerticalCreekHeight)
 #'
 #'
-#' HarvestableArea <- HarvestableAreaDefinition(plot = Plots,
-#'                                              dtm = DTMParacou,
+
+#' HarvestableArea <- HarvestableAreaDefinition(topography = DTMParacou,
 #'                                              verticalcreekheight = VerticalCreekHeight,
 #'                                              advancedloggingparameters = loggingparameters())
-#' plot(HarvestableArea)
+#'
+#' plot(HarvestableArea[[1]])
 #'
 HarvestableAreaDefinition <- function(
-  plot,
-  dtm,
+  topography,
   verticalcreekheight,
-  advancedloggingparameters
+  advancedloggingparameters = loggingparameters()
 ){
+
+
 
   # Variables
   PlotSlope <- PlotSlopePoint <- CreekVHeightPlotPoint <- PlotTib <- NULL
-  SlpCrit <- PlotSlopeCreekVHeight <- RasterExploit <- PolygoneExploit <- NULL
[…]

### 2021-12-20 R/harvestable.R

@@ -9,6 +9,11 @@
 #'@param topography Digital terrain model (DTM) of the inventoried plot (LiDAR
 #'  or SRTM) (\code{\link{DTMParacou}}) (RasterLayer)
 #'
+#'@param harvestablepolygons Accessible area of the inventoried plot
+#'  (default: \code{\link{HarvestableAreaDefinition}}) (sf polygons data.frame)
+#'
+#'@param maintrails Main trails defined at the entire harvestable area (sf polylines)
+#'
 #'@param plotslope Slopes (in radians) of the inventoried plot (with a
 #'  neighbourhood of 8 cells) (default: \code{\link{PlotSlope}}) (RasterLayer)
 #'
@@ -54,7 +59,7 @@
 #'@importFrom dplyr filter mutate select left_join if_else
 #'@importFrom tibble as_tibble add_column
 #'@importFrom sp coordinates proj4string
-#'@importFrom sf st_as_sf st_distance
+#'@importFrom sf st_as_sf st_distance st_contains
 #'@importFrom raster crs extract
 #'@importFrom utils setTxtProgressBar txtProgressBar
 #'
@@ -65,6 +70,8 @@
 #' data(DTMParacou)
 #' data(PlotSlope)
 #' data(SpeciesCriteria)
+#' data(HarvestablePolygons)
+#' data(MainTrails)
 #'
 #' inventory <- addtreedim(inventorycheckformat(Paracou6_2016),
 #' volumeparameters = ForestZoneVolumeParametersTable)
@@ -72,6 +79,7 @@
 #' inventory <- ONFGuyafortaxojoin(inventory, SpeciesCriteria)
 #'
 #' harvestableOutputs <- harvestable(inventory, topography = DTMParacou,
+#' harvestablepolygons = HarvestablePolygons, maintrails = MainTrails,
 #' plotslope = PlotSlope, diversification = TRUE, specieslax = FALSE,
 #' advancedloggingparameters = loggingparameters())
 #'
@@ -80,6 +88,8 @@
 harvestable <- function(
   inventory,
   topography,
+  harvestablepolygons,
+  maintrails,
   plotslope,
   diversification,
   specieslax = FALSE,
@@ -113,7 +123,7 @@ harvestable <- function(
   UpMinFD.species <- VernName.genus <- VernName.genus.genus <- NULL
   VernName.species <- VolumeCumSum <- Xutm <- Yutm <- aCoef <- NULL
   alpha <- alpha.family <- alpha.genus <- alpha.species <- bCoef <- NULL
[…]

### 2021-12-20 tests/testthat/test-treefelling.R

@@ -4,6 +4,8 @@ test_that("treefelling", {
   data(Paracou6_2016)
   data(DTMParacou)
   data(PlotSlope)
+  data("MainTrails")
+  data("HarvestablePolygons")
 
   MatrixInventory <- as.matrix(Paracou6_2016)
 
@@ -37,7 +39,8 @@ test_that("treefelling", {
                                               objectivelax = TRUE, topography = DTMParacou,
                                               plotslope = PlotSlope,
                                               speciescriteria = SpeciesCriteria,
-                                              advancedloggingparameters = loggingparameters())$inventory)
+                                              advancedloggingparameters = loggingparameters(),
+                                              maintrails = MainTrails, harvestablepolygons = HarvestablePolygons)$inventory)
 
   testinventory <- treefelling(inventory, scenario = "manual", fuel = "2",
                                directionalfelling = "2", MainTrail = MainTrail, ScndTrail = ScndTrail,

### 2021-12-20 R/Faire tourner d'autres data.Rmd

---
title: "Faire tourner d'autres data"
author: "Vincyane Badouard"
date: "20/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(sf)
```

# Harvestable area (prospection units)
```{r}
ggplot() +
  geom_sf(data = HADP6[[1]],
          aes(alpha = Harvestable),
          fill = "olivedrab") +
  labs(alpha = "Harvestable") +
  labs(title = "P6 zones exploitables")

ggplot() +
  geom_sf(data = UPLisseesP6) +
  labs(title = "P6 UP lissées")

ggplot() +
  geom_sf(data = HADP16[[1]],
          aes(alpha = Harvestable),
          fill = "olivedrab") +
  labs(alpha = "Harvestable") +
  labs(title = "P16 zones exploitables")

ggplot() +
  geom_sf(data = UPLisseesP16) +
  labs(title = "P16 UP lissées")

```

# Tree selection
```{r}
ParacouP16_EFI3_BEcreux_designation <- treeselectionoutputsP16RIL3fuelhollow$inventory

write.csv2(ParacouP16_EFI3_BEcreux_designation, "D:/VSC Kourou/Dataexemple/ParacouP16_EFI3_BEcreux_designation.csv")
```

```{r}
# treeselectionoutputs <- treeselectionoutputsP6RIL2
# treeselectionoutputs <- treeselectionoutputsP6RIL2broken
# treeselectionoutputs <- treeselectionoutputsP6RIL3
# treeselectionoutputs <- treeselectionoutputsP6RIL3fuel
# treeselectionoutputs <- treeselectionoutputsP6RIL3fuelhollow
# 
# treeselectionoutputs <- treeselectionoutputsP16RIL2
# treeselectionoutputs <- treeselectionoutputsP16RIL2broken
# treeselectionoutputs <- treeselectionoutputsP16RIL3
# treeselectionoutputs <- treeselectionoutputsP16RIL3fuel
treeselectionoutputs <- treeselectionoutputsP16RIL3fuelhollow

NewInventory <- treeselectionoutputs$inventory

NonHarvestable <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "non-harvestable"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HADP6[[1]]))

Harvestable <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "harvestable"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HADP6[[1]]))

HarvestableUp <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HADP6[[1]]))

Selected <- sf::st_as_sf(
  dplyr::filter(NewInventory, Selected == "1"), coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HADP6[[1]]))

Reserve <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "reserve"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HADP6[[1]]))

Future <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "future"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HADP6[[1]]))

ProbedHollow <- sf::st_as_sf(
  dplyr::filter(NewInventory, ProbedHollow == "1"), coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HADP6[[1]]))

VisibleDefect <- sf::st_as_sf(
  dplyr::filter(NewInventory, VisibleDefect == "1"), coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HADP6[[1]]))

```

```{r}
# enregistré avec une hauteur = 1000 or 1500
ggplot() +
  geom_sf(data = UPLisseesP16) +
  geom_sf(data = NonHarvestable,
          aes(colour = "Non-harvestable"), show.legend = "point") +
  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  geom_sf(data = Future,
          aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  geom_sf(data = HarvestableUp,
          aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  geom_sf(data = ProbedHollow,
          aes(colour = "Probed hollow"), show.legend = "point") +

  scale_colour_manual(values = c("Non-harvestable" = "grey",
                                 "Visible defect" = "pink", "Harvestable" = "skyblue",
                                 "HarvestableUp" = "blue", "Selected" = "red", "Future" = "orange",
                                 "Reserve" = "purple", "Probed hollow" = "forestgreen")) +
  labs(color = "Logging status") +
  labs(title = "P16 désignation EFI3 + BE dont creux")
```

### 2021-12-20 docs/VerticalCreekHeight.Rmd

---
title: "VerticalCreekHeight"
author: "Gaquiere Thomas"
date: "17/12/2021"
output: html_document
---

```{r setup, include=FALSE}
library(Rsagacmd)
library(raster)
library(rgdal)
library(sf)
library(tidyverse)
```

# Prenons un MNT (1m de résolution si possible) ----

```{r}
DTM <- 
```

# Création de réseau Hydro ----
## lien R - Saga-gis (saga-gis doit être installé sur la machine) ----

```{r}
Saga <- Rsagacmd::saga_gis(verbose=TRUE)
```

## 1 - Fill sinks xxl (Wang & Liu) (on comble les trous) ----

```{r}
FilledSinks <- Saga$ta_preprocessor$fill_sinks_xxl_wang_liu(elev = DTM, 
                                                            minslope = .01)
```

## 2 - Flow accumulation (top-down) (la composante flow de TotalCatchmentArea nous servira de grille d'initiation pour le réseau Hydro) ----

```{r}
TotalCatchmentArea <- Saga$ta_hydrology$flow_accumulation_top_down(elevation = FilledSinks, 
                                                                   method = 'Multiple Flow Direction')
```

## 3 - Channel Network ----

```{r}
ChannelNetwork <- Saga$ta_channels$channel_network(elevation = FilledSinks,
                                                   init_grid = TotalCatchmentArea$flow,
                                                   init_method = "Greater than",
                                                   init_value = 2250) # on colle à ce que fait l'ONF sauf qu'ici notre DEM a une résolution de 1m

```

On a maintenant un réseau hydro à partir du DEM de Paracou, je fabrique mon raster de distance verticale à la crique 
(indispensable pour le modèle HAND dans la fonction de definition d'UP) à la suite,
je pense qu'il est preferable que l'utilisateur rentre un DTM + un raster de distance verticale à la crique qui sera impérativement réalisé à partir de ce même DEM, sinon les x et y pourraient ne pas correspondre plus tard

# Distance Verticale à la crique ----

```{r}
DistancesCrique <- Saga$ta_channels$overland_flow_distance_to_channel_network(elevation = FilledSinks,
                                                                     channels = ChannelNetwork$chnlntwrk)
```

# Cet outil nous sort les distances verticale et horizontale à la crique de chacune des cellules de notre dtm

## Selection de la distance verticale à la crique ----

```{r}
CreekVerticalHeight <- DistancesCrique$distvert
```

```{r}
plot(CreekVerticalHeight,  breaks=c(0,2), col='red') # les jolis bas-fonds !
```

### 2021-12-21 R/FilterAccesExplArea.R
After Thomas pull request

@@ -1,15 +1,16 @@
-#' FilterAccesExplArea
+#' Filter access to harvestable zone
 #'
-#' @param harvestablepolygons Accessible area of the inventoried plot
-#'  (default: \code{\link{HarvestableAreaDefinition}}) (sf polygons data.frame)
+#' @param harvestablepolygons Accessible area of the inventoried plot (default:
+#'   \code{\link{HarvestableAreaDefinition}}) (sf polygons data.frame)
 #'
-#' @param maintrails Main trails defined at the entire harvestable area (sf polylines)
-#'
+#' @param MainTrails Main trails defined at the entire harvestable area (sf
+#'   polylines)
 #'
 #' @param advancedloggingparameters Other parameters of the logging simulator
-#' \code{\link{loggingparameters}} (list) MainTrail (multiline)
+#'   \code{\link{loggingparameters}} (list)
 #'
-#' @return Accessible area  of the inventoried plot according to selected logging scenario (sf polygons data.frame)
+#' @return Accessible area of the inventoried plot according to selected
+#'   logging scenario (sf polygons data.frame)
 #'
 #' @export
 #'
@@ -17,14 +18,21 @@
 #' @importFrom dplyr mutate filter
 #'
 #' @examples
+#' \dontrun{
+#' data(MainTrails)
+#' data(HarvestablePolygons)
 #'
-#'  AccessPolygones <-  FilterAccesExplArea (harvestablepolygons = HarvestablePolygons,
-#'  maintrails = MainTrails,
+#' AccessPolygones <- FilterAccesExplArea(
+#'  harvestablepolygons = HarvestablePolygons,
+#'  MainTrails = MainTrails,
 #'  advancedloggingparameters = loggingparameters())
+#'  }
 #'
-FilterAccesExplArea <- function (harvestablepolygons ,
-                                 maintrails ,
-                                 advancedloggingparameters = loggingparameters()) {
+FilterAccesExplArea <- function(
+  harvestablepolygons,
+  MainTrails,
+  advancedloggingparameters = loggingparameters()
+){
 
   # Global Variables
   Harvestable <- Access <- NULL
@@ -34,7 +42,7 @@ FilterAccesExplArea <- function (harvestablepolygons ,
 
   #function
 
-  maintrails <- maintrails %>%
+  MainTrails <- MainTrails %>%
[…]

### 2021-12-21 R/addtreedim.R

@@ -75,7 +75,7 @@ addtreedim <- function(
   TimberLoggedVolume <- LoggingStatus <- MaxFD <- MaxFD.genus <- NULL
   MaxFD.species <- MinFD <- MinFD.genus <- MinFD.species <- NULL
   NoHollowTimberLoggedVolume <- ParamCrownDiameterAllometry <- PlotSlope <- NULL
-  PlotTopo <- ProbedHollow <- ProbedHollowProba <- ScientificName <- NULL
+  ProbedHollow <- ProbedHollowProba <- ScientificName <- NULL
   Selected <- Slope <- SlopeCrit <- Species <- Species.genus <- NULL
   SpeciesCriteria <- Taxo <- Taxo.family <- Taxo.genus <- Taxo.species <- NULL
   TreeFellingOrientationSuccess <- TreeHarvestableVolume <- NULL

### 2021-12-21 tests/testthat/test-harvestable.R

@@ -25,13 +25,13 @@ test_that("harvestable", {
 
   Outputs1 <- harvestable(inventory,
                           diversification = T, specieslax = F, topography = DTMParacou, plotslope = PlotSlope,
-                          maintrails = MainTrails, harvestablepolygons = HarvestablePolygons)
+                          MainTrails = MainTrails, harvestablepolygons = HarvestablePolygons)
   Outputs2 <- harvestable(inventory,
                           diversification = F, specieslax = T, topography = DTMParacou, plotslope = PlotSlope,
-                          maintrails = MainTrails, harvestablepolygons = HarvestablePolygons)
+                          MainTrails = MainTrails, harvestablepolygons = HarvestablePolygons)
   Outputs3 <- harvestable(inventory,
                           diversification = F, specieslax = F, topography = DTMParacou, plotslope = PlotSlope,
-                          maintrails = MainTrails, harvestablepolygons = HarvestablePolygons)
+                          MainTrails = MainTrails, harvestablepolygons = HarvestablePolygons)
 
   testinventory1 <- Outputs1$inventory
   testinventory2 <- Outputs2$inventory
@@ -139,6 +139,6 @@ test_that("harvestable", {
 #   Distribution spatiale:
 #     - Arbres sur <22% de pente et arbres sur pente >22% si à 40 m maximum d’une zone <22%.
 #   - arbre non isolé : élimination des arbres à >100m des autres individus de la même espèce.
-#   - hors des pistes principales : dont les coordonnées n'appartiennent pas aux multilignes "MainTrail".
+#   - hors des pistes principales : dont les coordonnées n'appartiennent pas aux multilignes "MainTrails".
 # + Si diversification=F & specieslax=T, étiqueter "harvestable2nd" à la place d’"harvestable", les "Commercial"= "2" dans la colonne "LoggingStatus".
 # + HVinit= somme des valeurs de "TreeHarvestableVolume " des arbres dont "LoggingStatus" = "harvestable".

### 2021-12-21 tests/testthat/test-selected.R

@@ -19,7 +19,7 @@ test_that("selected", {
   harvestableOutputs <- harvestable(inventory0, diversification = TRUE, specieslax = FALSE,
                                     topography = DTMParacou, plotslope = PlotSlope,
                                     advancedloggingparameters = loggingparameters(),
-                                    maintrails = MainTrails, harvestablepolygons = HarvestablePolygons)
+                                    MainTrails = MainTrails, harvestablepolygons = HarvestablePolygons)
 
   inventory <- harvestableOutputs$inventory
   HVinit <- harvestableOutputs$HVinit
@@ -87,7 +87,7 @@ test_that("selected", {
   ## if (!diversification && specieslax)
   harvestableOutputs <- harvestable(inventory0,
                                     diversification = FALSE, specieslax = TRUE, topography = DTMParacou,
-                                    plotslope = PlotSlope, maintrails = MainTrails, harvestablepolygons = HarvestablePolygons)
+                                    plotslope = PlotSlope, MainTrails = MainTrails, harvestablepolygons = HarvestablePolygons)
   inventory <- harvestableOutputs$inventory
   HVinit <- harvestableOutputs$HVinit
 
@@ -112,7 +112,7 @@ test_that("selected", {
   # if (!diversification && !specieslax && objectivelax)
   harvestableOutputs <- harvestable(inventory0,
                                     diversification = FALSE,  specieslax = FALSE,
-                                    topography = DTMParacou, plotslope = PlotSlope, maintrails = MainTrails,
+                                    topography = DTMParacou, plotslope = PlotSlope, MainTrails = MainTrails,
                                     harvestablepolygons = HarvestablePolygons)
   inventory <- harvestableOutputs$inventory
   HVinit <- harvestableOutputs$HVinit
@@ -129,7 +129,7 @@ test_that("selected", {
   # if (diversification && objectivelax)
   harvestableOutputs <- harvestable(inventory0,
                                     diversification = TRUE, topography = DTMParacou, plotslope = PlotSlope,
-                                    maintrails = MainTrails,
+                                    MainTrails = MainTrails,
                                     harvestablepolygons = HarvestablePolygons)
   inventory <- harvestableOutputs$inventory
   HVinit <- harvestableOutputs$HVinit
@@ -156,7 +156,7 @@ test_that("selected", {
 
   harvestableOutputs <- harvestable(inventory0,
                                     diversification = TRUE, topography = DTMParacou, plotslope = PlotSlope,
[…]

### 2021-12-21 tests/testthat/test-timberharvestedvolume.R

@@ -13,7 +13,7 @@ test_that("timberharvestedvolume", {
                                               objectivelax = TRUE, topography = DTMParacou, plotslope = PlotSlope,
                                               speciescriteria = SpeciesCriteria,
                                               advancedloggingparameters = loggingparameters(),
-                                              maintrails = MainTrails, harvestablepolygons = HarvestablePolygons)$inventory)
+                                              MainTrails = MainTrails, harvestablepolygons = HarvestablePolygons)$inventory)
 
 
 

### 2021-12-29 R/Remove trees out of the plot.Rmd

---
title: "Remove trees out of the plot"
author: "Vincyane Badouard"
date: "28/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r}
library(Maria)
library(ggplot2)
library(sf)
library(dplyr)
library(tibble)
```

# Necessary data
```{r}
data(Paracou6_2016)
data(PlotMask) # SpatialPolygonsDataFrame (sp)

PlotMask <- st_as_sf(PlotMask) # sp to sf (sfc_POLYGON)

ggplot() +
  geom_sf(data = PlotMask, col = "red")
# PlotMask is only the boundaries of the plot
```

# Remove trees out of the plot

```{r}
inventory <- st_as_sf(Paracou6_2016, coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(PlotMask)) # set crs

TreesIn <- suppressWarnings(st_intersection(inventory, PlotMask)) %>% 
  add_column(TreesIn = "1") %>%
  select(idTree, TreesIn)

st_geometry(TreesIn) <- NULL # sf to data.frame
TreesIn <- unique(TreesIn)

inventory <- inventory %>%
  left_join(TreesIn, by = "idTree") %>% 
   mutate(TreesIn = ifelse(is.na(TreesIn),
                               "0", TreesIn))
  # select(-TreesIn)

class(inventory)
```

# Plot in & out trees
```{r}
In <- sf::st_as_sf(
  filter(inventory, TreesIn == "1"), coords = c("Xutm", "Yutm"))

Out <- sf::st_as_sf(
  filter(inventory, TreesIn == "0"), coords = c("Xutm", "Yutm"))

ggplot() +
  geom_sf(data = In, col = "green") +
  geom_sf(data = Out, col = "red")
```

### 2021-12-29 tests/testthat/test-loggingsimulation1.R
Parallelization and iterations summary function #48

@@ -121,5 +121,6 @@ test_that("loggingsimulation1", {
                                  advancedloggingparameters = FALSE),
                regexp = "The 'advancedloggingparameters' argument of the 'loggingsimulation' function must be a list")
 
+  # expect_true(class(Rslt) == "list")
 
 })

### 2021-12-30 R/Iterations summary.Rmd

---
title: "Iterations summary"
author: "Vincyane Badouard"
date: "29/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# save(Rslt, file = "../data/Rslt.Rdata")
load("../data/Rslt.Rdata")
```

Les stats qu'on veut faire : mean, sd, quantile

Sur les variables : c(HarvestableArea, VO, HVinit, TimberLoggedVolume, NoHollowTimberLoggedVolume, FuelVolume,
DamageVolume, LostBiomass)

# With 1 var
```{r}
HarvestableArea_mean <- mean(c(Rslt[[1]]$HarvestableArea, Rslt[[2]]$HarvestableArea))
HarvestableArea_sd <- sd(c(Rslt[[1]]$HarvestableArea, Rslt[[2]]$HarvestableArea))
HarvestableArea_quantile <- quantile(c(Rslt[[1]]$HarvestableArea, Rslt[[2]]$HarvestableArea))

```

# pour toutes les vars pour n iter
```{r}
var <- c("HarvestableArea", "VO", "HVinit", "TimberLoggedVolume", "NoHollowTimberLoggedVolume", "FuelVolume",
         "DamageVolume", "LostBiomass")

quantile(c(as.numeric(Rslt[[1]]["LostBiomass"]) : as.numeric(Rslt[[2]]["LostBiomass"])), probs = c(0.25, 0.75))

statsvars <- function(v, iter){

  itervalues <- c(as.numeric(Rslt[[1]][v]) : as.numeric(Rslt[[length(Rslt)]][v]))

  Mean <- round(mean(itervalues), digits = 1)
  Sd <- round(sd(itervalues), digits = 1)
  Q1 <- round(quantile(itervalues, probs = 0.25, digits = 1))
  Median <- round(median(itervalues), digits = 1)
  Q3 <- round(quantile(itervalues, probs = 0.75, digits = 1))
  Min <- round(min(itervalues), digits = 1)
  Max <- round(max(itervalues), digits = 1)

  output <- list(Mean = Mean, Sd = Sd, Min = Min, Q1 = Q1, Median = Median, Q3 = Q3, Max = Max)

  return(output)
}

RsltStats <- lapply(var, statsvars, 2)

unlist(RsltStats[8]) # numeric named vector

```

### 2021-12-30 R/Parallelization try.Rmd

---
title: "Parallelization try"
author: "Vincyane Badouard"
date: "29/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# libraries
```{r}
library(Maria)
library(parallel)
```

# data
```{r}
data(Paracou6_2016)
inventory <- Paracou6_2016
iter = 2
cores = 2
```

# Toy function
```{r}
rep <- function(iter, size) {replicate(iter, sample(1:4, size = size), simplify = F)}
rep(2, 2)
```

# lapply
```{r}
lapply(seq_len(3), rep, 2)
lapply(seq_len(3), function(x) sample(1:4))
lapply(seq_len(3), function(x) inventorycheckformat(inventory))

```

```{r}
cl <- makePSOCKcluster(getOption("cl.cores", cores)) # create a cluster

clusterExport(cl = cl, varlist = "inventory", envir = environment()) # cluster environment

parLapply(cl, seq_len(iter), function(x) sample(1:4))
parLapply(cl, seq_len(iter), function(x) Maria::inventorycheckformat(inventory))

stopCluster(cl) # stop the cluster
```

### 2021-12-30 R/Secontrails plots.Rmd
ScdTrails

---
title: "Secontrails plots"
author: "Vincyane Badouard"
date: "30/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r}
library(Maria)
library(ggplot2)
library(sf)
library(dplyr)
library(tibble)
```

# Data
```{r}
# save(secondtrails, file = "../data/secondtrails.Rdata")
data("HarvestablePolygons")
data("MainTrails")
```

# Outputs
```{r}
secondtrails$TrailsDensity

secondtrails[[1]] # 'paths'
class(secondtrails[[1]]) # SpatialLines (sp)

secondtrails[[2]] # 'lines' Sert à quoi ??
class(secondtrails[[2]]) # matrix

plot(secondtrails[[3]]) # SmoothedSecondTrails
class(secondtrails[[3]]) # sfc_MULTIPOLYGON

secondtrails[[4]] # TrailsDensity
class(secondtrails[[4]]) # "units" ??? A mettre en numeric !

new_inventory <- secondtrails[[5]] # inventory
class(secondtrails[[5]]) # data.frame

secondtrails[[6]] # CostRasterMean. Sert à quoi ??
class(secondtrails[[6]]) # RasterLayer

```

# Plots
```{r}
ggplot() +
  # Harvestable zones
  geom_sf(data = HarvestablePolygons,
          aes(alpha = Harvestable),
          fill = "olivedrab") +
  labs(alpha = "Harvestable") +
  labs(title = "P6 zones exploitables") +

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails[[3]]), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails[[1]]), col = "red")

```

# With tree selection
```{r}
NewInventory <- treeselectionoutputs$inventory # scenario = "RIL3", objectivelax = TRUE

NonHarvestable <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "non-harvestable"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HarvestablePolygons))

Harvestable <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "harvestable"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HarvestablePolygons))

HarvestableUp <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HarvestablePolygons))

Selected <- sf::st_as_sf(
  dplyr::filter(NewInventory, Selected == "1"), coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HarvestablePolygons))

Reserve <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "reserve"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HarvestablePolygons))

Future <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "future"),
  coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HarvestablePolygons))

ProbedHollow <- sf::st_as_sf(
  dplyr::filter(NewInventory, ProbedHollow == "1"), coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HarvestablePolygons))

VisibleDefect <- sf::st_as_sf(
  dplyr::filter(NewInventory, VisibleDefect == "1"), coords = c("Xutm", "Yutm")) %>% 
  st_set_crs(st_crs(HarvestablePolygons))
```

# Plot with tree selection
```{r}
ggplot() +
  # Harvestable zones
  geom_sf(data = HarvestablePolygons,
          aes(alpha = Harvestable),
          fill = "olivedrab") +
  labs(alpha = "Harvestable") +
  labs(title = "P6 zones exploitables") +

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails[[3]]), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails[[1]]), col = "red") +

  # Tree selection
  # geom_sf(data = NonHarvestable,
  #         aes(colour = "Non-harvestable"), show.legend = "point") +
  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  geom_sf(data = Future,
          aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  # geom_sf(data = HarvestableUp,
  #         aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  geom_sf(data = ProbedHollow,
          aes(colour = "Probed hollow"), show.legend = "point") +
  geom_sf(data = MainTrails) +

  scale_colour_manual(values = c("Non-harvestable" = "grey",
                                 "Visible defect" = "pink", "Harvestable" = "skyblue",
                                 "HarvestableUp" = "blue", "Selected" = "red", "Future" = "orange",
                                 "Reserve" = "purple", "Probed hollow" = "forestgreen")) +
  labs(color = "Logging status") +
  labs(title = "P16 EFI3")
```

# Plot with treefelling
```{r}
NewInventory <- treefelling(new_inventory, scenario = "RIL3", fuel = "0",
                            winching = NULL, directionalfelling = NULL,
                            MainTrails = MainTrails, ScndTrail = st_as_sf(secondtrails[[3]]) ,
                            advancedloggingparameters = loggingparameters())

NewInventory_crs <- NewInventory %>%
  getgeometry(TreePolygon) %>%
  sf::st_set_crs(sf::st_crs(MainTrails)) # set a crs
```

```{r}
ggplot() +
  # Harvestable zones
  geom_sf(data = HarvestablePolygons,
          aes(alpha = Harvestable),
          fill = "olivedrab") +
  labs(alpha = "Harvestable") +
  labs(title = "P6 zones exploitables") +

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails[[3]]), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails[[1]]), col = "red") +

  # Tree selection
  # geom_sf(data = NonHarvestable,
  #         aes(colour = "Non-harvestable"), show.legend = "point") +
  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  geom_sf(data = Future,
          aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  # geom_sf(data = HarvestableUp,
  #         aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = NewInventory_crs, # cuted trees
          alpha = 0.5, fill = "red") +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  geom_sf(data = ProbedHollow,
          aes(colour = "Probed hollow"), show.legend = "point") +
  geom_sf(data = MainTrails) +

  scale_colour_manual(values = c("Non-harvestable" = "grey",
                                 "Visible defect" = "pink", "Harvestable" = "skyblue",
                                 "HarvestableUp" = "blue", "Selected" = "red", "Future" = "orange",
                                 "Reserve" = "purple", "Probed hollow" = "forestgreen")) +
  labs(color = "Logging status") +
  labs(title = "P16 EFI3")
```

### 2021-12-30 R/HarvestableAreaDefinition.R

@@ -38,7 +38,16 @@
 #'   advancedloggingparameters = loggingparameters()
 #'   )
 #'
-#' plot(HarvestableAreaOutputs[[1]])
+#' library(ggplot2)
+#' library(sf)
+#' ggplot() +
+#' geom_sf(data = HarvestableAreaOutputs[[1]],
+#'         aes(alpha = Harvestable),
+#'         fill = "olivedrab") +
+#'   labs(alpha = "Harvestable") +
+#'   labs(title = "P6  Harvestable zones")
+#'
+#' HarvestableAreaOutputs[[2]]
 #' }
 #'
 HarvestableAreaDefinition <- function(

### 2021-12-30 R/SecondTrailsOpening.R

@@ -21,7 +21,12 @@
 #' @param CostMatrix List of list defining conditional weight over binned slopes
 #'   values
 #'
-#' @param scenarios The chosen scenario from scenariosparameters function
+#'@param scenario Logging scenario: "RIL1", "RIL2broken", "RIL2", "RIL3",
+#'  "RIL3fuel", "RIL3fuelhollow" or "manual"(character) (see the
+#'  \code{\link{vignette}})
+#'
+#'@param winching No cable or grapple = "0", only cable = "1", grapple + cable =
+#'  "2"
 #'
 #' @param fact Aggregation factor of cost raster resolution to initial DTM
 #'
@@ -31,10 +36,10 @@
 #' @return A list with :
 #' - raw second trails
 #' -
-#' - Smoothed secondary trails polygons
-#' - Second trails density (in m.ha^-1)
-#' - Updated inventory
-#' - A cost Raster (RasterLayer)
+#' - SmoothedSecondTrails: Smoothed secondary trails polygons (sfc_MULTIPOLYGON)
+#' - TrailsDensity: Second trails density (in m/ha)
+#' - inventory: Updated inventory
+#' - CostRasterMean: A cost Raster (RasterLayer)
 #'
 #' @importFrom sf st_cast st_as_sf st_intersection st_union st_sample st_join
 #'   st_buffer as_Spatial st_centroid st_set_precision st_make_valid st_set_agr
@@ -61,8 +66,6 @@
 #' data("SpeciesCriteria")
 #' data(VerticalCreekHeight)
 #'
-#' scenarios <- scenariosparameters(scenario = "RIL3")
-#'
 #' inventory <- ONFGuyafortaxojoin(addtreedim(cleaninventory(Paracou6_2016, PlotMask),
 #'  volumeparameters = ForestZoneVolumeParametersTable),SpeciesCriteria)
 #'
@@ -70,7 +73,7 @@
 #' treeselectionoutputs <- treeselection(inventory,
 #' topography = DTMParacou, plotslope = PlotSlope, MainTrails = MainTrails,
 #' harvestablepolygons = HarvestablePolygons,
-#' speciescriteria = SpeciesCriteria, objective = scenarios$objective,
+#' speciescriteria = SpeciesCriteria,
 #' scenario = "RIL3",
 #' objectivelax = TRUE,
 #' advancedloggingparameters = loggingparameters())
@@ -87,17 +90,31 @@
 #'                          list(Slope = 27, Cost = 600),
[…]

### 2021-12-31 R/DraftFunctions.Rmd
Parallelization and iterations summary function #48
Renaming

@@
 
+# LoggingSimulationOutputs <- Rslt
+# usethis::use_data(LoggingSimulationOutputs)
+
 ```
@@
   separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T) %>% 
-  mutate(Aggregative = ifelse(VernName == "Angélique" | VernName == "Gonfolo rose",
+  mutate(Aggregative = ifelse(CommercialName == "Angélique" | CommercialName == "Gonfolo rose",
                               TRUE, FALSE))
@@
 
-SpeciesCriteria$VernName <- tolower(SpeciesCriteria$VernName)
+SpeciesCriteria$CommercialName <- tolower(SpeciesCriteria$CommercialName)
 

### 2021-12-31 R/SecondTrailsOpening.R

@@ -6,7 +6,7 @@
 #' @param plotmask Inventoried plot mask (SpatialPolygonsDataFrame)
 #'
 #' @param treeselectionoutputs A list with:
-#' - your inventory with: "DistCrit", "Slope", "SlopeCrit", "LoggingStatus",
+#' - your inventory with: "DistCriteria", "Slope", "SlopeCriteria", "LoggingStatus",
 #' "Selected", "Up", "VolumeCumSum", "ProbedHollowProba", "ProbedHollow"
 #' new columns (see the outputs metadata in the \code{\link{vignette}}).
 #'
@@ -25,8 +25,14 @@
 #'  "RIL3fuel", "RIL3fuelhollow" or "manual"(character) (see the
 #'  \code{\link{vignette}})
 #'
-#'@param winching No cable or grapple = "0", only cable = "1", grapple + cable =
-#'  "2"
+#'@param winching
+#' "0": no cable or grapple (trail to tree foot)
+#' "1": only cable (default = 40m)
+#' "2": grapple (default = 6m) + cable (grapple priority)
+#' If grapple + cable (winching = "2") without fuel wood (fuel = "0")
+#'  recovery of the tree foot with grapple if possible (respected grapple
+#'  conditions) otherwise with cable with angle to the trail.
+#'  Avoidance of future/reserves if chosen.
 #'
 #' @param fact Aggregation factor of cost raster resolution to initial DTM
 #'
@@ -66,7 +72,7 @@
 #' data("SpeciesCriteria")
 #' data(VerticalCreekHeight)
 #'
-#' inventory <- ONFGuyafortaxojoin(addtreedim(cleaninventory(Paracou6_2016, PlotMask),
+#' inventory <- commercialcriteriajoin(addtreedim(cleaninventory(Paracou6_2016, PlotMask),
 #'  volumeparameters = ForestZoneVolumeParametersTable),SpeciesCriteria)
 #'
 #'
@@ -90,7 +96,7 @@
 #'                          list(Slope = 27, Cost = 600),
 #'                          list(Slope = Inf, Cost = 1000)),
 #'                     list(list(CostType = "Initial", CostValue = 1000),
-#'                          list(CostType = "Access", CostValue = 1E5),
+#'                          list(CostType = "Access", CostValue = 1000), # 1E5
 #'                          list(CostType = "BigTrees", CostValue = 500),
 #'                          list(CostType = "Reserves", CostValue = 500),
 #'                          list(CostType = "Futures", CostValue = 50),
[…]

### 2021-12-31 tests/testthat/test-futurereserve.R

@@ -6,7 +6,7 @@ test_that("futurereserve", {
   data(MainTrails)
 
   inventory <- addtreedim(cleaninventory(Paracou6_2016, PlotMask), volumeparameters = ForestZoneVolumeParametersTable)
-  inventory <- ONFGuyafortaxojoin(inventory, SpeciesCriteria)
+  inventory <- commercialcriteriajoin(inventory, SpeciesCriteria)
 
   harvestableOutputs <- harvestable(inventory, diversification = TRUE, specieslax = FALSE,
                                     topography = DTMParacou, plotslope = PlotSlope,
@@ -26,12 +26,12 @@ test_that("futurereserve", {
 
   advancedloggingparameters = loggingparameters()
 
-  # Future = Commercial == "1"
+  # Future = CommercialLevel == "1"
   FutureTrees <- testinventory %>%
     filter(LoggingStatus == "future")
 
 
-  expect_true(all(FutureTrees$Commercial == "1"
+  expect_true(all(FutureTrees$CommercialLevel == "1"
                   & (
                     (FutureTrees$Up == "0" &
                        (FutureTrees$DBH >= advancedloggingparameters$FutureTreesMinDiameter & FutureTrees$DBH < FutureTrees$MinFD))
@@ -42,7 +42,7 @@ test_that("futurereserve", {
   ReserveTrees <- testinventory %>%
     filter(LoggingStatus =="reserve")
 
-  expect_true(all(ReserveTrees$Commercial == "1"
+  expect_true(all(ReserveTrees$CommercialLevel == "1"
                   & (
                     (ReserveTrees$Up == "0" &
                        (ReserveTrees$DBH >= advancedloggingparameters$FutureTreesMinDiameter & ReserveTrees$DBH < ReserveTrees$MinFD))

### 2022-01-13 R/Secontrails plots.Rmd
Debug scdtrailopening done

@@
 
-secondtrails[[1]] # 'paths'
-class(secondtrails[[1]]) # SpatialLines (sp)
+secondtrails$paths # 'paths'
+class(secondtrails$paths) # SpatialLines (sp)
 
-secondtrails[[2]] # 'lines' Sert à quoi ??
-class(secondtrails[[2]]) # matrix
+secondtrails$lines # 'lines' Sert à quoi ??
+class(secondtrails$lines) # matrix
 
-plot(secondtrails[[3]]) # SmoothedSecondTrails
-class(secondtrails[[3]]) # sfc_MULTIPOLYGON
+plot(secondtrails$SmoothedSecondTrails) # SmoothedSecondTrails
+class(secondtrails$SmoothedSecondTrails) # sfc_MULTIPOLYGON
 
-secondtrails[[4]] # TrailsDensity
-class(secondtrails[[4]]) # "units" ??? A mettre en numeric !
+secondtrails$TrailsDensity # TrailsDensity
+class(secondtrails$TrailsDensity) # "units" ??? A mettre en numeric !
 
-new_inventory <- secondtrails[[5]] # inventory
-class(secondtrails[[5]]) # data.frame
+new_inventory <- secondtrails$inventory # inventory
+class(secondtrails$inventory ) # data.frame
 
-secondtrails[[6]] # CostRasterMean. Sert à quoi ??
-class(secondtrails[[6]]) # RasterLayer
+secondtrails$CostRasterAgg  # CostRasterMean. Sert à quoi ??
+class(secondtrails$CostRasterAgg) # RasterLayer
 
@@
   # 2ndary trails
-  geom_sf(data = st_as_sf(secondtrails[[3]]), col = "darkgreen") +
-  geom_sf(data = st_as_sf(secondtrails[[1]]), col = "red")
+  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
+  geom_sf(data = st_as_sf(secondtrails$paths), col = "red")
 
@@
 
-HarvestableUp <- sf::st_as_sf(
-  dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
-  coords = c("Xutm", "Yutm")) %>% 
-  st_set_crs(st_crs(HarvestablePolygons))
+# HarvestableUp <- sf::st_as_sf(
+#   dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
+#   coords = c("Xutm", "Yutm")) %>% 
+#   st_set_crs(st_crs(HarvestablePolygons))
 
@@
 
-Future <- sf::st_as_sf(
-  dplyr::filter(NewInventory, LoggingStatus == "future"),
-  coords = c("Xutm", "Yutm")) %>% 
-  st_set_crs(st_crs(HarvestablePolygons))
+# Future <- sf::st_as_sf(
+#   dplyr::filter(NewInventory, LoggingStatus == "future"),
+#   coords = c("Xutm", "Yutm")) %>% 
+#   st_set_crs(st_crs(HarvestablePolygons))
 
@@
   # 2ndary trails
-  geom_sf(data = st_as_sf(secondtrails[[3]]), col = "darkgreen") +
-  geom_sf(data = st_as_sf(secondtrails[[1]]), col = "red") +
+  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
+  geom_sf(data = st_as_sf(secondtrails$paths), col = "red") +
 
@@
           aes(colour = "Visible defect"), show.legend = "point") +
-  geom_sf(data = Future,
-          aes(colour = "Future"), show.legend = "point", size = 4) +
+  # geom_sf(data = Future,
+  #         aes(colour = "Future"), show.legend = "point", size = 4) +
   geom_sf(data = Reserve,
@@
   labs(color = "Logging status") +
-  labs(title = "P16 EFI3")
+  labs(title = "P6 EFI3 Hollow Fuel")
 ```

### 2022-01-14 docs/CreekDistancesRmd.Rmd

--- 2021-12-20 docs/VerticalCreekHeight.Rmd
@@
 ```{r}
-DTM <- 
+data("PlotMask")
+
+DATA_paracou_path <- paste0(Sys.getenv('DATAPATH'), "/GIS/Paracou/")
+
+DTM <- paste0(DATA_paracou_path,"Dem.sgrd")
 ```
@@
 ```{r}
-CreekVerticalHeight <- DistancesCrique$distvert
+  DistancesCrique$distvert <- mask(DistancesCrique$distvert, PlotMask)
+  DistancesCrique$distvert <- crop(DistancesCrique$distvert, PlotMask)
+
+  DistancesCrique$disthorz <- mask(DistancesCrique$disthorz, PlotMask)
+  DistancesCrique$disthorz <- crop(DistancesCrique$disthorz, PlotMask)
+
+CreekDistances <- list(distvert = DistancesCrique$distvert,distHorz = DistancesCrique$disthorz)
+
 ```
@@
 ```{r}
-plot(CreekVerticalHeight,  breaks=c(0,2), col='red') # les jolis bas-fonds !
+plot(CreekDistances$distvert,  breaks=c(0,2), col='red')
+
+plot(CreekDistances$distHorz,  breaks=c(0,30), col='red')
 ```

### 2022-01-14 R/VerticalCreekHeight.R
Work on scd trails

@@ -1,11 +1,0 @@
-#' Vertical creek height of Paracou plot 6
-#'
-#' Vertical creek height (in m) of plot 6 of Paracou (French Guiana) (1 m resolution,
-#' 2016)
-#'
-#' @format A Large RasterLayer
-#'
-#' To generate vertical creek height of any plot:
-#'  \code{\link{VerticalCreekHeight}} in 'docs' folder of the package
-#'
-"VerticalCreekHeight"

### 2022-01-14 tests/testthat/test-loggingsimulation.R

@@ -7,7 +7,7 @@ test_that("loggingsimulation", {
   # data(PlotMask) # inventoried plot mask
   # data(PlotSlope)
   # data(DTMParacou) # topography
-  # data(VerticalCreekHeight) # relative elevation
+  # data(CreekDistances) # relative elevation
   # data(SpeciesCriteria) # species exploitability criteria
   # data(ForestZoneVolumeParametersTable) # volume parameters
   # data(ParamCrownDiameterAllometry) # parameters values of the crown diameter allometry
@@ -15,7 +15,7 @@ test_that("loggingsimulation", {
 
   # Rslt <- loggingsimulation(
   #   Paracou6_2016, plotmask = PlotMask, topography = DTMParacou,
-  #   verticalcreekheight  = VerticalCreekHeight, speciescriteria = SpeciesCriteria,
+  #   creekdistances  = CreekDistances, speciescriteria = SpeciesCriteria,
   #   volumeparameters = ForestZoneVolumeParametersTable, scenario = "manual",
   #   objective = 20, fuel = "2", diversification = TRUE, winching = "2",
   #   directionalfelling = "2", specieslax = FALSE, objectivelax = TRUE,
@@ -24,7 +24,7 @@ test_that("loggingsimulation", {
 
   # Check args
   expect_error(loggingsimulation(Paracou6_2016, plotmask = PlotMask, topography = DTMParacou,
-                                 verticalcreekheight = RE, speciescriteria = SpeciesCriteria,
+                                 creekdistances = RE, speciescriteria = SpeciesCriteria,
                                  volumeparameters = ForestZoneVolumeParametersTable,
                                  crowndiameterparameters = ParamCrownDiameterAllometry, scenario = "RIL1",
                                  iter = FALSE, cores = FALSE),

### 2022-01-17 R/Secontrails plots.Rmd
Work on scd trails
run all version

@@
 ```{r}
-secondtrails$TrailsDensity
+secondtrails$RawSecondTrails # 'non-smoothed secondary trails
+class(secondtrails$RawSecondTrails) # SpatialLines (sp)
+plot(st_as_sf(secondtrails$RawSecondTrails))
 
-secondtrails$paths # 'paths'
-class(secondtrails$paths) # SpatialLines (sp)
+secondtrails$TrailsIdentity # information on sections of the trails
+class(secondtrails$TrailsIdentity) # matrix
 
-secondtrails$lines # 'lines' Sert à quoi ??
-class(secondtrails$lines) # matrix
-
-plot(secondtrails$SmoothedSecondTrails) # SmoothedSecondTrails
+plot(secondtrails$SmoothedSecondTrails) # Smoothed Secondary Trails
 class(secondtrails$SmoothedSecondTrails) # sfc_MULTIPOLYGON
@@
   geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
-  geom_sf(data = st_as_sf(secondtrails$paths), col = "red")
+  geom_sf(data = st_as_sf(secondtrails$RawSecondTrails), col = "red")
 
@@
 ```{r}
-NewInventory <- treeselectionoutputs$inventory # scenario = "RIL3", objectivelax = TRUE
+NewInventory <- treeselectionoutputs$inventory # objectivelax = TRUE
 
@@
 
-# HarvestableUp <- sf::st_as_sf(
-#   dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
-#   coords = c("Xutm", "Yutm")) %>% 
-#   st_set_crs(st_crs(HarvestablePolygons))
+HarvestableUp <- sf::st_as_sf(
+  dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
+  coords = c("Xutm", "Yutm")) %>%
+  st_set_crs(st_crs(HarvestablePolygons))
 
@@
 
-# Future <- sf::st_as_sf(
-#   dplyr::filter(NewInventory, LoggingStatus == "future"),
-#   coords = c("Xutm", "Yutm")) %>% 
-#   st_set_crs(st_crs(HarvestablePolygons))
+Future <- sf::st_as_sf(
+  dplyr::filter(NewInventory, LoggingStatus == "future"),
+  coords = c("Xutm", "Yutm")) %>%
+  st_set_crs(st_crs(HarvestablePolygons))
 
@@
   geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
-  geom_sf(data = st_as_sf(secondtrails$paths), col = "red") +
+  geom_sf(data = st_as_sf(secondtrails$RawSecondTrails), col = "red") +
 
@@
           aes(colour = "Selected"), show.legend = "point") +
-  geom_sf(data = ProbedHollow,
-          aes(colour = "Probed hollow"), show.legend = "point") +
+  # geom_sf(data = ProbedHollow,
+  #         aes(colour = "Probed hollow"), show.legend = "point") +
   geom_sf(data = MainTrails) +
@@
 ```{r}
+# enregistré avec une hauteur = 1000 or 1100 or 1500
+
 ggplot() +
@@
   # 2ndary trails
-  geom_sf(data = st_as_sf(secondtrails[[3]]), col = "darkgreen") +
-  geom_sf(data = st_as_sf(secondtrails[[1]]), col = "red") +
+  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
+  geom_sf(data = st_as_sf(secondtrails$RawSecondTrails), col = "red") +
 
@@
   labs(color = "Logging status") +
-  labs(title = "P6 EFI3 Hollow Fuel")
+  labs(title = "Paracou P6 EFI3")
+
+write.csv2(NewInventory, "C:/Users/Vincyane/Documents/Maria-pictures/ParacouP6_EFI3.csv") #  D:/VSC Kourou/Dataexemple
+
 ```

### 2022-01-17 R/Secontrails plots.Rmd

@@
   labs(alpha = "Harvestable") +
-  labs(title = "P6 zones exploitables") +
+  labs(title = "Paracou P6 zones exploitables") +
 
@@
           aes(colour = "Visible defect"), show.legend = "point") +
-  # geom_sf(data = Future,
-  #         aes(colour = "Future"), show.legend = "point", size = 4) +
+  geom_sf(data = Future,
+          aes(colour = "Future"), show.legend = "point", size = 4) +
   geom_sf(data = Reserve,
@@
   labs(color = "Logging status") +
-  labs(title = "P16 EFI3")
+  labs(title = "Paracou P16 EFI3")
 ```

### 2022-01-18 R/Secontrails plots.Rmd

@@
 data("HarvestablePolygons")
+data(DTMParacou)
+data(CreekDistances)
 data("MainTrails")
+```
+
+# Def UP
+```{r}
+HarvestableAreaOutputs27 <- harvestableareadefinition(
+  topography = DTMParacou,
+  creekdistances = CreekDistances,
+  advancedloggingparameters = loggingparameters(MaxAreaSlope = 27)
+)
+HarvesPolygons22 <-  HarvestableAreaOutputs$HarvestablePolygons
+HarvesPolygons27 <-  HarvestableAreaOutputs27$HarvestablePolygons
+
+HarvestableAreaOutputs27$HarvestableArea # 6.0683
+HarvestableAreaOutputs$HarvestableArea # 6.0683
+
+PlotSlope <-  HarvestableAreaOutputs$PlotSlope
 ```
@@
   # Harvestable zones
-  geom_sf(data = HarvestablePolygons,
+  geom_sf(data = HarvesPolygons27,
           aes(alpha = Harvestable),
@@
   labs(alpha = "Harvestable") +
-  labs(title = "Paracou P6 zones exploitables") +
+  labs(title = "Paracou P6 zones exploitables 22 et 27% de pente")+
+  geom_sf(data = HarvesPolygons22,
+          aes(alpha = Harvestable),
+          fill = "pink")
 

### 2022-01-24 R/Secontrails plots.Rmd
Plots

--- 2022-01-17 R/Secontrails plots.Rmd
@@
 ```{r}
-secondtrails$RawSecondTrails # 'non-smoothed secondary trails
-class(secondtrails$RawSecondTrails) # SpatialLines (sp)
+secondtrails$TrailsDensity
+
+secondtrails$RawSecondTrails # 'RawSecondTrails'
+class(secondtrails$RawSecondTrails) # SpatialTrailsIdentity (sp)
 plot(st_as_sf(secondtrails$RawSecondTrails))
 
-secondtrails$TrailsIdentity # information on sections of the trails
+secondtrails$TrailsIdentity # 'TrailsIdentity' Sert à quoi ??
 class(secondtrails$TrailsIdentity) # matrix
 
-plot(secondtrails$SmoothedSecondTrails) # Smoothed Secondary Trails
+plot(secondtrails$SmoothedSecondTrails) # SmoothedSecondTrails
 class(secondtrails$SmoothedSecondTrails) # sfc_MULTIPOLYGON
@@
 ```{r}
-NewInventory <- treeselectionoutputs$inventory # objectivelax = TRUE
+NewInventory <- treeselectionoutputs$inventory # scenario = "RIL3", objectivelax = TRUE
 
@@
 
-HarvestableUp <- sf::st_as_sf(
-  dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
-  coords = c("Xutm", "Yutm")) %>%
-  st_set_crs(st_crs(HarvestablePolygons))
+# HarvestableUp <- sf::st_as_sf(
+#   dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
+#   coords = c("Xutm", "Yutm")) %>% 
+#   st_set_crs(st_crs(HarvestablePolygons))
 
@@
 
-Future <- sf::st_as_sf(
-  dplyr::filter(NewInventory, LoggingStatus == "future"),
-  coords = c("Xutm", "Yutm")) %>%
-  st_set_crs(st_crs(HarvestablePolygons))
+# Future <- sf::st_as_sf(
+#   dplyr::filter(NewInventory, LoggingStatus == "future"),
+#   coords = c("Xutm", "Yutm")) %>% 
+#   st_set_crs(st_crs(HarvestablePolygons))
 
@@
           aes(colour = "Selected"), show.legend = "point") +
-  # geom_sf(data = ProbedHollow,
-  #         aes(colour = "Probed hollow"), show.legend = "point") +
+  geom_sf(data = ProbedHollow,
+          aes(colour = "Probed hollow"), show.legend = "point") +
   geom_sf(data = MainTrails) +
@@
 ```{r}
-# enregistré avec une hauteur = 1000 or 1100 or 1500
-
 ggplot() +
@@
   # 2ndary trails
-  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
-  geom_sf(data = st_as_sf(secondtrails$RawSecondTrails), col = "red") +
+  geom_sf(data = st_as_sf(secondtrails[[3]]), col = "darkgreen") +
+  geom_sf(data = st_as_sf(secondtrails[[1]]), col = "red") +
 
@@
   labs(color = "Logging status") +
-  labs(title = "Paracou P6 EFI3")
-
-write.csv2(NewInventory, "C:/Users/Vincyane/Documents/Maria-pictures/ParacouP6_EFI3.csv") #  D:/VSC Kourou/Dataexemple
-
+  labs(title = "P6 EFI3 Hollow Fuel")
 ```

### 2022-02-01 R/Secontrails plots.Rmd
scdtrailadj WIP

--- 2022-01-18 R/Secontrails plots.Rmd
@@
 data(CreekDistances)
+data(PlotMask)
 data("MainTrails")
@@
 ```{r}
-HarvestableAreaOutputs27 <- harvestableareadefinition(
+HarvestableAreaOutputs <- harvestableareadefinition(
   topography = DTMParacou,
   creekdistances = CreekDistances,
-  advancedloggingparameters = loggingparameters(MaxAreaSlope = 27)
+  plotmask = PlotMask,
+  scenario = "RIL2"
 )
@@
   # 2ndary trails
-  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
+  geom_sf(data = st_as_sf(secondtrails$SmoothedTrails), col = "darkgreen") +
   geom_sf(data = st_as_sf(secondtrails$RawSecondTrails), col = "red") +

### 2022-02-01 R/maintrailextract.R

@@ -1,0 +1,64 @@
+#' Generating maintrails function
+#'
+#' @param topography Digital terrain model (DTM) of the inventoried plot (LiDAR
+#'  or SRTM) (\code{\link{DTMParacou}}) (RasterLayer)
+#'
+#' @param advancedloggingparameters Other parameters of the logging simulator
+#'   \code{\link{loggingparameters}} (list)
+#'
+#' @return The maintrails outside of the topography raster (sf LINESTRING object)
+#'
+#' @export
+#'
+#' @importFrom raster res extend focal rasterToPolygons
+#' @importFrom sf st_as_sf st_cast
+#'
+#' @examples
+#' \dontrun{
+#' data(DTMParacou)
+#' MainTrails <- maintrailextract(DTMParacou)
+#'
+#' plot(DTMParacou)
+#' plot(Maintrails, add = T)
+#'
+#' }
+#'
+maintrailextract <- function(topography,
+                             advancedloggingparameters = loggingparameters()){
+
+  # Arguments check
+
+  if(!inherits(topography,"RasterLayer"))
+    stop("The 'topography' arguments of the 'maintrailextract' function must be RasterLayer")
+
+  # Variables
+  fact <- DTMExtExtended <- DTMExtended <- preMainTrails <- NULL
+  MainTrails <- NULL
+
+  #function
+
+  fact <- floor(advancedloggingparameters$SlopeDistance/res(topography)[1])
+
+    DTMExtExtended <- extend(topography, c(fact,fact)) # extend the extent
+
+    fill.boundaries <- function(x) {
+      center = 0.5 + (fact*fact/2)
+      if( is.na(x)[center] ) {
+        return( round(mean(x, na.rm=T),5) )
+      } else {
+        return( x[center] )
+      }
+    }
+
+    DTMExtended <- focal(DTMExtExtended,
+                         matrix(1,fact,fact),
+                         fun=fill.boundaries,
+                         na.rm=F, pad=T)
+
+    preMainTrails <- DTMExtended > -Inf
+    preMainTrails<- rasterToPolygons(preMainTrails, dissolve=T)
+    MainTrails <- preMainTrails %>% st_as_sf() %>% st_cast(to = 'LINESTRING', warn= FALSE)
+
+  return(MainTrails)
+
+}

### 2022-02-01 R/treefelling.R

@@ -36,8 +36,8 @@
 #' If the avoidance of future/reserve trees could not be performed,
 #' a message is returned.
 #'
-#'@param MainTrails Main trails (sf)
-#'@param ScndTrail Secondary trails (sf)
+#'@param maintrailsaccess Main trails access points (sf)
+#'@param scndtrail main and second trails (sf)
 #'
 #'@param advancedloggingparameters Other parameters of the logging simulator
 #'  \code{\link{loggingparameters}} (list)
@@ -92,41 +92,68 @@
 #' @examples
 #' data(Paracou6_2016)
 #' data(DTMParacou)
-#' data(PlotSlope)
+#' data(PlotMask)
 #' data(SpeciesCriteria)
-#' data(HarvestablePolygons)
+#' data(CreekDistances)
 #' data(MainTrails)
 #'
-#' pol1 <- list(matrix(c(286503, 582925,
-#'                       286503, 583240,
-#'                       286507, 583240,
-#'                       286507, 582925,
-#'                       286503, 582925) # the return
-#'                    ,ncol=2, byrow=TRUE))
-#' pol2 <- list(matrix(c(286650, 582925,
-#'                       286650, 583240,
-#'                       286654, 583240,
-#'                       286654, 582925,
-#'                       286650, 582925) # the return
-#'                    ,ncol=2, byrow=TRUE))
+#' scenariosparameters <- scenariosparameters(scenario = "manual",
+#'  winching = "2",
+#'  objective = 10,
+#'  fuel = "0",
+#'  diversification = TRUE,
+#'  directionalfelling = "0")
 #'
-#' PolList = list(pol1,pol2) #list of lists of numeric matrices
-#' ScndTrail <- sf::st_as_sf(sf::st_sfc(sf::st_multipolygon(PolList)))
-#' ScndTrail <- sf::st_set_crs(ScndTrail, sf::st_crs(MainTrails))
+#'
+#' HarvestableAreaOutputs <- harvestableareadefinition(
+#'   topography = DTMParacou,
+#'   creekdistances = CreekDistances,
+#'   maintrails = MainTrails,
+#'   plotmask = PlotMask,
+#'   scenario = "manual",winching = scenariosparameters$winching,
+#'   advancedloggingparameters = loggingparameters()
+#'   )
+#'
 #'
[…]

### 2022-02-04 R/DraftFunctions.Rmd

@@
 # usethis::use_data(ScenariosTable,overwrite = TRUE)
+```
+
+# Generate prospection units
+```{r}
+HarvestableAreaOutputsCable <- harvestableareadefinition(
+  topography = DTMParacou,
+  creekdistances = CreekDistances,
+  maintrails = MainTrails,
+  plotmask = PlotMask,
+  scenario = "manual", winching = "1",
+  advancedloggingparameters = loggingparameters()
+)
+
+# usethis::use_data(HarvestableAreaOutputsCable, overwrite = TRUE)
 ```

### 2022-02-07 R/DraftFunctions.Rmd
Clean after 2ndTrails

@@
 # usethis::use_data(HarvestableAreaOutputsCable, overwrite = TRUE)
+```
+
+# Secondary trails in Data
+```{r}
+scenario <- "manual"
+winching <- "2"
+objective <- 10
+fuel <- "2"
+diversification <- TRUE
+
+inventory <- addtreedim(cleaninventory(Paracou6_2016, PlotMask),
+                        volumeparameters = ForestZoneVolumeParametersTable)
+
+treeselectionoutputs <- suppressWarnings(treeselection(inventory,
+                                                       topography = DTMParacou,
+                                                       speciescriteria = SpeciesCriteria, objective = objective,
+                                                       scenario = "manual", fuel = fuel,
+                                                       diversification = diversification,
+                                                       winching = winching, specieslax = FALSE,
+                                                       objectivelax = TRUE, plotslope = HarvestableAreaOutputsCable$PlotSlope,
+                                                       harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
+                                                       advancedloggingparameters = loggingparameters()))
+
+SecondaryTrails <- secondtrailsopening(
+  topography = DTMParacou,
+  plotmask = PlotMask,
+  maintrails = MainTrails,
+  plotslope = HarvestableAreaOutputsCable$PlotSlope,
+  harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
+  machinepolygons = HarvestableAreaOutputsCable$MachinePolygons,
+  treeselectionoutputs = treeselectionoutputs,
+  CostMatrix = list(list(list(Slope = 3, Cost = 3),
+                         list(Slope = 5, Cost = 5),
+                         list(Slope = 12, Cost = 20),
+                         list(Slope = 22, Cost = 60),
+                         list(Slope = 35, Cost = 1000),
+                         list(Slope = Inf, Cost = Inf)),
+                    list(list(CostType = "Initial", CostValue = 1000),
+                         list(CostType = "Access", CostValue = Inf),
+                         list(CostType = "BigTrees", CostValue = 500),
+                         list(CostType = "Reserves", CostValue = 500),
+                         list(CostType = "Futures", CostValue = 50),
+                         list(CostType = "MainTrails", CostValue = 1E-4),
+                         list(CostType = "SecondTrails", CostValue = 0.1))),
+  scenario = "manual",
+  winching = winching,
+  advancedloggingparameters = loggingparameters())
+
+# usethis::use_data(SecondaryTrails, overwrite = TRUE)
 ```

### 2022-02-07 R/DraftFunctions.Rmd
Clean after 2ndTrails

--- 2022-02-04 R/DraftFunctions.Rmd
@@
 # usethis::use_data(HarvestableAreaOutputsCable, overwrite = TRUE)
+```
+
+# Secondary trails in Data
+```{r}
+scenario <- "manual"
+winching <- "2"
+objective <- 10
+fuel <- "2"
+diversification <- TRUE
+
+inventory <- addtreedim(cleaninventory(Paracou6_2016, PlotMask),
+                        volumeparameters = ForestZoneVolumeParametersTable)
+
+treeselectionoutputs <- suppressWarnings(treeselection(inventory,
+                                                       topography = DTMParacou,
+                                                       speciescriteria = SpeciesCriteria, objective = objective,
+                                                       scenario = scenario, fuel = fuel,
+                                                       diversification = diversification,
+                                                       winching = winching, specieslax = FALSE,
+                                                       objectivelax = TRUE, plotslope = HarvestableAreaOutputsCable$PlotSlope,
+                                                       harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
+                                                       advancedloggingparameters = loggingparameters()))
+
+SecondaryTrails <- secondtrailsopening(
+  topography = DTMParacou,
+  plotmask = PlotMask,
+  maintrails = MainTrails,
+  plotslope = HarvestableAreaOutputsCable$PlotSlope,
+  harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
+  machinepolygons = HarvestableAreaOutputsCable$MachinePolygons,
+  treeselectionoutputs = treeselectionoutputs,
+  scenario = scenario,
+  winching = winching,
+  advancedloggingparameters = loggingparameters())
+
+usethis::use_data(SecondaryTrails, overwrite = TRUE)
 ```

### 2022-02-07 R/maintrailextract.R

@@ -14,14 +14,12 @@
 #' @importFrom sf st_as_sf st_cast
 #'
 #' @examples
-#' \dontrun{
 #' data(DTMParacou)
 #' MainTrails <- maintrailextract(DTMParacou)
 #'
+#' library(raster)
 #' plot(DTMParacou)
-#' plot(MainTrails, add = T)
-#'
-#' }
+#' plot(MainTrails, add = TRUE)
 #'
 maintrailextract <- function(topography,
                              advancedloggingparameters = loggingparameters()){

### 2022-02-07 R/treefelling.R

@@ -91,74 +91,28 @@
 #'@importFrom stats runif
 #'
 #' @examples
-#' data(Paracou6_2016)
-#' data(DTMParacou)
-#' data(PlotMask)
-#' data(SpeciesCriteria)
-#' data(CreekDistances)
-#' data(HarvestableAreaOutputsCable)
-#' data(MainTrails)
+#' data(SecondaryTrails)
+#' data(SecondaryTrails)
 #'
-#' scenariosparameters <- scenariosparameters(scenario = "manual",
-#'  winching = "2",
-#'  objective = 10,
-#'  fuel = "0",
-#'  diversification = TRUE,
-#'  directionalfelling = "0")
+#' scenario <- "manual"
+#' winching <- "2"
+#' fuel <- "0"
+#' directionalfelling <- "0"
 #'
 #'
-#' inventory <- addtreedim(cleaninventory(Paracou6_2016, PlotMask),
-#' volumeparameters = ForestZoneVolumeParametersTable)
-#'
-#' treeselectionoutputs <- suppressWarnings(treeselection(inventory,
-#'   topography = DTMParacou,
-#'   speciescriteria = SpeciesCriteria,
-#'   scenario = "manual", objective = scenariosparameters$objective,
-#'   fuel = scenariosparameters$fuel,
-#'   diversification = scenariosparameters$diversification,
-#'   winching = scenariosparameters$winching,
-#'   specieslax = FALSE, objectivelax = TRUE,
-#'   plotslope = HarvestableAreaOutputsCable$PlotSlope,
-#'   harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
-#'   advancedloggingparameters = loggingparameters()))
-#'
-#' secondtrails <- secondtrailsopening(
-#'   topography = DTMParacou,
-#'   plotmask = PlotMask,
-#'   plotslope = HarvestableAreaOutputsCable$PlotSlope,
-#'   harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
-#'   machinepolygons = HarvestableAreaOutputsCable$MachinePolygons,
-#'   treeselectionoutputs = treeselectionoutputs,
-#'   CostMatrix = list(list(list(Slope = 3, Cost = 3),
-#'   list(Slope = 5, Cost = 5),
-#'   list(Slope = 12, Cost = 20),
-#'   list(Slope = 22, Cost = 60),
-#'   list(Slope = 35, Cost = 1000),
[…]

### 2022-02-09 tests/testthat/test-loggingsummary1.R
In loggingsimulation function + slope criteria in treefelling

@@ -1,27 +1,12 @@
 test_that("loggingsummary1", {
 
   # Data loading
-  # data(Paracou6_2016) # inventory
-  # data(PlotMask) # inventoried plot mask
-  # data(DTMParacou) # topography
-  # data(CreekDistances) # relative elevation
-  # data(SpeciesCriteria) # species exploitability criteria
-  # data(ForestZoneVolumeParametersTable) # volume parameters
-  # data(ParamCrownDiameterAllometry) # parameters values of the crown diameter allometry
+  data(LoggingSimulationOutputs)
 
   expect_error(loggingsummary1(x = TRUE),
                regexp = "The argument of the 'loggingsummary1' function must be a list")
 
-  # x <- suppressMessages(
-  #     loggingsimulation1(Paracou6_2016, topography = DTMParacou,
-  #                       verticalcreekheight  = DTMParacou, speciescriteria = SpeciesCriteria,
-  #                       volumeparameters = ForestZoneVolumeParametersTable, scenario = "manual",
-  #                       objective = 20, fuel = "2", diversification = TRUE, winching = "2",
-  #                       directionalfelling = "2", specieslax = FALSE, objectivelax = TRUE, harvestablepolygons = HarvestablePolygons,
-  #                       crowndiameterparameters = ParamCrownDiameterAllometry,
-  #                       advancedloggingparameters = loggingparameters())
-  #   )
-  #
-  # rslt <- capture.output(loggingsummary1(x))
+
+  rslt <- capture.output(loggingsummary1(LoggingSimulationOutputs))
 
   })

### 2022-02-15 R/DraftFunctions.Rmd
In loggingsimulation function + slope criteria in treefelling
Package renaming

@@
 library(EcoFoG)
-library(Maria)
+library(LoggingLab)
 library(readr)
@@
 # LoggingSimulationOutputs <- Rslt
-# usethis::use_data(LoggingSimulationOutputs)
+# usethis::use_data(LoggingSimulationOutputs, overwrite = TRUE)
+
+# LoggingSimulationOutputs_iter <- Rslt
+# usethis::use_data(LoggingSimulationOutputs_iter, overwrite = TRUE)
 
@@
 data(ForestZoneVolumeParametersTable) # The volume parameters data in the global environment
-# load(system.file("extdata", "BrokenParacou6_2016.rda", package = "Maria")) # the test inventory in the global environment
+# load(system.file("extdata", "BrokenParacou6_2016.rda", package = "LoggingLab")) # the test inventory in the global environment
 data(ParamCrownDiameterAllometry)

### 2022-02-15 R/Secontrails plots.Rmd
Package renaming

@@
 ```{r}
-library(Maria)
+library(LoggingLab)
 library(ggplot2)
@@
 
-write.csv2(NewInventory, "C:/Users/Vincyane/Documents/Maria-pictures/ParacouP6_EFI3.csv") #  D:/VSC Kourou/Dataexemple
+write.csv2(NewInventory, "C:/Users/Vincyane/Documents/LoggingLab-pictures/ParacouP6_EFI3.csv") #  D:/VSC Kourou/Dataexemple
 

### 2022-02-17 R/ParamCrownDiameterAllometry.R
Add full parameters reference + links to the vignette

@@ -3,15 +3,20 @@
 #' Parameters of crown diameter allometry used to compute the crown diameter of
 #' each tree, depending on its DBH (Diameter at Breast Height) and its species,
 #' genus or family (Aubry-Kientz et al.2019).
+#'
+#' @references Aubry-Kientz, Mélaine, et al. "A comparative assessment of the
+#'   performance of individual tree crowns delineation algorithms from ALS data
+#'   in tropical forests." Remote Sensing 11.9 (2019): 1086.
+#'
 #' @format A tibble with 371 rows and 7 variables: \describe{
 #'
 #'   \item{alpha}{Coefficient of the equation: ln(DBH) = alpha + beta ln(H*CD) +
-#'   error, with error~N(0,sigma^2). DBH: tree diameter at breast hight, H: tree height,
-#'   CD: tree crown diameter. Mean sigma^2 = 0.0295966977 (double)}
+#'   error, with error~N(0,sigma^2). DBH: tree diameter at breast hight, H: tree
+#'   height, CD: tree crown diameter. Mean sigma^2 = 0.0295966977 (double)}
 #'
 #'   \item{beta}{Coefficient of the equation: ln(DBH) = alpha + beta ln(H*CD) +
-#'   error, with error~N(0,sigma^2).DBH: tree diameter at breast hight, H: tree height,
-#'   CD: tree crown diameter. Mean sigma^2 = 0.0295966977 (double)}
+#'   error, with error~N(0,sigma^2).DBH: tree diameter at breast hight, H: tree
+#'   height, CD: tree crown diameter. Mean sigma^2 = 0.0295966977 (double)}
 #'
 #'   \item{Taxo}{Taxonomic level of the parameters (character)}
 #'

### 2022-02-17 R/createcanopy.R

@@ -5,7 +5,7 @@
 #'@param inventory Input inventory containing the crown diameter (CrownDiameter,
 #'  in m) (calculable with the addtreedim function) of each tree
 #'  (data.frame)(see the inputs formats and metadata in the
-#'  \code{\link{vignette}})
+#'  \code{\link{LoggingLab.html}})
 #'
 #'@return A dataframe with a column 'Crowns' containing the circles
 #'  (sfc_POLYGON) as trees crown, with their diameter filled in, representing

### 2022-02-17 R/harvestable.R

@@ -4,7 +4,7 @@
 #'  which trees are harvestable according to your harvestability criteria
 #'
 #'@param inventory Input inventory (see the inputs formats and metadata in the
-#'  \code{\link{vignette}}) (data.frame)
+#'  \code{\link{LoggingLab.html}}) (data.frame)
 #'
 #'@param topography Digital terrain model (DTM) of the inventoried plot (LiDAR
 #'  or SRTM) (\code{\link{DTMParacou}}) (RasterLayer)
@@ -25,7 +25,7 @@
 #'
 #'@param scenario Logging scenario: "RIL1", "RIL2broken", "RIL2", "RIL3",
 #'  "RIL3fuel", "RIL3fuelhollow" or "manual"(character) (see the
-#'  \code{\link{vignette}})
+#'  \code{\link{LoggingLab.html}})
 #'
 #'@param winching
 #' "0": no cable or grapple (trail to tree foot)

### 2022-02-17 R/loggingsimulation1.R

@@ -7,7 +7,7 @@
 #'  volume and damages quantification.
 #'
 #'@param inventory Input inventory (see the inputs formats and metadata in the
-#'  \code{\link{vignette}}) (data.frame)
+#'  \code{\link{LoggingLab.html}}) (data.frame)
 #'
 #'@param plotmask Inventoried plot mask (SpatialPolygonsDataFrame)
 #'
@@ -32,7 +32,7 @@
 #'
 #'@param scenario Logging scenario: "RIL1", "RIL2broken", "RIL2", "RIL3",
 #'  "RIL3fuel", "RIL3fuelhollow" or "manual"(character) (see the
-#'  \code{\link{vignette}})
+#'  \code{\link{LoggingLab.html}})
 #'
 #'@param objective Objective volume (m3/ha) (numeric)
 #'
@@ -84,7 +84,7 @@
 #'  \code{\link{loggingparameters}} (list)
 #'
 #'@return Input inventory (data.frame) with logging informations (list)
-#'(see the outputs metadata in the \code{\link{vignette}}).
+#'(see the outputs metadata in the \code{\link{LoggingLab.html}}).
 #'
 #'@seealso \code{\link{Paracou6_2016}}, \code{\link{SpeciesCriteria}},
 #'  \code{\link{ForestZoneVolumeParametersTable}},

### 2022-02-17 R/treefelling.R

@@ -1,11 +1,11 @@
 #'Tree felling
 #'
 #'@param inventory Input inventory (see the inputs formats and metadata in the
-#'  \code{\link{vignette}}) (data.frame)
+#'  \code{\link{LoggingLab.html}}) (data.frame)
 #'
 #'@param scenario Logging scenario: "RIL1", "RIL2broken", "RIL2", "RIL3",
 #'  "RIL3fuel", "RIL3fuelhollow" or "manual"(character) (see the
-#'  \code{\link{vignette}})
+#'  \code{\link{LoggingLab.html}})
 #'
 #'@param fuel Fuel wood exploitation: no exploitation = "0", exploitation of
 #'   damage and unused part of logged trees for fuel = "1", exploitation of
@@ -337,7 +337,7 @@ treefelling <- function(
 #'  \code{advancedloggingparameters} argument.
 #'
 #'@param inventory input inventory (see the inputs formats and metadata in the
-#'  \code{\link{vignette}}) (data.frame)
+#'  \code{\link{LoggingLab.html}}) (data.frame)
 #'
 #'@param fuel Fuel wood exploitation: no exploitation = "0", exploitation of
 #'   damage and unused part of logged trees for fuel = "1", exploitation of
@@ -354,7 +354,7 @@ treefelling <- function(
 #'  \code{\link{loggingparameters}} (list)
 #'
 #'@return Input inventory with the "TreeFellingOrientationSuccess" new column (see
-#'  the outputs metadata in the \code{\link{vignette}}).
+#'  the outputs metadata in the \code{\link{LoggingLab.html}}).
 #'@export
 #'
 #'@importFrom dplyr mutate rowwise

### 2022-02-17 R/loggingsimulation.R
\dontrun because it's too long

@@ -105,6 +105,7 @@
 #'@importFrom parallel makePSOCKcluster clusterExport parLapply stopCluster
 #'
 #' @examples
+#' \dontrun{
 #' data(Paracou6_2016) # inventory
 #' data(DTMParacou) # topography
 #' data(CreekDistances) # relative elevation
@@ -120,6 +121,7 @@
 #'  directionalfelling = "2", specieslax = FALSE, objectivelax = TRUE,
 #'  crowndiameterparameters = ParamCrownDiameterAllometry,
 #'  advancedloggingparameters = loggingparameters(), iter = 2, cores = 2)
+#'  }
 #'
 loggingsimulation <- function(
   inventory,

### 2022-02-17 R/loggingsimulation1.R

@@ -107,6 +107,7 @@
 #'@importFrom methods as
 #'
 #' @examples
+#' \dontrun{
 #' data(Paracou6_2016) # inventory
 #' data(PlotMask) # inventoried plot mask
 #' data(DTMParacou) # topography
@@ -123,6 +124,7 @@
 #'  directionalfelling = "2", specieslax = FALSE, objectivelax = TRUE,
 #'  crowndiameterparameters = ParamCrownDiameterAllometry,
 #'  advancedloggingparameters = loggingparameters())
+#'  }
 #'
 loggingsimulation1 <- function(
   inventory,

### 2022-04-20 R/PlotMask.R
"crs in UTM" in the doc

@@ -1,6 +1,6 @@
 #' PlotMask
 #'
 #' Mask of the plot 6 of Paracou (1m resolution, LiDAR campaign of 2016) (French Guiana)
-#' @format SpatialPolygonsDataFrame **with a crs**
+#' @format SpatialPolygonsDataFrame **with a crs in UTM**
 #'
 "PlotMask"

### 2022-05-03 R/inventorycheckformat.R
Improve the documentation and the vignette

@@ -1,8 +1,8 @@
 #' Check the input inventory data for the "LoggingLab" package
 #'
-#' @description Check if the input inventory data is compatible with the "LoggingLab"
-#'   package (see 'Required format of the inventory' section of the vignette
-#'   vignette)
+#' @description Check if the input inventory data is compatible with the
+#'   "LoggingLab" package (see 'Required format of the inventory' section of the
+#'   vignette vignette)
 #'
 #' @param inventory Input inventory (see the inputs formats and metadata in the
 #'   vignette) (data.frame)
@@ -103,14 +103,14 @@ inventorycheckformat <- function(
     GoodData <- FALSE
     GeneralStop <- paste (GeneralStop, "VernName variable is not found.")
   }
-  if(!('Xfield' %in% names(inventory))) {
-    GoodData <- FALSE
-    GeneralStop <- paste (GeneralStop, "Xfield variable is not found.")
-  }
-  if(!('Yfield' %in% names(inventory))) {
-    GoodData <- FALSE
-    GeneralStop <- paste (GeneralStop, "Yfield variable is not found.")
-  }
+  # if(!('Xfield' %in% names(inventory))) {
+  #   GoodData <- FALSE
+  #   GeneralStop <- paste (GeneralStop, "Xfield variable is not found.")
+  # }
+  # if(!('Yfield' %in% names(inventory))) {
+  #   GoodData <- FALSE
+  #   GeneralStop <- paste (GeneralStop, "Yfield variable is not found.")
+  # }
   if(!('Xutm' %in% names(inventory))) {
     GoodData <- FALSE
     GeneralStop <- paste (GeneralStop, "Xutm variable is not found.")

### 2022-05-03 R/maintrailextract.R

@@ -1,4 +1,4 @@
-#' Generating maintrails function
+#' Generate main skidding trail of the inventoried plot
 #'
 #' @param topography Digital terrain model (DTM) of the inventoried plot (LiDAR
 #'  or SRTM) (\code{\link{DTMParacou}}) (RasterLayer **with a crs in UTM**)
@@ -8,8 +8,11 @@
 #' @param advancedloggingparameters Other parameters of the logging simulator
 #'   \code{\link{loggingparameters}} (list)
 #'
-#' @return The maintrails outside of the topography raster (sf LINESTRING object
-#'   **with a crs in UTM**)
+#' @details The main trails are defined as lines at the edge and outside of the
+#'   plot.
+#'
+#' @return The main trail at the edge and outside of the topography raster (sf
+#'   LINESTRING object **with a crs in UTM**)
 #'
 #' @export
 #'

### 2022-05-03 R/selected.R

@@ -1,5 +1,8 @@
 #'Selection of trees to log
 #'
+#'@description Selection of trees to log among the exploitable trees, according
+#'  to the objective volume and the exploitable volume on the plot.
+#'
 #'@param inventory Input inventory (see the inputs formats and metadata in the
 #'  vignette) (data.frame)
 #'
@@ -23,9 +26,10 @@
 #'@param specieslax Allow diversification if the stand is too poor to reach the
 #'  objective volume without diversification, = FALSE by default (logical)
 #'
-#'@param VO Objective volume for the entire area of the plot (numeric value)
+#'@param VO Objective volume for the entire area of the plot (m3) (numeric
+#'  value)
 #'
-#'@param HVinit Harvestable volume in the plot for the chosen scenario
+#'@param HVinit Harvestable volume(m3) in the plot for the chosen scenario
 #'  (\code{\link{SpeciesCriteria}}) (numeric value)
 #'
 #'@param objectivelax Allow exploitation in case of non-achievement of the
@@ -34,16 +38,15 @@
 #'@param advancedloggingparameters Other parameters of the logging simulator
 #'  \code{\link{loggingparameters}} (list)
 #'
-#'@return Input inventory with
-#'- The trees selected for harvesting ("Selected")
-#'- if the Minimum Felling Diameter (MinFD) of their species has been raised
-#'  ("Up")
-#'- The cumulative harvestable volume of harvestable trees("VolumeCumSum").
-#'- The probability of a tree being probed hollow ("ProbedHollowProba") and the
-#'   probed hollow trees ("ProbedHollow").
-#'See the outputs metadata in the vignette
+#'@return Input inventory with:
+#'  - The trees selected for harvesting (*Selected*)
+#'  - if the Minimum Felling Diameter (*MinFD*) of their species has been raised
+#'      (*Up*)
+#'  - The probability of a tree being probed hollow (*ProbedHollowProba*) and
+#'      the probed hollow trees (*ProbedHollow*).
+#'See the outputs metadata in the vignette.
 #'
-#'2 sets of spatial points: (HollowTrees and EnergywoodTrees)
+#'2 sets of spatial points: (*HollowTrees* and *EnergywoodTrees*)
 #'
 #'@details This function allows the selection of trees to be exploited among the
 #'  exploitable trees. It also informs about the trees that were finally found
@@ -53,9 +56,9 @@
 #'  trees to reach the objective volume (if possible).
 #'
[…]

### 2022-05-03 R/inventorycheckformat.R
improve the documentation and the vignette

@@ -103,14 +103,14 @@ inventorycheckformat <- function(
     GoodData <- FALSE
     GeneralStop <- paste (GeneralStop, "VernName variable is not found.")
   }
-  if(!('Xfield' %in% names(inventory))) {
-    GoodData <- FALSE
-    GeneralStop <- paste (GeneralStop, "Xfield variable is not found.")
-  }
-  if(!('Yfield' %in% names(inventory))) {
-    GoodData <- FALSE
-    GeneralStop <- paste (GeneralStop, "Yfield variable is not found.")
-  }
+  # if(!('Xfield' %in% names(inventory))) {
+  #   GoodData <- FALSE
+  #   GeneralStop <- paste (GeneralStop, "Xfield variable is not found.")
+  # }
+  # if(!('Yfield' %in% names(inventory))) {
+  #   GoodData <- FALSE
+  #   GeneralStop <- paste (GeneralStop, "Yfield variable is not found.")
+  # }
   if(!('Xutm' %in% names(inventory))) {
     GoodData <- FALSE
     GeneralStop <- paste (GeneralStop, "Xutm variable is not found.")

### 2022-09-09 R/genaccesspts.R
Updated 2nd trail + harvestable

@@ -34,6 +34,7 @@
 #' @examples
 #'
 #' \dontrun{
+#' set.seed(1)
 #' data(MainTrails)
 #' data(HarvestableAreaOutputsCable)
 #' data(DTMParacou)
@@ -52,7 +53,7 @@ genaccesspts <- function(topography,
   # Arguments check
 
   if(!inherits(topography, "RasterLayer"))
-    stop("The 'topography' argument of the 'secondtrailsadjusted' function must
+    stop("The 'topography' argument of the 'genaccesspts' function must
          be RasterLayer")
 
   ##################################

### 2022-11-14 R/Paracou6_2016.R
uf_basic v0.0.1

@@ -5,14 +5,15 @@
 #'
 #' The columns required for the package are:
 #' - *Forest* (to apply the corresponding volume formula)
-#' - *Plot* (1 value)
-#' - *CensusYear* (1 value)
 #' - *PlotArea*
 #' - *idTree*
 #' - *Xutm* and *Yutm*
 #' - *CodeAlive*
-#' - *Family*, *Genus*, *Species* and *VernName*
-#' - *Circ* or *CircCorr*
+#' - *Family*, *Genus*, *Species*
+#' - *CircCorr*
+#' The columns optional for the package are:
+#' - *Plot* (1 value)
+#' - *CensusYear* (1 value)
 #'
 #' @format A tibble with 3620 rows and 26 variables:
 #' \describe{

### 2022-11-14 R/addtreedim.R

@@ -72,7 +72,7 @@ addtreedim <- function(
     stop("The 'advancedloggingparameters' argument of the 'addtreedim' function must be a list")
 
   # Global variables
-  Accessible <- Circ <- CircCorr <- CodeAlive <- NULL
+  Accessible <- CircCorr <- CodeAlive <- NULL
   Condition <- DBH <- NULL
   DeathCause <- DistCriteria <- Family  <- Zone <- NULL
   ForestZoneVolumeParametersTable <- Genus <- Logged <- NULL

### 2022-11-22 R/commercialcriteriajoin.R
Change timber and fuel wood computation functions + create crown part for fuel wood + correct mortality by trails

@@ -56,7 +56,7 @@ commercialcriteriajoin <- function(
   ProbedHollow <- ProbedHollowProba <- ScientificName <- NULL
   Selected <- Slope <- SlopeCriteria <- Species <- Species.genus <- NULL
   SpeciesCriteria <- Taxo <- Taxo.family <- Taxo.genus <- Taxo.species <- NULL
-  TreeFellingOrientationSuccess <- TreeHarvestableVolume <- NULL
+  TreeFellingOrientationSuccess <- NULL
   TreeHeight <- TrunkHeight <- Up <- UpMinFD <- UpMinFD.genus <- NULL
   UpMinFD.species <- CommercialName.genus <- NULL
   CommercialName.species <- VolumeCumSum <- Xutm <- Yutm <- aCoef <- NULL

### 2022-11-28 R/harvestable.R
Change ful function name + try 2 purge calculations + add LoggingResidualBiomass + add check rows everywhere

@@ -151,6 +151,8 @@ harvestable <- function(
   alpha <- alpha.family <- alpha.genus <- alpha.species <- bCoef <- NULL
   beta.family <- beta.genus <- beta.species <- geometry <- idTree <- HarvestableZone <- NULL
 
+  # initial inventory
+  inventory0 <- inventory
 
   #### Redefinition of the parameters according to the chosen scenario ####
   scenariosparameters <- scenariosparameters(scenario = scenario, winching = winching)
@@ -320,6 +322,10 @@ harvestable <- function(
   HVinit <- sum(HarvestableTable$TreeHarvestableVolume)
 
   harvestableOutputs <- list(inventory = inventory, HVinit = HVinit)
+
+  if(nrow(inventory) != nrow(inventory0))
+    stop("The number of rows between the input inventory and the output inventory
+         of the function harvestable() is not the same.The function must be corrected.")
 
   return(harvestableOutputs) # return the new inventory and the HVinit
 }

### 2022-11-28 tests/testthat/test-harvestablefuelwood.R

@@ -1,4 +1,4 @@
-test_that("exploitablefuelwoodvolume", {
+test_that("harvestablefuelwood", {
 
   # library(LoggingLab)
   # library(tidyverse)
@@ -68,49 +68,48 @@ test_that("exploitablefuelwoodvolume", {
 
   # Run function
 
-  Rslt_Fuel <- exploitablefuelwoodvolume(inventory_Fuel, scenario = "manual", fuel = "2",
-                                         TimberLoggedVolume = TimberLoggedVolume_Fuel,
-                                         NoHollowTimberLoggedVolume = NoHollowTimberLoggedVolume_Fuel,
-                                         advancedloggingparameters = loggingparameters())
+  Rslt_Fuel <- harvestablefuelwood(inventory_Fuel, scenario = "manual", fuel = "2",
+                                   TimberLoggedVolume = TimberLoggedVolume_Fuel,
+                                   NoHollowTimberLoggedVolume = NoHollowTimberLoggedVolume_Fuel,
+                                   advancedloggingparameters = loggingparameters())
 
-  Rslt_NoFuel <- exploitablefuelwoodvolume(inventory_NoFuel, scenario = "manual", fuel = "0",
-                                           TimberLoggedVolume = TimberLoggedVolume_NoFuel,
-                                           NoHollowTimberLoggedVolume = NoHollowTimberLoggedVolume_NoFuel,
-                                           advancedloggingparameters = loggingparameters())
+  Rslt_NoFuel <- harvestablefuelwood(inventory_NoFuel, scenario = "manual", fuel = "0",
+                                     TimberLoggedVolume = TimberLoggedVolume_NoFuel,
+                                     NoHollowTimberLoggedVolume = NoHollowTimberLoggedVolume_NoFuel,
+                                     advancedloggingparameters = loggingparameters())
 
   Rsltinventory_Fuel <- Rslt_Fuel$inventory
-  DamageBiomass_Fuel <- Rslt_Fuel$DamageBiomass
+  LoggingResidualBiomass_Fuel <- Rslt_Fuel$LoggingResidualBiomass
   FuelWoodBiomass_Fuel <-Rslt_Fuel$FuelWoodBiomass
 
   Rsltinventory_NoFuel <- Rslt_NoFuel$inventory
-  DamageBiomass_NoFuel <- Rslt_NoFuel$DamageBiomass
+  LoggingResidualBiomass_NoFuel <- Rslt_NoFuel$LoggingResidualBiomass
[…]

### 2023-02-28 R/loggingsummary.R
Update purge

@@ -43,8 +43,9 @@ loggingsummary <- function(x
 
   # Numeric values:
 
-  var <- c("HarvestableArea", "VO", "HVinit", "TimberLoggedVolume", "NoHollowTimberLoggedVolume", "FuelWoodBiomass",
-           "LoggingResidualBiomass", "LostBiomass", "TrailsDensity", "AdjustTrailsDensity")
+  var <- c("HarvestableArea", "VO", "HVinit", "TimberLoggedVolume", "NoHollowTimberLoggedVolume",
+           "TimberExtractedVolume", "FuelWoodBiomass", "LoggingResidualBiomass",
+           "LostBiomass", "TrailsDensity", "AdjustTrailsDensity")
 
   statsvars <- function(v, x){ # x the list, v the var
 
@@ -95,6 +96,12 @@ loggingsummary <- function(x
   cat('No hollow timber logged volume (m3):\n')
   print(unlist(RsltStats[5]))
   print(set_units(unlist(RsltStats[5])/HarvestableArea, m3/ha)) # Logged volume (m3) (only healthy trees)
+
+  cat('\n') # skip a line
+
+  cat('Timber extracted volume (timber volume after purge) (m3):\n') # timber volume after purge
+  print(unlist(RsltStats[4]))
+  print(set_units(unlist(RsltStats[4])/HarvestableArea, m3/ha)) # Logged volume (m3) (only healthy trees if fuel != "2", healthy + hollow trees if fuel = "2")
 
   cat('\n') # skip a line
 

### 2023-08-17 R/selected.R
For Review

@@ -84,8 +84,10 @@
 #' @examples
 #' data(Paracou6_2016)
 #' data(DTMParacou)
+#' data(PlotMask)
 #' data(HarvestableAreaOutputsCable)
 #' data(MainTrails)
+#' data(ForestZoneVolumeParametersTable)
 #'
 #' inventory <- addtreedim(cleaninventory(Paracou6_2016, PlotMask),
 #' volumeparameters = ForestZoneVolumeParametersTable)
@@ -93,7 +95,7 @@
 #' inventory <- commercialcriteriajoin(inventory, SpeciesCriteria)
 #'
 #' harvestableOutputs <- harvestable(inventory, topography = DTMParacou,
-#' diversification = TRUE, specieslax = FALSE,
+#' diversification = FALSE, specieslax = TRUE,
 #' plotslope = HarvestableAreaOutputsCable$PlotSlope,
 #' maintrails = MainTrails,
 #' harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
@@ -105,7 +107,7 @@
 #'
 #' selecInventory <- selected(inventory, topography = DTMParacou,
 #' scenario = "manual", fuel = "2", diversification = TRUE,
-#' VO = 125, HVinit = HVinit, specieslax = FALSE, objectivelax = TRUE,
+#' VO = 20, HVinit = HVinit, specieslax = TRUE, objectivelax = TRUE,
 #' advancedloggingparameters = loggingparameters())$inventory
 #'
 selected <- function(
@@ -213,6 +215,7 @@ selected <- function(
       inventory <- inventory %>%
         mutate(Condition = ifelse(LoggingStatus == "harvestable2nd"|LoggingStatus == "harvestable",TRUE, FALSE)) %>%
         group_by(Condition) %>%
+        arrange(CommercialLevel) %>% # add for reviewer
         arrange(desc(TreeHarvestableVolume)) %>%
         mutate(VolumeCumSum = cumsum(TreeHarvestableVolume)) %>%
         ungroup() %>%
@@ -250,6 +253,7 @@ selected <- function(
       inventory <- inventory %>%
         mutate(Condition = ifelse(LoggingStatus == "harvestable",TRUE, FALSE)) %>%
         group_by(Condition) %>%
+        arrange(CommercialLevel) %>% # add for reviewer
         arrange(desc(TreeHarvestableVolume)) %>%
[…]

### 2023-08-30 docs/Article example.Rmd
try to fix 2nd trails and harvestableareadef issues

---
title: "Article example"
author: "Vincyane Badouard"
date: "`r Sys.Date()`"
output: html_document
---

# Data and libraries
```{r}
data(Paracou6_2016) # inventory
data(PlotMask) # inventoried plot mask
data(DTMParacou) # topography
data(CreekDistances) # relative elevation
data(SpeciesCriteria) # species exploitability criteria
data(ForestZoneVolumeParametersTable) # volume parameters
data(ParamCrownDiameterAllometry) # parameters values of the crown diameter allometry

library(LoggingLab)
```

# Simulation
```{r}
Rslt <- loggingsimulation(
  inventory = Paracou6_2016,
  plotmask = PlotMask, topography = DTMParacou,
  creekverticaldistance = CreekDistances$distvert,
  creekhorizontaldistance = CreekDistances$disthorz,
  speciescriteria = SpeciesCriteria,
  volumeparameters = ForestZoneVolumeParametersTable,
  scenario = "manual",
  objective = 30, fuel = "2", diversification = TRUE, winching = "2",
  directionalfelling = "2", specieslax = FALSE, objectivelax = TRUE,
  crowndiameterparameters = ParamCrownDiameterAllometry,
  advancedloggingparameters = loggingparameters(),
  iter = 30, cores = 15)

```

# Time
```{r}
SimulTime <- microbenchmark::microbenchmark(

  loggingsimulation(
    inventory = Paracou6_2016,
    plotmask = PlotMask, topography = DTMParacou,
    creekverticaldistance = CreekDistances$distvert,
    creekhorizontaldistance = CreekDistances$disthorz,
    speciescriteria = SpeciesCriteria,
    volumeparameters = ForestZoneVolumeParametersTable,
    scenario = "manual",
    objective = 30, fuel = "2", diversification = TRUE, winching = "2",
    directionalfelling = "2", specieslax = FALSE, objectivelax = TRUE,
    crowndiameterparameters = ParamCrownDiameterAllometry,
    advancedloggingparameters = loggingparameters(),
    iter = 30, cores = 15), times = 1L
)
```

# Summary
```{r}
loggingsummary(Rslt)
```

# Plot data prep
```{r}

NewInventory <- Rslt[[1]]$inventory
MainTrails <- Rslt[[1]]$MainTrails
HarvestablePolygons <- Rslt[[1]]$HarvestablePolygons
MachinePolygons <- Rslt[[1]]$MachinePolygons
SmoothedTrails <- Rslt[[1]]$SmoothedTrails
AdjustSmoothedTrails <- Rslt[[1]]$AdjustSmoothedTrails

NewInventory_crs <- NewInventory %>%
  getgeometry(TreePolygon) %>%
  sf::st_set_crs(sf::st_crs(MainTrails)) # set a crs

Harvestable <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "harvestable"),
  coords = c("Xutm", "Yutm")) %>%
  st_set_crs(st_crs(MainTrails))

HarvestableUp <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
  coords = c("Xutm", "Yutm")) %>%
  st_set_crs(st_crs(MainTrails))

Selected <- sf::st_as_sf(
  dplyr::filter(NewInventory, Selected == "1"), coords = c("Xutm", "Yutm")) %>%
  st_set_crs(st_crs(MainTrails))

Reserve <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "reserve"),
  coords = c("Xutm", "Yutm")) %>%
  st_set_crs(st_crs(MainTrails))

Future <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "future"),
  coords = c("Xutm", "Yutm")) %>%
  st_set_crs(st_crs(MainTrails))

ProbedHollow <- sf::st_as_sf(
  dplyr::filter(NewInventory, ProbedHollow == "1"),
  coords = c("Xutm", "Yutm")) %>%
  st_set_crs(st_crs(MainTrails))

VisibleDefect <- sf::st_as_sf(
  dplyr::filter(NewInventory, VisibleDefect == "1"),
  coords = c("Xutm", "Yutm")) %>%
  st_set_crs(st_crs(MainTrails))

```

# Plot
```{r}
library(tidyverse)
library(sf)

ggplot() +

  labs(title = "Paracou P6 - RIL3 with fuelwood & hollow trees") +

  # MainTrails
  geom_sf(data = MainTrails,
          aes(color = "MainTrails")) +
  # Harvestable zones
  geom_sf(data = HarvestablePolygons,
          fill = "olivedrab", alpha = 0.1) +
  geom_sf(data = MachinePolygons,
          fill = "olivedrab", alpha = 0.5) +
  labs(alpha = "Harvestable") +

  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  geom_sf(data = Future,
          aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  geom_sf(data = HarvestableUp,
          aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  geom_sf(data = ProbedHollow,
          aes(colour = "Probed hollow"), show.legend = "point") +

  # 2ndary trails
  geom_sf(data = st_as_sf(SmoothedTrails),
          aes(color = "Initial-trails"),alpha = 0.5) +
  # geom_sf(data = st_as_sf(SecondaryTrails$RawSecondTrails),
  #         color = "green",alpha = 0.5) +

  # 2ndary trails adjusted
  geom_sf(data = st_as_sf(AdjustSmoothedTrails),
          aes(color = "Adjusted-trails"),alpha = 0.5) +
  # geom_sf(data = st_as_sf(ScdTrailsAdj$RawSecondTrails),
  #         color = "red",alpha = 0.5) +

  # cuted trees
  geom_sf(data = NewInventory_crs, 
          alpha = 0.5, fill = "darkgreen") +

  scale_colour_manual(name = "Logging status",
                      values = c("Visible defect" = "pink",
                                 "Harvestable" = "skyblue",
                                 "HarvestableUp" = "blue", "Selected" = "red",
                                 "Future" = "orange",
                                 "Reserve" = "purple",
                                 "Probed hollow" = "forestgreen",
                                 "Harvestable area" = "olivedrab", 
                                 "Initial-trails" = "darkgreen" ,
                                 "Adjusted-trails" = "darkred",
                                 "MainTrails" = "red"))
# scale_fill_manual(name = "Logging structures",
#                   values = c("Harvestable area" = "olivedrab", 
#                              "Initial-trails" = "darkgreen" ,
#                              "Adjusted-trails" = "darkred",
#                              "MainTrails" = "red"))
```
```{r}
ggplot() +

  labs(title = "Paracou P6 - RIL3 with fuelwood & hollow trees") +

  # Harvestable zones
  geom_sf(data = HarvestablePolygons,
          fill = "olivedrab", alpha = 0.1) +
  geom_sf(data = MachinePolygons,
          fill = "olivedrab", alpha = 0.5) +
  labs(alpha = "Harvestable") +

  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  geom_sf(data = Future,
          aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  geom_sf(data = HarvestableUp,
          aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  geom_sf(data = ProbedHollow,
          aes(colour = "Probed hollow"), show.legend = "point") +

  scale_colour_manual(name = "Logging status",
                      values = c("Visible defect" = "pink",
                                 "Harvestable" = "skyblue",
                                 "HarvestableUp" = "blue", "Selected" = "red",
                                 "Future" = "orange",
                                 "Reserve" = "purple",
                                 "Probed hollow" = "forestgreen"))
```

# Damage volume computing on Margaux's simulations
Plots (5): "SautLavilette", "Paracou11", "MontagnePlomb", "Acarouany", "Paracou16".  
Scenario: "2" = RIL2 without cable, "3" = RIL2 with cable  
Iterations number: 30 per plot.  
TotalResidualVolume: damage volume (m3) per harvestable hectare
```{r}
residual_volume_ha <- readr::read_csv("D:/VSC ManagFores/residual_volume_ha.csv")
residual_volume_ha
unique(residual_volume_ha$plot)
unique(residual_volume_ha$scenario)
```
## Per plot and scenario
```{r}
AverageResidualVolumes <- residual_volume_ha %>%
  group_by(plot, scenario) %>%
  mutate(AverageResidualVolume_ha = mean(TotalResidualVolume_ha)) %>%
  mutate(MaxResidualVolume_ha = max(TotalResidualVolume_ha)) %>%
  mutate(MinResidualVolume_ha = min(TotalResidualVolume_ha)) %>%
  select(plot,scenario,
         AverageResidualVolume_ha,
         MaxResidualVolume_ha, MinResidualVolume_ha) %>%
  unique()

AverageResidualVolumes
mean(AverageResidualVolumes$AverageResidualVolume_ha)
max(AverageResidualVolumes$AverageResidualVolume_ha)
min(AverageResidualVolumes$AverageResidualVolume_ha)
quantile(AverageResidualVolumes$AverageResidualVolume_ha)
```

## Per scenario
```{r}
AverageResidualVolumes_scenar <- residual_volume_ha %>%
  group_by(scenario) %>%
  mutate(AverageResidualVolume_ha = mean(TotalResidualVolume_ha)) %>%
  mutate(RV2.5 = quantile(TotalResidualVolume_ha, probs = 0.025)) %>%
  mutate(RV97.5 = quantile(TotalResidualVolume_ha, probs = 0.975)) %>%
  mutate(MaxResidualVolume_ha = max(TotalResidualVolume_ha)) %>%
  mutate(MinResidualVolume_ha = min(TotalResidualVolume_ha)) %>%
  select(scenario,
         AverageResidualVolume_ha,
         MaxResidualVolume_ha, MinResidualVolume_ha,
         RV2.5, RV97.5) %>%
  unique()

AverageResidualVolumes_scenar
mean(AverageResidualVolumes$AverageResidualVolume_ha)
quantile(AverageResidualVolumes$AverageResidualVolume_ha, probs = c(0.025, 0.975))
```

### 2023-08-30 R/HarvestableAreaDefinition.R

@@ -1,14 +1,19 @@
 #' Harvestable zones definition within the plot
 #'
+#' @description The simulator avoids the water sources buffer zones and slopes
+#'   inaccessible to machinery by taking the highest maximum slope percentage
+#'   tolerated by the machines.
+#'
+#'
 #' @param topography Digital terrain model (DTM) of the inventoried plot (LiDAR
 #'  or SRTM) (\code{\link{DTMParacou}}) (RasterLayer **with a crs in UTM**)
 #'
-#'@param creekverticaldistance Relative vertical distance
+#' @param creekverticaldistance Relative vertical distance
 #'  (1 m resolution) from nearest channel network
 #'  (RasterLayer **with a crs in UTM**) (See \code{\link{CreekDistances}})
 #'  To generate creek distances: \code{\link{CreekDistances}} in 'Articles'.
 #'
-#'@param creekhorizontaldistance Relative horizontal distance
+#' @param creekhorizontaldistance Relative horizontal distance
 #'  (1 m resolution) from nearest channel network
 #'  (RasterLayer **with a crs in UTM**) (See \code{\link{CreekDistances}})
 #'  To generate creek distances: \code{\link{CreekDistances}} in 'Articles'.
@@ -199,7 +204,11 @@ harvestableareadefinition <- function(
 
   PlotTib <- cbind(PlotTib,PlotSlopePoint %>% st_as_sf() %>% st_drop_geometry())
 
-  SlpCrit <- atan(advancedloggingparameters$MaxTrailCenterlineSlope/100)
+  # Take the maximum slope threshold:
+  maxslope <- max(advancedloggingparameters$MaxTrailCenterlineSlope,
+                  advancedloggingparameters$GrappleMaxslope)
+
+  SlpCrit <- atan(maxslope/100)
 
   CreekHDistCrit <- advancedloggingparameters$WaterSourcesBufferZone
   CreekVDistCrit <- advancedloggingparameters$WaterSourcesRelativeHeight
@@ -221,22 +230,25 @@ harvestableareadefinition <- function(
 
 
 
-  HarvestablePolygonsFoT <- PolygonHarvestableFoT %>% st_as_sf() %>% st_cast(to = "POLYGON", warn = FALSE)
+  HarvestablePolygonsFoT <- PolygonHarvestableFoT %>%
+    st_as_sf() %>%
[…]
